### 2018-10-29 theory/theory.tex
gets first part of theory into repo

\documentclass[onecolumn, amsmath, amsfonts, amssymb]{aastex62}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{bm}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}
\newcommand{\pro}{\ensuremath{\text{Ro}_{\text{p}}}}
\newcommand{\con}{\ensuremath{\text{Ro}_{\text{c}}}}

\usepackage{color}
\newcommand{\gv}[1]{{\color{blue} #1}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figs/}}

\begin{document}
\section{Hydrodynamic Impulse}
The theory that we're going to use to describe thermals relies on hydrodynamic impulse,
and since we happen to be looking at \emph{stratified} domains, we're lucky that
\citet{shivamoggi2010} went through the work of deriving impulse in anelastic atmospheres.
He finds that for an anelastic fluid (e.g., one where $\Div{\rho_0\bm{u}} = 0$ for 
a constant $\rho_0(z)$), the impulse is
\begin{equation}
\bm{I} = \frac{1}{2}\int_{\mathcal{V}} \bm{r}\times(\nabla\times(\rho_0\bm{u}))d\bm{r},
\label{eqn:impulse}
\end{equation}
where $\bm{r} \equiv x\hat{x} + y\hat{y} + z\hat{z}$ is the position vector and $\mathcal{V}$ is a closed volume.
Basically our theory will consist of two parts:
\begin{enumerate}
\item An expectation for the time-derivative of the impulse of the thermal based on its
density excess (and/or other thermodynamic properties)
\item The time-derivative of an approximate expression for the thermal's impulse when it is
in its evolved vortex-ring state.
\end{enumerate}
Our expectation is that these two things will be approximately equal, and will tell us something
about the size of the thermal as it descends and thus its entrainment.

\subsection{Volumetric \& Surface terms of the impulse}
For the first part of our theory we'll need to find the time-derivative of the impulse. Before we do that, 
we need to break apart the impulse expression into surface terms and volumetric terms (as Daniel did in an email
on 9/4/2018). First, the component of the impulse in the $i$th direction for $i$ in $(x,y,z)$ is
$$
[\bm{r}\times(\grad\times(\rho_0\bm{u}))]_i = 
\grad_i(\rho_0\bm{u}) \cdot \bm{r}- (\bm{r}\cdot\grad)(\rho_0 u)_i = 
r_j\frac{\partial}{\partial x_i}(\rho_0 u)_j - r_j \frac{\partial}{\partial x_j}(\rho_0 u)_i.
$$
By definition, each of the RHS terms can be further expanded as
$$
r_j\frac{\partial}{\partial x_i}(\rho_0 u)_j =
\frac{\partial}{\partial x_i}(r_j(\rho_0 u)_j) - \delta_{ij}(\rho_0 u)_j,\qquad\text{and}
\qquad
r_j \frac{\partial}{\partial x_j}(\rho_0 u)_i =
\frac{\partial}{\partial x_j}(r_j(\rho_0 u)_i) - 3(\rho_0 u)_i.
$$
Plugging these expanded expressions in, we find that
$$
[\bm{r}\times(\grad\times(\rho_0\bm{u}))]_i = 
\frac{\partial}{\partial x_i}(r_j(\rho_0 u)_j) -
\frac{\partial}{\partial x_j}(r_j(\rho_0 u)_i) +
2(\rho_0 u)_i.
$$
Plugging back in to the full impulse defn in Eqn.~\ref{eqn:impulse}, we find
\begin{equation}
\bm{I} = \int_{\mathcal{V}} (\rho_0 \bm{u}) d\bm{r} + 
\frac{1}{2}\int_{\mathcal{V}} [\grad (\bm{r}\cdot(\rho_0 \bm{u})) - \grad \cdot(\bm{r}(\rho_0\bm{u}))] d\bm{r}.
\end{equation}
As this integral is being done over a closed volume, the last integral can be expressed in terms of surface terms,
\begin{equation}
\bm{I} = \int_{\mathcal{V}} (\rho_0 \bm{u}) d\bm{r} + 
\frac{1}{2}\int_{\mathcal{S}} d\bm{S}(\bm{r}\cdot(\rho_0 \bm{u})) - d\bm{S} \cdot(\bm{r}(\rho_0\bm{u})).
\end{equation}

\bibliography{biblio.bib}
\end{document}

### 2018-10-29 theory/theory.tex
more theory updates

@@
 \frac{1}{2}\int_{\mathcal{S}} d\bm{S}(\bm{r}\cdot(\rho_0 \bm{u})) - d\bm{S} \cdot(\bm{r}(\rho_0\bm{u})).
+\label{eqn:surface_impulse}
 \end{equation}
+
+\subsection{Time derivative of the impulse}
+The time derivative of the impulse is \citep{shivamoggi2010},
+\begin{equation}
+\frac{\partial \bm{I}}{\partial t} = \int_{\mathcal{V}}\frac{\partial}{\partial t}(\rho_0 \bm{u}) d\bm{r}.
+\end{equation}
+I'm not totally convinced this is right. There's not much explanation of this in the paper. In an unbounded
+fluid (which I think is what he's using this expression for), it makes sense that the surface terms
+in Eqn.~\ref{eqn:surface_impulse} drop out. I'm not entirely sure why $d/dt \rightarrow \partial/\partial t$
+inside of the derivative. Given a fairly standard combination of an ideal 
+momentum equation and continuity equation,
+$$
+\frac{\partial}{\partial t}{\rho_0 \bm{u}} + \grad\cdot(\rho_0\bm{u}\bm{u}) = -\grad P - (\rho_0 + \rho_1) g \hat{z}.
+$$
+Now technically this whole $\rho_1$ term doesn't jive with the anelastic approximation (where $\rho$ can't change),
+but I'm hesitant to put the equations into a $\varpi$ and $S_1$ formulation, because I don't think they accurately describe
+the thermal's evolution. Subtracting out hydrostatic balance, we have something like
+$$
+\frac{\partial}{\partial t}{\rho_0 \bm{u}} = - \grad\cdot(\rho_0\bm{u}\bm{u}) - \grad P_1 - \rho_1 g \hat{z}.
+$$
+and thus the change in impulse over time is
+\begin{equation}
+\frac{\partial \bm{I}}{\partial t} = 
+\int_{\mathcal{V}}\left(
+- \grad\cdot(\rho_0\bm{u}\bm{u}) - \grad P_1 - \rho_1 g \hat{z}
+\right)d\bm{r}
+= -\int_{\mathcal{V}}\rho_1 g\hat{z} d\bm{r} -
+\int_{\mathcal{S}} [d\bm{S}\cdot(\rho_0\bm{u}\bm{u}) + d\bm{S}P_1].
+\end{equation}
+Generally (in \citet{shivamoggi2010} and I think other thermal work), the
+surface terms here are said to be zero (at least, under appropriate boundary
+conditions), and so we're left with
+\begin{equation}
+\boxed{
+\frac{d\bm{I}}{dt} = -gM_1 \hat{z}, \qquad M_1 \equiv \int_{\mathcal{V}}\rho_1 dV
+}.
+\end{equation}
+Or, your change in impulse over time is directly proportional to the excess mass
+in the thermal.
+
+\subsection{Approximate expression for the impulse}
+Going back to Eqn.~\ref{eqn:impulse}, we can see that the impulse contains two expressions:
+\begin{equation}
+\bm{I} = \frac{1}{2}\int_{\mathcal{V}}\bm{r}\times(\grad\times(\rho_0\bm{u}))d\bm{r} 
+= \frac{1}{2} \int_{\mathcal{V}} \left(\rho_0 \bm{r}\times \bm{\omega} + \bm{r} \times(\grad\rho_0 \times \bm{u}) \right) d\bm{r},
+\end{equation}
+where $\bm{\omega} = \grad\times\bm{u}$ is the vorticity.  The first term is identical to the term that shows up
+in boussinesq flows, and is basically \citep{saffman1970}
+$$
+\frac{1}{2} \int_{\mathcal{V}} \rho_0 \bm{r}\times \bm{\omega} = \rho_0 c R^2 \Gamma \hat{z},
+$$
+where $R$ is the radius of the vortex ring, $\Gamma$ is its circulation, and $c$ is some constant describing its
+aspect ratio. The second term here is
+$$
+\bm{r}\times(\grad\rho_0 \times\bm{u}) = (\bm{r}\cdot\bm{u})\grad\rho_0 - (\bm{r}\cdot\grad\rho_0)\bm{u}).
+$$
+Assuming that $\grad \rho_0 = \partial_z \rho_0 \hat{z}$, this becomes
+$$
+\bm{r}\times(\grad\rho_0 \times\bm{u}) = (-uz\hat{x} - vz\hat{y} + (xu + yv)\hat{z}).
+$$
+We don't care about the $x$ and $y$ terms here, because the main impulse of the thermal is vertical. We're essentially left with
+$$
+I_z = \rho_0 c R^2 \Gamma + \frac{1}{2}\int_{\mathcal{V}} u_{\perp} r_{\perp} \frac{\partial \rho_0}{\partial z} \bm{r}.
+$$
+If the thermal is small, and $\partial \rho_0 /\partial z$ is constant across the thermal, the last term drops out
+($u_{\perp} r_{\perp}$ at the bottom of the thermal cancels out with $u_{\perp} r_{\perp}$ at the top of the thermal).
+If the thermal is large and the stratification of the background varies across the thermal's size, then we need to worry
+about that second term.
 

### 2018-10-31 theory/theory.tex
finished theory - ish

--- 2018-10-29 theory/theory.tex
@@
 \frac{1}{2}\int_{\mathcal{S}} d\bm{S}(\bm{r}\cdot(\rho_0 \bm{u})) - d\bm{S} \cdot(\bm{r}(\rho_0\bm{u})).
+\label{eqn:surface_impulse}
 \end{equation}
+
+\section{Time derivative of the impulse}
+The time derivative of the impulse is found from taking a time derivative of 
+Eqn.~\ref{eqn:surface_impulse} and assuming that the fluid we're studying is unbounded
+so that the surface terms don't change in time \citep[as in][]{shivamoggi2010},
+\begin{equation}
+\frac{d \bm{I}}{d t} = \int_{\mathcal{V}}\frac{\partial}{\partial t}(\rho_0 \bm{u}) d\bm{r}.
+\end{equation}
+(Aside: the unbounded assumption / the assumption that the surface integrals don't matter
+seems a little sketchy to me for our sims, but it's common practice. Let's try it.
+Also, I'm not entirely sure why $d/dt \rightarrow \partial/\partial t$
+inside of the derivative, but oh well).
+
+By combining the non-viscous momentum and and anelastic continuity equations,
+\begin{equation}
+\begin{split}
+\Div{\rho_0 \bm{u}} = 0, \\
+\rho_0\frac{\partial \bm{u}}{\partial t} + \rho_0(\bm{u}\cdot\grad)\bm{u} =
+-\grad P - \rho g \hat{z},
+\end{split}
+\end{equation}
+where here I'm keeping the full $\rho$ on the buoyant term, we can find an 
+equation for the expression in our impulse time derivative,
+$$
+\frac{\partial}{\partial t}{\rho_0 \bm{u}} + \grad\cdot(\rho_0\bm{u}\bm{u}) = -\grad P - (\rho_0 + \rho_1) g \hat{z}.
+$$
+Subtracting out hydrostatic balance, we have something like
+$$
+\frac{\partial}{\partial t}{\rho_0 \bm{u}} = - \grad\cdot(\rho_0\bm{u}\bm{u}) - \grad P_1 - \rho_1 g \hat{z}.
+$$
+and thus the change in impulse over time is
+\begin{equation}
+\frac{\partial \bm{I}}{\partial t} = 
+-\int_{\mathcal{V}}\left(
+\grad\cdot(\rho_0\bm{u}\bm{u}) + \grad P_1 + \rho_1 g \hat{z}
+\right)d\bm{r}
+= -\int_{\mathcal{V}}\rho_1 g\hat{z} d\bm{r} -
+\int_{\mathcal{S}} [d\bm{S}\cdot(\rho_0\bm{u}\bm{u}) + d\bm{S}P_1].
+\end{equation}
+Generally \citep[in][and I think in other thermal work]{shivamoggi2010}, the
+surface terms here are said to be zero (at least, under appropriate boundary
+conditions), and so we're left with
+\begin{equation}
+\boxed{
+\frac{d\bm{I}}{dt} = -gM_1 \hat{z}, \qquad M_1 \equiv \int_{\mathcal{V}}\rho_1 dV
+}.
+\label{eqn:dI_dt}
+\end{equation}
+Or, your change in impulse over time is directly proportional to the excess mass
+in the thermal, or the integrated buoyant force over your thermal.
+
+\paragraph{Rough Estimate of $M_1$ size} 
+For a thermal whose entropy perturbation is $\epsilon$, the temperature perturbation
+is $T_{1, therm} = T_0(e^{\epsilon/c_P} - 1) \approx T_0\epsilon/c_P$, and the associated
+density perturbation to maintain pressure equilibrium is 
+$\rho_1 = P_0 / (T_0 + T_{1, therm}) - \rho_0$ where $\rho = \rho_0 + \rho_1$. For
+$P_0 = \rho_0T_0$, this is $\rho_1 = \rho_0( [1 + T_{1, therm}]^{-1} - 1) \approx -\rho_0 \epsilon / c_P$.
+So for positive $\epsilon$ (a hot thermal), we have a low density region, and for a falling
+cold thermal (with negative $\epsilon$), we have a density excess. The total mass excess in the
+thermal to start with is something like $M_1 \approx -\pi r_{therm}^2 \epsilon \rho_{0, therm} / c_P$,
+assuming the density is fairly constant across the thermal. I'll do this calculation more
+exactly at some point in the future, but this is a good rough estimate.
+
+\section{Approximate expression for the impulse}
+Going back to Eqn.~\ref{eqn:impulse}, we can see that the impulse can be simply expanded
+into two expressions:
+\begin{equation}
+\bm{I} = \frac{1}{2}\int_{\mathcal{V}}\bm{r}\times(\grad\times(\rho_0\bm{u}))d\bm{r} 
+= \frac{1}{2} \int_{\mathcal{V}} \left(\rho_0 \bm{r}\times \bm{\omega} + \bm{r} \times(\grad\rho_0 \times \bm{u}) \right) d\bm{r},
+\end{equation}
+where $\bm{\omega} = \grad\times\bm{u}$ is the vorticity.  The first term is identical to the term that shows up
+in boussinesq flows, and \emph{under the assumption that $\rho$ is constant across the
+thermal's depth} becomes \citep{saffman1970}
+$$
+\frac{1}{2} \int_{\mathcal{V}} \rho_0 \bm{r}\times \bm{\omega} d\bm{r} = \rho_0 c R^2 \Gamma \hat{z},
+$$
+where $R$ is the radius of the vortex ring, $\Gamma$ is its circulation, and $c$ is some constant describing its
+aspect ratio. The second term here is
+$$
+\bm{r}\times(\grad\rho_0 \times\bm{u}) = (\bm{r}\cdot\bm{u})\grad\rho_0 - (\bm{r}\cdot\grad\rho_0)\bm{u}.
+$$
+Assuming that $\grad \rho_0 = \partial_z \rho_0 \hat{z}$, this becomes
+$$
+\bm{r}\times(\grad\rho_0 \times\bm{u}) = (-uz\hat{x} - vz\hat{y} + (xu + yv)\hat{z}).
+$$
+We don't care about the $x$ and $y$ terms here, because the main impulse of the thermal is vertical. We're essentially left with
+$$
+I_z = \rho_0 c R^2 \Gamma + \frac{1}{2}\int_{\mathcal{V}} u_{\perp} r_{\perp} \frac{\partial \rho_0}{\partial z} \,d\bm{r}.
+$$
+If the thermal is small, as we assumed in evaluating the first part, then
+$\partial \rho_0 /\partial z$ is constant across the thermal, and the last term drops out
+($u_{\perp} r_{\perp}$ at the bottom of the thermal cancels out with $u_{\perp} r_{\perp}$ at the top of the thermal
+where it's oppositely signed).
+If the thermal is large and the stratification of the background varies across the thermal's size, then we need to worry
+about that second term.
+
+For now, dropping the last term, we can say that for a small thermal, the time derivative of
+the impulse should be roughly (assuming constant $c$)
+$$
+\frac{d I_z}{dt} = \frac{d}{dt}\left(\rho_0 c R^2 \Gamma\right) 
+= c\left(R^2 \Gamma \frac{d\rho_0}{dt} + 2\Gamma \rho_0 R \frac{d R}{dt} + \rho_0 R^2 \frac{d\Gamma}{dt}\right)
+$$
+Note that $d\rho_0/dt = d\rho_0/dz \cdot dz/dt = w d\rho_0/dz$, and so
+\begin{equation}
+\boxed{
+\frac{d I_z}{dt} = c\left(\Gamma R^2 w \frac{\partial \rho_0}{\partial z}\bigg|_{z=z_{th}}
++ 2 \rho_0 \Gamma R \frac{dR}{dt} + \rho_0 R^2 \frac{d\Gamma}{dt}\right)
+}
+\label{eqn:dIz_dt}
+\end{equation}
+
+\section{Putting it together: Theory for a small, anelastic thermal}
+Basically the theory comes down to this: If this impulse framework is good for understanding
+thermals, then Eqns.~\ref{eqn:dI_dt} \& \ref{eqn:dIz_dt} should be equal to each other.
+In other words, we expect
+\begin{equation}
+-g M_1 \approx c\left(\Gamma R^2 w \frac{\partial \rho_0}{\partial z}\bigg|_{z=z_{th}}
++ 2 \rho_0 \Gamma R \frac{dR}{dt} + \rho_0 R^2 \frac{d\Gamma}{dt}\right).
+\end{equation}
+This expression is slightly different from our first take at this theory. On the left,
+we have mass instead of entropy. On the right, we're not assuming that the circulation
+is constant.
 

### 2018-12-20 theory/theory.tex
adds scaling arguments

@@
 + 2 \rho_0 \Gamma R \frac{dR}{dt} + \rho_0 R^2 \frac{d\Gamma}{dt}\right).
+\label{eqn:theory_result}
 \end{equation}
@@
 
+\subsection{Thermal Growth predictions}
+Now we're going to take the theory we derived above in Eqn.~\ref{eqn:theory_result}
+and make it practical  We're going to make the following four assumptions:
+\begin{enumerate}
+\item \textbf{Assumption 1:} Circulation is constant in time, $\Gamma \neq \Gamma(t)$.
+\item \textbf{Assumption 2:} The integrated mass anomaly (or entropy, depending on how the equations
+are framed) is constant in time, $M_1 \neq M_1(t)$.
+\item \textbf{Assumption 3:} The depth of the thermal follows a power-law in time,
+$d(t) = L_z - z(t) \approx d_0 t^{\alpha}$. This also means that vertical velocity is defined
+$w = \partial z / \partial t = - \partial d / \partial t = - d_0 \alpha t^{\alpha - 1}$.
+\item \textbf{Assumption 4:} The radius of the thermal follows a different power-law in time,
+$R(t) \approx R_0 t^{\beta}$.
+\end{enumerate}
+Under these assumptions, Eqn.~\ref{eqn:theory_result} becomes, after some rearranging,
+\begin{equation}
+C_1 \equiv -\frac{g M_1}{c \Gamma R_0^2}  = 
+t^{2\beta - 1}\left(-d_0 t^{\alpha} \frac{\partial \rho_0}{\partial z} + 2 \rho_0 \right)
+=
+\rho_0 t^{2\beta - 1}\left(-d_0 t^{\alpha} \frac{\partial \ln \rho_0}{\partial z} + 2 \right)
+\label{eqn:simple_theory}
+\end{equation}
+Now, for an adiabatic polytrope with adiabatic index $m_{ad} = (\gamma - 1)^{-1} = 1.5$ if $\gamma = 5/3$,
+the local density of the thermal varies as
+$$
+\rho_0(t) = (1 + L_z - z(t))^{m_{ad}} = (1 + d(t))^{m_{ad}}, \qquad
+\frac{\partial \ln \rho_0}{\partial z} = -m_{ad}\frac{1}{1 + d(t)}
+$$
+
+Let's look at this in two limits -- large stratification ($d \gg 1$) and small stratification ($d \rightarrow 0$). 
+First, we examine large stratification. 
+In this regime, it's more instructive to use the $\ln \rho_0$ form of
+eqn. \ref{eqn:simple_theory}, where
+\begin{equation}
+\rho_0(t) \approx 
+d(t)^{m_{ad}} \approx d_0^{m_{ad}} t^{m_{ad}\alpha},
+\qquad
+\frac{\partial \ln \rho_0}{\partial z} \approx 
+-m_{ad} h^{-1}(t) \approx -(m_{ad}/d_0) t^{-\alpha}.
+\end{equation}
+Plugging these approximations in, we find
+$$
+C_1 \approx d_0^{m_{ad}} t^{m_{ad}\alpha + 2\beta - 1}(2 - m_{ad}).
+$$
+In order for this equation to be true, we need the time dependence to fall out of the
+equation, so
+\begin{equation}
+m_{ad}\alpha + 2\beta - 1 = 0\,\,\rightarrow\,\, \beta = 0.5 - m_{ad} \alpha / 2.
+\end{equation}
+Thus, in the large stratification limit, we have a relation for how quickly the
+radius scales compared to the depth.
+
+For small stratification, the situation is muddier, but it's easier to use the $\rho_0$
+and $\partial \rho_0 / \partial z$ form of eqn.~\ref{eqn:simple_theory}. Taylor expanding
+$\rho_0$ around $d = 0$, we find
+$$
+\rho_0 \approx 1 + m_{ad} d + \cdots, \qquad 
+\frac{\partial \rho_0}{\partial z} = -\frac{\partial \rho_0}{\partial d} \approx -(m_{ad} + \cdots) .
+$$
+After plugging in these approximations, we find
+$$
+C_1 \approx t^{2\beta - 1 + \alpha}(2 + 3m_{ad} d_0).
+$$
+Thus, in order for time dependence to fall out of this equation, we require
+\begin{equation}
+\alpha + 2\beta - 1 = 0\,\,\rightarrow\,\, \beta = 0.5 (1 -  \alpha).
+\end{equation}
+Which is interesting. In the boussinesq case, $\alpha = \beta = 0.5$, but here we see
+that in the slightly (but importantly) stratified case, if $\alpha = 0.5$, $\beta = 0.25$.
+
+One interesting result is that in both cases we find that
+$$
+\beta = 0.5 - X \alpha / 2,
+$$
+where $X = m_{ad}$ for the highly stratified case, and where maybe $X = 1$ for the minimally
+stratified case. Regardless, the inclusion of stratification makes the scaling of the radius with
+time less strong, and that scaling can be negative.
+
 \bibliography{biblio.bib}

### 2019-01-29 theory/vorticity/vorticity.tex
adds rough vorticity pdf

\documentclass[onecolumn, amsmath, amsfonts, amssymb]{aastex62}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{bm}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}
\newcommand{\pro}{\ensuremath{\text{Ro}_{\text{p}}}}
\newcommand{\con}{\ensuremath{\text{Ro}_{\text{c}}}}

\usepackage{color}
\newcommand{\gv}[1]{{\color{blue} #1}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figs/}}

\begin{document}
\section{Vorticity arguments for entrainment}
\subsection{Quick Boussinesq argument}
The arguments in this section were inspired by Brett's paper draft, which Nadir sent me
around DFD time. Specifically, his arguments around "expansion by the creation of baroclinicity"
section.  He argues (in different terms, but mathematically the same)
that, for a boussinesq system with this momentum equation,
$$
\partial_t \bm{u}  + \grad\varpi - T_1 \hat{z} + \mathcal{R}\grad\times\bm{\omega} = -\bm{u}\times\bm{\omega},
$$
the system has a vorticity equation of the form,
\begin{equation}
\frac{D\bm{\omega}}{Dt} = -\frac{\partial T_1}{\partial r} + (\bm{\omega}\cdot\grad)\bm{u} + \mathcal{R}\grad^2\bm{\omega}.
\end{equation}
If we think of an azimuthally-symmetric thermal with no velocity in the $\hat{\phi}$ direction
and with vorticity only in the $\hat{\phi}$ direction, then we get, essentially,
\begin{equation}
\frac{D\omega_\phi}{Dt} = -\frac{\partial T_1}{\partial r} + \frac{u_r \omega_\phi}{r} + \mathcal{R}\grad^2\omega_\phi.
\end{equation}
Just based on some right-hand-rule arguments, $\omega_\phi$ will be positive in the vortex ring
core for an upflow (hot) thermal, and it will be negative for a downflow (cold) thermal.
In a upflow thermal, $\partial_r T_1$ is positive in the thermal center and negative at radii
larger than the vortex core's radius. In a downflow thermal, these signs are switched. This means
that $(-\partial_r T_1)$ \emph{destroys} vorticity for $r < r_{th}$ and \emph{creates} vorticity
for $r > r_{th}$ for both upflows and downflows. Thus, buoyancy creates entrainment through
the destruction of vorticity in the vortex core (and the creation of it further out).

\subsection{Expansion to stratification}
So that's the argument for the Boussinesq case. Which is great. What about the stratified
case?  The fully compressible momentum equation that we solve takes the form
$$
\frac{\partial\bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
- \grad T - T \grad\ln\rho + \bm{g} + \text{viscous terms}.
$$
I'm going to drop the viscous terms for this analysis. Assuming $\bm{g} \equiv -\grad\phi$
for some potential $\phi$, if we take the curl of this equation to retrieve the vorticity equation,
we retrieve
$$
\frac{D\bm{\omega}}{D t} = % + (\bm{u}\cdot\grad)\bm{\omega} = 
(\bm{\omega}\cdot\grad)\bm{u} - \bm{\omega}(\grad\cdot\bm{u}) - \grad T \times \grad\ln\rho.
$$
So here we have a different-looking buoyancy term, and we've added back in the
$\bm{\omega}(\grad\cdot\bm{u})$ term because we're no longer incompressible. If we make the
same assumptions as above in the boussinesq case (azimuthally symmetric vortex ring), we find
$$
\frac{D\omega_\phi}{D t} = 
\frac{u_r\omega_\phi}{r} - \omega_\phi(\grad\cdot\bm{u}) - \grad T \times \grad\ln\rho.
$$
In the anelastic limit ($\partial_t \ln\rho = 0$, so $\ln_rho_1 = 0$), the continuity
equation can be expressed as $\grad\cdot\bm{u} = -\bm{u}\cdot\grad\ln\rho$. And, since the
density field isn't allowed to evolve and $\grad\ln\rho_0$ only varies in the $z$ direction
(the direction of stratification, we wind up with
$$
\frac{D\omega_\phi}{D t} = 
\frac{u_r\omega_\phi}{r} + u_z\omega_\phi\frac{\partial \ln\rho_0}{\partial z} - \grad T \times \grad\ln\rho.
$$
Assuming no variation in the phi direction, and assuming that $\grad\ln\rho = \grad\ln\rho_0$
and only has a z-component, the buoyancy term can be easily reduced to
$\grad T \times \grad\ln\rho_0 = -(\grad_r T_1)(\grad_z\ln\rho_0)\hat{\phi}$. Thus, the
ideal vorticity equation is
\begin{equation}
\frac{D \omega_\phi}{D t} = \frac{\partial T_1}{\partial r}\frac{\partial\ln\rho_0}{\partial z}
+ \frac{u_r\omega_\phi}{r} + u_z \omega_\phi \frac{\partial\ln\rho_0}{\partial z}.
\end{equation}
Since $\partial\ln\rho_0/\partial z$ is always negative, we can see that the first term, the
buoyancy term, has the same effect as in the Boussinesq case -- it causes entrainment by
destroying vorticity in the center of the thermal and adding it to the outside. The new term,
$u_z \omega_\phi (\partial\ln\rho_0/\partial z)$, however, requires some examination. We know
that the vertical velocity can be broken up into the velocity of the thermal frame
(let's call it $w_{th}$), and fluctuations around that, $u_z = w_{th} + w'$. Thus, we find
$$
u_z\omega_\phi = \omega_\phi w_{th} + \omega_\phi w'.
$$
For a downflowing (cold) thermal, $w_{th}$ and $\omega_\phi$ are both negative, so their
product is positive. For a upflowing thermal, both are positive and so is their product, so
the first term is positive definite. For a down (up) thermal, $w'$ is negative (positive) in the
thermal core, and positive (negative) outside of it. Thus, the second term is positive-definite
in the thermal core and negative-definite outside of it. To obtain the full stratification
term, we must multiply by $\partial_z\ln\rho_0$, which is negative everywhere.

We can thus re-write this equation as
\begin{equation}
\frac{D \omega_\phi}{D t} = -\frac{\partial T_1}{\partial r}\bigg|\frac{\partial\ln\rho_0}{\partial z}\bigg|
+ \frac{u_r\omega_\phi}{r} - \bigg| w_{th} \omega_\phi \frac{\partial\ln\rho_0}{\partial z}\bigg|
- w' \omega_\phi \bigg|\frac{\partial\ln\rho_0}{\partial z}\bigg|.
\end{equation}

\begin{table}
\label{table:signs}
\begin{center}
\begin{tabular}{ c c c }
\hline																	
Term	& Inside Thermal (cold / hot) 	& Outside Thermal (cold / hot)\\
\hline
$-\frac{\partial T_1}{\partial r}\bigg|\frac{\partial\ln\rho_0}{\partial z}\bigg|$ 	& + / - & - / + \\
$-\bigg| w_{th} \omega_\phi \frac{\partial\ln\rho_0}{\partial z}\bigg|$ 			& - / - & - / - \\
$-w' \omega_\phi \bigg|\frac{\partial\ln\rho_0}{\partial z}\bigg|$					& - / - & + / + \\	
\hline																	
\end{tabular}
\end{center}
\end{table}

So we can see that the third term is acting in an anti-buoyant manner for the cold thermal,
and a buoyant manner for the hot thermal. Cool.

\bibliography{biblio.bib}
\end{document}

### 2019-02-20 notes_theory/vorticity/vorticity.tex
repo reshuffle, start of paper

--- 2019-01-29 theory/vorticity/vorticity.tex
@@
 for $r > r_{th}$ for both upflows and downflows. Thus, buoyancy creates entrainment through
-the destruction of vorticity in the vortex core (and the creation of it further out).
+the destruction of vorticity for $r < r_{th}$ (and the creation of it further out).
 
@@
 $$
-In the anelastic limit ($\partial_t \ln\rho = 0$, so $\ln_rho_1 = 0$), the continuity
+In the anelastic limit ($\partial_t \ln\rho = 0$, so $\ln{\rho_1} = 0$), the continuity
 equation can be expressed as $\grad\cdot\bm{u} = -\bm{u}\cdot\grad\ln\rho$. And, since the
-density field isn't allowed to evolve and $\grad\ln\rho_0$ only varies in the $z$ direction
+density field isn't allowed to evolve and $\grad\ln\rho$ only varies in the $z$ direction
 (the direction of stratification, we wind up with
@@
 - w' \omega_\phi \bigg|\frac{\partial\ln\rho_0}{\partial z}\bigg|.
+\label{eqn:stratified_vorticity}
 \end{equation}
+So we have one buoyancy term and ``two'' new stratification-related terms in the vorticity
+equation. We examine their signs in Table \ref{table:signs}, and we see that, for a downflowing
+thermal, the last term in Eqn.~\ref{eqn:stratified_vorticity} acts in an anti-buoyant manner
+and should reduce entrainment. The implications of these new terms on circulation should be examined
+(but I ran out of time to do that carefully here).
 
-\begin{table}
+\begin{table}[h!]
+\caption{An examination of the signs of the terms in Eqn.~\ref{eqn:stratified_vorticity}.
+Signs are given for the terms at radii smaller than the vorticity peak ($r < r_{th}$,
+``inside thermal'') and
+also radii larger than that peak ($r > r_{th}$, ``outside thermal''). The sign of the
+term is given first for a cold thermal, then for a hot thermal (e.g., ``+/-'' means that
+the term is positive for a cold thermal and negative for a hot one).}
 \label{table:signs}
@@
 
-So we can see that the third term is acting in an anti-buoyant manner for the cold thermal,
-and a buoyant manner for the hot thermal. Cool.
+\section{Circulation Equation}
+So we've seen that the \emph{vorticity} equation gains a new term that can help
+phenomenologically explain the effects of stratification on a thermal. Now we turn to
+the circulation equation. To get there, we go through the normal steps of Kelvin's
+circulation theorem. We start off with the definition of the time derivative of circulation
+\begin{equation}
+\frac{d\Gamma}{dt} = \frac{d}{dt} \oint \bm{u}\cdot d\bm{x} 
+= \oint \frac{d \bm{u}}{dt}\cdot d\bm{x} + \oint \bm{u}\cdot\frac{d}{dt}d\bm{x}.
+\end{equation}
+In the last term in the above equation, if we think about a piece of a line element
+$d\bm{x}$ connecting two fluid parcels, the edges of the line are stretched by the
+difference in velocity at its two endpoints, $d( d\bm{x})dt = d\bm{u}$. Plugging this
+into the above integral (in the limit $d\bm{x} \rightarrow 0$),
+$$
+\oint\bm{u}\cdot\frac{d}{dt}d\bm{x} = \oint \bm{u}\cdot d\bm{u}
+= \oint d|\bm{u}|^2 / 2 = 0,
+$$
+and this integral is zero along a closed path. Thus, the change in time of circulation
+is simply
+\begin{equation}
+\frac{d\Gamma}{dt} = \oint \frac{d\bm{u}}{dt} \cdot d\bm{x}.
+\end{equation}
+At this point we specify that the velocity we care about, $\bm{u}$, is the velocity
+in the inertial frame, and so
+\begin{equation}
+\frac{d \bm{u}}{dt} = \frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u}
+= -\grad T - T \grad\ln\rho + \bm{g} + \grad\cdot\stressT.
+\end{equation}
+In other words, the RHS of the moment equation gets substituted directly into the integral,
+$$
+\frac{d\Gamma}{dt} = \oint \left[\left( - T \grad\ln\rho + \grad\cdot\stressT\right) -
+\left(\grad T - \grad \phi\right)\right] \cdot d\bm{x},
+$$
+where $\bm{g} \equiv -\grad\phi$ is defined by its potential. The last two terms in this 
+integral are conservative forces, and their integral around a closed loop is zero. Thus,
+we have
+\begin{equation}
+\frac{d\Gamma}{dt} = -\oint\left[T_0\grad\ln\rho_0 + T_1\grad\ln\rho_0 + T_0\grad\ln\rho_1 +
+T_1\grad\ln\rho_1\right]\cdot d\bm{x}
++ \oint (\grad\cdot\stressT)\cdot d\bm{x},
+\end{equation}
+Let's go ahead and ignore the stress tensor for now and use
+Stokes' theorem, and make some of the assumptions we did earlier (azimuthal symmetry,
+only velocity in $(\hat{r}, \hat{z})$ directions, background is only stratified in 
+$\hat{z}$ direction). We arrive at
+\begin{equation}
+\frac{d\Gamma}{dt} = \iint\left( \frac{\partial T_1}{\partial r}\frac{\partial\ln\rho_0}{\partial z}
++ \frac{\partial T_0}{\partial z}\frac{\partial \ln\rho_1}{\partial r} 
++ \frac{\partial T_1}{\partial z}\frac{\partial \ln\rho_1}{\partial r} 
+- \frac{\partial T_1}{\partial r}\frac{\partial \ln\rho_1}{\partial z}\right)
+\cdot d\bm{A}
+\end{equation}
+In our non-dimensionalized system, $\partial_z T_0 = -1$, and 
+$\partial_z \ln\rho_0 = -m_{ad}/T_0$, so we can rewrite
+\begin{equation}
+\frac{d\Gamma}{dt} = -\iint\left( \frac{m_{ad}}{T_0}\frac{\partial T_1}{\partial r}
++ \frac{\partial \ln\rho_1}{\partial r} 
++ \frac{\partial T_1}{\partial z}\frac{\partial \ln\rho_1}{\partial r} 
+- \frac{\partial T_1}{\partial r}\frac{\partial \ln\rho_1}{\partial z}\right)
+\cdot d\bm{A}.
+\end{equation}
+For a cold thermal, $\ln\rho_1 > 0$ and $T_1 < 0$, so the signs of their r-derivatives will be
+opposite one another, and the two terms in the integral will work against one another. Furthermore,
+the r-derivatives will have different signs near the axis of symmetry and far from it, so likely
+\emph{both of the first two terms cancel out entirely}. We're left with
+\begin{equation}
+\frac{d\Gamma}{dt} = -\iint\left( 
+\frac{\partial T_1}{\partial z}\frac{\partial \ln\rho_1}{\partial r} 
+- \frac{\partial T_1}{\partial r}\frac{\partial \ln\rho_1}{\partial z}\right)
+\cdot d\bm{A}.
+\end{equation}
+I think for similar reasons that the first two terms disappeared, these terms will also
+disappear. If you break up the thermal into four ``quadrants'' (upper left, upper right,
+lower left, lower right) and examine the sign of these terms in each of those, we also see
+that they work against one another. If buoyancy isn't important, 
+we'll be left with just the viscous terms,
+\begin{equation}
+\frac{d\Gamma}{dt} = \oint(\grad\cdot\stressT)\cdot d\bm{x},
+\end{equation}
+But *maybe* those buoyancy
+terms aren't as perfectly symmetric as we think, and they should be measured.
+
+\textbf{What we've learned:} The buoyancy term shows up in a more complex manner in the
+equation for $d\Gamma/dt$, but it probably goes away due to symmetry arguments. I'll need
+to take some measurements from the DNS to know for sure.
 

### 2019-02-20 tex/stratified_thermals.tex
repo reshuffle, start of paper

\documentclass[twocolumn, amsmath, amsfonts, amssymb, trackchanges]{aastex62}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{bm}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}
\newcommand{\pro}{\ensuremath{\text{Ro}_{\text{p}}}}
\newcommand{\con}{\ensuremath{\text{Ro}_{\text{c}}}}

\usepackage{color}
\newcommand{\gv}[1]{{\color{blue} #1}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figs/}{../tex/figs/}}

\received{October 19, 2018}
\revised{\today}
\accepted{??}%\today}
\submitjournal{ApJ}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TITLE & AUTHORS
\shorttitle{Entrainment of thermals in stratified atmospheres}
\shortauthors{Anders et al.}

\begin{document}
\title{Entrainment of low Mach number thermals in stratified atmospheres}

\correspondingauthor{Evan H. Anders}
\email{evan.anders@colorado.edu}

\author[0000-0002-3433-4733]{Evan H. Anders}
\affil{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affil{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}
\author[0000-0002-7635-9728]{Daniel Lecoanet}
\affil{Stuff}
\author[0000-0001-8935-219X]{Benjamin P. Brown}
\affil{Dept. Astrophysical \& Planetary Sciences, University of Colorado -- Boulder, Boulder, CO 80309, USA}
\affil{Laboratory for Atmospheric and Space Physics, Boulder, CO 80303, USA}

\begin{abstract}
\end{abstract}

\keywords{hydrodynamics --- turbulence --- entrainment}

%%%%% Body of the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INTRODUCTION
\section{Introduction}
\label{sec:intro}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EXPERIMENT SECTION
\section{Experiment} 
\label{sec:experiment}

We perform direct numerical simulations of the evolution of dry thermals
by solving the fully compressible Navier-Stokes equations,
\begin{gather}
\frac{D \ln\rho}{Dt} = -\Div{\bm{u}}
	\label{eqn:continuity}
\\
\frac{D \bm{u}}{D t} =
-\frac{1}{\rho}\grad P + \bm{g} + \Div{\stressT}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{D T}{D t} + (\gamma - 1)T\Div{\bm{u}} + \frac{1}{\rho c_V}\Div{-\rho\chi\grad T} = 
\frac{1}{\rho c_V}(\stressT \cdot \grad)\cdot \bm{u},
	\label{eqn:dim_bouss_energy}
\end{gather}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESULTS SECTION
\section{Results}
\label{sec:results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CONCLUSION SECTION
\section{Discussion}
\label{sec:discussion}

\begin{acknowledgements}
This work was supported by NASA Headquarters under the NASA Earth and Space
Science Fellowship Program -- Grant 80NSSC18K1199.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocation GID s1647.
\end{acknowledgements}

\appendix
\section{Table of Simulations}
\label{appendix:table}

%\begin{deluxetable*}{c c c c c c c c c c c c c c c}
%\tabletypesize{\footnotesize}
%\caption{Table of simulation information
%\label{table:simulation_info}
%}
%\tablehead{																																															
%\colhead{Ra$_{\text{top}}$}	&	\colhead{Ta$_{\text{top}}$}	&	\colhead{Ro$_{\text{p, top}}$}	&	\colhead{Ra$_{\text{mid}}$}	&	\colhead{Ta$_{\text{mid}}$}	&	\colhead{Ro$_{\text{p, mid}}$}	&	\colhead{\con}	&	\colhead{$\mathcal{S}$}	&	\colhead{$L_x/L_z$}	&	\colhead{(nz,	nx,	ny)}	&					\colhead{Ro}      	&	\colhead{Re$_{\parallel}$} 	&	\colhead{Re$_{\perp}$}	&	\colhead{Nu}      	}														
%\startdata																																															
%\multicolumn{3}{l}{\textbf{Constant \pro$\,$, path III}}\\
%1.8	$\times 10^{	5	}$	&	4.1	$\times 10^{	7	}$	&	0.60	&	1.4	$\times 10^{	7	}$	&	3.0	$\times 10^{	9	}$	&	1.03	&	0.067	&	1.1	&	0.51	&	(256,		32,		32)	&	0.015	&	19.4	&	2.5	&	1.2	\\				
%1.2	$\times 10^{	9	}$	&	5.2	$\times 10^{	12	}$	&	0.60	&	9.2	$\times 10^{	10	}$	&	3.8	$\times 10^{	14	}$	&	1.03	&	0.015	&	3.0	&	0.07	&	(2048,		64,		64)	&	0.026	&	1771	&	32.0	&	15.4	\\				
%5.2	$\times 10^{	2	}$	&	4.6	$\times 10^{	3	}$	&	0.96	&	3.8	$\times 10^{	4	}$	&	3.4	$\times 10^{	5	}$	&	1.64	&	0.333	&	1.13	&	2.28	&	(64,		64,		64)	&	0.074	&	4.2	&	2.5	&	1.2	\\				
%3.8	$\times 10^{	8	}$	&	3.1	$\times 10^{	11	}$	&	0.96	&	2.8	$\times 10^{	10	}$	&	2.3	$\times 10^{	13	}$	&	1.64	&	0.035	&	6.0	&	0.12	&	(2048,		64,		64)	&	0.129	&	3906	&	113	&	66.9	\\				
%7.9	$\times 10^{	1	}$	&	1.0	$\times 10^{	2	}$	&	1.58	&	5.8	$\times 10^{	3	}$	&	7.4	$\times 10^{	3	}$	&	2.70	&	0.888	&	1.56	&	4.44	&	(64,		64,		64)	&	0.303	&	4.4	&	4.9	&	1.7	\\				
%1.4	$\times 10^{	7	}$	&	9.7	$\times 10^{	8	}$	&	1.58	&	1.0	$\times 10^{	9	}$	&	7.2	$\times 10^{	10	}$	&	2.70	&	0.119	&	10.0	&	0.30	&	(512,		128,		128)	&	0.376	&	1257	&	94.9	&	40.1	\\				
%\hline																																															
%\multicolumn{3}{l}{\textbf{Constant \con$\,$, path II}}\\
%8.6	$\times 10^{	4	}$	&	8.6	$\times 10^{	6	}$	&	0.74	&	6.3	$\times 10^{	6	}$	&	6.3	$\times 10^{	8	}$	&	1.26	&	0.1	&	1.47	&	0.68	&	(128,		128,		128)	&	0.051	&	40.2	&	6.7	&	2.2	\\				
%2.6	$\times 10^{	6	}$	&	2.6	$\times 10^{	8	}$	&	1.13	&	1.9	$\times 10^{	8	}$	&	1.9	$\times 10^{	10	}$	&	1.93	&	0.1	&	4.64	&	0.39	&	(256,		512,		512)	&	0.27	&	565	&	53.2	&	33.3	\\				
%1.4	$\times 10^{	3	}$	&	1.6	$\times 10^{	4	}$	&	1.01	&	1.1	$\times 10^{	5	}$	&	1.2	$\times 10^{	6	}$	&	1.72	&	0.3	&	1.47	&	1.90	&	(64,		128,		128)	&	0.124	&	11.3	&	5.4	&	1.8	\\				
%1.1	$\times 10^{	6	}$	&	1.2	$\times 10^{	7	}$	&	2.29	&	7.8	$\times 10^{	7	}$	&	8.6	$\times 10^{	8	}$	&	3.93	&	0.3	&	14.7	&	0.65	&	(192,		384,		384)	&	0.808	&	529	&	83.5	&	27.3	\\				
%5.5	$\times 10^{	1	}$	&	5.5	$\times 10^{	1	}$	&	1.65	&	4.0	$\times 10^{	3	}$	&	4.0	$\times 10^{	3	}$	&	2.82	&	1.0	&	1.47	&	4.84	&	(64,		128,		128)	&	0.303	&	3.6	&	4.4	&	1.5	\\				
%2.8	$\times 10^{	6	}$	&	2.8	$\times 10^{	6	}$	&	6.39	&	2.0	$\times 10^{	8	}$	&	2.0	$\times 10^{	8	}$	&	10.93	&	1.0	&	100	&	0.82	&	(256,		512,		512)	&	3.357	&	1099	&	220	&	46.6	\\				
%\hline																																															
%\multicolumn{3}{l}{\textbf{Constant $\mathcal{S}$, path I}}\\
%1.9	$\times 10^{	1	}$	&	1.1	$\times 10^{	-1	}$	&	10.00	&	1.4	$\times 10^{	3	}$	&	7.9	$\times 10^{		}$	&	17.12	&	13.2	&	2.0	&	9.91	&	(64,		64,		64)	&	3.668	&	3.0	&	10.2	&	1.7	\\				
%3.0	$\times 10^{	6	}$	&	1.1	$\times 10^{	9	}$	&	0.70	&	2.2	$\times 10^{	8	}$	&	8.1	$\times 10^{	10	}$	&	1.20	&	0.052	&	2.0	&	0.30	&	(512,		128,		128)	&	0.053	&	242	&	17.9	&	6.0	\\				
%3.0	$\times 10^{	1	}$	&	2.0	$\times 10^{	-1	}$	&	10.00	&	2.2	$\times 10^{	3	}$	&	1.5	$\times 10^{	1	}$	&	17.12	&	12.2	&	3.0	&	9.48	&	(64,		64,		64)	&	4.418	&	5.0	&	15.5	&	2.1	\\				
%1.3	$\times 10^{	7	}$	&	5.6	$\times 10^{	9	}$	&	0.80	&	9.7	$\times 10^{	8	}$	&	4.2	$\times 10^{	11	}$	&	1.37	&	0.048	&	3.0	&	0.23	&	(512,		128,		128)	&	0.08	&	592	&	33.4	&	13.6	\\				
%\enddata																																															
%\tablecomments{
%Input parameters and output parameters for select simulations are shown. For each of
%the eight paths in Fig. \ref{fig:parameter_space}b, we show information for the lowest and
%highest (Ra, Ta) point on that path. The first six rows show information for constant
%$\pro\,$ paths, the next six for constant \con$\,$ paths, and the last four for constant $\mathcal{S}$ paths.
%We show the input Ra, Ta, and \pro$\,$ at the top of the atmosphere, as well as their
%stratification-weighted values at the midplane of the atmosphere, which provide a more direct
%comparison to Boussinesq values \citep{unnoetall1960}. We also provide the input \con$\,$ at the
%top of the atmosphere, $\mathcal{S}$, aspect ratio ($L_x/L_z$), and coefficient resolution
%(nz, nx, ny). Each dimension of the physical grid is 3/2 the size of the coefficient grid 
%for adequate dealiasing of quadratic nonlinear terms.
%Output values of Ro, Re$_{\parallel}$, Re$_{\perp}$, and Nu are also provided.
%This table in its entirety is published as a supplemental \texttt{.csv} file with this
%manuscript and also online in a Zenodo repository \citep{supp_andersetall2019}.
%}
%\end{deluxetable*}
%

\bibliography{../tex/biblio.bib}

\listofchanges
\end{document}

### 2019-03-13 notes_theory/theory_mar2019/theory_mar2019.tex
theory notes

\documentclass[onecolumn, amsmath, amsfonts, amssymb]{aastex62}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{bm}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}
\newcommand{\pro}{\ensuremath{\text{Ro}_{\text{p}}}}
\newcommand{\con}{\ensuremath{\text{Ro}_{\text{c}}}}

\usepackage{color}
\newcommand{\gv}[1]{{\color{blue} #1}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figs/}}

\begin{document}
\section{What we know}
From the simulations we've done so far, when viscous heating is neglected, we have the
following understanding of thermals:
\begin{enumerate}
\item The \emph{total entropy} of the thermal, $\rho s_1$, is conserved in the absence of
viscous heating.
\item For a low-$\epsilon$, low-Mach-number thermal, in which the total entropy is conserved
and the anelastic approximation is appropriate, we have two more pieces of knowledge:
\begin{enumerate}
\item From simple momentum equation arguments, the thermal's momentum increases linearly due
to the constant buoyant force, $\int \rho w dV \sim \rho w V = \rho s_1 g / c_p t = B t$.
\item From an anelastic-like impulse formulation with $\rho_1/\rho_0 \ll 1$, we also
know that the impulse linearly increases, $\rho \pi R^2 \Gamma = Bt$
\citep[][eqn 36 modified to buoyant vortex ring]{shivamoggi2010}.
\end{enumerate}
\item The thermal can be approximated as an ellipsoid whose principal semi-axes have lengths
$a = b = R$ and $c = h/2$, where $R$ is the radius of the thermal and $h/2$ is half the height
of the thermal volume. In other words, its horizontal cross-sections are circles and it's a bit
squished, so it's not quite a sphere. We can probably assume that $h \propto R$, and so
the volume of the thermal can be written $V = m R^3$ for some constant $m$.
\item The depth of the thermal follows a power law in time, $d = d_0t^\alpha$.
\item The circulation in the thermal, $\Gamma$, is constant.
\end{enumerate}

\section{Putting the pieces together}
From piece of knowledge 2 above, we see that $\rho V w \sim \rho R^2 \Gamma$. Plugging in
piece of knowledge 3, we find $R w \sim \Gamma / m$. Since $w$, the thermal downward velocity,
is the derivative of its depth, $w = \partial_t (d_0 t^\alpha) = \alpha d_0 t^{\alpha-1}$, 
we see that
\begin{equation}
R \sim \frac{\Gamma}{\alpha d_0 m} t^{1 - \alpha}.
\label{eqn:R_scale}
\end{equation}

With that figured out, we can go back to piece of knowledge numbers 2 and 3 above, and see
that $\rho V w \sim m \rho R^3 w \sim B t$, or that $(\Gamma/[\alpha d_0])^3 m^{-2} t^{3(1-\alpha) - (1-\alpha)}\rho = Bt$.
Dividing both sides by $t$ and rearranging a bit, we find
$$
\rho t^{1 - 2\alpha} = m^2 B \left(\frac{\alpha d_0}{\Gamma}\right)^3 = \text{const.}
$$
Taking a time-derivative, and rearranging, we find
\begin{equation}
\frac{\partial \ln \rho}{\partial t} = \frac{2\alpha - 1}{t}.
\end{equation}
So a simple $1 / t$ fit to $\partial \ln\rho / \partial t$, or perhaps even better, a moving
average of $t \partial_t \ln\rho$ (not what I'm doing right now), gives us the value of $\alpha$!

\bibliography{biblio.bib}
\end{document}

### 2019-03-13 tex/stratified_thermals.tex
theory notes

@@
 We perform direct numerical simulations of the evolution of dry thermals
-by solving the fully compressible Navier-Stokes equations,
+in an ideal gas whose pressure ($P$), temperature ($T$), and density ($\rho$)
+follow a nondimensional ideal gas law of $P = \rho T$.
+We evolving the temperature, log density ($\ln\rho$), and velocity vector
+($\bm{u} = u\hat{x} + v\hat{y} + z\hat{z}$) according to the fully compressible Navier-Stokes equations,
 \begin{gather}
@@
 \\
-\frac{D \bm{u}}{D t} =
--\frac{1}{\rho}\grad P + \bm{g} + \Div{\stressT}, 
-	\label{eqn:dim_bouss_momentum}
+\begin{align}
+&\frac{D \bm{u}}{D t} =
+-\grad T - T \grad\ln\rho + \bm{g} + \Div{\stressT}, 
+\end{align}
+	\label{eqn:full_momentum}
 \\
-\frac{D T}{D t} + (\gamma - 1)T\Div{\bm{u}} + \frac{1}{\rho c_V}\Div{-\rho\chi\grad T} = 
-\frac{1}{\rho c_V}(\stressT \cdot \grad)\cdot \bm{u},
-	\label{eqn:dim_bouss_energy}
+\begin{align}
+\frac{D T}{D t} + (\gamma - 1)T\Div{\bm{u}} + \frac{1}{\rho c_V}\Div{-\rho\chi\grad T} =\\
+\frac{1}{\rho c_V}(\stressT \cdot \grad)\cdot \bm{u}, \nonumber
+\end{align}
+	\label{eqn:full_energy}
+\end{gather}
+where $\chi$ is the thermal diffusivity and with the viscous stress tensor given by
+\begin{equation}
+\Pi_{ij} \equiv \mu\left(\frac{\partial u_i}{\partial x_j} + 
+\frac{\partial u_j}{\partial x_i} - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right),
+	\label{eqn:stress_tensor}
+\end{equation}
+where $\delta_{ij}$ is the Kronecker delta and with $\mu = \rho\nu$ is the
+dynamic viscosity and $\nu$ is the kinematic viscosity.
+We split our thermodynamics into a time-stationary adiabatic background component
+and a time-evolving fluctuation away from that background as
+$T = T_0(z) + T_1(x, y, z, t)$ and $\ln\rho = \ln\rho_0(z) + \ln\rho_1(x, y, z, t)$.
+We specify the background atmosphere as an adiabatic polytrope, as in
+\cite{anders&brown2017}, so that
+\begin{equation}
+T_0(z) = (1 + L_z - z), \qquad \ln\rho_0(z) = m_{ad}\ln(T_0),
+\end{equation}
+where $L_z$ is the domain depth, and $m_{ad} = 1/(\gamma-1) = 1.5$ is the
+adiabatic polytropic index. In the construction of these atmospheres, 
+we assume that gravity $\bm{g} = -g\hat{z}$ is everywhere constant and that the
+background atmosphere is in hydrostatic equilibrium such that
+$\partial_z T_0 + T_0 \partial_z\ln\rho_0 - g = 0$.
+
+We assume a Pradtl number of
+unity, $\text{Pr} = \nu/\chi = 1$, everywhere in the domain. We furthermore assume
+that $\nu$ and $\chi$ are uniform everywhere in the domain, and that a negligibly
+small diffusivity, $\chi_B = 0$ acts on the pure background terms in the thermal flux
+such that
+$$
+\frac{1}{\rho_0 c_V}\grad\cdot(-\rho \chi_B \grad T) = 0.
+$$
+Under all of these assumptions, the equations we solve become
+\begin{gather}
+\frac{D \ln\rho_1}{Dt} = -\Div{\bm{u}} - w\partial_z\ln\rho_0
+	\label{eqn:solved_continuity}
+\\
+\begin{align}
+&\frac{D \bm{u}}{D t} =
+-\grad T_1 - T_0 \grad\ln\rho_1 - T_1\partial_z\rho_0\hat{z} - T_1\grad\ln\rho_1 + \Div{\stressT}, 
+\end{align}
+	\label{eqn:solved_momentum}
+\\
+\begin{align}
+&\frac{D T_1}{D t} + w\partial_z T_0 +  (\gamma - 1)(T_0 + T_1)\Div{\bm{u}} 
+\\&- \frac{1}{c_V}\left\{\chi\left(\grad^2 T_1 + \partial_z\ln\rho_0\partial_z T_1 
++ \partial_z\ln\rho_1\partial_z T_0 + \grad\ln\rho_1 \cdot\grad T_1\right)  \right\}=\nonumber\\
+&\frac{1}{\rho c_V}(\stressT \cdot \grad)\cdot \bm{u}, \nonumber
+\end{align}
+	\label{eqn:solved_energy}
 \end{gather}

### 2019-03-14 notes_theory/theory_mar2019/theory_mar2019.tex
improved march theory notes

@@
 \begin{document}
-\section{What we know}
+\section{State of the problem}
+In these thermal simulations, as far as I can tell, we have \emph{eight} variables
+\begin{enumerate}
+\item $B$, the integrated total entropy leading to buoyancy
+\item $V$, the thermal volume
+\item $R$, the radius of the thermal
+\item $h$, the thermal's vertical extent (`radius' in z-direction)
+\item $w$, the thermal bulk vertical velocity
+\item $z$, the height of the thermal
+\item $\Gamma$, the circulation of the vortex ring
+\item $\rho$, the local density at the height of the thermal.
+\item $t$, time.
+\end{enumerate}
 From the simulations we've done so far, when viscous heating is neglected, we have the
@@
 \begin{enumerate}
-\item The \emph{total entropy} of the thermal, $\rho s_1$, is conserved in the absence of
-viscous heating.
-\item For a low-$\epsilon$, low-Mach-number thermal, in which the total entropy is conserved
-and the anelastic approximation is appropriate, we have two more pieces of knowledge:
+\item $B = \text{const} \propto \rho s_1$
+\item $h = A R$, where $A$ is a constant.
+\item $V = (4/3)\pi h R^2 = (4/3)\pi A R^3 = m R^3$.
+\item $w = \frac{\partial z}{\partial t}$
+\item $\rho = (1 + L_z - z)^{1.5}$ (for our polytropes)
+\item $\rho V w \sim B t$ (momentum linearly increases)
+\item $\rho \pi R^2 \Gamma \sim B t$ \citep[e.g., eqn 36 of ][]{shivamoggi2010}.
+\end{enumerate}
+That's 9 unknowns, and 7 equations. There's two pieces of the puzzle we're missing.
+Ideally, $\Gamma = \text{const}$, and then we're left with one more equation, but we
+can't even be sure that's the case.
+
+\section{Putting the pieces together in the Boussinesq-y limit}
+In the boussinesq limit, we can make two more assumptions:
 \begin{enumerate}
-\item From simple momentum equation arguments, the thermal's momentum increases linearly due
-to the constant buoyant force, $\int \rho w dV \sim \rho w V = \rho s_1 g / c_p t = B t$.
-\item From an anelastic-like impulse formulation with $\rho_1/\rho_0 \ll 1$, we also
-know that the impulse linearly increases, $\rho \pi R^2 \Gamma = Bt$
-\citep[][eqn 36 modified to buoyant vortex ring]{shivamoggi2010}.
+\item $\Gamma = \text{const}$
+\item $\rho = \text{const}$.
 \end{enumerate}
-\item The thermal can be approximated as an ellipsoid whose principal semi-axes have lengths
-$a = b = R$ and $c = h/2$, where $R$ is the radius of the thermal and $h/2$ is half the height
-of the thermal volume. In other words, its horizontal cross-sections are circles and it's a bit
-squished, so it's not quite a sphere. We can probably assume that $h \propto R$, and so
-the volume of the thermal can be written $V = m R^3$ for some constant $m$.
-\item The depth of the thermal follows a power law in time, $d = d_0t^\alpha$.
-\item The circulation in the thermal, $\Gamma$, is constant.
-\end{enumerate}
+By these assumptions, eqn 7 above gives us $R \propto t^{1/2}$. Plugging that in to 
+eqn 6 gives $w \propto t^{-1/2}$, and thus $z(t) \propto t^{1/2}$.
 
-\section{Putting the pieces together}
-From piece of knowledge 2 above, we see that $\rho V w \sim \rho R^2 \Gamma$. Plugging in
-piece of knowledge 3, we find $R w \sim \Gamma / m$. Since $w$, the thermal downward velocity,
-is the derivative of its depth, $w = \partial_t (d_0 t^\alpha) = \alpha d_0 t^{\alpha-1}$, 
-we see that
-\begin{equation}
-R \sim \frac{\Gamma}{\alpha d_0 m} t^{1 - \alpha}.
-\label{eqn:R_scale}
-\end{equation}
-
-With that figured out, we can go back to piece of knowledge numbers 2 and 3 above, and see
-that $\rho V w \sim m \rho R^3 w \sim B t$, or that $(\Gamma/[\alpha d_0])^3 m^{-2} t^{3(1-\alpha) - (1-\alpha)}\rho = Bt$.
-Dividing both sides by $t$ and rearranging a bit, we find
-$$
-\rho t^{1 - 2\alpha} = m^2 B \left(\frac{\alpha d_0}{\Gamma}\right)^3 = \text{const.}
-$$
-Taking a time-derivative, and rearranging, we find
-\begin{equation}
-\frac{\partial \ln \rho}{\partial t} = \frac{2\alpha - 1}{t}.
-\end{equation}
-So a simple $1 / t$ fit to $\partial \ln\rho / \partial t$, or perhaps even better, a moving
-average of $t \partial_t \ln\rho$ (not what I'm doing right now), gives us the value of $\alpha$!
+\section{What do we need to do in the stratified limit?}
+Come up with two more constraints. We need to understand how and why $\Gamma$ changes with
+time, and we need to understand how $w$, or $r$, or $z$ varies with time.
 

### 2019-03-25 notes_theory/circulation/circulation.tex
adds circulation notes

\documentclass[onecolumn, amsmath, amsfonts, amssymb]{aastex62}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{bm}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}
\newcommand{\pro}{\ensuremath{\text{Ro}_{\text{p}}}}
\newcommand{\con}{\ensuremath{\text{Ro}_{\text{c}}}}

\usepackage{color}
\newcommand{\gv}[1]{{\color{blue} #1}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figs/}}

\begin{document}
\title{Circulation in an anelastic system}
\section{Momentum and Vorticity equations}
The anelastic momentum equation takes the form of eqn 27 in \cite{lecoanet&all2014},
\begin{equation}
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u}
= -\grad \varpi + \frac{g}{c_P} S_1 \hat{z} + \Div{\stressT}.
\label{eqn:momentum}
\end{equation}
Taking the curl of Eqn.~\ref{eqn:momentum}, we can retrieve the vorticity equation in two
forms:
\begin{gather}
\frac{\partial \bm{\omega}}{\partial t}
= \nabla \times \left[ \bm{u}\times\bm{\omega} + \frac{g}{c_P} S_1 \hat{z} + \Div{\stressT}  \right]
\label{eqn:vorticity_1}
\\
\frac{\partial \bm{\omega}}{\partial t} + \bm{u}\cdot\grad\bm{\omega}
= -\bm{\omega}\DivU + \bm{\omega}\cdot\grad\bm{u} 
+ \nabla \times \left[ \frac{g}{c_P} S_1 \hat{z} + \Div{\stressT}  \right]
\label{eqn:vorticity_2}
\end{gather}

\section{Integral identities}
As circulation is defined as the path-integral of velocity (or the surface integral of
vorticity), it is useful to know a vector identity for each of these types of integrals.
For an arbitrary vector field, $\bm{Q}$, the langrangian derivative
($D/Dt = \partial/\partial t + \bm{u}\cdot\grad$) of its line integral around contour $C$ is
\begin{equation}
\frac{D}{Dt}\oint_C \bm{Q}\cdot d\bm{x} 
= \oint_C\frac{D \bm{Q}}{D t}\cdot d\bm{x} + \oint_C\bm{Q} \cdot d\bm{u}.
\label{eqn:line_integral}
\end{equation}
The lagrangian derivative of a surface integral along a surface $A$ is
\citep[Eqn.~4.45 of][]{choudhuri1998},
\begin{equation}
\frac{D}{Dt}\iint_A d\bm{S}\cdot\bm{Q}
= \iint_A d\bm{S}\cdot\left[\frac{\partial \bm{Q}}{\partial t} - \grad\times(\bm{u}\times\bm{Q})\right].
\label{eqn:area_integral}
\end{equation}

\section{Circulation from the momentum equation}
Starting with Eqn.~\ref{eqn:momentum} and using Eqn.~\ref{eqn:line_integral} with $\bm{Q} = \bm{u}$,
we acknowledge that the second term in Eqn.~\ref{eqn:line_integral} is
\begin{equation}
\oint_C \bm{u}\cdot d\bm{u} = \frac{1}{2} \oint_C d|\bm{u}^2| = 0,
\end{equation}
as it is a closed loop integral of a perfect differential. Thus, we have
\begin{equation}
\frac{D \Gamma}{D t} = \frac{D}{Dt} \oint_C \bm{u}\cdot d\bm{x} = \oint_C \frac{D\bm{u}}{Dt}\cdot d\bm{x}
= \oint_C \left[-\grad\varpi + \frac{g}{c_P} S_1 \hat{z} + \Div{\stressT}  \right]\cdot d\bm{x}
\end{equation}
Since the closed loop integral conservative force (e.g., $-\grad\varpi$) is zero, we are left
with
\begin{equation}
\frac{D \Gamma}{D t} 
= \oint_C \left[\frac{g}{c_P} S_1 \hat{z} + \Div{\stressT}  \right]\cdot d\bm{x}
\label{eqn:circulation_momentum}
\end{equation}

\section{Circulation from the vorticity equation}
Starting with Eqn.~\ref{eqn:vorticity_1} and using Eqn.~\ref{eqn:area_integral} with
$\bm{Q} = \bm{\omega}$, we rather simply retrieve
\begin{equation}
\frac{D \Gamma}{Dt} = \frac{D}{Dt}\iint_A d\bm{S}\cdot\bm{\omega}
= \iint_A d\bm{S} \cdot\left[\frac{\partial \bm{\omega}}{\partial t} - \grad\times(\bm{u}\times\bm{\omega})\right]
= \iint_A d\bm{S} \cdot\grad\times\left[\bm{u}\times\bm{\omega} + \frac{g}{c_P}S_1 \hat{z} + \Div{\stressT} - \bm{u}\times\bm{\omega}\right].
\end{equation}
Or, simplifying,
\begin{equation}
\frac{D \Gamma}{Dt} 
= \iint_A d\bm{S} \cdot\grad\times\left[\frac{g}{c_P}S_1 \hat{z} + \Div{\stressT}\right].
\label{eqn:circulation_vorticity}
\end{equation}
Assuming that Stokes' theorem holds for the contour $C$ around area $A$, the definitions
of circulation for Eqns.~\ref{eqn:circulation_momentum} and \ref{eqn:circulation_vorticity}
are equivalent, and only buoyant and viscous terms should have any effect on the circulation
in the thermal.

\bibliography{biblio.bib}
\end{document}

### 2019-03-25 notes_theory/theory_mar2019/theory_mar2019.tex
adds circulation notes

@@
 \item $\rho$, the local density at the height of the thermal.
-\item $t$, time.
 \end{enumerate}
@@
 \item $B = \text{const} \propto \rho s_1$
-\item $h = A R$, where $A$ is a constant.
-\item $V = (4/3)\pi h R^2 = (4/3)\pi A R^3 = m R^3$.
-\item $w = \frac{\partial z}{\partial t}$
-\item $\rho = (1 + L_z - z)^{1.5}$ (for our polytropes)
+\item $h = A R$, where $A$ is a constant [this assumption may not be true at high stratification].
+\item $V = (4/3)\pi h R^2 = (4/3)\pi A R^3 = V_0 R^3$.
+\item $w = \frac{\partial z}{\partial t} = -\frac{\partial d}{\partial t}$ (with depth $d \equiv L_z - z$)
+\item $\rho = (1 + L_z - z)^{m_{ad}} = (1 + d)^{m_{ad}}$, with $m_{ad} = (\gamma-1)^{-1} = 1.5$ (for our polytropes)
 \item $\rho V w \sim B t$ (momentum linearly increases)
@@
 \end{enumerate}
-That's 9 unknowns, and 7 equations. There's two pieces of the puzzle we're missing.
-Ideally, $\Gamma = \text{const}$, and then we're left with one more equation, but we
-can't even be sure that's the case.
+That's 8 unknowns, and 7 equations. There's one piece of the puzzle we're missing:
+what happens with $\Gamma$ over time?
+Ideally, $\Gamma = \text{const}$, but we can't be sure that's the case.
 
-\section{Putting the pieces together in the Boussinesq-y limit}
-In the boussinesq limit, we can make two more assumptions:
+\section{Low stratification limit}
+In the limit of a lightly stratified thermal, we make one more assumption:
 \begin{enumerate}
-\item $\Gamma = \text{const}$
-\item $\rho = \text{const}$.
+\item $\Gamma = \text{const}$ (our eqn \# 8)
 \end{enumerate}
-By these assumptions, eqn 7 above gives us $R \propto t^{1/2}$. Plugging that in to 
-eqn 6 gives $w \propto t^{-1/2}$, and thus $z(t) \propto t^{1/2}$.
+We also know that, under this assumption, and also in this regime where eqn 2 is valid,
+from dividing eqn 6 by 7, 
+$$
+w R \sim \frac{\pi\Gamma}{V_0}.
+$$
+In general, this suggests that $w \propto t^{-\alpha}$ and $R \propto t^{\alpha}$, such that
+when multiplied together they return a constant. With this, we return to eqn 6 or 7, and get
+\begin{equation}
+\rho R^2 = \frac{B}{\pi \Gamma} t
+\label{eqn:theory_eqn_6_and_7}
+\end{equation}
+With our ansatz of $R \propto t^{\alpha}$, we know that $\rho \sim t^{1 - 2\alpha}$.
+But we also know from the stratification of our domain that 
+$\rho = (1 + d)^{m_{ad}} \sim t^{1 - 2\alpha}$, and that $d \sim -t^{1-\alpha}$ (from
+theory equation 4, definitionally). If we neglect the `1' in the $\rho$ definition for now,
+we thus get $m_{ad}(1 - \alpha) = (1 - 2\alpha)$, or
+$$
+\alpha = \frac{1 - m_{ad}}{2 - m_{ad}} = -1
+$$
+><
 
 \section{What do we need to do in the stratified limit?}
-Come up with two more constraints. We need to understand how and why $\Gamma$ changes with
-time, and we need to understand how $w$, or $r$, or $z$ varies with time.
+Figure out what happens to the circulation.
 

### 2019-03-29 notes_theory/theory_apr2019/theory_apr.tex
puts up pre-pdp theory

\documentclass[onecolumn, amsmath, amsfonts, amssymb]{aastex62}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{bm}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}
\newcommand{\pro}{\ensuremath{\text{Ro}_{\text{p}}}}
\newcommand{\con}{\ensuremath{\text{Ro}_{\text{c}}}}

\usepackage{color}
\newcommand{\gv}[1]{{\color{blue} #1}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figs/}}

\begin{document}
\section{Description of stratified thermals}
In the thermal simulations, we have nine variables, although many of them are geometric and
likely intrinsically linked. These variables are:
\begin{enumerate}
\item $B$, the integrated total entropy leading to buoyancy
\item $V$, the thermal volume
\item $R$, the radius of the thermal
\item $r$, the radius (from axis of symmetry) of the thermal's vortex torus.
\item $R_z$, the thermal's radius in the z-direction (we assume it is an oblate spheroid)
\item $w$, the thermal bulk vertical velocity
\item $z$, the height of the thermal
\item $\Gamma$, the circulation of the vortex ring
\item $\rho$, the local density at the height of the thermal.
\end{enumerate}
From the simulations we've done so far, when viscous heating and detrainment are neglected, and the
diffusivities are sufficiently low (Re is sufficiently high) such that diffusive terms are not dominant, the following
equations seem to govern the thermal evolution:
\begin{gather}
B = \int \rho s_1 dV = \text{const}, \\
R_z = R/A,\qquad \text{ where $A$ is a constant aspect ratio },\\
r = f R, \qquad \text{ where $f$ is a constant fraction }, \\
V = (4/3)\pi h R^2 = (4/3)\pi R^3/A = V_0 R^3 = (V_0/f^3) r^3, \\
w = \frac{\partial z}{\partial t},\\
\rho = [1 + (\grad T)_{ad}(z - F^{-1})]^{m_{ad}} = T^{m_{ad}}, \text{(where $F = L_{thermal}/L_{box}$)}\\
\rho V w = B t + M_0,  \label{eqn:momentum} \\
\frac{1}{2}\rho r^2 \Gamma = B t + I_0, \label{eqn:impulse} \\
\Gamma \sim \text{const.}
\end{gather}
Note that all of these equations are azimuthal averages, I think. You'd probably have to
multiply by $2\pi$ to retrieve the ``full'' values in a 3D sim.

\section{Solve it out}
One thing that we have here that we didn't have a month ago is the constant offsets in
the impulse and momentum: $I_0$ and $M_0$.  They make it so that plugging the two together
is less straightforward that we had once thought, but it's still possible. From 
Eqn.~\ref{eqn:impulse}, we solve for
\begin{equation}
r = \sqrt{2\frac{B t + I_0}{\rho\Gamma}}.
\end{equation}
Plugging this in to Eqn.~\ref{eqn:momentum}, we get
\begin{equation}
\rho V w = \left(\frac{V_0}{f^3}\right)\rho r^3 w
= \left(\frac{V_0}{f^3}\right)\rho w \left(2\frac{B t + I_0}{\rho\Gamma}\right)^{3/2} = Bt + M_0,
\end{equation}
or, with $w = dz/dt$,
\begin{equation}
\rho^{-1/2}dz = \left(\frac{f^3 \Gamma^{3/2}}{2^{3/2}}\right)\frac{Bt + M_0}{(Bt + I_0)^{3/2}}dt
\end{equation}
But we know that $\rho = T^{m_{ad}},$ with $T$ the temperature, and $dT = (\grad T)_{ad} dz$,
and we can define $\tau = Bt + I_0$, with $d\tau = B dt$. Substituting these in, we retrieve
\begin{equation}
T^{-m_{ad}/2}dT 
= \left(\frac{f^3 \Gamma^{3/2}(\grad T)_{ad}}{2^{3/2} B}\right)\frac{\tau + M_0 - I_0}{\tau^{3/2}}d\tau.
\end{equation}
Defining a constant $C \equiv [f^3 \Gamma(\grad T)_{ad}]/[2^{3/2} B]$, we can write this more simply,
\begin{equation}
T^{-m_{ad}/2}dT = C\sqrt{\Gamma}\left(\frac{d\tau}{\tau^{1/2}} + \frac{M_0 - I_0}{\tau^{3/2}}d\tau\right).
\end{equation}
The choice to leave $\sqrt{\Gamma}$ outside of $C$ occurs because the value of $\tau$ is likely
negative for a downward thermal, and combining the $\sqrt{\Gamma}$ with $\tau$ keeps the 
numbers finite. On the bright side, these are all just power-law integrals, and with our choice 
of $m_{ad} = 3/2$, we retrieve
\begin{equation}
4 T\bigg|_{T(t=0)}^{T} 
= 2C\sqrt{\Gamma}\left(\tau^{1/2} - \frac{M_0 - I_0}{\tau^{1/2}}\right)\bigg|_{\tau(t=0)}^{\tau}
\end{equation}
Plugging things in and rearranging, our final equation for the evolution of temperature with time
is
\begin{equation}
T(t) = \left[\frac{C\sqrt{\Gamma}}{2}
\left(\sqrt{Bt + I_0} + \frac{I_0 - M_0}{\sqrt{Bt + I_0}} - 2\sqrt{I_0} + \frac{M_0}{\sqrt{I_0}}\right)
+ T(t=0)^{1/4}\right]^{4},
\end{equation}
where the thermal velocity can be simply retrieved as just
\begin{equation}
w = (\grad T)_{ad}^{-1}\frac{\partial T}{\partial t},
\end{equation}
where, for completeness, we solve out
\begin{equation}
\frac{\partial T}{\partial t} 
= B C \sqrt{\Gamma}( T^{3/4} ) \left(\frac{1}{(B t + I_0)^{1/2}} + \frac{M_0 - I_0}{(B t + I_0)^{3/2}}\right).
\end{equation}

\bibliography{biblio.bib}
\end{document}

### 2019-04-12 notes_theory/theory_apr2019/theory_apr.tex
cleaner thermal theory

@@
 \rho = [1 + (\grad T)_{ad}(z - F^{-1})]^{m_{ad}} = T^{m_{ad}}, \text{(where $F = L_{thermal}/L_{box}$)}\\
-\rho V w = B t + M_0,  \label{eqn:momentum} \\
+\rho V w = \beta B t + M_0,  \label{eqn:momentum} \\
 \frac{1}{2}\rho r^2 \Gamma = B t + I_0, \label{eqn:impulse} \\
@@
 \rho V w = \left(\frac{V_0}{f^3}\right)\rho r^3 w
-= \left(\frac{V_0}{f^3}\right)\rho w \left(2\frac{B t + I_0}{\rho\Gamma}\right)^{3/2} = Bt + M_0,
+= \left(\frac{V_0}{f^3}\right)\rho w \left(2\frac{B t + I_0}{\rho\Gamma}\right)^{3/2} = \beta Bt + M_0,
 \end{equation}
@@
 \begin{equation}
-\rho^{-1/2}dz = \left(\frac{f^3 \Gamma^{3/2}}{2^{3/2}}\right)\frac{Bt + M_0}{(Bt + I_0)^{3/2}}dt
+\rho^{-1/2}dz = \left(\frac{f^3 \Gamma^{3/2}}{2^{3/2}V_0}\right)\frac{\beta Bt + M_0}{(Bt + I_0)^{3/2}}dt
 \end{equation}
 But we know that $\rho = T^{m_{ad}},$ with $T$ the temperature, and $dT = (\grad T)_{ad} dz$,
-and we can define $\tau = Bt + I_0$, with $d\tau = B dt$. Substituting these in, we retrieve
+and we can define $\tau = (Bt + I_0)/\Gamma$, with $d\tau = (B/\Gamma) dt$ (these choice of constants
+ensure that $\tau$ is positive definite and monotonically increases). Substituting these in, we retrieve
 \begin{equation}
 T^{-m_{ad}/2}dT 
-= \left(\frac{f^3 \Gamma^{3/2}(\grad T)_{ad}}{2^{3/2} B}\right)\frac{\tau + M_0 - I_0}{\tau^{3/2}}d\tau.
+= \left(\frac{f^3 \Gamma^{3/2}(\grad T)_{ad}}{2^{3/2}V_0 B}\right)\frac{\beta \tau + M_0 - \beta I_0}{\tau^{3/2}}d\tau.
 \end{equation}
-Defining a constant $C \equiv [f^3 \Gamma(\grad T)_{ad}]/[2^{3/2} B]$, we can write this more simply,
+Defining a constant $C \equiv [f^3 \Gamma(\grad T)_{ad}]/[2^{3/2} V_0]$, we can write this more simply,
 \begin{equation}
-T^{-m_{ad}/2}dT = C\sqrt{\Gamma}\left(\frac{d\tau}{\tau^{1/2}} + \frac{M_0 - I_0}{\tau^{3/2}}d\tau\right).
+T^{-m_{ad}/2}dT = C\left(\beta \frac{\Gamma}{B}\tau^{-1/2}d\tau + \frac{M_0 - \beta I_0}{B}\tau^{-3/2}d\tau\right).
 \end{equation}
-The choice to leave $\sqrt{\Gamma}$ outside of $C$ occurs because the value of $\tau$ is likely
-negative for a downward thermal, and combining the $\sqrt{\Gamma}$ with $\tau$ keeps the 
-numbers finite. On the bright side, these are all just power-law integrals, and with our choice 
-of $m_{ad} = 3/2$, we retrieve
+These are all just power-law integrals, and so long as
+we avoid the special case where $m_{ad} = 2$ (the left-hand integral is a log then), we retrieve
 \begin{equation}
-4 T\bigg|_{T(t=0)}^{T} 
-= 2C\sqrt{\Gamma}\left(\tau^{1/2} - \frac{M_0 - I_0}{\tau^{1/2}}\right)\bigg|_{\tau(t=0)}^{\tau}
+\frac{1}{1 - m_{ad}/2} T^{1 - m_{ad}/2}\bigg|_{T(t=0)}^{T} 
+= 2C\left(\beta\frac{\Gamma}{B} \tau^{1/2} - \frac{M_0 - \beta I_0}{B}\tau^{-1/2}\right)\bigg|_{\tau(t=0)}^{\tau}
 \end{equation}
+For simplicity of writing, I define
+$$
+F(\tau) = \beta\frac{\Gamma}{B} \tau^{1/2} - \frac{M_0 - \beta I_0}{B}\tau^{-1/2}.
+$$
 Plugging things in and rearranging, our final equation for the evolution of temperature with time
@@
 \begin{equation}
-T(t) = \left[\frac{C\sqrt{\Gamma}}{2}
-\left(\sqrt{Bt + I_0} + \frac{I_0 - M_0}{\sqrt{Bt + I_0}} - 2\sqrt{I_0} + \frac{M_0}{\sqrt{I_0}}\right)
-+ T(t=0)^{1/4}\right]^{4},
+T(t) = \left[2(1 - m_{ad}/2)C\{F[\tau] - F[\tau(t=0)]\}
++ T(t=0)^{1-m_{ad}/2}\right]^{1/(1 - m_{ad}/2)},
 \end{equation}
@@
 \frac{\partial T}{\partial t} 
-= B C \sqrt{\Gamma}( T^{3/4} ) \left(\frac{1}{(B t + I_0)^{1/2}} + \frac{M_0 - I_0}{(B t + I_0)^{3/2}}\right).
+= C ( T^{m_{ad}/2} ) \left(\beta\tau^{-1/2} + \frac{M_0 - \beta I_0}{\Gamma}\tau^{-3/2}\right).
 \end{equation}
+In our simulations where $m_{ad} = 3/2$, we get the solution where $1 - m_{ad}/2 = 1/4$.
 

### 2019-04-17 notes_theory/theory_apr2019/theory_apr.tex
adds some theory work and cleanup

@@
 diffusivities are sufficiently low (Re is sufficiently high) such that diffusive terms are not dominant, the following
-equations seem to govern the thermal evolution:
+equations seem to govern the thermal evolution (note that these equations are azimuthally averaged,
+so the quantities here are divided by $2\pi$ compared to their full ``true'' volume averaged
+quantities):
 \begin{gather}
@@
 r = f R, \qquad \text{ where $f$ is a constant fraction }, \\
-V = (4/3)\pi h R^2 = (4/3)\pi R^3/A = V_0 R^3 = (V_0/f^3) r^3, \\
+V = (2/3) h R^2 = (2/3) R^3/A = V_0 R^3 = (V_0/f^3) r^3, \\
 w = \frac{\partial z}{\partial t},\\
@@
 
-\section{Solve it out}
+\section{Solution for Temperature, height, and velocity}
 One thing that we have here that we didn't have a month ago is the constant offsets in
@@
 T^{-m_{ad}/2}dT 
-= \left(\frac{f^3 \Gamma^{3/2}(\grad T)_{ad}}{2^{3/2}V_0 B}\right)\frac{\beta \tau + M_0 - \beta I_0}{\tau^{3/2}}d\tau.
+= \left(\frac{f^3 \Gamma(\grad T)_{ad}}{2^{3/2}V_0 B}\right)\frac{\beta\Gamma \tau + M_0 - \beta I_0}{\tau^{3/2}}d\tau.
 \end{equation}
-Defining a constant $C \equiv [f^3 \Gamma(\grad T)_{ad}]/[2^{3/2} V_0]$, we can write this more simply,
+Defining a constant $C \equiv [f^3 \Gamma(\grad T)_{ad}]/[2^{3/2} V_0 B]$, we can write this more simply,
 \begin{equation}
-T^{-m_{ad}/2}dT = C\left(\beta \frac{\Gamma}{B}\tau^{-1/2}d\tau + \frac{M_0 - \beta I_0}{B}\tau^{-3/2}d\tau\right).
+T^{-m_{ad}/2}dT = C\left(\beta \Gamma\tau^{-1/2}d\tau + (M_0 - \beta I_0)\tau^{-3/2}d\tau\right).
+\label{eqn:integrand}
 \end{equation}
@@
 \begin{equation}
-\frac{1}{1 - m_{ad}/2} T^{1 - m_{ad}/2}\bigg|_{T(t=0)}^{T} 
-= 2C\left(\beta\frac{\Gamma}{B} \tau^{1/2} - \frac{M_0 - \beta I_0}{B}\tau^{-1/2}\right)\bigg|_{\tau(t=0)}^{\tau}
+\frac{1}{1 - m_{ad}/2} T^{1 - m_{ad}/2}\bigg|_{T_0}^{T} 
+= 2C\left(\beta\Gamma \tau^{1/2} - (M_0 - \beta I_0)\tau^{-1/2}\right)\bigg|_{\tau_0}^{\tau}
 \end{equation}
-For simplicity of writing, I define
+For simplicity of writing, I define $\alpha^{-1} =  1 - m_{ad}/2$ and 
 $$
-F(\tau) = \beta\frac{\Gamma}{B} \tau^{1/2} - \frac{M_0 - \beta I_0}{B}\tau^{-1/2}.
+\xi(\tau) = \beta\Gamma \tau^{1/2} - (M_0 - \beta I_0)\tau^{-1/2}.
 $$
@@
 \begin{equation}
-T(t) = \left[2(1 - m_{ad}/2)C\{F[\tau] - F[\tau(t=0)]\}
-+ T(t=0)^{1-m_{ad}/2}\right]^{1/(1 - m_{ad}/2)},
+T(t) = \left[\frac{2C}{\alpha}(\xi[\tau] - \xi[\tau_0])
++ T_0^{1/\alpha}\right]^{\alpha},
 \end{equation}
-where the thermal velocity can be simply retrieved as just
+where the thermal velocity and height can be simply retrieved as just
 \begin{equation}
-w = (\grad T)_{ad}^{-1}\frac{\partial T}{\partial t},
+w = (\grad T)_{ad}^{-1}\frac{\partial T}{\partial t}, \qquad z = (\grad T)_{ad}^{-1}(T - 1) + F^{-1}
 \end{equation}
@@
 \frac{\partial T}{\partial t} 
-= C ( T^{m_{ad}/2} ) \left(\beta\tau^{-1/2} + \frac{M_0 - \beta I_0}{\Gamma}\tau^{-3/2}\right).
+= C \frac{B}{\Gamma}( T^{m_{ad}/2} ) \left(\beta\Gamma\tau^{-1/2} + (M_0 - \beta I_0)\tau^{-3/2}\right)
+.
 \end{equation}
-In our simulations where $m_{ad} = 3/2$, we get the solution where $1 - m_{ad}/2 = 1/4$.
+In our simulations where $m_{ad} = 3/2$, we get the solution where $\alpha = 4$.
+
+\section{Density solution}
+It's pretty straight-forward to find the solution for density now that we have the solution
+for temperature. Returning to Eqn.~\ref{eqn:integrand}, we substitute $T = \rho^{1/m_{ad}}$ and
+$dT = (1/m_{ad})\rho^{m_{ad}^{-1} - 1} d\rho$ to get
+\begin{equation}
+\frac{1}{m_{ad}}\rho^{-3/2 + m_{ad}^{-1}}d\rho = C\left(\beta \Gamma\tau^{-1/2}d\tau + (M_0 - \beta I_0)\tau^{-3/2}d\tau\right).
+\end{equation}
+In the limiting case where $m_{ad} = 2$, the LHS is $\rho^{-1}$ and is a log integral. For
+cases where $m_{ad} < 2$, We integrate to get
+\begin{equation}
+(m_{ad}^{-1} - 0.5)^{-1}m_{ad}\rho^{m_{ad}^{-1} - 1/2}\bigg|_{\rho_0}^{\rho} = 2 C \xi(\tau)\bigg|_{\tau_0}^{\tau}
+\end{equation}
+I'll now define $\chi^{-1} = m_{ad}^{-1} - 0.5$, rearrange, and find
+\begin{equation}
+\rho = \left[\frac{2 C}{m_{ad}\chi}(\xi[\tau] - \xi[\tau_0]) + \rho_0^{1/\chi}\right]^\chi,
+\end{equation}
+and $\chi = 6$ for our $m_{ad} = 3/2$ solutions.
+
+\section{Leading order evolution}
+What we eventually find from all of our derivations here is that, to leading order in $\tau$,
+\begin{gather}
+\rho = \left(\frac{2 C\beta\Gamma}{m_{ad}\chi}\right)^{\chi} \tau^{\chi/2} \\
+T    = \left(\frac{2 C \beta \Gamma}{\alpha}\right)^{\alpha} \tau^{\alpha/2} \\
+w    = \frac{C B \beta}{(\grad T)_{ad}}\left(\frac{2 C}{\alpha}\right)^{\alpha - 1} \tau^{\alpha/2 - 1},
+\end{gather}
+where $\alpha = 2$ and $\chi = 3$ for $m_{ad} = 3/2$.
+
+%\section{Entrainment rate}
+%As in \cite{lecoanet&jeevanjee2018}, we want to know what the entrainment rate is, or
+%\begin{equation}
+%\epsilon = \frac{d \ln V}{dz} \sim 3 \frac{d\ln r}{dz}.
+%\end{equation}
+%We also know that
+%\begin{equation}
+%r = \sqrt{2 \tau / \rho} \sim \sqrt{2\left(\frac{m_{ad}\chi}{2 C \beta \Gamma}\right)^{\chi} \tau^{1-\chi/2}},
+%\end{equation}
+%so
+%\begin{equation}
+%\epsilon \sim \frac{3}{2}(1 - \chi/2)\frac{d\ln \tau}{dz} 
+%= \frac{3}{2}(1 - \chi / 2) \frac{d \ln \tau}{d\tau}\frac{d\tau}{dt}\frac{dt}{dz}
+%= \frac{3}{2}\frac{B}{\Gamma}(1 - \chi/2)\frac{1}{\tau w}
+%\end{equation}
+%For $\chi = 6$, $\alpha = 4$, this becomes
+%\begin{equation}
+%\epsilon \propto \tau^{-2}
+%\end{equation}
 

### 2019-04-26 notes_theory/theory_apr2019/theory_apr.tex
adds 2D anelastic simulation script

@@
 diffusivities are sufficiently low (Re is sufficiently high) such that diffusive terms are not dominant, the following
-equations seem to govern the thermal evolution (note that these equations are azimuthally averaged,
-so the quantities here are divided by $2\pi$ compared to their full ``true'' volume averaged
-quantities):
+equations seem to govern the thermal evolution:
 \begin{gather}
-B = \int \rho s_1 dV = \text{const}, \\
+B = \int \rho s_1 dV = 2\pi \iint \rho s_1 r dr dz = \text{const}, \\
 R_z = R/A,\qquad \text{ where $A$ is a constant aspect ratio },\\
 r = f R, \qquad \text{ where $f$ is a constant fraction }, \\
-V = (2/3) h R^2 = (2/3) R^3/A = V_0 R^3 = (V_0/f^3) r^3, \\
+V = (4/3)\pi h R^2 = (4/3)\pi R^3/A = V_0 R^3 = (V_0/f^3) r^3, \\
 w = \frac{\partial z}{\partial t},\\
@@
 \rho V w = \beta B t + M_0,  \label{eqn:momentum} \\
-\frac{1}{2}\rho r^2 \Gamma = B t + I_0, \label{eqn:impulse} \\
+\pi\rho r^2 \Gamma = B t + I_0, \label{eqn:impulse} \\
 \Gamma \sim \text{const.}
 \end{gather}
-Note that all of these equations are azimuthal averages, I think. You'd probably have to
-multiply by $2\pi$ to retrieve the ``full'' values in a 3D sim.
 
@@
 \begin{equation}
-r = \sqrt{2\frac{B t + I_0}{\rho\Gamma}}.
+r = \sqrt{\frac{B t + I_0}{\pi\rho\Gamma}}.
 \end{equation}
@@
 \rho V w = \left(\frac{V_0}{f^3}\right)\rho r^3 w
-= \left(\frac{V_0}{f^3}\right)\rho w \left(2\frac{B t + I_0}{\rho\Gamma}\right)^{3/2} = \beta Bt + M_0,
+= \left(\frac{V_0}{f^3}\right)\rho w \left(\frac{B t + I_0}{\pi\rho\Gamma}\right)^{3/2} = \beta Bt + M_0,
 \end{equation}
@@
 \begin{equation}
-\rho^{-1/2}dz = \left(\frac{f^3 \Gamma^{3/2}}{2^{3/2}V_0}\right)\frac{\beta Bt + M_0}{(Bt + I_0)^{3/2}}dt
+\rho^{-1/2}dz = \left(\frac{f^3 (\pi\Gamma)^{3/2}}{V_0}\right)\frac{\beta Bt + M_0}{(Bt + I_0)^{3/2}}dt
 \end{equation}
@@
 T^{-m_{ad}/2}dT 
-= \left(\frac{f^3 \Gamma(\grad T)_{ad}}{2^{3/2}V_0 B}\right)\frac{\beta\Gamma \tau + M_0 - \beta I_0}{\tau^{3/2}}d\tau.
+= \left(\frac{\pi^{3/2}f^3 \Gamma(\grad T)_{ad}}{V_0 B}\right)\frac{\beta\Gamma \tau + M_0 - \beta I_0}{\tau^{3/2}}d\tau.
 \end{equation}
-Defining a constant $C \equiv [f^3 \Gamma(\grad T)_{ad}]/[2^{3/2} V_0 B]$, we can write this more simply,
+Defining a constant $C \equiv [\pi^{3/2} f^3 \Gamma(\grad T)_{ad}]/[V_0 B]$, we can write this more simply,
 \begin{equation}

### 2019-04-26 code/AN_2D_thermal.py

@@ -1,0 +1,283 @@
+"""
+Dedalus script for simulating a 2D, azimuthally-symmetric thermal in an adiabatic polytrope.
+Equations are LBR Anelastic, as in Brown et al. 2012 and Lecoanet et al. 2014, rescaled
+on a freefall velocity scale with the length scale set by the diameter of the thermal.
+
+This code must be used with a version of Dedalus after commit  0128fa0 by Keaton Burns 
+on 2019-02-21, such that the problem.add_equation() function has the 'tau' keyword.
+
+A 'Buoyancy time' is the freefall timescale if the length were set as the domain depth,
+rather than the thermal depth. In our nondimensional units, if the domain depth is
+Lz, t_b = sqrt(Lz), and in general it takes ~12 buoyancy times for a "boussinesq" thermal
+to cross the domain (e.g., n_rho = 0.01), whereas more stratified thermals take less time
+(e.g., at n_rho = 2, it takes about 7 buoyancy times to cross the domain).
+
+Usage:
+    AN_2D_thermal.py [options]
+
+Options:
+    --n_rho=<n_rho>       number of density scale heights [default: 4]
+    --Reynolds=<Re>       Reynolds number [default: 6e2]
+    --Prandtl=<Pr>        Prandtl number [default: 1]
+    --nz=<n>              Number of z coefficients [default: 256]
+    --nr=<n>              Number of r coefficients [default: 128]
+
+    --wall_hours=<t>      Number of wall hours to run for max [default: 7.5]
+    --run_time_buoy=<rt>  Number of buoyancy times to run for [default: 10.0]
+
+    --aspect=<a>          Domain runs from [0, Lr], with Lr = aspect*Lz [default: 0.25]
+    --label=<l>           an optional string at the end of the output directory for easy identification
+
+    --rk443               If flagged, timestep using RK443. Else, SBDF2.
+
+    --Lz=<L>              The depth of the domain, in thermal diameters [default: 20]
+
[…]

### 2019-04-26 code/AN_2D_thermal.py
adds initial 2D run script

@@ -16,7 +16,7 @@ Usage:
     AN_2D_thermal.py [options]
 
 Options:
-    --n_rho=<n_rho>       number of density scale heights [default: 4]
+    --n_rho=<n_rho>       number of density scale heights [default: 0.5]
     --Reynolds=<Re>       Reynolds number [default: 6e2]
     --Prandtl=<Pr>        Prandtl number [default: 1]
     --nz=<n>              Number of z coefficients [default: 256]
@@ -228,7 +228,7 @@ out_dt = 0.08*t_b
 slices   = solver.evaluator.add_file_handler('{:s}/slices'.format(data_dir),   sim_dt=out_dt, max_writes=20, mode='overwrite')
 profiles = solver.evaluator.add_file_handler('{:s}/profiles'.format(data_dir), sim_dt=out_dt, max_writes=20, mode='overwrite')
 scalars  = solver.evaluator.add_file_handler('{:s}/scalars'.format(data_dir),   sim_dt=out_dt, max_writes=1e4, mode='overwrite')
-for f in ['S1', 'S1r', 'u', 'ur', 'w', 'wr' 'V', 'Vr', 'p']:
+for f in ['S1', 'S1r', 'u', 'ur', 'w', 'wr', 'V', 'Vr', 'p']:
     slices.add_task(f, name=f, layout='g')
     profiles.add_task('integ({}, "z")/Lz'.format(f), name='{}_z_avg'.format(f), layout='g')
     profiles.add_task('integ(r*({}), "r")/Lr'.format(f), name='{}_r_avg'.format(f), layout='g')

### 2019-04-26 code/AN_2D_thermal.py
AN implementation fixes

@@ -72,7 +72,7 @@ m_ad      = 1/(gamma-1)
 Cp        = gamma*m_ad
 Cv        = Cp/gamma
 grad_T_ad = -(np.exp(n_rho/m_ad) - 1)/Lz #adiabatic temperature gradient
-g         = -grad_T_ad * (1 + m_ad)      #gravity
+g         = (1 + m_ad) #* -grad_T_ad     #gravity
 t_b       = np.sqrt(Lz)                  #atmospheric buoyancy time
 
 Lr        = aspect*Lz
@@ -165,7 +165,8 @@ problem.substitutions['t_phir']             = '(u_phir - u_phi/r)'
 problem.substitutions['visc_L_u']      = '((xi_L/Re)*(Lap_r(u, ur) + (1./3)*DivUr))'
 problem.substitutions['visc_L_w']      = '((xi_L/Re)*(Lap(w, wr)   + (1./3)*dz(DivU)))'
 problem.substitutions['visc_R_u']      = '((xi_R/Re)*(Lap_r(u, ur) + (1./3)*DivUr))'
-problem.substitutions['visc_R_w']      = '((xi_R/Re)*(Lap(w, wr)   + (1./3)*dz(DivU)))'# Sometimes old formulation was stable with this on RHS:- (1./3)*(ln_rho0_z*dz(w) + w*ln_rho0_zz)))'
+#problem.substitutions['visc_R_w']      = '((xi_R/Re)*(Lap(w, wr)   + (1./3)*dz(DivU)))'# Sometimes old formulation was stable with this on RHS:- (1./3)*(ln_rho0_z*dz(w) + w*ln_rho0_zz)))'
+problem.substitutions['visc_R_w']      = '((xi_R/Re)*(Lap(w, wr)   - (1./3)*(ln_rho0_z*dz(w) + w*ln_rho0_zz)))'
 
 #Energy equation diffusivity substitutions
 problem.substitutions['diff_L']        = '( (xi_L/(Re*Pr*Cv))*Lap(S1, S1r) )'
@@ -173,7 +174,7 @@ if kappa_mu:
     problem.substitutions['diff_R']    = '( ((Re*Pr*Cv)**(-1))*(xi*ln_T0_z*dz(S1) + xi_R*Lap(S1, S1r)) )'
 else:
[…]

### 2019-04-26 notes_theory/nondim_anelastic/nondim_anelastic.tex
adds nondim anelastic notes

\documentclass[onecolumn, amsmath, amsfonts, amssymb]{aastex62}
\usepackage{mathtools}
\usepackage{natbib}
\usepackage{bm}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

\newcommand{\appropto}{\mathpalette\approptoinn\relax}
\newcommand{\pro}{\ensuremath{\text{Ro}_{\text{p}}}}
\newcommand{\con}{\ensuremath{\text{Ro}_{\text{c}}}}

\usepackage{color}
\newcommand{\gv}[1]{{\color{blue} #1}}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figs/}}

\begin{document}
\section{The anelastic equations}
We write the anelastic equations under a constant dynamic diffusivity formulation 
($\mu = \rho\nu = \text{const}$, $\kappa = \rho\chi = \text{const}$)
as in \citet{lecoanet&all2014}, eqns.~27-29,
\begin{gather}
\DivU = -w\partial_z\ln\rho = \frac{w}{H_\rho(z)} 
\label{eqn:dim_continuity}\\
\partial_t \bm{u} + \bm{u}\cdot\grad\bm{u} + \grad \varpi = -\bm{g}\frac{S_1}{c_P} 
+ \frac{\mu}{\rho_0}\left[\grad^2 \bm{u} + \frac{1}{3}\grad(\DivU)\right]
\label{eqn:dim_momentum}\\
\partial_t S_1 + \bm{u}\cdot\grad S_1 = 
+\frac{\kappa}{\rho c_V}\left[\grad^2 S_1 + \partial_z\ln T_0\cdot\partial_z S_1\right]
+ \frac{\mu}{\rho T}\sigma_{ij}\partial_{x_i}u_j,
\label{eqn:dim_entropy}
\end{gather}
with the modified stress tensor
\begin{equation}
\sigma_{ij} = \left(\partial_{x_i}u_j + \partial_{x_j}u_i - \frac{2}{3}\delta_{ij}\DivU\right).
\end{equation}
Here, the $c_V^{-1}$ shows up in the diffusion term because we're aiming for as close of a
one-to-one comparison with the FC temperature equation as possible. There, we had
$F = -\kappa \grad T_1 \approx -\kappa c_v^{-1} T_0 \grad S_1$ in the anelastic limit.

\subsection{Nondimensional anelastic equations}
We then nondimensionalize as in \citet{lecoanet&jeevanjee2018}, (where all of the terms from the
previous, dimension-ful equations now have $\sim$ over them):
\begin{equation}
\begin{split}
\tilde{\grad}\rightarrow(\tilde{L}_{th}^{-1})\grad, \qquad&
\tilde{S}_1 \rightarrow(\Delta\tilde{S})S_1,\\
\tilde{\bm{u}} \rightarrow (\tilde{u}_{th})\bm{u}, \qquad&
\tilde{\varpi} \rightarrow (\tilde{u}_{th}^2)\varpi,\\
\partial_{\tilde{t}} \rightarrow (\tilde{u}_{th}/\tilde{L}_{th})\partial_t,\qquad&
\end{split}
\end{equation}
with
\begin{equation}
\tilde{u}_{th}^2 = \frac{g \tilde{L}_{th} \Delta \tilde{s}}{c_P}, \qquad
\text{Re}_{\text{ff}} = \frac{\tilde{u}_{th} \tilde{L}_{th}}{\nu}, \qquad
\text{Pr}_{\text{ff}} = \frac{\tilde{u}_{th} \tilde{L}_{th}}{\chi}.
\end{equation}
Here we acknowledge that $\mu = \nu$ and $\chi = \kappa$ when $\rho = 1$ (at the top
of the domain), so these values are specified at the upper boundary, but will increase
with depth.

Under these assumptions, eqns.~\ref{eqn:dim_momentum} \& \ref{eqn:dim_entropy} become
(with $\bm{g} = - g \hat{z}$),
\begin{gather}
\partial_t \bm{u} + \bm{u}\cdot\grad\bm{u} + \grad \varpi = S_1\hat{z} 
+ \frac{1}{\text{Re}_{\text{ff}}}\left[\grad^2 \bm{u} + \frac{1}{3}\grad(\DivU)\right] \\
\partial_t S_1 + \bm{u}\cdot\grad S_1 = 
\frac{1}{\text{Re}_{\text{ff}}}\left(\frac{1}{\text{Pr}_{\text{ff}}\rho_0c_V }[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]
+ \frac{g \tilde{L}_{th}}{\rho_0 T_0 c_P}\sigma_{ij}\partial_{x_i}u_j \right),
\end{gather}
The viscous heating term is a bit ugly, but it's truly not too bad.
This formulation is great in that we can set up experiments in boxes
which are exactly the same size as in \citet{lecoanet&jeevanjee2018} (e.g., 10 x 20), with
a thermal whose diameter is 1 length unit, and then we can evolve for some tens of time units
to get it to the bottom of the domain.

\subsection{Nondimensional atmosphere}
In order to make these equations work, it's important that the atmosphere also be scaled 
appropriately. In a normal polytrope, we have
\begin{gather}
T_0= (1 + \tilde{L}_z - \tilde{z}), \\
\rho_0 = T^m,
\end{gather}
with $\tilde{L}_z = e^{n_\rho/m} - 1$ and the adiabatic temperature gradient
$\partial_{\tilde{z}} T_{ad} = -g/c_P = -1$, so $g = c_P$. We want to maintain the stratification
of these fields, as that's already nondimensionalized ($\rho_0 = T_0= 1$ at the top of the atmosphere),
but we need to rescale the length scales. Thus, let's acknowledge that the true stratification
here is $T_0= 1 + (\partial_{\tilde{z}} T_{ad})(\tilde{z} - \tilde{L}_z)$. If we take out the
dimensionality of $\tilde{z} = \tilde{L}_{th} z$ and $\tilde{L}_z = \tilde{L}_{th} L_z$, then
we get $T_0= 1 + (\tilde{L}_{th}\partial_{\tilde{z}} T_{ad})(z - Lz)$. Thus, in these domains,
$\partial_z T_{ad} = (\tilde{L}_{th}\partial_{\tilde{z}} T_{ad})$.

So, what is $\tilde{L}_{th}$? Well, if we have a dimensional polytrope whose depth is
$\tilde{L}_z = (e^{n_\rho/m} - 1)$, and we want 20 thermals to fit in that depth, then
$\tilde{L}_{th} = \tilde{L}_z / 20$, or since 20 is the nondimensional $L_z$, 
$\tilde{L}_{th} = ((e^{n_\rho/m} - 1))/L_z$.

The resulting stratification is just a more careful specification of where we started,
\begin{gather}
T_0 = 1 + \partial_z T_{ad} (z - L_{exp}) \\
\rho_0 = T^m,
\end{gather}
with $\partial_z T_{ad} = (\tilde{L}_{th}\partial_{\tilde{z}} T_{ad})$ and
$\tilde{L}_{th} = ((e^{n_\rho/m} - 1))/L_z$. These stratified terms enter the
equations mostly in log form,
\begin{equation}
\begin{split}
\partial_z \ln T_0= \frac{\partial_z T_{ad}}{T} \\
\partial_z \ln\rho_0 = \frac{m\partial_z T_{ad}}{T}
\end{split}
\end{equation}
In the case of low stratification, $\tilde{L}_{th} \rightarrow 0$, so $\partial_z T_{ad} \rightarrow 0$
meanwhile $\rho_0 \rightarrow T_0 \rightarrow 1$, and our equations take on their boussinesq form.

\bibliography{biblio.bib}
\end{document}

### 2019-04-30 notes_theory/hrho_div_therm/hrho_therm.py
adds theory plot to notes

@@ -1,0 +1,44 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+
+Lz = 20
+n_rho       = np.logspace(-2, 1, 100) #float(args['--n_rho'])
+
+################
+# Set up atmosphere info
+################
+gamma     = 5./3                         #adiabatic index
+m_ad      = 1/(gamma-1)
+Cp        = gamma*m_ad
+Cv        = Cp/gamma
+grad_T_ad = -(np.exp(n_rho/m_ad) - 1)/Lz #adiabatic temperature gradient
+g         = (1 + m_ad) #* -grad_T_ad     #gravity
+
+Lr        = Lz
+radius    = 0.5       #Thermal radius, by definition, in nondimensionalization
+delta_r   = radius/5  #Thermal smoothing width
+
+#(r0, z0) is the midpoint of the (spherical) thermal
+r0        = 0
+z0        = Lz - 3*radius
+
+# Adjust the Re at the top of the domain if in a kappa_mu formulation so that the input Re 
+# is the freefall Re at the height of the initial thermal
+rho_therm = (1 + grad_T_ad*(z0 - Lz))**m_ad
+H_rho_therm = -(1 + grad_T_ad*(z0-Lz))/(grad_T_ad*m_ad)
+f = interp1d(n_rho, 1/H_rho_therm)
+
+plt.loglog(n_rho, 1/H_rho_therm, lw=1)
+for n in [0.01, 0.1, 0.5, 1, 2, 3, 4, 5, 7]:
+    plt.axhline(f(n), c='k', ls='--', lw=0.5)
+    plt.axvline(n, c='k', ls='--',    lw=0.5)
+    plt.scatter(n, f(n), c='k')
+    plt.text(n*1.1, f(n)/1.5, n)
+
+inv_f = interp1d(1/H_rho_therm, n_rho)
+plt.scatter(inv_f(0.31), 0.31, 100,  c='red', marker='*')
+
+plt.xlabel(r'$n_\rho$')
+plt.ylabel(r'$L_{th}/H_\rho$')
+plt.savefig('r_div_H_vs_nrho.png', dpi=200)

### 2019-04-30 code/AN_2D_thermal.py
swaps out BCs, removes confusing windowing functions.

@@ -115,28 +115,6 @@ problem = de.IVP(domain, variables=['u', 'w', 'ur', 'wr', 'S1', 'S1r', 'p'])
 problem.meta['u', 'w', 'S1r', 'p']['r']['dirichlet'] = True
 problem.parameters['u_phi'] = problem.parameters['u_phir'] = 0
 
-
-def Smoother(*args):
-    z = args[0].data
-    Lz = args[1].value
-    dr = args[2].value
-    if len(z) > 0:
-        return window(z, Lz=Lz, dr=dr)
-    else:
-        return z
-
-def window(z, Lz=20, dr=0.2):
-    window1= (erf((z-0.025*Lz)/dr)+1)/2
-    window2= -(erf((z-0.975*Lz)/dr)-1)/2
-    return window1*window2
-
-def de_smoother(*args, domain=domain, F=Smoother):
-    return de.operators.GeneralFunction(domain, layout='g', func=F, args=args)
-
-de.operators.parseables['S'] = de_smoother
-problem.substitutions['window'] = '(S(z,Lz,Lz/100))'
-problem.substitutions['edges'] = '(1 - window)'
-
 problem.parameters['pi']         = np.pi
 problem.parameters['Lz']         = Lz
 problem.parameters['Lr']         = Lr
@@ -150,11 +128,11 @@ problem.parameters['Pr']         = Pr
 problem.parameters['Lnondim']    = -grad_T_ad #scaling factor from unscaled polytropes -- for viscous heating term.
 
 problem.substitutions['T']            = '(1 + grad_T_ad*(z - Lz))'
-problem.substitutions['T0']           = '(edges + window*T)'
-problem.substitutions['rho0']         = '(edges + window*(T)**(m_ad))'              
-problem.substitutions['ln_rho0_z']    = '(edges + window*m_ad*grad_T_ad/T)'         
-problem.substitutions['ln_rho0_zz']   = '(edges - window*m_ad*grad_T_ad**2/T**2)'  
-problem.substitutions['ln_T0_z']      = '(edges + window*grad_T_ad/T)'              
+problem.substitutions['T0']           = '(T)'
+problem.substitutions['rho0']         = '((T)**(m_ad))'              
+problem.substitutions['ln_rho0_z']    = '(m_ad*grad_T_ad/T)'         
[…]

### 2019-04-30 tex/stratified_thermals.tex
gets paper writing actually started

--- 2019-02-20 tex/stratified_thermals.tex
@@
 
-\received{October 19, 2018}
+\received{\today}
 \revised{\today}
@@
 %% TITLE & AUTHORS
-\shorttitle{Entrainment of thermals in stratified atmospheres}
+\shorttitle{Stratified Thermals}
 \shortauthors{Anders et al.}
@@
 \begin{document}
-\title{Entrainment of low Mach number thermals in stratified atmospheres}
+\title{Entrainment of low Mach number thermals in stratified domains}
 
@@
 \label{sec:intro}
+(Para 1) Brief intro to solar convective conundrum.
+
+(Para 2) Entropy rain history and expansion by Axel
+
+(Para 3) Boussinesq thermals and their filling factor vs. depth.
+
+(Para 4) What we're doing here, how it fits into this context.
+
+(Para 5) Standard last paragraph of an intro?
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% THEORY SECTION
+\section{Theory}
+\label{sec:theory}
+The evolution of thermals as buoyant vortex rings has been well described in
+the unstratified, Boussinesq limit for decades (as early as e.g., CITE, and
+see \citet{lecoanet&jeevanjee2018} for other sources). Buoyant motions 
+in the atmospheres of stars and planets are generally large enough to feel the
+atmospheric stratification, and therefore a more thorough tratment of the
+evolution of thermals in stratified domains is required to understand the nature
+of thermal entrainment in nature.
+
+In this work, we focus on the non-dissipative, low Mach number regime, 
+in which the ideal anelastic equations are a decent approximation to the fully
+compressible equations. In this regime, the buoyancy is directly proportional to the
+specific entropy. In the absence of diffusion, or in the limit where diffusivities
+are sufficiently small, the volume-integrated total entropy is constant,
+\begin{equation}
+B \equiv \int_{\mathcal{V}} \rho\, s\, dV = \text{const},
+\end{equation}
+where $s = c_V \ln T - R \ln\rho$ is the specific entropy, with $c_V$ the
+specific heat at constant volume and $R$ the ideal gas constant.
+
+In a stratified domain, the hydrodynamic impulse is defined
+\citet{shivamoggi2010},
+\begin{equation}
+\bm{I} = \frac{1}{2}\int_{\mathcal{V}} \bm{x}\times(\grad\times(\rho\bm{u}))dV,
+\end{equation}
+where $\bm{x}$ is the position vector, $\bm{u}$ is vector velocity, $\rho$ is density,
+and $\mathcal{V}$ is the volume being integrated over. Furthermore, changes in the impulse
+can be expressed
+\begin{equation}
+\frac{\partial\bm{I}}{\partial t} = \int_{\mathcal{V}}\frac{\partial}{\partial t}(\rho \bm{u})dV
+= B\hat{z} + S,
+\end{equation}
+where $S$ is a combination of surface terms that disappears upon appropriate boundary conditions
+on $\mathcal{V}$ \citep{shivamoggi2010}. As we have assumed that the buoyancy, $B$, is constant,
+we can straightforwardly integrate
+\begin{equation}
+I_z = B t + I_0,
+\end{equation}
+for some constant $I_0$.
+
+(need to work through this section carefully).
+Assuming an adiabatically stratified atmosphere in
+hydrostatic equilibrium, the vertical momentum equation is
+\begin{equation}
+ = - \partial_z \varpi +  g\frac{S_1}{c_P},
+\label{eqn:buoyancy}
+\end{equation}
+where $w$ is vertical velocity, $S_1$ is specific entropy, $\varpi$ is the reduced pressure,
+$D/Dt = \partial_t + (\bm{u}\cdot\grad)$ is the (eulerian? lagrangian?)
+derivative, $g$ is gravity, and $c_P$ is the specific heat at constant pressure.
+In the anelastic approximation, the density stratification is constant in time. 
+OH GOD I DON'T KNOW THIS MATH WELL MAGIC MAGIC MAGIC.
+By doing magic, we arrive at
+\begin{equation}
+P_z = \beta B t + P_0.
+\end{equation}
+
+Under the assumption that the thermal develops into a thin-core 
+propagating vortex ring whose vortex core is radius $r$ away from the axis of symmetry, 
+the impulse can be approximated as $I_z \approx \pi \rho r^2 \Gamma$, where 
+$\Gamma$ is the circulation of the thermal vortex, which we assume to be constant. 
+Rearranging, we find our first result,
+\begin{equation}
+r = \sqrt{\frac{B t + I_0}{\pi\rho\Gamma}}.
+\label{eqn:r_theory}
+\end{equation}
+In the limit where $\rho \rightarrow \text{constant}$, as in the Boussinesq regime,
+we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime by
+\citet{lecoanet&jeevanjee2018}. We find that the inclusion of stratification adds the
+additional complexity of $r \propto \rho^{-1/2}$, such that downward-propogating 
+vortex rings (as studied here) will not entrain to the same degree as boussinesq thermals,
+and upward-propogating rings will entrain more.
+
+We further assume that the volume-integrated momentum, $P_z \approx \rho V w_{th}$,
+where $w_{th}$ is the vertical velocity of the thermal as a whole, and the volume
+of the fluid region propogating with the thermal is a spheroid, $V = V_0 r^3$, for
+some constant $V_0$. Plugging Eqn.~\ref{eqn:r_theory} into this approximation, we
+find that
+\begin{equation}
+\rho^{-1/2}w = \left(\frac{(\pi\Gamma)^{3/2}}{V_0}\right)\frac{\beta B t + M_0}{(B t + I_0)^{3/2}}.
+\end{equation}
+Substituting $w = dz/dt$ and $\tau \equiv (Bt + I_0)/\Gamma$, We retrieve
+\begin{equation}
+\frac{dz}{\sqrt{\rho(z)}} 
+= \left(\frac{\pi^{3/2}\Gamma}{V_0}\right)
+\left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
+\end{equation}
+If the atmospheric stratification in which the thermal is falling is known, this
+result can be straightforwardly integrated with $\rho(z)$ plugged in in order to
+find the position of the thermal versus time. While we will leave this result
+general for now, we will plug in our polytropic stratification at the end of
+section \ref{sec:experiment}, and show that the resulting expression does a
+good job of explaining the evolution of thermals in these atmospheres in
+section \ref{sec:results}.
 
@@
 \label{sec:experiment}
+blah blah blah polytrope blah blah blah (do it with a general length scale).
 
-We perform direct numerical simulations of the evolution of dry thermals
-by solving the fully compressible Navier-Stokes equations,
-\begin{gather}
-\frac{D \ln\rho}{Dt} = -\Div{\bm{u}}
-	\label{eqn:continuity}
-\\
-\frac{D \bm{u}}{D t} =
--\frac{1}{\rho}\grad P + \bm{g} + \Div{\stressT}, 
-	\label{eqn:dim_bouss_momentum}
-\\
-\frac{D T}{D t} + (\gamma - 1)T\Div{\bm{u}} + \frac{1}{\rho c_V}\Div{-\rho\chi\grad T} = 
-\frac{1}{\rho c_V}(\stressT \cdot \grad)\cdot \bm{u},
-	\label{eqn:dim_bouss_energy}
-\end{gather}
+blah blah blah 2D anelastic blah blah blah, nondimm'd for a direct comparison with
+boussinesq.
+
+blah blah blah 3D Fully compressible blah blah blah
+
+blah blah blah thermal initial conditions, pressure equilibrium blah blah blah.
+
+blah blah blah comparison of 2D and 3D blah blah blah. z v t, r v z, w v z. Also side-by-side
+pictoral comparison with diff.
+
+blah blah blah T(t) and derivative blah blah blah.
 
@@
 \label{sec:results}
+Picture of a big old grid of z v t, r v z, w v z.
+
+Pretty picture showing thermal evolution (comparing low and high stratification).
+
+Verification of theory by simulations
+
+Table of found parameters for the fits
+
+Two regimes: stalling and falling.
 
@@
 \label{sec:discussion}
+Wild speculation about extensions to the solar regime. Do things on the sun shrink
+to the point where they viscously dissipate?
+
+Talk about what would happen if we were to study up-thermals.
+
+Extensions, and the fact that we trust these results will likely hold in the solar regime.
 
@@
 \appendix
+\section{Thermal Tracking}
+\label{appendix:tracking}
+
 \section{Table of Simulations}

### 2019-05-01 code/plotting/evolution_colormeshes.py
some updates to run scripts; adds the first plotting file!

@@ -1,0 +1,87 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+import h5py
+
+dirs = [    ('../AN_2D_thermal_nrho0.5_Re6e2_Pr1_aspect0.25_Lz20', (1, 0), (2, 18), (5, 17)) ,
+            ('../apr30/AN_2D_thermal_nrho3_Re6e2_Pr1_aspect0.125_Lz20' , (1,0), (2, 12),  (4, 5))]
+
+
+gs = gridspec.GridSpec(1000, 1000)
+
+subplots = [    ( (50, 0),    400, 150 ),  ( (50, 150),  400, 150 ),
+                ( (50, 350),  400, 150 ),  ( (50, 500),  400, 150 ),
+                ( (50, 700),  400, 150 ),  ( (50, 850),  400, 150 ),
+                ( (550, 0),   400, 150 ),  ( (550, 150), 400, 150 ),
+                ( (550, 350), 400, 150 ),  ( (550, 500), 400, 150 ),
+                ( (550, 700), 400, 150 ),  ( (550, 850), 400, 150 )
+            ]
+
+fig = plt.figure(figsize=(7.5, 5))
+axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
+
+plot_count = 0
+for i, ax in enumerate(axs):
+    dir_ind = int(i % 2)
+    this_dir = dirs[dir_ind][0]
+    filenum  = dirs[dir_ind][1 + (plot_count % 3)][0]
+    imgnum   = dirs[dir_ind][1 + (plot_count % 3)][1]
+    print(filenum)
+    f  = h5py.File('{:s}/slices/slices_s{}.h5'.format(this_dir, filenum), 'r')
+    cf = h5py.File('{:s}/thermal_analysis/contour_file.h5'.format(this_dir), 'r')
+
+    r = f['scales']['r']['1.0'].value
+    z = f['scales']['z']['1.0'].value
+    rr, zz = np.meshgrid(r.flatten(), z.flatten())
+    t = f['scales']['sim_time'].value[imgnum]
+
+    contour = cf['contours'].value[20*(filenum-1)+imgnum,:]
+
+    if int(plot_count / 3) < 1:
+        field = f['tasks']['w'].value[imgnum,:]
+    else:
+        field = f['tasks']['S1'].value[imgnum,:]
[…]

### 2019-05-01 tex/stratified_thermals.tex
some experiment section writing

@@
 \newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
-\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
+\newcommand{\td}[1]{\ensuremath{\widetilde{#1}}}
 \newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
@@
 \label{sec:theory}
+
+\subsection{Phenomenological description of thermal evolution}
+The initial conditions of the thermals studied in this work are spherical
+entropy perturbations with zero initial velocity, as depicted in 
+Fig.~\ref{fig:evolution_colormeshes}a. Buoyant forces cause these perturbations
+to fall and develop into vortex rings, as depicted in 
+Figs.~\ref{fig:evolution_colormeshes}c-f.
+
+\begin{figure*}[t!]
+    \includegraphics[width=\textwidth]{evolution_colormeshes.png}
+    \caption{
+    \label{fig:evolution_colormeshes} }
+\end{figure*}
+
+\subsection{Theoretical description of thermal evolution}
 The evolution of thermals as buoyant vortex rings has been well described in
@@
 \label{sec:experiment}
-blah blah blah polytrope blah blah blah (do it with a general length scale).
 
-blah blah blah 2D anelastic blah blah blah, nondimm'd for a direct comparison with
-boussinesq.
+\subsection{Polytropic Atmospheres}
+We study an ideal gas whose equation of state is $P = \rho T$ and whose stratification
+is a perfectly adiabatic polytrope,
+\begin{gather}
+T_0 = 1 + (\grad_{\text{ad}})(z - L_z) \\
+\rho_0 = T_0^{m_{\text{ad}}},
+\end{gather}
+where $m_{\text{ad}} = (\gamma-1)^{-1}$, and where the adiabatic 
+temperature gradient is $\grad_{\text{ad}} = - g / c_P$.
 
-blah blah blah 3D Fully compressible blah blah blah
+\subsection{Anelastic Equations}
+The anelastic equations are \citep{lecoanet&all2014},
+\begin{gather}
+\td{\grad}\cdot\td{\bm{u}} = -\td{w}\partial_{\tilde{z}} \ln\rho_0 \\
+\frac{D \td{\bm{u}}}{D \td{t}} = -\td{\grad} \td{\varpi} + g\frac{\td{S_1}}{c_P}\hat{z} + \frac{1}{\rho_0}\td{\grad}\cdot\left(\mu\td{\lilstressT}\right) \\
+\frac{D \td{S_1}}{D\td{t}} = \frac{1}{\rho c_P}\td{\grad}\cdot\left(\kappa T_0 \td{\grad} \td{S_1}\right) + \frac{\mu}{\rho_0 T_0}\td{\sigma_{ij}}\partial_{\td{x_i}}\td{u_j}.
+\end{gather}
+where $D/D\td{t} = \partial/\partial \td{t} + \td{\bm{u}}\cdot\td{\grad}$ and the viscous stress tensor is
+\begin{equation}
+\td{\sigma_{ij}} = \left(\partial_{\td{x_i}}\td{u_j} + \partial_{\td{x_j}}\td{u_i} - \frac{2}{3}\delta_{ij}\td{\grad}\cdot\td{\bm{u}}\right).
+\end{equation}
 
-blah blah blah thermal initial conditions, pressure equilibrium blah blah blah.
+We nondimensionalize these equations as in \citet{lecoanet&jeevanjee2018} such that
+the length scale is the diameter of the thermal and the velocity scale is the freefall
+velocity,
+\begin{equation}
+\begin{split}
+\td{\grad}\rightarrow(\td{L}_{th}^{-1})\grad, \qquad&
+\td{S}_1 \rightarrow(\Delta\td{S})S_1,\\
+\td{\bm{u}} \rightarrow (\td{u}_{th})\bm{u}, \qquad&
+\td{\varpi} \rightarrow (\td{u}_{th}^2)\varpi,\\
+\partial_{\tilde{t}} \rightarrow (\td{u}_{th}/\td{L}_{th})\partial_t,\qquad&
+\end{split}
+\end{equation}
+with
+\begin{equation}
+\tilde{u}_{th}^2 = \frac{g \tilde{L}_{th} \Delta \tilde{s}}{c_P}, \qquad
+\text{Re}_{\text{ff}} = \frac{\tilde{u}_{th} \tilde{L}_{th}}{\nu}, \qquad
+\text{Pr}_{\text{ff}} = \frac{\tilde{u}_{th} \tilde{L}_{th}}{\chi}.
+\end{equation}
+The resulting equations are very similar to the boussinesq equations,
+\begin{gather}
+\DivU = -w \partial_z \ln\rho_0, \\
+\begin{split}
+\partial_t \bm{u} + \bm{u}\cdot\grad\bm{u} = \\
+- \grad \varpi + S_1\hat{z} 
++ \frac{1}{\text{Re}_{\text{ff}}}\left[\grad^2 \bm{u} + \frac{1}{3}\grad(\DivU)\right] 
+\end{split}\\
+\begin{split}
+\partial_t S_1 + \bm{u}\cdot\grad S_1 = \\
+\frac{1}{\text{Re}_{\text{ff}}}\left(\frac{1}{\text{Pr}_{\text{ff}}\rho_0c_P }[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\right.\\\left.
++ \frac{-(\grad_{ad})}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right)
+\end{split}
+\end{gather}
 
+\subsection{Fully Compressible Equations}
+The fully compressible equations, under the same assumptions as above, are
+\begin{gather}
+\frac{D \ln\rho}{Dt} + \DivU = 0 \\
+\frac{D \bm{u}}{D t} = -\grad T - T\grad\ln\rho - g\hat{z} + \frac{1}{\rho}\grad\cdot\left(\mu\lilstressT\right) \\
+\frac{D T}{Dt} + (\gamma-1)T\DivU  = \frac{1}{\rho c_V}\grad\cdot\left(\kappa \grad T\right) + \frac{\mu}{\rho c_V}\sigma_{ij}\partial_{x_i}u_j.
+\end{gather}
+
+\subsection{Initial Conditions}
+We set the initial specific entropy perturbation as
+\begin{equation}
+S_1 = - A(1 - \text{erf}\left(\frac{r - r_{th}}{\delta}\right))/2,
+\end{equation}
+where in the FC cases $A = 10^{-4}$ and in the nondimensionalized AN cases,
+$A = 1$. Here, $r = \sqrt{x^2 + y^2 + (z - z_0)^2}$, where $z_0 = Lz - 3*r_{th}$,
+and $r_{th} = Lz/40$ is the radius of the thermal.
+
+In the fully compressible equations, it is essential that the initial conditions be in pressure
+equilibrium such that the low mach number nature of the thermal can be studied. In order to 
+achieve this pressure balance, we set
+\begin{equation}
+\ln\rho_1 = S_1/c_P, \qquad T_1 = T_0(e^{-\ln\rho_1} - 1).
+\end{equation}
+
+\subsection{Solution for thermal evolution in a Polytrope}
+
+\subsection{Verification of 2D Anelastic approximation}
 blah blah blah comparison of 2D and 3D blah blah blah. z v t, r v z, w v z. Also side-by-side
 pictoral comparison with diff.
-
-blah blah blah T(t) and derivative blah blah blah.
 

### 2019-05-02 code/AN_2D_thermal.py
changes CFL & adds checkpointing / plotting revamp

@@ -33,6 +33,10 @@ Options:
     --Lz=<L>              The depth of the domain, in thermal diameters [default: 20]
 
     --chi_nu              If true, use a constant diffusivity (rather than constant dynamic diffusivity) eqn formulation
+    --safety=<s>          Safety factor base [default: 25]
+    --out_cadence=<o>     Time cadence of output saves in buoyancy times [default: 0.08]  
+
+    --restart=<file>      Name of file to restart from, if starting from checkpoint
 
 """
 import os
@@ -51,6 +55,8 @@ logger = logging.getLogger(__name__)
 
 from docopt import docopt
 args = docopt(__doc__)
+
+from logic.checkpointing import Checkpoint
 
 ################
 # Read in args
@@ -197,7 +203,7 @@ problem.add_equation("(S1r - dr(S1)) = 0")
 problem.add_equation("(ur  - dr(u))  = 0")
 problem.add_equation("(wr  - dr(w))  = 0")
 #Continuity
-problem.add_equation("scale_c*(DivU_true) = -scale_c*(w*ln_rho0_z)")
+problem.add_equation("scale_c*(DivU_true) = -scale_c*(w*ln_rho0_z)", tau=False)
 #Momentum equations
 problem.add_equation("scale_m*(dt(u) +  dr(p)      - visc_L_u) = scale_m*(-UdotGradU_r     + visc_R_u    )", tau=False)
 problem.add_equation("scale_m*(dt(w) +  dz(p) - S1 - visc_L_w) = scale_m*(-UdotGrad(w, wr) + visc_R_w    )", tau=False)
@@ -227,9 +233,22 @@ z = domain.grid(0)
 S1 = solver.state['S1']
 S1r = solver.state['S1r']
 
-r_IC = np.sqrt((z - z0)**2 + (r - r0)**2)
-S1['g'] = -1*(1 - erf((r_IC - radius)/delta_r))/2
-S1.differentiate('r', out=S1r)
+logger.info('checkpointing in {}'.format(data_dir))
+checkpoint = Checkpoint(data_dir)
+mode = 'overwrite'
+restart = args['--restart']
+#initial conditions
+if restart is None:
+    r_IC = np.sqrt((z - z0)**2 + (r - r0)**2)
+    S1['g'] = -1*(1 - erf((r_IC - radius)/delta_r))/2
+    S1.differentiate('r', out=S1r)
+    # Initial timestep
+    start_dt = 1e-4*t_b
+else:
[…]

### 2019-05-02 tex/stratified_thermals.tex
writes intro; rearranges and improves experiment section.

@@
 \label{sec:intro}
-(Para 1) Brief intro to solar convective conundrum.
+Recent observations of solar convection have revealed a convective conundrum.
+Power spectra have revealed weaker flows than anticipated at large length scales,
+calling into question the existence of so-called ``giant cells'' driven by deep
+convection which would manifest as powerful, large-scale motions at the solar
+surface. This discrepancy between theory and observations has called into question
+our fundamental understanding of convection, sparking fruitful investigations into
+the nature of convection in the Sun.
 
-(Para 2) Entropy rain history and expansion by Axel
+\cite{spruit1997} hypothesized that convective motions may be driven entirely by
+cool downflows at the surface of the Sun, and \citet{brandenburg2016} expanded
+upon this ``entropy rain'' hypothesis. Brandenburg's work includes a careful
+expansion of mixing length theory to incorporate flux contributions from nonlocal
+convective motions, and handles this theory in a horizontally-averaged sense.
+He includes some discussion of possible flow morphologies which could be manifestations
+of this entropy rain, and even includes some brief simulations of propogating
+Hill vortices. However, these simulations and discussions did not include 
+include a fundamental piece of entropy rain: it is buoyant, and has an entropy
+deviation from the background atmosphere.
 
-(Para 3) Boussinesq thermals and their filling factor vs. depth.
+If entropy rain does evolve into downward propagating buoyant vortex rings, it is
+important to understand how buoyancy effects the filling factor of these basic
+convective elements. In the context of Earth's atmosphere, so-called ``thermals''
+are thought to be the nucleus of cloud formation. Thermals are buoyant areas
+of fluid which evolve into propagating buoyant vortex rings, and their
+evolution in the Boussinesq limit have been well studied in the laboratory
+for decades (see e.g., CITE), and more recently have been studied through
+Direct Numerical Simulation (DNS) in the laminar and turbulent regime
+\citep{lecoanet&jeevanjee2018}. One fundamental result of these studies of
+thermals is that they experience a large degree of entrainment: their size expands
+with height and their propagation velocity slows despite their buoyant nature.
+However, we do not know of a study in which the propagation of these thermals,
+and thus the nature of their entrainment, is affected by a 
+significant atmospheric stratification.
 
-(Para 4) What we're doing here, how it fits into this context.
+In the absence of buoyantly-induced entrainment, \citet{brandenburg2016}
+suggests that the filling factor, $f$, of vortex rings should decrease like
+$f \propto \rho^{\alpha}$ for horizontal compression and $f \propto \rho^{\alpha}$ for 
+spherical compression. On the other hand, the filling factor of Boussinesq
+thermals \emph{increases} like $f \propto d$, where $d$ is the depth propagated.
+In this work, we extend the study of \citet{lecoanet&jeevanjee2018} to study
+the propagation of low-Mach number, cold thermals in stratified domains, and how
+buoyant entrainment affects the scaling of their filling factor with depth. If
+buoyant entrainment is a dominant effect, it is possible that these buoyant vortex rings
+would simply grow too large and stall before reaching the bottom of the solar convection zone.
+On the other hand, if the compression effects suggested by \citet{brandenburg2016} are the
+dominant effect, then it is possible that these thermals could propagate to the bottom of the solar
+convection zone, or potentially shrink to a sufficiently small size where thermal dissipation is
+significant.
 
-(Para 5) Standard last paragraph of an intro?
+We lay out our work as follows. In section \ref{sec:theory}, we develop a theoretical description
+of thermals in a stratified domain. In section \ref{sec:experiment}, we describe and verify
+the experiments conducted in this work. In section \ref{sec:results}, we compare the results
+of our experiments to the theory developed in section \ref{sec:theory}. Finally, in section
+\ref{sec:discussion}, we discuss what our results imply for the entropy rain hypothesis.
 
@@
 \subsection{Phenomenological description of thermal evolution}
-The initial conditions of the thermals studied in this work are spherical
-entropy perturbations with zero initial velocity, as depicted in 
-Fig.~\ref{fig:evolution_colormeshes}a. Buoyant forces cause these perturbations
-to fall and develop into vortex rings, as depicted in 
-Figs.~\ref{fig:evolution_colormeshes}c-f.
+We show pictorally the evolution of a cold thermal from rest in 
+Fig.~\ref{fig:evolution_colormeshes}. In Fig.~\ref{fig:evolution_colormeshes}a,
+the evolution of a thermal in a weakly stratified domain with
+$n_\rho = 0.5$ density scale heights is shown. In Fig.~\ref{fig:evolution_colormeshes}b,
+the evolution of a thermal in an appreciably stratified domain with
+$n_\rho = 3$ density scale heights is shown. While the initial conditions are
+identical in both domains (spherical specific entropy perturbations of the
+same magnitude whose diameters are 5\% of the domain depth), and while in both cases
+the thermal quickly evolves into a propagating buoyant vortex ring, we find that the
+$n_\rho = 0.5$ case entrains and grows with depth, similarly to the Boussinesq regime.
+On the other hand, the $n_\rho = 3$ case has a radius which remains approximately constant
+over time, and it reaches the bottom of the domain in many fewer nondimensional freefall
+time units.
 
 \begin{figure*}[t!]
-    \includegraphics[width=\textwidth]{evolution_colormeshes.png}
+    \includegraphics[width=\columnwidth]{evolution_colormeshes.png}
     \caption{
@@
 \left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
+\label{eqn:general_theory}
 \end{equation}
@@
 
-\subsection{Polytropic Atmospheres}
-We study an ideal gas whose equation of state is $P = \rho T$ and whose stratification
-is a perfectly adiabatic polytrope,
-\begin{gather}
-T_0 = 1 + (\grad_{\text{ad}})(z - L_z) \\
-\rho_0 = T_0^{m_{\text{ad}}},
-\end{gather}
-where $m_{\text{ad}} = (\gamma-1)^{-1}$, and where the adiabatic 
-temperature gradient is $\grad_{\text{ad}} = - g / c_P$.
-
-\subsection{Anelastic Equations}
-The anelastic equations are \citep{lecoanet&all2014},
+\subsection{Anelastic Simulations}
+In this work, we primarily study the evolution of 2D, azimuthally symmetric, anelastic
+thermals in cylindrical coordinates. 
+We later verify that these simulations produce the same results a 3D fully compressible
+simulations in 3D cartesian domains (see sec. REF). 
+The LBR anelastic equations are \citep{lecoanet&all2014},
 \begin{gather}
@@
 \end{gather}
-where $D/D\td{t} = \partial/\partial \td{t} + \td{\bm{u}}\cdot\td{\grad}$ and the viscous stress tensor is
+where terms with tildes are dimensional, and where
+$D/D\td{t} = \partial/\partial \td{t} + \td{\bm{u}}\cdot\td{\grad}$. In our azimuthally symetric
+domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have
+no azimuthal velocity, $u_\phi$, we assume that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$. 
+Under this approximation, the components of the stress tensor are
 \begin{equation}
-\td{\sigma_{ij}} = \left(\partial_{\td{x_i}}\td{u_j} + \partial_{\td{x_j}}\td{u_i} - \frac{2}{3}\delta_{ij}\td{\grad}\cdot\td{\bm{u}}\right).
+\begin{split}
+&\td{\sigma}_{rr} = 2\frac{\partial \td{u_r}}{\partial \td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,
+\td{\sigma}_{rz}     = \td{\sigma}_{zr} = \frac{\partial \td{w}}{\partial \td{r}} + \frac{\partial \td{u_r}}{\partial \td{z}}, \\
+&\td{\sigma}_{\phi\phi} = 2\frac{\td{u_r}}{\td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,\,
+\td{\sigma}_{r\phi}  = \td{\sigma}_{\phi r}  = 0, \\
+&\td{\sigma}_{zz}       = 2\frac{\partial \td{w}}{\partial \td{z}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}}, \,\,\,\,\,\,
+\td{\sigma}_{\phi z} = \td{\sigma}_{z \phi}  = 0,\qquad
+\end{split}
 \end{equation}
+Furthermore, we assume that the dynamic viscosity, $\mu = \rho \nu$, and the
+thermal conductivity, $\kappa = \rho \chi$, are both uniform throughout the domain.
+The diffusivities
+$\nu$ and $\chi$ therefore scale inversely with the density.
 
-We nondimensionalize these equations as in \citet{lecoanet&jeevanjee2018} such that
-the length scale is the diameter of the thermal and the velocity scale is the freefall
-velocity,
+We nondimensionalize these equations in the same manner as in
+\citet{lecoanet&jeevanjee2018} such that
+the length scale is the diameter of the initial thermal perturbation
+and the velocity scale is the freefall velocity. The timescale is thus
+the freefall crossing time of this unit length. Mathematically,
 \begin{equation}
@@
 \end{equation}
-The resulting equations are very similar to the boussinesq equations,
+As the diffusivities scale with depth, Re$_{\text{ff}}$ is specified at the
+thermal's initial depth.
+The resulting equations are,
 \begin{gather}
@@
 \begin{split}
-\partial_t \bm{u} + \bm{u}\cdot\grad\bm{u} = \\
-- \grad \varpi + S_1\hat{z} 
+\partial_t \bm{u} + \bm{u}\cdot\grad\bm{u} =& \\
+- \grad \varpi + S_1\hat{z} &
 + \frac{1}{\text{Re}_{\text{ff}}}\left[\grad^2 \bm{u} + \frac{1}{3}\grad(\DivU)\right] 
@@
 \begin{split}
-\partial_t S_1 + \bm{u}\cdot\grad S_1 = \\
-\frac{1}{\text{Re}_{\text{ff}}}\left(\frac{1}{\text{Pr}_{\text{ff}}\rho_0c_P }[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\right.\\\left.
-+ \frac{-(\grad_{ad})}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right)
+\partial_t S_1 + \bm{u}\cdot\grad S_1 =& \\
+\frac{1}{\text{Re}_{\text{ff}}}\left(\frac{1}{\text{Pr}_{\text{ff}}\rho_0c_P }\right.&[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\\
+&+ \left.\frac{-(\grad_{ad})}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right)
 \end{split}
 \end{gather}
+where in this nondimensionalization, the adiabatic temperature gradient is defined
+in the next subsection.
 
-\subsection{Fully Compressible Equations}
-The fully compressible equations, under the same assumptions as above, are
+\subsection{Atmosphere \& Initial conditions}
+We study an ideal gas whose equation of state is $P = \rho T$ and whose stratification
+is a perfectly adiabatic polytrope,
+\begin{gather}
+T_0 = 1 + (\grad_{\text{ad}})(z - L_z) \\
+\rho_0 = T_0^{m_{\text{ad}}},
+\end{gather}
+where $m_{\text{ad}} = (\gamma-1)^{-1}$, and the adiabatic temperature 
+gradient in these nondimensional atmospheres is
+$$
+\grad_{\text{ad}} = -\frac{(e^{n_\rho/m_{ad}} - 1)}{L_z}\frac{m_{ad} + 1}{c_P},
+$$
+where $L_z$ is the atmospheric depth in units of thermal diameters.
+
+To initialize the simulation, we specify a spherical initial specific entropy perturbation,
+\begin{equation}
+S_1 = - A(1 - \text{erf}\left(\frac{r' - r_{th}}{\delta}\right))/2,
+\label{eqn:thermal_IC}
+\end{equation}
+where $A = 1$ for our scaled equations.
+Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3*r_{th}$,
+with the thermal radius set as $r_{th} = 0.5$, and a smoothing width, $\delta = 0.1$.
+
+\subsection{Fully Compressible Simulations}
+In order to verify the validity of our 2D Anelastic simulations, we evolve select
+thermals according to the 3D Navier Stokes equations in a cartesian domain. We use
+the $(T, \ln\rho)$ formulation of the equations in which we have previously studied fully compressible
+convection at low and high Mach number \citep{anders&brown2017, lecoanet&all2014},
 \begin{gather}
@@
 \end{gather}
+where the viscous stress tensor is defined as
+\begin{equation}
+\sigma_{ij} = \left(\partial_{x_i}u_j + \partial_{x_j}u_i - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right).
+\end{equation}
+These equations are nondimensionalized on the temperature gradient length scale such that
+$\grad_{\text{ad}} = -1$ and the nondimensional timescale is the sound crossing time of that
+unit length.
 
-\subsection{Initial Conditions}
-We set the initial specific entropy perturbation as
-\begin{equation}
-S_1 = - A(1 - \text{erf}\left(\frac{r - r_{th}}{\delta}\right))/2,
-\end{equation}
-where in the FC cases $A = 10^{-4}$ and in the nondimensionalized AN cases,
-$A = 1$. Here, $r = \sqrt{x^2 + y^2 + (z - z_0)^2}$, where $z_0 = Lz - 3*r_{th}$,
-and $r_{th} = Lz/40$ is the radius of the thermal.
-
-In the fully compressible equations, it is essential that the initial conditions be in pressure
-equilibrium such that the low mach number nature of the thermal can be studied. In order to 
-achieve this pressure balance, we set
+In setting the specific entropy, $S = c_V \ln T - R^{-1}\ln\rho$, to an equivalent condition
+to that specified in  Eqn.~\ref{eqn:thermal_IC}, we note that it is essential that the
+initial perturbation be in pressure equilibrium. The set of initial conditions that achieves this
+is
 \begin{equation}
@@
 \end{equation}
+We specify the magnitude of the initial entropy perturbations as 
+$A = \epsilon = 10^{-4}$, such that the mach number of the resultant thermal is O($10^{-2}$) or less.
+
+The depth of the atmosphere in these fully compressible domains is set by the number of density
+scale heights as $L_z = e^{n_\rho/m_{ad}} - 1$, and in order to compare results from these
+simulations to our nondimensionalized thermal simulations, we rescale all length scales in
+post-processing by $\ell = 20/L_z$, all timescales by $\tau = \sqrt{\ell \epsilon}$, and
+the entropy by $s = \epsilon^{-1}$.
 
 \subsection{Solution for thermal evolution in a Polytrope}
+Here we take the general theory described in Eqn.~\ref{eqn:general_theory} and apply it
+to the specific case of the polytropes we study here. 
+We note that, $\rho_0 = T_0^{m_{ad}}$ and
+$dT_0 = (\grad_{\text{ad}}) dz$, such that we must solve
+\begin{equation}
+T_0^{-m_{ad}/2} dT_0 
+= \left(\frac{\pi^{3/2}\Gamma\grad_{\text{ad}}}{V_0}\right)
+\left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
+\label{eqn:general_theory}
+\end{equation}
+Assuming that $m_{ad} < 2$ and through the use of simple power law integrals, we
+find that
+\begin{equation}
+T_0(t) = \left(C[\xi(\tau) - \xi(\tau_0)] + T_0(t_0)^{1/\alpha}  \right)^{\alpha},
+\end{equation}
+with
+\begin{equation}
+\xi(\tau) = \beta\Gamma\tau^{1/2} - (M_0 - \beta I_0) \tau^{-1/2},
+\end{equation}
+$C \equiv (2 \pi^{3/2} \Gamma (\grad_{\text{ad}}))/(\alpha V_0 B)$
 

### 2019-05-02 tex/stratified_thermals.tex
some paper updates, starts getting 3D data in

@@
 \label{appendix:tracking}
+We use a thermal tracking algorithm very similar to the one used in 
+\citet{lecoanet&jeevanjee2018} and inspired by the work of 
+\citet{romps&all2015}.
+
+We begin by measuring the thermal's height versus
+time. To do so, we average the domain's entropy profile in radius and azimuth
+to create an average profile of entropy with height, and then we use
+scipy's brentq function on the derivative of that profile to find its maximum.
+
+Next, we find the best fit of the thermal's height vs. time according to our theory
+and derive that fit according to Eqn.~\ref{eqn:theory_velocity} to find the bulk
+vertical velocity of the thermal, $w_b$. We then calculate the streamfunction of
+the velocity field as in \citet{romps&all2015},
+\begin{equation}
+\frac{\partial \psi}{\partial r} = 2\pi \rho r (w - w_b),
+\end{equation}
+with the boundary condition that $\psi = 0$ at $r = 0$. The contour defined by $\psi = 0$
+from this solution is taken to be the outline of the thermal, and the volume of the thermal
+is taken to be the volume radially inward from that contour.
 
@@
 
-%\begin{deluxetable*}{c c c c c c c c c c c c c c c}
-%\tabletypesize{\footnotesize}
-%\caption{Table of simulation information
-%\label{table:simulation_info}
-%}
-%\tablehead{																																															
-%\colhead{Ra$_{\text{top}}$}	&	\colhead{Ta$_{\text{top}}$}	&	\colhead{Ro$_{\text{p, top}}$}	&	\colhead{Ra$_{\text{mid}}$}	&	\colhead{Ta$_{\text{mid}}$}	&	\colhead{Ro$_{\text{p, mid}}$}	&	\colhead{\con}	&	\colhead{$\mathcal{S}$}	&	\colhead{$L_x/L_z$}	&	\colhead{(nz,	nx,	ny)}	&					\colhead{Ro}      	&	\colhead{Re$_{\parallel}$} 	&	\colhead{Re$_{\perp}$}	&	\colhead{Nu}      	}
-%\startdata																																															
-%\multicolumn{3}{l}{\textbf{Constant \pro$\,$, path III}}\\
-%1.8	$\times 10^{	5	}$	&	4.1	$\times 10^{	7	}$	&	0.60	&	1.4	$\times 10^{	7	}$	&	3.0	$\times 10^{	9	}$	&	1.03	&	0.067	&	1.1	&	0.51	&	(256,		32,		32)	&	0.015	&	19.4	&	2.5	&	1.2	\\				
-%1.2	$\times 10^{	9	}$	&	5.2	$\times 10^{	12	}$	&	0.60	&	9.2	$\times 10^{	10	}$	&	3.8	$\times 10^{	14	}$	&	1.03	&	0.015	&	3.0	&	0.07	&	(2048,		64,		64)	&	0.026	&	1771	&	32.0	&	15.4	\\				
-%5.2	$\times 10^{	2	}$	&	4.6	$\times 10^{	3	}$	&	0.96	&	3.8	$\times 10^{	4	}$	&	3.4	$\times 10^{	5	}$	&	1.64	&	0.333	&	1.13	&	2.28	&	(64,		64,		64)	&	0.074	&	4.2	&	2.5	&	1.2	\\				
-%3.8	$\times 10^{	8	}$	&	3.1	$\times 10^{	11	}$	&	0.96	&	2.8	$\times 10^{	10	}$	&	2.3	$\times 10^{	13	}$	&	1.64	&	0.035	&	6.0	&	0.12	&	(2048,		64,		64)	&	0.129	&	3906	&	113	&	66.9	\\				
-%7.9	$\times 10^{	1	}$	&	1.0	$\times 10^{	2	}$	&	1.58	&	5.8	$\times 10^{	3	}$	&	7.4	$\times 10^{	3	}$	&	2.70	&	0.888	&	1.56	&	4.44	&	(64,		64,		64)	&	0.303	&	4.4	&	4.9	&	1.7	\\				
-%1.4	$\times 10^{	7	}$	&	9.7	$\times 10^{	8	}$	&	1.58	&	1.0	$\times 10^{	9	}$	&	7.2	$\times 10^{	10	}$	&	2.70	&	0.119	&	10.0	&	0.30	&	(512,		128,		128)	&	0.376	&	1257	&	94.9	&	40.1	\\				
-%\hline																																															
-%\multicolumn{3}{l}{\textbf{Constant \con$\,$, path II}}\\
-%8.6	$\times 10^{	4	}$	&	8.6	$\times 10^{	6	}$	&	0.74	&	6.3	$\times 10^{	6	}$	&	6.3	$\times 10^{	8	}$	&	1.26	&	0.1	&	1.47	&	0.68	&	(128,		128,		128)	&	0.051	&	40.2	&	6.7	&	2.2	\\				
-%2.6	$\times 10^{	6	}$	&	2.6	$\times 10^{	8	}$	&	1.13	&	1.9	$\times 10^{	8	}$	&	1.9	$\times 10^{	10	}$	&	1.93	&	0.1	&	4.64	&	0.39	&	(256,		512,		512)	&	0.27	&	565	&	53.2	&	33.3	\\				
-%1.4	$\times 10^{	3	}$	&	1.6	$\times 10^{	4	}$	&	1.01	&	1.1	$\times 10^{	5	}$	&	1.2	$\times 10^{	6	}$	&	1.72	&	0.3	&	1.47	&	1.90	&	(64,		128,		128)	&	0.124	&	11.3	&	5.4	&	1.8	\\				
-%1.1	$\times 10^{	6	}$	&	1.2	$\times 10^{	7	}$	&	2.29	&	7.8	$\times 10^{	7	}$	&	8.6	$\times 10^{	8	}$	&	3.93	&	0.3	&	14.7	&	0.65	&	(192,		384,		384)	&	0.808	&	529	&	83.5	&	27.3	\\				
-%5.5	$\times 10^{	1	}$	&	5.5	$\times 10^{	1	}$	&	1.65	&	4.0	$\times 10^{	3	}$	&	4.0	$\times 10^{	3	}$	&	2.82	&	1.0	&	1.47	&	4.84	&	(64,		128,		128)	&	0.303	&	3.6	&	4.4	&	1.5	\\				
-%2.8	$\times 10^{	6	}$	&	2.8	$\times 10^{	6	}$	&	6.39	&	2.0	$\times 10^{	8	}$	&	2.0	$\times 10^{	8	}$	&	10.93	&	1.0	&	100	&	0.82	&	(256,		512,		512)	&	3.357	&	1099	&	220	&	46.6	\\				
-%\hline																																															
-%\multicolumn{3}{l}{\textbf{Constant $\mathcal{S}$, path I}}\\
-%1.9	$\times 10^{	1	}$	&	1.1	$\times 10^{	-1	}$	&	10.00	&	1.4	$\times 10^{	3	}$	&	7.9	$\times 10^{		}$	&	17.12	&	13.2	&	2.0	&	9.91	&	(64,		64,		64)	&	3.668	&	3.0	&	10.2	&	1.7	\\				
-%3.0	$\times 10^{	6	}$	&	1.1	$\times 10^{	9	}$	&	0.70	&	2.2	$\times 10^{	8	}$	&	8.1	$\times 10^{	10	}$	&	1.20	&	0.052	&	2.0	&	0.30	&	(512,		128,		128)	&	0.053	&	242	&	17.9	&	6.0	\\				
-%3.0	$\times 10^{	1	}$	&	2.0	$\times 10^{	-1	}$	&	10.00	&	2.2	$\times 10^{	3	}$	&	1.5	$\times 10^{	1	}$	&	17.12	&	12.2	&	3.0	&	9.48	&	(64,		64,		64)	&	4.418	&	5.0	&	15.5	&	2.1	\\				
-%1.3	$\times 10^{	7	}$	&	5.6	$\times 10^{	9	}$	&	0.80	&	9.7	$\times 10^{	8	}$	&	4.2	$\times 10^{	11	}$	&	1.37	&	0.048	&	3.0	&	0.23	&	(512,		128,		128)	&	0.08	&	592	&	33.4	&	13.6	\\				
-%\enddata																																															
-%\tablecomments{
-%Input parameters and output parameters for select simulations are shown. For each of
-%the eight paths in Fig. \ref{fig:parameter_space}b, we show information for the lowest and
-%highest (Ra, Ta) point on that path. The first six rows show information for constant
-%$\pro\,$ paths, the next six for constant \con$\,$ paths, and the last four for constant $\mathcal{S}$ paths.
-%We show the input Ra, Ta, and \pro$\,$ at the top of the atmosphere, as well as their
-%stratification-weighted values at the midplane of the atmosphere, which provide a more direct
-%comparison to Boussinesq values \citep{unnoetall1960}. We also provide the input \con$\,$ at the
-%top of the atmosphere, $\mathcal{S}$, aspect ratio ($L_x/L_z$), and coefficient resolution
-%(nz, nx, ny). Each dimension of the physical grid is 3/2 the size of the coefficient grid 
-%for adequate dealiasing of quadratic nonlinear terms.
-%Output values of Ro, Re$_{\parallel}$, Re$_{\perp}$, and Nu are also provided.
-%This table in its entirety is published as a supplemental \texttt{.csv} file with this
-%manuscript and also online in a Zenodo repository \citep{supp_andersetall2019}.
-%}
-%\end{deluxetable*}
-%
+\begin{deluxetable*}{c c c c c c}
+\tabletypesize{\footnotesize}
+\caption{Table of simulation information
+\label{table:simulation_info}
+}
+\tablehead{																																															
+\colhead{$n_\rho$} & \colhead{$L_{thermal}/H_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
+\startdata																																															
+\multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
+0.1 	& 					&	128			& 512			& 45 	&	100	\\
+0.5 	& 					&	128			& 512			& 45 	&	100	\\
+1	 	& 					&	128			& 512			& 45 	&	100	\\
+2	 	& 					&	256			& 512			& 30 	&	100	\\
+3	 	& 					&	512			& 1024			& 30 	&	100	\\
+4	 	& 					&	1024		& 1024			& 30 	&	100	\\
+5	 	& 					&			& 			&  	&		\\
+6	 	& 					&			& 			&  	&		\\
+7	 	& 					&			& 			&  	&		\\
+\multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
+0.5 	& 					&	256			& 512			& 45 	&	0.6	\\
+1	 	& 					&	256			& 512			& 45 	&	0.6	\\
+2	 	& 					&	256			& 1024			& 45 	&	0.6	\\
+3	 	& 					&	256			& 2048			& 45 	&	0.6	\\
+\enddata																																															
+\tablecomments{
+}
+\end{deluxetable*}
 

### 2019-05-02 code/FC_3D_thermal.py

@@ -1,0 +1,309 @@
+"""
+Stratified fully compressible thermals in an adibatically stratified polytrope.
+Mu and Kappa are constant with depth.
+
+Usage:
+    FC_thermal_falling.py [options]
+
+Options:
+    --Reynolds=<Reynolds>                Reynolds number [default: 5e2]
+    --Prandtl=<Prandtl>                  Prandtl number = nu/kappa (top) [default: 1]
+    --n_rho=<n_rho>                      Density scale heights across layer [default: 1]
+    --epsilon=<epsilon>                  Amplitude of perturbation [default: 1e-4]
+
+    --gamma=<gamma>                      Gamma of ideal gas (cp/cv) [default: 5/3]
+    --aspect=<aspect_ratio>              Physical aspect ratio of the atmosphere (Lx = Ly = aspect*[diameter of thermal]) [default: 0.5]
+
+    --nz=<nz>                            vertical z (chebyshev) resolution [default: 512]
+    --nx=<nx>                            Horizontal x (Fourier) resolution [default: 256]
+    --ny=<ny>                            Horizontal y (Fourier) resolution [default: 256]
+    --mesh=<mesh>                        Processor mesh
+
+    --run_time=<run_time>                Run time, in hours [default: 7.5]
+    --run_time_buoy=<run_time_buoy>      Run time, in buoyancy times
+
+    --restart=<restart_file>             Restart from checkpoint
+
+    --safety_factor=<safety_factor>      Determines CFL Danger.  Higher=Faster [default: 0.2]
+
+    --label=<label>                      Additional label for run output directory
+    --join                               If flagged, join files at end of run
+    --out_cadence=<cadence>              Fraction of a buoyancy time on which to output [default: 0.08]                    
+
+    --chi_nu                             If flagged, do chi/nu formulation
+
+    --verbose
+    --SBDF2                              If flagged use SBDF2 timestepper
+    --443                                If flagged, use RK443 instead of RK222
+    --no_VH                              If flagged, don't include viscous heating
+"""
+import sys
+import os
[…]

### 2019-05-02 code/logic/equations.py

@@ -1,0 +1,343 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+
+from dedalus import public as de
+from mpi4py import MPI
+
+
+class FullyCompressibleEquations:
+    """
+    An abstract class containing the fully compressible equations which must
+    be extended to specify the type of diffusivities
+
+    Attributes
+    ----------
+    de_domain   : A DedalusDomain object
+        The domain on which the equations are solved
+    atmosphere  : An IdealGasAtmosphere object
+        The atmosphere in which the equations are solved
+    variables   : list
+        A list of strings of problem variables.
+    problem     : A Dedalus Problem object
+        The problem in which the equations are solved.
+    """
+    def __init__(self, de_domain, atmosphere):
+        """
+        Construct the equation class. Inputs are described in the class docstring.
+        """
+        self.de_domain = de_domain
+        self.atmosphere = atmosphere
+        self.variables = ['u','u_z','v', 'v_z', 'w','w_z','T1', 'T1_z', 'ln_rho1']
+        if not self.de_domain.threeD:
+            self.variables.remove('v')
+            self.variables.remove('v_z')
+
+        self.problem = de.IVP(self.de_domain.domain, variables=self.variables)
+        if not self.de_domain.threeD:
+            self.problem.substitutions['v'] = '0'
+            self.problem.substitutions['v_z'] = '0'
+            self.problem.substitutions['dy(A)'] = '0*A'
+
+    def set_equations(self, *args, **kwargs):
+        """ 
+        Sets the fully compressible equations of in a ln_rho / T formulation. These
+        equations take the form:
+        
+        D ln ρ + ∇ · u = 0
+        D u = - ∇ T - T∇ ln ρ - gẑ + (1/ρ) * ∇ · Π
+        D T + (γ - 1)T∇ · u - (1/[ρ Cv]) ∇ · (- Kap∇ T) = (1/[ρ Cv])(Π ·∇ )·u 
+        
+        Where
+
+        D = ∂/∂t + (u · ∇ ) 
+
+        and
+
+        Π = - Mu (∂u_i/∂x_j + ∂u_j/∂x_i - (2/3)D_{ij}∇ · u)
+
[…]

### 2019-05-02 code/logic/output.py

@@ -1,0 +1,91 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+
+from dedalus import public as de
+
+def initialize_output(data_dir, solver, threeD=False, output_cadence=1, writes_per=2, mode='overwrite', threeD_factor=1):
+    """
+    Initializes output tasks for a convection simulation.
+
+    Parameters
+    ----------
+    data_dir    : string
+        The root directory in which to save the output tasks
+    solver      : A Dedalus solver object
+        The solver for the simulation that output is for.
+    threeD      : bool, optional
+        If True, simulation is 3D.
+    output_cadence : float, optional
+        The output cadence of writes (in simulation time units)
+    writes_per     : int, optional
+        The maximum number of output writes per file.
+    mode           : string, optional
+        "overwrite" or "append" -- The Dedalus output mode.
+    threeD_factor  : float, optional
+        A factor to multiply output_cadence by to increase (or decrease) the time between outputs.
+    """
+    # VOLUMES AND SLICES
+    analysis_tasks = OrderedDict()
+    slices = solver.evaluator.add_file_handler(data_dir+'slices', sim_dt=output_cadence, max_writes=writes_per, mode=mode, parallel=False)
+    analysis_tasks['slices'] = slices
+    if threeD:
+        volumes = solver.evaluator.add_file_handler(data_dir+'volumes', sim_dt=output_cadence*threeD_factor, max_writes=writes_per, mode=mode, parallel=False)
+        analysis_tasks['volumes'] = volumes
+        volumes.add_task('Vort_x',     name='vorticity_x')
+        volumes.add_task('Vort_y',     name='vorticity_y')
+        volumes.add_task('u',          name='u')
+        volumes.add_task('v',          name='v')
+        volumes.add_task('w',          name='w')
+        volumes.add_task('T1',         name='T1')
+        volumes.add_task('rho_fluc',   name='rho_fluc')
+        volumes.add_task('s1',         name='entropy')
+
+        slices.add_task('interp(w, x = 0)',         name='w x mid')
+        slices.add_task('interp(w, y = 0)',         name='w y mid')
+        slices.add_task('interp(s1, x = 0)',        name='s x mid')
[…]

### 2019-05-03 code/plotting/evolution_colormeshes.py
figure updates

@@ -5,23 +5,25 @@ import matplotlib.gridspec as gridspec
 import numpy as np
 import h5py
 
-dirs = [    ('../apr30/AN_2D_thermal_nrho0.5_Re6e2_Pr1_aspect0.25_Lz20', (1, 0), (2, 18), (5, 17)) ,
-            ('../apr30/AN_2D_thermal_nrho3_Re6e2_Pr1_aspect0.125_Lz20' , (1,0), (2, 12),  (4, 5))]
+dirs = [    ('../may03/AN_2D_thermal_nrho0.5_Re6e2_Pr1_aspect0.25_Lz20', (1, 0), (2, 18), (5, 17)) ,
+            ('../may03/AN_2D_thermal_nrho3_Re6e2_Pr1_aspect0.25_Lz20' , (1,0), (2, 12),  (4, 5))]
 
 
 gs = gridspec.GridSpec(1000, 1000)
 
-subplots = [    ( (100, 50),    900, 450 ),  ( (100, 550),  900, 450 )
-            ]
+subplots = [    ( (100, 50),    900, 450 ),  ( (100, 550),  900, 450 ) ]
+colorbar = [    ( (50, 50),    50, 450 ),  ( (50, 550),  50, 450 ) ]
 
 fig = plt.figure(figsize=(3.25, 3))
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
+cax = plt.subplot(gs.new_subplotspec( (50, 50),    50, 950 ))
 
 plot_count = 0
 for i, ax in enumerate(axs):
     this_dir = dirs[i][0]
     for j, info in enumerate(dirs[i][1:]):
         filenum, imgnum = info
+        print('opening file ', this_dir, filenum, imgnum)
         f  = h5py.File('{:s}/slices/slices_s{}.h5'.format(this_dir, filenum), 'r')
         cf = h5py.File('{:s}/thermal_analysis/contour_file.h5'.format(this_dir), 'r')
 
@@ -30,6 +32,10 @@ for i, ax in enumerate(axs):
         rr, zz = np.meshgrid(r.flatten(), z.flatten())
         t = f['scales']['sim_time'].value[imgnum]
 
+        n_rho = float(this_dir.split('_nrho')[-1].split('_Re')[0])
+        grad_T = -(np.exp(n_rho/1.5)-1)/20
+        rho = 1#(1 + grad_T*(zz-20))**1.5
+
[…]

### 2019-05-03 code/plotting/results_panels.py

@@ -1,0 +1,79 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+import h5py
+
+CASES = [0.1, 0.5, 1, 2, 3, 4]
+r_bounds = [(0, 2), (0, 2), (0, 1.5), (0, 1), (0, 3./4), (0, 3./4)]
+ROOT_DIR='../may03/'
+DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect0.25_Lz20/'.format(ROOT_DIR,case) for case in CASES] 
+
+height, width = 5, 6.5
+pad = 50
+h_pad = 100
+p_height = int(np.round((1000 - 2*pad)/len(CASES)))
+p_width  = int(np.round((1000 - 2*pad - h_pad)/3))
+
+gs = gridspec.GridSpec(1000, 1000)
+
+subplots = []
+for i in range(len(CASES)):
+    for j in range(3):
+        if j > 0:
+            hpad = h_pad + pad
+        else:
+            hpad = pad
+        subplots.append( ( (pad+i*p_height, hpad+j*p_width), p_height, p_width))
+
+fig = plt.figure(figsize=(width, height))
+axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
+
+
+for i, direc in enumerate(DIRS):
+    f = h5py.File('{:s}/thermal_analysis/final_outputs.h5'.format(direc), 'r')
+    for j in range(3):
+        ax = axs[i*3+j]
+        if j == 0:
+            x, y     = f['times'].value, f['d_measured'].value
+            x_t, y_t = f['times'].value, f['d_theory'].value
+        elif j == 1:
+            x, y     = f['d_measured'].value, f['r_measured'].value
+            x_t, y_t = f['d_theory'].value,   f['r_theory'].value
+        elif j == 2:
+            x, y     = f['d_measured'].value[2:-2], f['w_measured'].value
+            x_t, y_t = f['d_theory'].value[2:-2],   f['w_theory'].value
+            ax.yaxis.tick_right()
+            ax.yaxis.set_label_position("right")
+        ax.plot(x, y, c='k', marker='o', lw=0, markersize=1, markeredgecolor='black')
+        ax.plot(x_t, y_t, c='orange', lw=1)
+
+        if j == 0:
+            ax.set_xlim(0, 50)
+            ax.set_ylim(0, 20)
[…]

### 2019-05-03 code/AN_2D_thermal.py
Big ol' commit of pleiades work on Friday

@@ -33,8 +33,8 @@ Options:
     --Lz=<L>              The depth of the domain, in thermal diameters [default: 20]
 
     --chi_nu              If true, use a constant diffusivity (rather than constant dynamic diffusivity) eqn formulation
-    --safety=<s>          Safety factor base [default: 25]
-    --out_cadence=<o>     Time cadence of output saves in buoyancy times [default: 0.08]  
+    --safety=<s>          Safety factor base [default: 0.08]
+    --out_cadence=<o>     Time cadence of output saves in buoyancy times [default: 0.2]  
 
     --restart=<file>      Name of file to restart from, if starting from checkpoint
 
@@ -243,7 +243,7 @@ if restart is None:
     S1['g'] = -1*(1 - erf((r_IC - radius)/delta_r))/2
     S1.differentiate('r', out=S1r)
     # Initial timestep
-    start_dt = 1e-4*t_b
+    start_dt = 1e-3*t_b
 else:
     logger.info("restarting from {}".format(restart))
     start_dt = checkpoint.restart(restart, solver)
@@ -277,9 +277,8 @@ safety_factor = float(args['--safety'])
 if args['--rk443']:
     safety_factor *= 4
 CFL = flow_tools.CFL(solver, initial_dt=start_dt, cadence=1, safety=safety_factor,
-                     max_change=1.5, min_change=0.5, max_dt=1e-2*t_b, threshold=0.05)
-CFL.add_velocities(('u', 'w'))
-#CFL.add_velocity(('w'), axis=0)
+                     max_change=1.5, min_change=0.5, max_dt=1e-3*t_b, threshold=0.05)
+CFL.add_velocities(('w', 'u'))
 
 # Flow properties
 flow = flow_tools.GlobalFlowProperty(solver, cadence=1)

### 2019-05-03 code/FC_3D_thermal.py

@@ -3,7 +3,7 @@ Stratified fully compressible thermals in an adibatically stratified polytrope.
 Mu and Kappa are constant with depth.
 
 Usage:
-    FC_thermal_falling.py [options]
+    FC_3D_thermal.py [options]
 
 Options:
     --Reynolds=<Reynolds>                Reynolds number [default: 5e2]

### 2019-05-03 code/join_data.py

@@ -1,0 +1,45 @@
+'''
+Join distributed dedalus output data.
+
+Usage:
+      join_data.py <case>... [--data_type=<data_type> --cleanup]
+
+Options:
+      --data_type=<data_type>      Type of data to join; if provided join a single data.
+      --cleanup                    Cleanup after join
+
+'''
+
+import os
+import sys
+import logging
+logger = logging.getLogger(__name__)
+
+import dedalus.public
+from dedalus.tools  import post
+
+from docopt import docopt
+
+args = docopt(__doc__)
+
+data_dir = args['<case>'][0]
+base_path = os.path.abspath(data_dir)+'/'
+
+cleanup = args['--cleanup']
+
+logger.info("joining data from Dedalus run {:s}".format(data_dir))
+
+if args['--data_type'] is not None:
+    data_types=[args['--data_type']]
+else:
+    data_types = ['final_checkpoint', 'checkpoint', 'volumes', 'profiles', 'slices', 'scalars']
+
+for data_type in data_types:
+    logger.info("merging {}".format(data_type))
+    try:
+        print(base_path+data_type)
+        post.merge_process_files('{:s}/{:s}/'.format(base_path,data_type), cleanup=cleanup)
+    except:
+        logger.info("missing {}".format(data_type))
+        
+logger.info("done join operation for {:s}".format(data_dir))

### 2019-05-03 code/logic/output.py

@@ -34,15 +34,16 @@ def initialize_output(data_dir, solver, threeD=False, output_cadence=1, writes_p
     if threeD:
         volumes = solver.evaluator.add_file_handler(data_dir+'volumes', sim_dt=output_cadence*threeD_factor, max_writes=writes_per, mode=mode, parallel=False)
         analysis_tasks['volumes'] = volumes
-        volumes.add_task('Vort_x',     name='vorticity_x')
-        volumes.add_task('Vort_y',     name='vorticity_y')
         volumes.add_task('u',          name='u')
         volumes.add_task('v',          name='v')
         volumes.add_task('w',          name='w')
         volumes.add_task('T1',         name='T1')
-        volumes.add_task('rho_fluc',   name='rho_fluc')
         volumes.add_task('s1',         name='entropy')
 
+        slices.add_task('interp(u, x = 0)',         name='u x mid')
+        slices.add_task('interp(u, y = 0)',         name='u y mid')
+        slices.add_task('interp(v, x = 0)',         name='v x mid')
+        slices.add_task('interp(v, y = 0)',         name='v y mid')
         slices.add_task('interp(w, x = 0)',         name='w x mid')
         slices.add_task('interp(w, y = 0)',         name='w y mid')
         slices.add_task('interp(s1, x = 0)',        name='s x mid')
@@ -50,12 +51,12 @@ def initialize_output(data_dir, solver, threeD=False, output_cadence=1, writes_p
         slices.add_task('interp(Vort_x, x = 0)',    name='vorticity x mid')
         slices.add_task('interp(Vort_y, y = 0)',    name='vorticity y mid')
     else:
-        slices.add_task('Vort_y',       name='vorticity_y')
+        slices.add_task('Vort_y',       name='V')
         slices.add_task('u',            name='u')
         slices.add_task('w',            name='w')
         slices.add_task('T1',           name='T1')
         slices.add_task('rho_fluc',     name='rho_fluc')
-        slices.add_task('s1',           name='entropy')
+        slices.add_task('s1',           name='S1')
         slices.add_task('enstrophy',    name='enstrophy')
 
     #PROFILES

### 2019-05-03 code/logic/post_processing.py

@@ -1,0 +1,1034 @@
+"""
+Analysis functionality for a 2D, cylindrically symmetric thermal's properties 
+
+Usage:
+    thermal_analysis.py --root_dir=<dir> [options]
+
+Options:
+    --root_dir=<root_dir>               Directory pointing to 'slices', etc
+    --plot                              If flagged, plot colormesh during analysis
+    --no_analyze                        If flagged, do not do full analysis
+    --n_files=<n>                           Number of files [default: 10000]
+    --get_contour                       If flagged, do full contour solve
+    --iterative                         If flagged, use results of previous solve to inform new solve
+"""
+import os
+import glob
+import logging
+logger = logging.getLogger(__name__)
+
+import h5py
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+from scipy.interpolate import interp1d, RegularGridInterpolator
+from scipy.optimize import brentq
+import scipy.optimize as scop
+
+from dedalus import public as de
+
+class DedalusIntegrator():
+    """
+    A simple class for post-processing thermal data
+    """
+    def __init__(self, nr, nz, Lr, Lz, *args, r_cheby=False, **kwargs):
+        """
+        Initialize the domain. Sets up a 2D (z, r) grid, with chebyshev
+        decomposition in the z-direction and fourier decomposition in the r-direction.
+
+        Inputs:
+        -------
+        nr, nz  : ints
+            Number of coefficients in r- and z- direction
+        Lr, Lz  : floats
+            The size of the domain in the r- and z- direction
+        *args, **kwargs : tuple, dict
+            Arguments and keyword arguments for the DedalusIntegrator._polytrope_initialize() function
+        """
+        self.Lz, self.Lr = Lz, Lr
+        if r_cheby:
+            self.r_basis = de.Chebyshev('r', nr, interval=(0,Lr))
+            self.z_basis = de.Fourier('z', nz, interval=(0, Lz))
+            self.domain = de.Domain([self.z_basis, self.r_basis], grid_dtype=np.float64)
+            self.r              = self.domain.grid(1)
+            self.z              = self.domain.grid(0)
+        else:
[…]

### 2019-05-03 code/plotting/evolution_colormeshes.py

@@ -34,10 +34,13 @@ for i, ax in enumerate(axs):
 
         n_rho = float(this_dir.split('_nrho')[-1].split('_Re')[0])
         grad_T = -(np.exp(n_rho/1.5)-1)/20
-        rho = 1#(1 + grad_T*(zz-20))**1.5
+        rho = (1 + grad_T*(zz-20))**1.5
 
         contour = cf['contours'].value[20*(filenum-1)+imgnum,:]
         contours = cf['contours'].value 
+
+        if j > 0:
+            rho *= np.max(contour)**3
         
         field = f['tasks']['S1'].value[imgnum,:]
         f.close()

### 2019-05-03 code/thermal_analysis.py

@@ -29,1013 +29,9 @@ import scipy.optimize as scop
 
 from dedalus import public as de
 
+from logic.post_processing import * #pull in most of the functions used here
+
 FILETYPE='.png'
-
-#entropy_key = 'entropy'   #'S1'
-#u_key       = 'u_r'       #'u'
-#V_key       = 'vorticity' #'V'
-entropy_key = 'S1'
-u_key       = 'u'
-V_key       = 'V'
-w_key       = 'w'
-
-
-class DedalusIntegrator():
-    """
-    A simple class for post-processing thermal data
-    """
-    def __init__(self, nr, nz, Lr, Lz, *args, r_cheby=False, **kwargs):
-        """
-        Initialize the domain. Sets up a 2D (z, r) grid, with chebyshev
-        decomposition in the z-direction and fourier decomposition in the r-direction.
-
-        Inputs:
-        -------
-        nr, nz  : ints
-            Number of coefficients in r- and z- direction
-        Lr, Lz  : floats
-            The size of the domain in the r- and z- direction
-        *args, **kwargs : tuple, dict
-            Arguments and keyword arguments for the DedalusIntegrator._polytrope_initialize() function
-        """
-        self.Lz, self.Lr = Lz, Lr
-        if r_cheby:
-            self.r_basis = de.Chebyshev('r', nr, interval=(0,Lr))
-            self.z_basis = de.Fourier('z', nz, interval=(0, Lz))
-            self.domain = de.Domain([self.z_basis, self.r_basis], grid_dtype=np.float64)
-            self.r              = self.domain.grid(1)
-            self.z              = self.domain.grid(0)
-        else:
-            self.r_basis = de.Fourier('r', nr, interval=(0,Lr))
-            self.z_basis = de.Chebyshev('z', nz, interval=(0, Lz))
-            self.domain = de.Domain([self.r_basis, self.z_basis], grid_dtype=np.float64)
-            self.r              = self.domain.grid(0)
-            self.z              = self.domain.grid(1)
-        self.T0             = self.domain.new_field()
-        self.rho0           = self.domain.new_field()
-        self.rho0_z         = self.domain.new_field()
-        self.grad_ln_rho0   = self.domain.new_field()
-        self.fields = [self.T0, self.rho0, self.rho0_z, self.grad_ln_rho0]
-        self.fd1 = self.domain.new_field()
-        self.fd2 = self.domain.new_field()
[…]

### 2019-05-03 tex/stratified_thermals.tex
paper progress

@@
 
-\begin{figure*}[t!]
+\begin{figure}[t!]
     \includegraphics[width=\columnwidth]{evolution_colormeshes.png}
@@
     \label{fig:evolution_colormeshes} }
-\end{figure*}
+\end{figure}
 
@@
 in the atmospheres of stars and planets are generally large enough to feel the
-atmospheric stratification, and therefore a more thorough tratment of the
-evolution of thermals in stratified domains is required to understand the nature
-of thermal entrainment in nature.
+atmospheric stratification, and therefore a more thorough treatment of the
+evolution of thermals in stratified domains is required to understand 
+thermal entrainment in nature.
 
@@
 in which the ideal anelastic equations are a decent approximation to the fully
-compressible equations. In this regime, the buoyancy is directly proportional to the
-specific entropy. In the absence of diffusion, or in the limit where diffusivities
-are sufficiently small, the volume-integrated total entropy is constant,
+compressible equations. In this regime, buoyant forces can be expressed explicitly
+in terms of the entropy. In the the limit where diffusivities
+are sufficiently small and therea re no thermal sources or sinks, 
+the volume-integrated total entropy inside of a buoyant vortex ring is constant,
 \begin{equation}
@@
 In a stratified domain, the hydrodynamic impulse is defined
-\citet{shivamoggi2010},
+\citep{shivamoggi2010},
 \begin{equation}
@@
 where $\bm{x}$ is the position vector, $\bm{u}$ is vector velocity, $\rho$ is density,
-and $\mathcal{V}$ is the volume being integrated over. Furthermore, changes in the impulse
-can be expressed
+and $\mathcal{V}$ is the volume being integrated over. Impulse is equivalent to the time-integrated
+work acting on the fluid resulting in the current fluid motion. 
+Changes in the impulse can be expressed as
 \begin{equation}
@@
 where $S$ is a combination of surface terms that disappears upon appropriate boundary conditions
-on $\mathcal{V}$ \citep{shivamoggi2010}. As we have assumed that the buoyancy, $B$, is constant,
-we can straightforwardly integrate
+on $\mathcal{V}$ \citep{shivamoggi2010}. In this context where buoyancy is the only source of
+work and the buoyancy, $B$, is constant, the impulse can be straightforwardly integrated as
 \begin{equation}
@@
 \end{equation}
-for some constant $I_0$.
-
-(need to work through this section carefully).
-Assuming an adiabatically stratified atmosphere in
-hydrostatic equilibrium, the vertical momentum equation is
-\begin{equation}
- = - \partial_z \varpi +  g\frac{S_1}{c_P},
-\label{eqn:buoyancy}
-\end{equation}
-where $w$ is vertical velocity, $S_1$ is specific entropy, $\varpi$ is the reduced pressure,
-$D/Dt = \partial_t + (\bm{u}\cdot\grad)$ is the (eulerian? lagrangian?)
-derivative, $g$ is gravity, and $c_P$ is the specific heat at constant pressure.
-In the anelastic approximation, the density stratification is constant in time. 
-OH GOD I DON'T KNOW THIS MATH WELL MAGIC MAGIC MAGIC.
-By doing magic, we arrive at
-\begin{equation}
-P_z = \beta B t + P_0.
-\end{equation}
-
+for some constant $I_0$. In the limiting regime where all of the buoyant fluid initially
+located in the thermal remains in the buoyant vortex ring, $I_0 \rightarrow 0$, but as
+some of the buoyant fluid is generally detrained in the initial spin-up to a vortex ring,
+it is important to keep the factor of $I_0$.
 Under the assumption that the thermal develops into a thin-core 
 propagating vortex ring whose vortex core is radius $r$ away from the axis of symmetry, 
-the impulse can be approximated as $I_z \approx \pi \rho r^2 \Gamma$, where 
-$\Gamma$ is the circulation of the thermal vortex, which we assume to be constant. 
+the impulse can be well approximated as $I_z \approx \pi \rho r^2 \Gamma$, where 
+$\Gamma = \iint (\grad\times\bm{u}) dr dz$ is the circulation in the vortex ring.
+Under this approximation, it becomes clear that so long as the vortex core is bounded
+by $\mathcal{V}$, the volume integrated over is rather arbitrary, as most of the circulation
+is located in the concentrated vortex ring.
+
+The vertical momentum of the thermal is less straightforward to find than the momentum. 
+Upon weighting the momentum equation (Eqn.~\ref{eqn:AN_momentum_full}) by the density, 
+Assuming an adiabatically stratified atmosphere in
+hydrostatic equilibrium, the change in volume integrated momentum over time is
+\begin{equation}
+\frac{D \bm{P}}{Dt} = \frac{D}{Dt}\int_{\mathcal{V}}\rho\bm{u} dV
+= \int_{\mathcal{V}} \rho\frac{D\bm{u}}{Dt} dV
+\approx B\hat{z} - \int_{\mathcal{V}} \rho\grad\varpi dV.
+\end{equation}
+As noted by \citet{tarshish&all2018}, only infinitesimally small buoyant regions of
+fluid accelerate according exactly according to their buoyant nature. Any buoyant anomaly
+with a finite size disrupts its fluid environment, and this disruption results in
+pressure terms which reduce the efficacy of the buoyant fluid in driving motions. 
+In their work with Boussinesq thermals, they find that the true buoyant acceleration
+can be well approximated by scaling down the buoyant force by a factor of O($1/2$).
+Taking their work into account, we assume that the vertical momentum of the thermal
+follows
+\begin{equation}
+P_z = \beta B t + P_0,
+\end{equation}
+where in this work we set $\beta = 1/2$.
+
 Rearranging, we find our first result,
@@
 vortex rings (as studied here) will not entrain to the same degree as boussinesq thermals,
-and upward-propogating rings will entrain more.
+and upward-propogating rings will entrain more. In the absence of buoyancy ($B = 0$),
+this result aligns with the prediction for purely horizontal compression noted by
+\citet{brandenburg2016} of $r^2 \propto \rho^{-1}$.
 
@@
 \frac{dz}{\sqrt{\rho(z)}} 
-= \left(\frac{\pi^{3/2}\Gamma}{V_0}\right)
+= \left(\frac{\pi^{3/2}\Gamma}{V_0 B}\right)
 \left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
@@
 section \ref{sec:results}.
+
+\subsection{Parameterization}
+
+\begin{deluxetable*}{c c c c c c}
+\tabletypesize{\footnotesize}
+\caption{Simulation output parameterization
+\label{table:simulation_info}
+}
+\tablehead{																																															
+\colhead{$n_\rho$} & \colhead{$L_{thermal}/H_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
+\startdata																																															
+\multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
+0.1 	& 					&	256			& 512			& 49 	&	0.2	\\
+0.5 	& 					&	256			& 512			& 42.5 	&	0.2	\\
+1	 	& 					&	256			& 512			& 38 	&	0.2	\\
+2	 	& 					&	256			& 512			& 31.75	&	0.2	\\
+3	 	& 					&	512			& 1024			& 27.25	&	0.2	\\
+4	 	& 					&	1024		& 1024			& 25 	&	0.2	\\
+5	 	& 					&			& 			&  	&		\\
+6	 	& 					&			& 			&  	&		\\
+7	 	& 					&			& 			&  	&		\\
+\multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
+0.5 	& 					&	256			& 512			& 45 	&	0.2	\\
+1	 	& 					&	256			& 512			& 45 	&	0.2	\\
+2	 	& 					&	256			& 1024			& 45 	&	0.2	\\
+3	 	& 					&	256			& 2048			& 45 	&	0.2	\\
+\enddata																																															
+\tablecomments{
+}
+\end{deluxetable*}
 
@@
 \begin{gather}
-\td{\grad}\cdot\td{\bm{u}} = -\td{w}\partial_{\tilde{z}} \ln\rho_0 \\
-\frac{D \td{\bm{u}}}{D \td{t}} = -\td{\grad} \td{\varpi} + g\frac{\td{S_1}}{c_P}\hat{z} + \frac{1}{\rho_0}\td{\grad}\cdot\left(\mu\td{\lilstressT}\right) \\
-\frac{D \td{S_1}}{D\td{t}} = \frac{1}{\rho c_P}\td{\grad}\cdot\left(\kappa T_0 \td{\grad} \td{S_1}\right) + \frac{\mu}{\rho_0 T_0}\td{\sigma_{ij}}\partial_{\td{x_i}}\td{u_j}.
+\td{\grad}\cdot\td{\bm{u}} = -\td{w}\partial_{\tilde{z}} \ln\rho_0 
+\label{eqn:AN_continuity_full}\\
+\frac{D \td{\bm{u}}}{D \td{t}} = -\td{\grad} \td{\varpi} + g\frac{\td{S_1}}{c_P}\hat{z} + \frac{1}{\rho_0}\td{\grad}\cdot\left(\mu\td{\lilstressT}\right)
+\label{eqn:AN_momentum_full}\\
+\frac{D \td{S_1}}{D\td{t}} = \frac{1}{\rho c_P}\td{\grad}\cdot\left(\kappa T_0 \td{\grad} \td{S_1}\right) + \frac{\mu}{\rho_0 T_0}\td{\sigma_{ij}}\partial_{\td{x_i}}\td{u_j}
+\label{eqn:AN_energy_full}.
 \end{gather}
@@
 T_0^{-m_{ad}/2} dT_0 
-= \left(\frac{\pi^{3/2}\Gamma\grad_{\text{ad}}}{V_0}\right)
+= \left(\frac{\pi^{3/2}\Gamma\grad_{\text{ad}}}{V_0 B}\right)
 \left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
@@
 \multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	& 					&	128			& 512			& 45 	&	100	\\
-0.5 	& 					&	128			& 512			& 45 	&	100	\\
-1	 	& 					&	128			& 512			& 45 	&	100	\\
-2	 	& 					&	256			& 512			& 30 	&	100	\\
-3	 	& 					&	512			& 1024			& 30 	&	100	\\
-4	 	& 					&	1024		& 1024			& 30 	&	100	\\
+0.1 	& 					&	256			& 512			& 49 	&	0.2	\\
+0.5 	& 					&	256			& 512			& 42.5 	&	0.2	\\
+1	 	& 					&	256			& 512			& 38 	&	0.2	\\
+2	 	& 					&	256			& 512			& 31.75	&	0.2	\\
+3	 	& 					&	512			& 1024			& 27.25	&	0.2	\\
+4	 	& 					&	1024		& 1024			& 25 	&	0.2	\\
 5	 	& 					&			& 			&  	&		\\
@@
 \multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
-0.5 	& 					&	256			& 512			& 45 	&	0.6	\\
-1	 	& 					&	256			& 512			& 45 	&	0.6	\\
-2	 	& 					&	256			& 1024			& 45 	&	0.6	\\
-3	 	& 					&	256			& 2048			& 45 	&	0.6	\\
+0.5 	& 					&	256			& 512			& 45 	&	0.2	\\
+1	 	& 					&	256			& 512			& 45 	&	0.2	\\
+2	 	& 					&	256			& 1024			& 45 	&	0.2	\\
+3	 	& 					&	256			& 2048			& 45 	&	0.2	\\
 \enddata																																															

### 2019-05-10 code/logic/post_processing.py
gets thermal analysis working quite well

@@ -38,53 +38,50 @@ def linear_fit(x, a, b):
     """ A linear fit: y = a* x + b """
     return a*x + b
 
-def theory_C(B, Gamma, V0, beta, chi, grad_T_ad=-1):
+def theory_C(B0, Gamma, f, chi, beta, grad_T_ad=-1):
     """ The constant in stratified thermals theory """
-    return np.pi**(3./2) * Gamma * grad_T_ad * chi / (V0 * B * beta**(1./2))
+    return np.pi**(3./2) * Gamma**2 * grad_T_ad * beta / (f * B0 * chi**(1./2))
 
-def theory_T(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
+#def theory_T(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
+#    """ The temperature profile (vs time) from stratified thermals theory """
+#    C0 = theory_C(B, Gamma, V0, beta, chi, grad_T_ad=grad_T_ad)
+#    tau = (B * t + I0)/Gamma
+#    tau0 = I0/Gamma
+#    Tpow = 1 - (m_ad/2)
+#    tau_int  = np.sqrt(tau )*(Gamma - (M0 - I0)/tau)
+#    tau_int0 = np.sqrt(tau0)*(Gamma - (M0 - I0)/tau0)
+#    return (2*Tpow*C0*(tau_int-tau_int0) + T0**(Tpow))**(1./Tpow)
+#
+#def theory_dT_dt(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
+#    """ The temperature derivative (vs time) from stratified thermals theory """
+#    C0 = theory_C(B, Gamma, V0, beta, chi, grad_T_ad=grad_T_ad)
+#    this_T = theory_T(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=grad_T_ad, m_ad=m_ad)
+#    tau = (B * t + I0)/Gamma
+#    dtau_dt = B/Gamma
+#    return C0*dtau_dt*this_T**(m_ad/2)*(Gamma/np.sqrt(tau) + (M0 - I0)/np.sqrt(tau**3))
+
+def theory_r(t, B0, Gamma0, chi, t_off, rho_f=None):
[…]

### 2019-05-10 code/thermal_analysis.py

@@ -50,7 +50,6 @@ def post_process(root_dir, plot=False, get_contour=True, analyze=True, out_dir='
     #If flagged, solve thermal tracking algorithm to get contour
     if get_contour:
         post.measure_cb()
-        post.fit_w_cb(iterative=iterative)
         post.calculate_contour(iterative=iterative)
 
     #### Step 3.
@@ -80,31 +79,15 @@ def post_process(root_dir, plot=False, get_contour=True, analyze=True, out_dir='
     radius       = output_file['radius'].value
     output_file.close()
 
-    #Read in fit quantities
-    fit_file = h5py.File('{:s}/fit_file.h5'.format(post.full_out_dir), 'r')
-    fit_B     = fit_file['fit_B'].value 
-    fit_M0    = fit_file['fit_M0'].value  
-    fit_I0    = fit_file['fit_I0'].value  
-    fit_beta  = fit_file['fit_beta'].value    
-    fit_chi   = fit_file['fit_chi'].value    
-    fit_Gamma = fit_file['fit_Gamma'].value     
-    fit_V0    = fit_file['fit_V0'].value  
-    fit_T0    = fit_file['fit_T0'].value  
-
-    w_cb         = fit_file['w_cb'].value
-    cb_T_fit     = fit_file['cb_T_fit'].value
-    T0 = vortex_T     = fit_file['vortex_T'].value
-    vortex_w     = fit_file['vortex_w'].value
-    rho0 = vortex_rho   = fit_file['vortex_rho'].value
-    therm_radius = fit_file['vortex_radius'].value
-    height       = fit_file['vortex_height'].value
-    fit_file.close()
+    cb_file           = h5py.File('{:s}/z_cb_file.h5'.format(post.full_out_dir), 'r')
+    T0 = vortex_T     = cb_file['vortex_T'].value
+    vortex_w          = cb_file['vortex_w'].value
+    rho0 = vortex_rho = cb_file['vortex_rho'].value
+    therm_radius      = cb_file['vortex_radius'].value
+    height            = cb_file['vortex_height'].value
[…]

### 2019-05-10 code/logic/post_processing.py
theory alignment with paper writeup

@@ -38,32 +38,13 @@ def linear_fit(x, a, b):
     """ A linear fit: y = a* x + b """
     return a*x + b
 
-def theory_C(B0, Gamma, f, chi, beta, grad_T_ad=-1):
+def theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=-1):
     """ The constant in stratified thermals theory """
-    return np.pi**(3./2) * Gamma**2 * grad_T_ad * beta / (f * B0 * chi**(1./2))
-
-#def theory_T(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
-#    """ The temperature profile (vs time) from stratified thermals theory """
-#    C0 = theory_C(B, Gamma, V0, beta, chi, grad_T_ad=grad_T_ad)
-#    tau = (B * t + I0)/Gamma
-#    tau0 = I0/Gamma
-#    Tpow = 1 - (m_ad/2)
-#    tau_int  = np.sqrt(tau )*(Gamma - (M0 - I0)/tau)
-#    tau_int0 = np.sqrt(tau0)*(Gamma - (M0 - I0)/tau0)
-#    return (2*Tpow*C0*(tau_int-tau_int0) + T0**(Tpow))**(1./Tpow)
-#
-#def theory_dT_dt(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
-#    """ The temperature derivative (vs time) from stratified thermals theory """
-#    C0 = theory_C(B, Gamma, V0, beta, chi, grad_T_ad=grad_T_ad)
-#    this_T = theory_T(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=grad_T_ad, m_ad=m_ad)
-#    tau = (B * t + I0)/Gamma
-#    dtau_dt = B/Gamma
-#    return C0*dtau_dt*this_T**(m_ad/2)*(Gamma/np.sqrt(tau) + (M0 - I0)/np.sqrt(tau**3))
+    return (beta * grad_T_ad * Gamma0 * np.pi**(3./2) / f) * np.sqrt(Gamma0/(B0 * chi))
 
 def theory_r(t, B0, Gamma0, chi, t_off, rho_f=None):
     """ The temperature profile (vs time) from stratified thermals theory """
-    tau = B0*(t+t_off)/Gamma0
[…]

### 2019-05-10 code/plotting/results_panels.py

@@ -32,17 +32,21 @@ sm.set_array([])
 
 for i, direc in enumerate(DIRS):
     f = h5py.File('{:s}/thermal_analysis/final_outputs.h5'.format(direc), 'r')
-    x, y     = f['times'].value, f['d_measured'].value
-    x_t, y_t = f['times'].value, f['d_theory'].value
+    ft = h5py.File('{:s}/thermal_analysis/z_cb_file.h5'.format(direc), 'r')
+    x, y     = ft['times'].value, f['d_measured'].value
+    x_t, y_t = ft['times'].value, f['d_theory'].value
+    f.close()
+    ft.close()
     color = sm.to_rgba(i+1)
     ax.plot(x[::2], y[::2], marker='o', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.5), markerfacecolor=(*color[:-1], 0.2))
     if CASES[i] in CASES_3D:
         f_3D = h5py.File('{:s}/thermal_analysis/final_outputs.h5'.format(dict_3D[CASES[i]]), 'r')
-        x_3D, y_3D     = f_3D['times'].value, f_3D['d_measured'].value
+        f_3Dt = h5py.File('{:s}/thermal_analysis/z_cb_file.h5'.format(dict_3D[CASES[i]]), 'r')
+        x_3D, y_3D     = f_3Dt['times'].value, f_3D['d_measured'].value
         f_3D.close()
+        f_3Dt.close()
         ax.plot(x_3D[::2], y_3D[::2], marker='+', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.7))
     ax.plot(x_t, y_t, c=color, lw=1)
-    f.close()
 
 ax.set_xlim(0, 50)
 ax.set_ylim(0, 20)

### 2019-05-10 code/thermal_analysis.py

@@ -164,9 +164,9 @@ def post_process(root_dir, plot=False, get_contour=True, analyze=True, out_dir='
     fit_t_off = fit[0]
     scale_t += fit_t_off    
 
-    bounds = ((0,       0.5*f0), 
-              (2*T0[0], 1.5*f0))
-    p0 = (T0[0], f0)
+    bounds = ((0,                        0.5*f0), 
+              (1 + (vortex_T.max()-1)/2, 1.5*f0))
+    p0 = (1, f0)
     this_T_theory      = lambda times, T, f:  theory_T(times, fit_B0, fit_Gamma0, f, fit_chi, fit_beta, 0, T, grad_T_ad=post.grad_T_ad, m_ad=post.m_ad)
     (fit_T0, fit_f), pcov = scop.curve_fit(this_T_theory, scale_t[this_fit], T0[this_fit], bounds=bounds, p0=p0, maxfev=1e4)
 

### 2019-05-10 tex/stratified_thermals.tex
huge changes to paper text

@@
 
+\begin{figure}[t!]
+    \includegraphics[width=\columnwidth]{overview_fig.png}
+    \caption{
+    \label{fig:overview} }
+\end{figure}
+
 In the absence of buoyantly-induced entrainment, \citet{brandenburg2016}
@@
 
-\subsection{Theoretical description of thermal evolution}
+\subsection{Evolution of momentum and impulse}
 The evolution of thermals as buoyant vortex rings has been well described in
@@
 evolution of thermals in stratified domains is required to understand 
-thermal entrainment in nature.
+thermal entrainment in nature. We will use a description of the momentum and
+impulse acting on the thermal to develop a theory of depth of thermals as a function
+of time, as well as the growth of their radii with depth.
 
-In this work, we focus on the non-dissipative, low Mach number regime, 
-in which the ideal anelastic equations are a decent approximation to the fully
-compressible equations. In this regime, buoyant forces can be expressed explicitly
-in terms of the entropy. In the the limit where diffusivities
-are sufficiently small and therea re no thermal sources or sinks, 
-the volume-integrated total entropy inside of a buoyant vortex ring is constant,
+In this work, we study an ideal gas and 
+focus on the ideal, low Mach number regime in an adiabatically
+stratified atmosphere. In this regime, a linearized equation of state describes
+the thermodynamics well, and the fully compressible Euler momentum equation
+takes the form \citep{brown&all2012},
 \begin{equation}
-B \equiv \int_{\mathcal{V}} \rho\, s\, dV = \text{const},
+\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} = 
+-\grad\varpi - \frac{S_1}{c_P}\bm{g},
+\label{eqn:euler_momentum}
 \end{equation}
-where $s = c_V \ln T - R \ln\rho$ is the specific entropy, with $c_V$ the
-specific heat at constant volume and $R$ the ideal gas constant.
+where $\bm{u}$ is the velocity, $\varpi = P_1 / \rho_0$ is the reduced pressure,
+$S = c_V\ln T - R\ln\rho$ is the specific entropy, and thermodynamics are broken
+down into background (subscript 0) and fluctuating (subscript 1) components.
+In this work we find it instructive to examine the full momentum, and so multiplying
+this equation by the density, we obtain,
+\begin{equation}
+\frac{\partial (\rho\bm{u})}{\partial t} + \bm{u}\cdot\grad(\rho\bm{u}) + \rho\bm{u}(\DivU)
+= -\rho\grad\varpi - \rho\frac{S_1}{c_P}\bm{g}.
+\label{eqn:rho_euler_momentum}
+\end{equation}
+Hereafter we will define the Lagrangian derivative,
+$D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$, and we acknowledge that 
+the Langrangian derivative commutes with a volume integral such that
+\begin{equation*}
+\frac{D}{Dt}\int_{\mathcal{V}} f dV = \int_{\mathcal{V}} \left[\frac{Df}{Dt} + f(\DivU)\right]dV.
+\end{equation*}
+Volume-integrating Eqn.~\ref{eqn:rho_euler_momentum}, we thus find
+\begin{equation}
+\frac{D\bm{M}}{Dt} = \int_{\mathcal{V}}\left(-\rho\grad\varpi - \rho\frac{S_1}{c_P}\bm{g}\right)dV,
+\label{eqn:int_momentum_eqn}
+\end{equation}
+where the volume-integrated momentum is defined $\bm{M} \equiv \int_{\mathcal{V}}\rho\bm{u} dV$.
+At this point we will make the assumption of a plane-parallel atmosphere in which the gravity
+is constant, $\bm{g} = -g\hat{z}$, and note that the z-component of the volume-integrated
+momentum evolves according to
+\begin{equation}
+\frac{D M_z}{Dt} = \int_{\mathcal{V}}\left( -\rho\frac{\partial \varpi}{\partial z} + \rho g \frac{S_1}{c_P} \right)dV.
+\label{eqn:Mz_definition}
+\end{equation}
+At this point, we find it useful to define the total buoyancy,
+\begin{equation}
+B \equiv \int_{\mathcal{V}} \rho\, S_1\, \frac{g}{c_P}\, dV,
+\label{eqn:tot_buoyancy}
+\end{equation}
+as in the absence of viscosity and detrainment, this is a conserved quantity during
+thermal evolution (REFERENCE FIGURE). Furthermore, in the Boussinesq limit, the
+work of \citet{tarshish&all2018} shows that pressure terms reduce the efficacy of
+the buoyancy in changing the momentum by effectively reducing the buoyant acceleration
+by some factor $\beta \sim 0.5$. As a result, we can approximate the growth of a thermal's
+momentum according to
+\begin{equation}
+\frac{D M_z}{Dt} \approx \beta B.
+\label{eqn:theory_momentum}
+\end{equation}
 
-In a stratified domain, the hydrodynamic impulse is defined
+After describing the growth of the thermal's integrated momentum with time, we turn
+our attention to th ehydrodynamic impulse, which in the stratified limit is defined
 \citep{shivamoggi2010},
@@
 \end{equation}
-where $\bm{x}$ is the position vector, $\bm{u}$ is vector velocity, $\rho$ is density,
-and $\mathcal{V}$ is the volume being integrated over. Impulse is equivalent to the time-integrated
+where $\bm{x}$ is the position vector. Impulse is equivalent to the time-integrated
 work acting on the fluid resulting in the current fluid motion. 
-Changes in the impulse can be expressed as
+Per \citet{shivamoggi2010}, changes in the impulse can be expressed as
+\begin{equation*}
+\frac{D\bm{I}}{D t} = \int_{\mathcal{V}}\frac{\partial(\rho\bm{u})}{\partial t}dV
+= B\hat{z} - \int_{\mathcal{V}}\left[\rho\grad\varpi + \Div{\rho\bm{u}\bm{u}}\right]dV ,
+\end{equation*}
+where, importantly, the \emph{eulerian} derivative of the momentum is inside of the volume
+integral here. Under the proper specification of boundary conditions, 
+the integral term is zero, and the vertical impulse of a thermal thus straightforwardly
+changes in time as
 \begin{equation}
-\frac{\partial\bm{I}}{\partial t} = \int_{\mathcal{V}}\frac{\partial}{\partial t}(\rho \bm{u})dV
-= B\hat{z} + S,
+\frac{D I_z}{D t} = B.
+\label{eqn:change_in_impulse}
 \end{equation}
-where $S$ is a combination of surface terms that disappears upon appropriate boundary conditions
-on $\mathcal{V}$ \citep{shivamoggi2010}. In this context where buoyancy is the only source of
-work and the buoyancy, $B$, is constant, the impulse can be straightforwardly integrated as
+We have thus retrieved the two findings on which our theory of thermal evolution
+will be built: \emph{both the impulse and momentum experience constant changes in
+time determined by the buoyant nature of the thermal}.
+
+\subsection{Parameterized description of thermal evolution}
+\begin{figure}[t!]
+    \includegraphics[width=\columnwidth]{constants.png}
+    \caption{
+    \label{fig:constants} }
+\end{figure}
+
+We first note, as in Fig.~\ref{fig:constants}a, that the buoyancy in our thermals
+is not necessarily perfectly constant in time, and that effects like detrainment result
+in a minor reduction of the buoyant signature of our thermals. We thus express the
+buoyancy in terms of two constants,
 \begin{equation}
-I_z = B t + I_0,
+B \approx \chi B_0,
 \end{equation}
-for some constant $I_0$. In the limiting regime where all of the buoyant fluid initially
-located in the thermal remains in the buoyant vortex ring, $I_0 \rightarrow 0$, but as
-some of the buoyant fluid is generally detrained in the initial spin-up to a vortex ring,
-it is important to keep the factor of $I_0$.
-Under the assumption that the thermal develops into a thin-core 
-propagating vortex ring whose vortex core is radius $r$ away from the axis of symmetry, 
-the impulse can be well approximated as $I_z \approx \pi \rho r^2 \Gamma$, where 
-$\Gamma = \iint (\grad\times\bm{u}) dr dz$ is the circulation in the vortex ring.
-Under this approximation, it becomes clear that so long as the vortex core is bounded
-by $\mathcal{V}$, the volume integrated over is rather arbitrary, as most of the circulation
-is located in the concentrated vortex ring.
-
-The vertical momentum of the thermal is less straightforward to find than the momentum. 
-Upon weighting the momentum equation (Eqn.~\ref{eqn:AN_momentum_full}) by the density, 
-Assuming an adiabatically stratified atmosphere in
-hydrostatic equilibrium, the change in volume integrated momentum over time is
+where $B_0$ is the initial buoyancy of the thermal, and $\chi$ is a constant of
+O(1) which represents this detrainment. We then integrating 
+Eqn.~\ref{eqn:change_in_impulse} in time,
+\begin{equation*}
+I_z = \chi B_0 t + I_0.
+\end{equation*}
+In the low-Mach number limit in which changes in density from the background are negligible,
+the impulse of a vortex ring can be approximated as
+\begin{equation*}
+I_z \approx \pi \rho r^2 \Gamma_0,
+\end{equation*}
+where $r$ is the radius of the thermal from its axis
+of symmetry to the maxima of its buoyant signature, and
+$\Gamma_0 = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the integrated circulation
+in a cross-section of the vortex ring. We take $\Gamma_0$ to be constant, which is
+a decent assumption in our experiments, see Fig.~\ref{fig:constants}b.
+Combining these two expressions, we retrieve our first result,
 \begin{equation}
-\frac{D \bm{P}}{Dt} = \frac{D}{Dt}\int_{\mathcal{V}}\rho\bm{u} dV
-= \int_{\mathcal{V}} \rho\frac{D\bm{u}}{Dt} dV
-\approx B\hat{z} - \int_{\mathcal{V}} \rho\grad\varpi dV.
-\end{equation}
-As noted by \citet{tarshish&all2018}, only infinitesimally small buoyant regions of
-fluid accelerate according exactly according to their buoyant nature. Any buoyant anomaly
-with a finite size disrupts its fluid environment, and this disruption results in
-pressure terms which reduce the efficacy of the buoyant fluid in driving motions. 
-In their work with Boussinesq thermals, they find that the true buoyant acceleration
-can be well approximated by scaling down the buoyant force by a factor of O($1/2$).
-Taking their work into account, we assume that the vertical momentum of the thermal
-follows
-\begin{equation}
-P_z = \beta B t + P_0,
-\end{equation}
-where in this work we set $\beta = 1/2$.
-
-Rearranging, we find our first result,
-\begin{equation}
-r = \sqrt{\frac{B t + I_0}{\pi\rho\Gamma}}.
+r = \sqrt{\frac{\chi B_0 t + I_0}{\pi\rho\Gamma_0}}.
 \label{eqn:r_theory}
 \end{equation}
-In the limit where $\rho \rightarrow \text{constant}$, as in the Boussinesq regime,
+In the Boussinesq limit where $\rho \rightarrow \text{constant}$, 
 we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime by
@@
 additional complexity of $r \propto \rho^{-1/2}$, such that downward-propogating 
-vortex rings (as studied here) will not entrain to the same degree as boussinesq thermals,
+vortex rings (as studied here) will entrain less than boussinesq thermals,
 and upward-propogating rings will entrain more. In the absence of buoyancy ($B = 0$),
@@
 
-We further assume that the volume-integrated momentum, $P_z \approx \rho V w_{th}$,
-where $w_{th}$ is the vertical velocity of the thermal as a whole, and the volume
-of the fluid region propogating with the thermal is a spheroid, $V = V_0 r^3$, for
-some constant $V_0$. Plugging Eqn.~\ref{eqn:r_theory} into this approximation, we
-find that
+The momentum can likewise be integrated like the impulse,
+\begin{equation*}
+M_z = \beta\chi B_0 t + M_0.
+\end{equation*}
+For the proper choice of vertical velocity, $w_{\text{th}}$, and volume, $\mathcal{V}$, the
+momentum can be expressed precisely as 
+\begin{equation*}
+M_z = \rho \mathcal{V} w_{\text{th}},
+\end{equation*}
+and the volume can be approximated as $\mathcal{V} = f r^3$, where $f$ is a parameter
+which we take to be constant. This assumption is perhaps not as perfect as the
+assumptions of constant $B_0$ or $\Gamma_0$ (see Fig.~\ref{fig:constants}c), but
+it is nevertheless not a bad assumption. Combining our approximate expressions,
+and inserting our theoretical description of $r$ (Eqn.~\ref{eqn:r_theory}),
+we retrieve
 \begin{equation}
-\rho^{-1/2}w = \left(\frac{(\pi\Gamma)^{3/2}}{V_0}\right)\frac{\beta B t + M_0}{(B t + I_0)^{3/2}}.
+\rho^{-1/2} w_{\text{th}} = \left(\frac{(\pi \Gamma)^{3/2}}{f}\right)\frac{\beta\chi B_0 t + M_0}{(\chi B_0 t + I_0)^{3/2}}.
 \end{equation}
-Substituting $w = dz/dt$ and $\tau \equiv (Bt + I_0)/\Gamma$, We retrieve
+Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and making the
+assumption that the vortex ring starts at a ``virtual origin'' (CITE) at $t = 0$ where
+it has no impulse or momentum ($I_0 = M_0 = 0$), an integrable expression for the evolution
+of thermal position over time can be retrieved,
 \begin{equation}
-\frac{dz}{\sqrt{\rho(z)}} 
-= \left(\frac{\pi^{3/2}\Gamma}{V_0 B}\right)
-\left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
-\label{eqn:general_theory}
+\frac{dz_{\text{th}}}{\rho(z_{\text{th}})^{1/2}} =
+\left(\frac{\beta(\pi\Gamma)^{3/2}}{f(\chi B_0)^{1/2}}\right)\frac{dt}{t^{1/2}}
+\label{eqn:dz_theory}
 \end{equation}
 If the atmospheric stratification in which the thermal is falling is known, this
-result can be straightforwardly integrated with $\rho(z)$ plugged in in order to
-find the position of the thermal versus time. While we will leave this result
-general for now, we will plug in our polytropic stratification at the end of
-section \ref{sec:experiment}, and show that the resulting expression does a
-good job of explaining the evolution of thermals in these atmospheres in
-section \ref{sec:results}.
-
-\subsection{Parameterization}
-
-\begin{deluxetable*}{c c c c c c}
-\tabletypesize{\footnotesize}
-\caption{Simulation output parameterization
-\label{table:simulation_info}
-}
-\tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$L_{thermal}/H_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
-\startdata																																															
-\multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	& 					&	256			& 512			& 49 	&	0.2	\\
-0.5 	& 					&	256			& 512			& 42.5 	&	0.2	\\
-1	 	& 					&	256			& 512			& 38 	&	0.2	\\
-2	 	& 					&	256			& 512			& 31.75	&	0.2	\\
-3	 	& 					&	512			& 1024			& 27.25	&	0.2	\\
-4	 	& 					&	1024		& 1024			& 25 	&	0.2	\\
-5	 	& 					&			& 			&  	&		\\
-6	 	& 					&			& 			&  	&		\\
-7	 	& 					&			& 			&  	&		\\
-\multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
-0.5 	& 					&	256			& 512			& 45 	&	0.2	\\
-1	 	& 					&	256			& 512			& 45 	&	0.2	\\
-2	 	& 					&	256			& 1024			& 45 	&	0.2	\\
-3	 	& 					&	256			& 2048			& 45 	&	0.2	\\
-\enddata																																															
-\tablecomments{
-}
-\end{deluxetable*}
+result can be integrated with $\rho(z_{\text{th}})$ plugged in in order to
+find the position of the thermal as a function of time. We leave this result
+general for now, and will integrate it using the polytropic stratification used in
+our simulations at the end of section \ref{sec:experiment}.
 
@@
 thermals in cylindrical coordinates. 
-We later verify that these simulations produce the same results a 3D fully compressible
-simulations in 3D cartesian domains (see sec. REF). 
+We later verify that select simulations produce the same results as 3D fully compressible
+simulations in cartesian domains (see sec. REF). 
 The LBR anelastic equations are \citep{lecoanet&all2014},
@@
 domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have
-no azimuthal velocity, $u_\phi$, we assume that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$. 
+no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$. 
 Under this approximation, the components of the stress tensor are
@@
 &\td{\sigma}_{rr} = 2\frac{\partial \td{u_r}}{\partial \td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,
+\td{\sigma}_{\phi\phi} = 2\frac{\td{u_r}}{\td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}}, \\
+&\td{\sigma}_{zz}       = 2\frac{\partial \td{w}}{\partial \td{z}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,\,
 \td{\sigma}_{rz}     = \td{\sigma}_{zr} = \frac{\partial \td{w}}{\partial \td{r}} + \frac{\partial \td{u_r}}{\partial \td{z}}, \\
-&\td{\sigma}_{\phi\phi} = 2\frac{\td{u_r}}{\td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,\,
-\td{\sigma}_{r\phi}  = \td{\sigma}_{\phi r}  = 0, \\
-&\td{\sigma}_{zz}       = 2\frac{\partial \td{w}}{\partial \td{z}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}}, \,\,\,\,\,\,
-\td{\sigma}_{\phi z} = \td{\sigma}_{z \phi}  = 0,\qquad
+&\td{\sigma}_{r\phi}  = \td{\sigma}_{\phi r}  
+ = \td{\sigma}_{\phi z} = \td{\sigma}_{z \phi}  = 0,\qquad
 \end{split}
 \end{equation}
-Furthermore, we assume that the dynamic viscosity, $\mu = \rho \nu$, and the
-thermal conductivity, $\kappa = \rho \chi$, are both uniform throughout the domain.
-The diffusivities
-$\nu$ and $\chi$ therefore scale inversely with the density.
+Furthermore, we assume that the dynamic viscosity, $\mu = \rho_0 \nu$, and the
+thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform throughout the domain and
+constant in time.
+The diffusivities $\nu$ and $\chi$ therefore scale inversely with the density.
 
@@
 \begin{split}
-\partial_t \bm{u} + \bm{u}\cdot\grad\bm{u} =& \\
+\partial_t \bm{u} + \bm{u}\cdot\grad&\bm{u} = \\
 - \grad \varpi + S_1\hat{z} &
@@
 \frac{1}{\text{Re}_{\text{ff}}}\left(\frac{1}{\text{Pr}_{\text{ff}}\rho_0c_P }\right.&[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\\
-&+ \left.\frac{-(\grad_{ad})}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right)
+&+ \left.\frac{-(\grad_{\text{ad}})}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right),
 \end{split}
 \end{gather}
-where in this nondimensionalization, the adiabatic temperature gradient is defined
-in the next subsection.
+where $\grad_{\text{ad}} \equiv \tilde{L}_{\text{th}} \frac{g}{c_P}$.
 
@@
 T_0 = 1 + (\grad_{\text{ad}})(z - L_z) \\
-\rho_0 = T_0^{m_{\text{ad}}},
+\rho_0 = T_0^{\,m_{\text{ad}}},
+\label{eqn:polytrope}
 \end{gather}
 where $m_{\text{ad}} = (\gamma-1)^{-1}$, and the adiabatic temperature 
-gradient in these nondimensional atmospheres is
-$$
-\grad_{\text{ad}} = -\frac{(e^{n_\rho/m_{ad}} - 1)}{L_z}\frac{m_{ad} + 1}{c_P},
-$$
-where $L_z$ is the atmospheric depth in units of thermal diameters.
+gradient in these nondimensional atmospheres is set with $g = m_{\text{ad}} + 1$
+and $\tilde{L}_{\text{th}} = (e^{n_\rho/m_{\text{ad}}} - 1)/L_z$, where
+$n_\rho$ is the number of density scale heights spanned by the atmosphere
+and $L_z = 20$ is the nondimensional depth of the atmosphere in units of
+thermal diameters.
 
@@
 \begin{equation}
-S_1 = - A(1 - \text{erf}\left(\frac{r' - r_{th}}{\delta}\right))/2,
+S_1 = - \frac{A}{2}\left[1 - \text{erf}\left(\frac{r' - r_{th}}{\delta}\right)\right],
 \label{eqn:thermal_IC}
@@
 where $A = 1$ for our scaled equations.
-Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3*r_{th}$,
+Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3r_{\text{th}}$,
 with the thermal radius set as $r_{th} = 0.5$, and a smoothing width, $\delta = 0.1$.
@@
 the $(T, \ln\rho)$ formulation of the equations in which we have previously studied fully compressible
-convection at low and high Mach number \citep{anders&brown2017, lecoanet&all2014},
+convection at low and high Mach number \citep{lecoanet&all2014, anders&brown2017},
 \begin{gather}
@@
 $\grad_{\text{ad}} = -1$ and the nondimensional timescale is the sound crossing time of that
-unit length.
+unit length at the top of the domain.
 
@@
 
-The depth of the atmosphere in these fully compressible domains is set by the number of density
-scale heights as $L_z = e^{n_\rho/m_{ad}} - 1$, and in order to compare results from these
-simulations to our nondimensionalized thermal simulations, we rescale all length scales in
-post-processing by $\ell = 20/L_z$, all timescales by $\tau = \sqrt{\ell \epsilon}$, and
-the entropy by $s = \epsilon^{-1}$.
+The depth of the atmosphere in these fully compressible domains is set to $L_z = e^{n_\rho/m_{ad}} - 1$.
+In order to compare results from these
+simulations to our Anelastic thermal simulations, we rescale all outputs in post-processing
+by a length scale factor of $\ell = 20/L_z$, a timescales factor of  $\tau = \sqrt{\ell \epsilon}$,
+and a specific entropy scaling of $s = \epsilon^{-1}$.
+
+\subsection{Numerics}
+We evolve our simulations forward in time using the 
+Dedalus\footnote{\url{http://dedalus-project.org/}} 
+pseudospectral framework \citep{burns&all2016} to time-evolve
+our equations. For our 2D simulations, we use 
+using an implicit-explicit (IMEX), third-order, four-stage
+Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997},
+and for our 3D simulations we use the second order
+semi-implicit backward differentiation formulation
+SBDF2 \citep{wang&ruuth2008}.
+
+Our 3D simulations are decomponsed on Fourier bases in the horizontal
+directions ($x, y \in [-L_r, L_r]$) and Chebyshev bases vertically
+($z \in [0, L_z]$) with impenetrable, stress free, fixed-temperature
+boundary conditions at the upper and lower boundaries 
+($T_1 = w = \partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
+Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and
+Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of
+$\partial_r S_1 = w = (\grad\times\bm{u})_{\phi} = 0$ at $r = L_r$.
 
 \subsection{Solution for thermal evolution in a Polytrope}
-Here we take the general theory described in Eqn.~\ref{eqn:general_theory} and apply it
-to the specific case of the polytropes we study here. 
-We note that, $\rho_0 = T_0^{m_{ad}}$ and
-$dT_0 = (\grad_{\text{ad}}) dz$, such that we must solve
+Now that the atmospheric density is specific, we can 
+find an explicit solution for Eqn.~\ref{eqn:dz_theory} to compare
+to the results of our simulations. As temperature and height are
+linearly related in our atmospheres, we find it instructive to use
+temperature as a integration parameter.
+We note that, $\rho = T^{m_{ad}}$ and
+$dT = (\grad_{\text{ad}}) dz_{th}$, such that we must solve
 \begin{equation}
-T_0^{-m_{ad}/2} dT_0 
-= \left(\frac{\pi^{3/2}\Gamma\grad_{\text{ad}}}{V_0 B}\right)
-\left(\beta\Gamma\tau^{-1/2} + [M_0 - \beta I_0]\tau^{-3/2}\right)d\tau.
-\label{eqn:general_theory}
+\int_{T_0}^{T_{\text{th}}} T^{-m_{ad}/2} dT 
+= \left(\frac{\beta(\pi\Gamma)^{3/2}\grad_{\text{ad}}}{f(\chi B)^{1/2}}\right)
+\int_{0}^{t + t_{\text{off}}} t^{-1/2} dt.
 \end{equation}
-Assuming that $m_{ad} < 2$ and through the use of simple power law integrals, we
-find that
+defining $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma^3/(\chi B)}$
+and $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and 
+ssuming that $m_{\text{ad}} < 2$ (which is valid for our case of $m_{\text{ad}} = 1.5$
+studied here) we find that
 \begin{equation}
-T_0(t) = \left(C[\xi(\tau) - \xi(\tau_0)] + T_0(t_0)^{1/\alpha}  \right)^{\alpha},
+T_{\text{th}} = \left(\frac{2C}{ \alpha } \sqrt{t + t_{\text{off}}} + T_0^{1/\alpha}  \right)^{\alpha}.
+\label{eqn:theory_T}
 \end{equation}
-with
+In the limit of large stratification, we thus find that $T_{\text{th}} \propto t^2$ for
+our case of $\alpha = 4$. The temperature can be straightforwardly converted to height
+by a rearrangement of Eqn.~\ref{eqn:polytrope},
 \begin{equation}
-\xi(\tau) = \beta\Gamma\tau^{1/2} - (M_0 - \beta I_0) \tau^{-1/2},
+z_{\text{th}} = (T_{\text{th}} - 1)/\grad_{\text{ad}} + L_z
 \end{equation}
-$C \equiv (2 \pi^{3/2} \Gamma (\grad_{\text{ad}}))/(\alpha V_0 B)$
+The thermal is thus described in terms of seven total parameters:
+\begin{enumerate}
+\item $T_0$ and $t_{\text{off}}$, the temperature of the thermal's virtual origin, and
+the time before the simulation's $t = 0$ at which the thermal was located at its virtual origin,
+\item $B_0$ and $\Gamma$, the measurable buoyancy and circulation of the vortex ring, and
+\item $f$, $\chi$, and $\beta$, fitting parameters which describe the nature of the vortex
+ring's evolution.
+\end{enumerate}
+The measured values of these parameters for the cases studied in this paper are presented
+in table \ref{table:parameters}.
 
-\subsection{Verification of 2D Anelastic approximation}
-blah blah blah comparison of 2D and 3D blah blah blah. z v t, r v z, w v z. Also side-by-side
-pictoral comparison with diff.
+\begin{deluxetable*}{c c c c c c c c c}
+\tabletypesize{\footnotesize}
+\caption{Simulation output parameterization
+\label{table:parameters}
+}
+\tablehead{																																															
+\colhead{$n_\rho$} & \colhead{$\grad_{\text{ad}}$} & \colhead{$T_0$} & \colhead{$t_{\text{off}}$} & \colhead{$B$} & \colhead{$\Gamma$} & \colhead{$f$} & \colhead{$\chi$} & \colhead{$\beta$}	}	
+\startdata																																															
+\multicolumn{9}{l}{\textbf{2D Anelastic Simulations}}\\
+0.1 	& $3.45 \times 10^{-3}$		& 0.985	& 0.166	& -0.547 & -2.17 & 7.01	& 1.04	& 0.499	\\
+0.5 	& $1.98 \times 10^{-2}$		& 0.918	& 0.704	& -0.568 & -2.12 & 7.04	& 0.976	& 0.490	\\
+1	 	& $4.74 \times 10^{-2}$		& 0.827	& 1.09 	& -0.601 & -2.05 & 7.07	& 0.915	& 0.480	\\
+2	 	& $0.140$             		& 0.677	& 1.26	& -0.712 & -1.89 & 7.08	& 0.841 & 0.456	\\
+3	 	& $0.319$             		& 0.619	& 1.01	& -0.946 & -1.73 & 7.08	& 0.808	& 0.436	\\
+4	 	& $0.667$             		& 0.698	& 0.622	& -1.47	 & -1.59 & 7.10	& 0.793	& 0.422	\\
+5	 	& $1.352$             		&			& 			&	 &	&	&	&	\\
+\multicolumn{9}{l}{\textbf{3D Fully Compressible Simulations}}\\    
+0.5 	& 	$1.98 \times 10^{-2}$	& 0.924	& 0.583	& -0.568 & -2.12 & 6.66	& 0.978	& 0.452	\\
+1	 	& 	$4.74 \times 10^{-2}$	& 0.832	& 1.26	& -0.601 & -2.05 & 6.88	& 0.902	& 0.454	\\
+2	 	& 	$0.140$             	& 0.666	& 1.53	& -0.711 & -1.89 & 7.08	& 0.822	& 0.450	\\
+\enddata																																															
+\tablecomments{ Values from fully compressible simulations have been rescaled
+in post-processing for direct comparison with 2D anelastic cases}
+\end{deluxetable*}
 
@@
 \label{sec:results}
-Picture of a big old grid of z v t, r v z, w v z.
 
-Pretty picture showing thermal evolution (comparing low and high stratification).
+\begin{figure}[t!]
+    \includegraphics[width=\columnwidth]{results_panels_d_v_t.png}
+    \caption{
+    \label{fig:results_d_v_t} }
+\end{figure}
 
-Verification of theory by simulations
+\begin{figure}[t!]
+    \includegraphics[width=\columnwidth]{results_panels_vs_depth.png}
+    \caption{
+    \label{fig:results_vs_depth} }
+\end{figure}
 
-Table of found parameters for the fits
+In Fig. \ref{fig:results_d_v_t}, we show the measured depth $d_{\text{th}} = L_z - z_{\text{th}}$
+of the thermal as a function of time for low and high stratification. 
+At very low stratification
+(e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths,
+and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$. As the stratification
+increases, 
+the thermal begins to transit the domain more quickly and approaches the limit of 
+$d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_T}. The
+theoretical fits for depth from the prediction of Eqn.~\ref{eqn:theory_T} are plotted over
+the measured data and show remarkable agreement.
 
-Two regimes: stalling and falling.
+In Fig.~\ref{fig:results_vs_depth}a, we plot the measured thermal radius vs. depth, with the
+theoretical predictions of Eqns.~\ref{eqn:r_theory} \& \ref{eqn:theory_T} plotted as lines
+over the data. In the low stratification limit, the radius of the thermal grows linearly with
+depth, $r \propto d$, aligning with the Boussinesq limit shown in \citet{lecoanet&jeevanjee2018} 
+This growth of the thermal is the result of entrainment of environmental fluid and
+results an an accompany decceleration like $w \propto d^{-1}$ in the Boussinesq limit, 
+as is shown in Fig.~\ref{fig:results_vs_depth}b.
+However, as stratification increases, the thermal entrains less environmental fluid and
+expands less, eventually even contracting with depth in the high-stratification limit. 
+This lessened entrainment is, unsurprisingly, accompanied by greater acceleration of the thermal.
+As in the case of depth vs. time, the overplotted theoretical predictions show excellent
+agreement with the measured data.
+
+These results suggest that there are two regimes of downflowing thermal behavior:
+\begin{enumerate}
+\item A low-stratification ``stalling'' regime, in which the thermal entrains environmental
+fluid and slows down, acting much like the Boussinesq regime, and
+\item A high-stratification ``falling'' regime, in which the thermal falls fast enough
+that compression due to the atmospheric stratification results in minimal entrainment and
+the thermal accelerates as it falls deeper into the atmosphere.
+\end{enumerate}
+However, we note that both of these regimes could result in interesting problems for the
+entropy rain hypothesis. If solar convection were comprised of thermals in the stalling regime,
+it is unlikely that such elements would ever make it to the base of the solar convection zone, 
+stalling much closer to the solar surface and depositing their entropy signature there -- possibly
+agreeing with the hypothesis of supergranulation as the largest buoyantly driven scale of
+solar motion. On the other hand, if solar convection is comprised of thermals in the falling
+regime, then it is possible that as these thermals compress and accelerate, diffusive effects
+and potentially viscous heating could become important. We discuss these possibilities further
+in section \ref{sec:discussion}
+
+\subsection{Verification of 2D Anelastic approximation}
+\begin{figure*}[t!]
+    \includegraphics[width=\textwidth]{diff_AN_FC.png}
+    \caption{
+    \label{fig:diff} }
+\end{figure*}
+
+In Fig.~\ref{fig:diff}, we display in more detail a comparison of our 2D Anelastic and
+3D Fully Compressible cases. In Fig.~\ref{fig:diff}a, depth vs time is shown, and the
+fractional difference between FC and AN cases is shown in Fig.~\ref{fig:diff}b.
+Differences between the two cases are $\leq 2$\% for all times, with greater error towards
+the end of the simulations as the FC simulations begin to interact with the impenetrable
+boundary at the bottom of their simulation domains.  In Fig.~\ref{fig:diff}c, radius
+vs. depth is shown, and the fractional difference between FC and AN cases is shown in
+Fig.~\ref{fig:diff}d. Aside from the very end of the simulation when the FC boundary conditions
+begin to matter, there is remarkable agreement between the two cases, with $< 1$\% differences
+between the two cases after early times in which the thermal is still developing into a vortex
+ring.
+
+This close agreement between low Mach number Fully Compressible simulations and Anelastic
+simulations parallels the agreement between the equation sets seen in \citet{lecoanet&all2014},
+and gives us confidence in our anelastic results at higher levels of stratification, where
+the 2D simulations are much more numerically feasible than the 3D fully compressible simulations.
 
@@
 \label{sec:discussion}
-Wild speculation about extensions to the solar regime. Do things on the sun shrink
-to the point where they viscously dissipate?
+In this work we have extended the theory of the evolution of buoyant thermals into the
+low-Mach number, stratified regime and have shown that that theory has remarkable agreement
+with the results of both Anelastic and Fully compressible simulations.
 
-Talk about what would happen if we were to study up-thermals.
-
-Extensions, and the fact that we trust these results will likely hold in the solar regime.
+We should have some discussion on these topics:
+\begin{enumerate}
+\item speculation about extensions to the solar regime. Do things on the sun shrink
+to the point where they viscously dissipate? Do they stall?
+\item Talk about what would happen if we were to study up-thermals.
+\item Extensions, and we trust that these results should hold in the regime of solar convection
+where things are turbulent.
+\end{enumerate}
 
@@
 time. To do so, we average the domain's entropy profile in radius and azimuth
-to create an average profile of entropy with height, and then we use
-scipy's brentq function on the derivative of that profile to find its maximum.
-
-Next, we find the best fit of the thermal's height vs. time according to our theory
-and derive that fit according to Eqn.~\ref{eqn:theory_velocity} to find the bulk
-vertical velocity of the thermal, $w_b$. We then calculate the streamfunction of
+to create an average profile of entropy with height, and then assume that the
+thermal's vortex core is located at the entropy minima of each of those profiles.
+We numerically differentiate these found values of height vs. time using
+(insert numerical differentiation technique here) and then calculate the streamfunction of
 the velocity field as in \citet{romps&all2015},
 \begin{equation}
-\frac{\partial \psi}{\partial r} = 2\pi \rho r (w - w_b),
+\frac{\partial \psi}{\partial r} = 2\pi \rho r (w - w_{\text{th}}),
 \end{equation}
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$L_{thermal}/H_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
+\colhead{$n_\rho$} & \colhead{$L_r$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
 \startdata																																															
-\multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	& 					&	256			& 512			& 49 	&	0.2	\\
-0.5 	& 					&	256			& 512			& 42.5 	&	0.2	\\
-1	 	& 					&	256			& 512			& 38 	&	0.2	\\
-2	 	& 					&	256			& 512			& 31.75	&	0.2	\\
-3	 	& 					&	512			& 1024			& 27.25	&	0.2	\\
-4	 	& 					&	1024		& 1024			& 25 	&	0.2	\\
-5	 	& 					&			& 			&  	&		\\
-6	 	& 					&			& 			&  	&		\\
-7	 	& 					&			& 			&  	&		\\
-\multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
-0.5 	& 					&	256			& 512			& 45 	&	0.2	\\
-1	 	& 					&	256			& 512			& 45 	&	0.2	\\
-2	 	& 					&	256			& 1024			& 45 	&	0.2	\\
-3	 	& 					&	256			& 2048			& 45 	&	0.2	\\
+\multicolumn{6}{l}{\textbf{2D Anelastic Simulations}}\\
+0.1 	& 	7				&	512			& 512			& 49 	&	0.1	\\
+0.5 	& 	7				&	512			& 512			& 42.5 	&	0.1	\\
+1	 	& 	5				&	512			& 512			& 38 	&	0.1	\\
+2	 	& 	5				&	512			& 512			& 31.75	&	0.1	\\
+3	 	& 	5				&	1024		& 1024			& 27.25	&	0.1	\\
+4	 	& 	5				&	1024		& 1024			& 25 	&	0.075	\\
+5	 	& 	2.4				&	1024		& 1024			& 22.8 	&	0.05	\\
+\multicolumn{6}{l}{\textbf{3D Fully Compressible Simulations}}\\
+0.5 	& 	5				&	256			& 512			& 42.5 		&	0.8	\\
+1	 	& 	4				&	256			& 512			& 38 	 	&	0.8	\\
+2	 	& 	3.5				&	256			& 1536			& 31.75 	&	0.8	\\
 \enddata																																															

### 2019-05-10 code/plotting/constants.py
updates to figures

@@ -1,0 +1,75 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+import h5py
+
+aspect = [0.35, 0.35, 0.25, 0.25, 0.25, 0.25]
+CASES = [0.1, 0.5, 1, 2, 3, 4]
+ROOT_DIR='../good_2D_runs/'
+DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
+
+height, width = 4, 3.25 
+
+gs = gridspec.GridSpec(1000, 1000)
+fig = plt.figure(figsize=(width, height))
+
+subplots = []
+p_width = 1000#int(np.floor(1000-2*pad)/3)
+pad = 30
+p_height = int(np.floor((850-2*pad)/3))
+for j in range(3):
+    subplots.append( ( (70+j*(p_height+pad), 0), p_height, p_width))
+
+fig = plt.figure(figsize=(width, height))
+axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
+cax = plt.subplot(gs.new_subplotspec(*((0, 0), 50, 1000)))
+
+norm = matplotlib.colors.Normalize(vmin=1, vmax=len(DIRS))
+sm   = plt.cm.ScalarMappable(cmap='viridis_r', norm=norm)
+sm.set_array([])
+
+for i, direc in enumerate(DIRS):
+    f = h5py.File('{:s}/thermal_analysis/post_analysis.h5'.format(direc), 'r')
+    t, Gam, S, V     = f['times'].value, f['int_circ'].value, f['int_rho_s1'].value, f['int_vol'].value
+    f.close()
+
+    f = h5py.File('{:s}/thermal_analysis/z_cb_file.h5'.format(direc), 'r')
+    r, d     = f['vortex_radius'].value, 20 - f['vortex_height'].value
+    f.close()
+
+    color = sm.to_rgba(i+1)
+    good = S < 0.5*S.min()
+    good[:10] = True
+    V0 = V/r**3
[…]

### 2019-05-10 code/plotting/diff_AN_FC.py

@@ -1,0 +1,102 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+import h5py
+
+aspect = [0.35, 0.25, 0.25]
+CASES = [0.5, 1, 2]
+TOFF  = [0.704, 1.09, 1.26]
+ROOT_DIR='../good_2D_runs/'
+DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
+
+CASES_3D = [0.5, 1, 2]
+AR_3D    = [0.5, 0.4, 0.35]
+TOFF_3D  = [0.583, 1.26, 1.53]
+THREED_DIR = '../good_3D_runs/'
+DIRS_3D=['{:s}FC_3D_thermal_Re6e2_Pr1_eps1.00e-4_nrho{}_aspect{}/'.format(THREED_DIR,nrho, ar) for nrho, ar in zip(CASES_3D, AR_3D)] 
+dict_3D = {}
+for i in range(len(CASES_3D)):
+    dict_3D[CASES_3D[i]] = DIRS_3D[i]
+
+
+height, width = 2.5, 6.5 
+
+gs = gridspec.GridSpec(1000, 1000)
+fig = plt.figure(figsize=(width, height))
+
+subplots = []
+pad = 100
+p_width = int(np.floor(1000-1*pad)/2)
+p_height = int(np.floor(1000)/3)
+subplots = [( (0, 0),                    p_height*2, p_width),
+            ( (0, pad+p_width),          p_height*2, p_width),
+            ( (p_height*2, 0),           p_height,   p_width),
+            ( (p_height*2, pad+p_width), p_height, p_width)
+            ]
+
+fig = plt.figure(figsize=(width, height))
+axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
+
+norm = matplotlib.colors.Normalize(vmin=1, vmax=6)
+sm   = plt.cm.ScalarMappable(cmap='viridis_r', norm=norm)
+sm.set_array([])
+
+for i, direc in enumerate(DIRS):
+    f = h5py.File('{:s}/thermal_analysis/z_cb_file.h5'.format(direc), 'r')
[…]

### 2019-05-10 code/plotting/overview_fig.py

@@ -1,0 +1,92 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+from scipy.interpolate import interp1d
+import h5py
+
+def theory_C(B, Gamma, V0, beta, chi, grad_T_ad=-1):
+    """ The constant in stratified thermals theory """
+    return np.pi**(3./2) * Gamma * grad_T_ad * chi / (V0 * B * beta**(1./2))
+
+def theory_T(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
+    """ The temperature profile (vs time) from stratified thermals theory """
+    C0 = theory_C(B, Gamma, V0, beta, chi, grad_T_ad=grad_T_ad)
+    tau = (B * t + I0)/Gamma
+    tau0 = I0/Gamma
+    Tpow = 1 - (m_ad/2)
+    tau_int  = np.sqrt(tau )*(Gamma - (M0 - I0)/tau)
+    tau_int0 = np.sqrt(tau0)*(Gamma - (M0 - I0)/tau0)
+    return (2*Tpow*C0*(tau_int-tau_int0) + T0**(Tpow))**(1./Tpow)
+
+def theory_dT_dt(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
+    """ The temperature derivative (vs time) from stratified thermals theory """
+    C0 = theory_C(B, Gamma, V0, beta, chi, grad_T_ad=grad_T_ad)
+    this_T = theory_T(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=grad_T_ad, m_ad=m_ad)
+    tau = (B * t + I0)/Gamma
+    dtau_dt = B/Gamma
+    return C0*dtau_dt*this_T**(m_ad/2)*(Gamma/np.sqrt(tau) + (M0 - I0)/np.sqrt(tau**3))
+
+
+def theory_r(t, B, I0, Gamma, beta, rho_f=None):
+    """ The temperature profile (vs time) from stratified thermals theory """
[…]

### 2019-05-10 code/plotting/results_panels.py

@@ -38,23 +38,23 @@ for i, direc in enumerate(DIRS):
     f.close()
     ft.close()
     color = sm.to_rgba(i+1)
-    ax.plot(x[::2], y[::2], marker='o', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.5), markerfacecolor=(*color[:-1], 0.2))
+    ax.plot(x[::3], y[::3], marker='o', lw=0, markersize=4, markeredgecolor=(*color[:-1], 0.8), markerfacecolor=(*color[:-1], 0.2))
     if CASES[i] in CASES_3D:
         f_3D = h5py.File('{:s}/thermal_analysis/final_outputs.h5'.format(dict_3D[CASES[i]]), 'r')
         f_3Dt = h5py.File('{:s}/thermal_analysis/z_cb_file.h5'.format(dict_3D[CASES[i]]), 'r')
         x_3D, y_3D     = f_3Dt['times'].value, f_3D['d_measured'].value
         f_3D.close()
         f_3Dt.close()
-        ax.plot(x_3D[::2], y_3D[::2], marker='+', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.7))
-    ax.plot(x_t, y_t, c=color, lw=1)
+        ax.plot(x_3D[::3], y_3D[::3], marker='+', lw=0, markersize=4, markeredgecolor=(*color[:-1], 0.9))
+    ax.plot(x_t, y_t, c='k', lw=0.5)
 
 ax.set_xlim(0, 50)
 ax.set_ylim(0, 20)
 ax.set_ylabel('depth')
 ax.set_xlabel(r'$t/t_b$')
 
-ax.plot([100, 101], [100, 101], lw=0, marker='o', c='k', markersize=3, markerfacecolor=(0,0,0,0.2), markeredgecolor=(0,0,0,0.5), label='2D AN')
-ax.plot([100, 101], [100, 101], lw=0, marker='+', c='k', markersize=3, label='3D FC')
+ax.plot([100, 101], [100, 101], lw=0, marker='o', c='k', markersize=4, markerfacecolor=(0,0,0,0.2), markeredgecolor=(0,0,0,0.8), label='2D AN')
+ax.plot([100, 101], [100, 101], lw=0, marker='+', c='k', markersize=4, label='3D FC')
 ax.legend(loc='lower right', frameon=False, fontsize=8, handletextpad=0)
 
 cb = plt.colorbar(sm, cax=cax, orientation='horizontal')
[…]

### 2019-05-10 tex/stratified_thermals.tex
close to a full rough raft

@@
 \received{\today}
-\revised{\today}
+\revised{??}
 \accepted{??}%\today}
@@
 \author[0000-0002-7635-9728]{Daniel Lecoanet}
-\affil{Stuff}
+\affil{Princeton Center for Theoretical Science, Princeton, NJ 08544, USA}
+\affil{Department of Astrophysical Sciences, Princeton, NJ 08544, USA}
 \author[0000-0001-8935-219X]{Benjamin P. Brown}
@@
 Recent observations of solar convection have revealed a convective conundrum.
-Power spectra have revealed weaker flows than anticipated at large length scales,
+Power spectra have revealed weaker flows than anticipated at large length scales
+\citep{hanasoge&all2012, greer&all2015},
 calling into question the existence of so-called ``giant cells'' driven by deep
@@
 surface. This discrepancy between theory and observations has called into question
-our fundamental understanding of convection, sparking fruitful investigations into
-the nature of convection in the Sun.
+our fundamental understanding of convection, sparking numerous targeted investigations
+the nature of convection in the Sun 
+\citep{featherstone&hindman2016, omara&all2016, cossette&rast2016, kapyla&all2017,
+hotta2017}.
 
@@
 evolution in the Boussinesq limit have been well studied in the laboratory
-for decades (see e.g., CITE), and more recently have been studied through
+for decades \citep[see e.g.][]{morton&all1956, scorer1957}, 
+and more recently have been studied through
 Direct Numerical Simulation (DNS) in the laminar and turbulent regime
@@
     \includegraphics[width=\columnwidth]{overview_fig.png}
-    \caption{
+    \caption{We have plotted the evolution of the filling factor, or radius
+	squared, of a buoyant vortex ring with depth (the $n_\rho = 3$ case examined
+	later in this work). Overplotted in a thin
+	solid line is the prediction for filling factor growth in the Boussinesq
+	case, and in the thin dashed line is plotted the prediction for pure horizontal
+	compression, as in \citet{brandenburg2016}.
     \label{fig:overview} }
@@
 suggests that the filling factor, $f$, of vortex rings should decrease like
-$f \propto \rho^{\alpha}$ for horizontal compression and $f \propto \rho^{\alpha}$ for 
+$f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for 
 spherical compression. On the other hand, the filling factor of Boussinesq
-thermals \emph{increases} like $f \propto d$, where $d$ is the depth propagated.
+thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth propagated.
+These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true
+propagation of a thermal in an appreciably stratified environment.
+
 In this work, we extend the study of \citet{lecoanet&jeevanjee2018} to study
-the propagation of low-Mach number, cold thermals in stratified domains, and how
-buoyant entrainment affects the scaling of their filling factor with depth. If
-buoyant entrainment is a dominant effect, it is possible that these buoyant vortex rings
+the propagation of low-Mach number, cold thermals in stratified domains. We are
+specifically interested in how
+buoyant entrainment affects the scaling of the thermal radius, or filling factor, with depth. If
+buoyant entrainment is a dominant effect, it is possible that entropy rain
 would simply grow too large and stall before reaching the bottom of the solar convection zone.
@@
 
-We lay out our work as follows. In section \ref{sec:theory}, we develop a theoretical description
-of thermals in a stratified domain. In section \ref{sec:experiment}, we describe and verify
+In section \ref{sec:theory}, we develop a theoretical description
+of thermals in a stratified domain. In section \ref{sec:experiment}, we describe 
 the experiments conducted in this work. In section \ref{sec:results}, we compare the results
@@
     \includegraphics[width=\columnwidth]{evolution_colormeshes.png}
-    \caption{
+    \caption{The evolution of $\rho S_1 r^3$, or the total entropy weighted by
+	the cube of the thermal radius, is shown for two thermals. On the left is
+	a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights and 
+	on the right is a thermal in a strongly stratified domain with $n_\rho = 3$.
+	While both start with precisely the same initial condition, the case with low stratification
+	expands with depth like the boussinesq case, whereas the strongly stratified thermal
+	compresses with depth.
     \label{fig:evolution_colormeshes} }
@@
     \includegraphics[width=\columnwidth]{constants.png}
-    \caption{
+    \caption{Plotted are time traces for three quantities which we assume to be constant
+	in our thermal theory. In (a) and (b), the circulation and buoyancy, divided by their
+	maxima, are plotted vs. depth. We see that with increasing stratification, there is marginally
+	more detrainment of both of these quantities, but to first order they are constant over the
+	evolution of the thermal. In (c) the constant $f = V/r^3$ is plotted; after significant
+	noise during the development of the vortex ring, this quantity remains relatively constant, 
+	and increasingly approaches a constant with depth.
     \label{fig:constants} }
@@
     \includegraphics[width=\columnwidth]{results_panels_d_v_t.png}
-    \caption{
+    \caption{Shown are the measured depths of thermals as a function of time for all 2D
+	Anelastic and 3D Fully compressible simulations conducted in this work. Overplotted
+	is the theoretical prediction for depth as a function of time.
     \label{fig:results_d_v_t} }
@@
     \includegraphics[width=\columnwidth]{results_panels_vs_depth.png}
-    \caption{
+    \caption{Shown are (a) the measured radii of thermals as a function of depth and
+	(b) the measured thermal velocities as a function of depth for all 2D
+	Anelastic and 3D Fully compressible simulations conducted in this work. Overplotted
+	are the predictions from theory.
     \label{fig:results_vs_depth} }
@@
     \includegraphics[width=\textwidth]{diff_AN_FC.png}
-    \caption{
+    \caption{Measured values of (a) depth vs. time and (c) radius vs. depth are plotted
+	for both the 2D anelastic and 3D fully compressible simulations. The fractional
+	difference between anelastic and fully compressible results are respectively shown
+	in (b) and (d).
     \label{fig:diff} }

### 2019-05-10 code/plotting/constants.py
figure improvements

@@ -55,7 +55,7 @@ for i in (0, 1, 2):
 axs[2].set_ylabel('w')
 axs[0].set_ylabel(r'$\Gamma/\Gamma_{\mathrm{max}}$')
 axs[1].set_ylabel(r'$B/B_{\mathrm{max}}$')
-axs[2].set_ylabel(r'$V_0/V_{0,f}$')
+axs[2].set_ylabel(r'$f/f_{\mathrm{final}}$')
 axs[2].set_xlabel('depth')
 
 

### 2019-05-10 code/plotting/diff_AN_FC.py

@@ -55,18 +55,18 @@ for i, direc in enumerate(DIRS):
     color = sm.to_rgba(i+2)
     for j, x2, y2, x3, y3 in zip(range(2), (t, d), (d, r), (t3, d3), (d3, r3)):
         l = np.min((len(y2), len(y3)))
-        axs[j].plot(x2[:l:3], y2[:l:3], marker='o', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.5), markerfacecolor=(*color[:-1], 0.2))
-        axs[j].plot(x3[:l:3], y3[:l:3], marker='x', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.5), markerfacecolor=(*color[:-1], 0.2))
+        axs[j].plot(x2[:l], y2[:l], marker='o', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.8), markerfacecolor=(*color[:-1], 0.2), markeredgewidth=0.5)
+        axs[j].plot(x3[:l], y3[:l], marker='x', lw=0, markersize=2, markeredgecolor='k', markerfacecolor='k', markeredgewidth=0.5)#markeredgecolor=(*color[:-1], 0.9), markerfacecolor=(*color[:-1], 0.2))
 
         axs[j+2].axhline(1e-2, c='k', lw=0.25)
         axs[j+2].axhline(10**(-1.5), c='k', lw=0.25)
         axs[j+2].axhline(10**(-2.5), c='k', lw=0.25)
 
-        diff = (1 - y2/y3)[:l:3]
+        diff = (1 - y2/y3)[:l]
         pos  = diff > 0
         neg  = diff < 0
-        axs[j+2].plot(x2[:l:3][pos], diff[pos], markerfacecolor=color, markeredgecolor=color, marker='o', lw=0, markersize=3)
-        axs[j+2].plot(x2[:l:3][neg], -diff[neg], markerfacecolor=(*color[:-1], 0), markeredgecolor=color, marker='o', lw=0, markersize=3)
+        axs[j+2].plot(x2[:l][pos], diff[pos], markerfacecolor=color, markeredgecolor=color, marker='o', lw=0, markersize=2, markeredgewidth=0.35)
+        axs[j+2].plot(x2[:l][neg], -diff[neg], markerfacecolor=(*color[:-1], 0), markeredgecolor=color, marker='o', lw=0, markersize=2, markeredgewidth=0.35)
[…]

### 2019-05-10 tex/stratified_thermals.tex
a little wordsmithing

@@
 
+In the following sections, we will use a description of the impulse and momentum of these
+thermals, as determined by their buoyant nature, to describe the evolution of their depth
+and radii with time.
+
 \begin{figure}[t!]
@@
 The evolution of thermals as buoyant vortex rings has been well described in
-the unstratified, Boussinesq limit for decades (as early as e.g., CITE, and
-see \citet{lecoanet&jeevanjee2018} for other sources). Buoyant motions 
-in the atmospheres of stars and planets are generally large enough to feel the
-atmospheric stratification, and therefore a more thorough treatment of the
-evolution of thermals in stratified domains is required to understand 
-thermal entrainment in nature. We will use a description of the momentum and
-impulse acting on the thermal to develop a theory of depth of thermals as a function
-of time, as well as the growth of their radii with depth.
+the unstratified, Boussinesq limit for decades 
+\citep[see e.g.][for a description and sources]{lecoanet&jeevanjee2018}.
+Here we lay out a description of the momentum and
+impulse of the thermal which will later be used 
+to describe thermal properties like radii and depth vs. time.
 

### 2019-05-20 tex/stratified_thermals.tex
puts sentences onto their own lines for easier future change tracking

@@
 Recent observations of solar convection have revealed a convective conundrum.
-Power spectra have revealed weaker flows than anticipated at large length scales
-\citep{hanasoge&all2012, greer&all2015},
-calling into question the existence of so-called ``giant cells'' driven by deep
-convection which would manifest as powerful, large-scale motions at the solar
-surface. This discrepancy between theory and observations has called into question
-our fundamental understanding of convection, sparking numerous targeted investigations
-the nature of convection in the Sun 
-\citep{featherstone&hindman2016, omara&all2016, cossette&rast2016, kapyla&all2017,
-hotta2017}.
+Power spectra have revealed weaker flows than anticipated at large length scales \citep{hanasoge&all2012, greer&all2015}, calling into question the existence of so-called ``giant cells'' driven by deep convection which would manifest as powerful, large-scale motions at the solar surface.
+This discrepancy between theory and observations has called into question our fundamental understanding of convection, sparking numerous targeted investigations the nature of convection in the Sun  \citep{featherstone&hindman2016, omara&all2016, cossette&rast2016, kapyla&all2017, hotta2017}.
 
-\cite{spruit1997} hypothesized that convective motions may be driven entirely by
-cool downflows at the surface of the Sun, and \citet{brandenburg2016} expanded
-upon this ``entropy rain'' hypothesis. Brandenburg's work includes a careful
-expansion of mixing length theory to incorporate flux contributions from nonlocal
-convective motions, and handles this theory in a horizontally-averaged sense.
-He includes some discussion of possible flow morphologies which could be manifestations
-of this entropy rain, and even includes some brief simulations of propogating
-Hill vortices. However, these simulations and discussions did not include 
-include a fundamental piece of entropy rain: it is buoyant, and has an entropy
-deviation from the background atmosphere.
+\cite{spruit1997} hypothesized that convective motions may be driven entirely by cool downflows at the surface of the Sun, and \citet{brandenburg2016} expanded upon this ``entropy rain'' hypothesis. 
+Brandenburg's work includes a careful expansion of mixing length theory to incorporate flux contributions from nonlocal convective motions, and handles this theory in a horizontally-averaged sense.
+He includes some discussion of possible flow morphologies which could be manifestations of this entropy rain, and even includes some brief simulations of propogating Hill vortices. 
+However, these simulations and discussions did not include include a fundamental piece of entropy rain: it is buoyant, and has an entropy deviation from the background atmosphere.
 
-If entropy rain does evolve into downward propagating buoyant vortex rings, it is
-important to understand how buoyancy effects the filling factor of these basic
-convective elements. In the context of Earth's atmosphere, so-called ``thermals''
-are thought to be the nucleus of cloud formation. Thermals are buoyant areas
-of fluid which evolve into propagating buoyant vortex rings, and their
-evolution in the Boussinesq limit have been well studied in the laboratory
-for decades \citep[see e.g.][]{morton&all1956, scorer1957}, 
-and more recently have been studied through
-Direct Numerical Simulation (DNS) in the laminar and turbulent regime
-\citep{lecoanet&jeevanjee2018}. One fundamental result of these studies of
-thermals is that they experience a large degree of entrainment: their size expands
-with height and their propagation velocity slows despite their buoyant nature.
-However, we do not know of a study in which the propagation of these thermals,
-and thus the nature of their entrainment, is affected by a 
-significant atmospheric stratification.
+If entropy rain does evolve into downward propagating buoyant vortex rings, it is important to understand how buoyancy effects the filling factor of these basic convective elements. 
+In the context of Earth's atmosphere, so-called ``thermals'' are thought to be the nucleus of cloud formation. 
+Thermals are buoyant areas of fluid which evolve into propagating buoyant vortex rings, and their evolution in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently have been studied through Direct Numerical Simulation (DNS) in the laminar and turbulent regime \citep{lecoanet&jeevanjee2018}.
+One fundamental result of these studies of thermals is that they experience a large degree of entrainment: their size expands with height and their propagation velocity slows despite their buoyant nature.
+However, we do not know of a study in which the propagation of these thermals, and thus the nature of their entrainment, is affected by a significant atmospheric stratification.
 
@@
     \includegraphics[width=\columnwidth]{overview_fig.png}
-    \caption{We have plotted the evolution of the filling factor, or radius
-	squared, of a buoyant vortex ring with depth (the $n_\rho = 3$ case examined
-	later in this work). Overplotted in a thin
-	solid line is the prediction for filling factor growth in the Boussinesq
-	case, and in the thin dashed line is plotted the prediction for pure horizontal
-	compression, as in \citet{brandenburg2016}.
+    \caption{
+	We have plotted the evolution of the filling factor, or radius squared, of a buoyant vortex ring with depth (the $n_\rho = 3$ case examined later in this work). 
+	Overplotted in a thin solid line is the prediction for filling factor growth in the Boussinesq case, and in the thin dashed line is plotted the prediction for pure horizontal compression, as in \citet{brandenburg2016}.
     \label{fig:overview} }
@@
 
-In the absence of buoyantly-induced entrainment, \citet{brandenburg2016}
-suggests that the filling factor, $f$, of vortex rings should decrease like
-$f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for 
-spherical compression. On the other hand, the filling factor of Boussinesq
-thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth propagated.
-These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true
-propagation of a thermal in an appreciably stratified environment.
+In the absence of buoyantly-induced entrainment, \citet{brandenburg2016} suggests that the filling factor, $f$, of vortex rings should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression.
+On the other hand, the filling factor of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth propagated.
+These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true propagation of a thermal in an appreciably stratified environment.
 
-In this work, we extend the study of \citet{lecoanet&jeevanjee2018} to study
-the propagation of low-Mach number, cold thermals in stratified domains. We are
-specifically interested in how
-buoyant entrainment affects the scaling of the thermal radius, or filling factor, with depth. If
-buoyant entrainment is a dominant effect, it is possible that entropy rain
-would simply grow too large and stall before reaching the bottom of the solar convection zone.
-On the other hand, if the compression effects suggested by \citet{brandenburg2016} are the
-dominant effect, then it is possible that these thermals could propagate to the bottom of the solar
-convection zone, or potentially shrink to a sufficiently small size where thermal dissipation is
-significant.
+In this work, we extend the study of \citet{lecoanet&jeevanjee2018} to study the propagation of low-Mach number, cold thermals in stratified domains. 
+We are specifically interested in how buoyant entrainment affects the scaling of the thermal radius, or filling factor, with depth. 
+If buoyant entrainment is a dominant effect, it is possible that entropy rain would simply grow too large and stall before reaching the bottom of the solar convection zone.
+On the other hand, if the compression effects suggested by \citet{brandenburg2016} are the dominant effect, then it is possible that these thermals could propagate to the bottom of the solar
+convection zone, or potentially shrink to a sufficiently small size where thermal dissipation is significant.
 
-In section \ref{sec:theory}, we develop a theoretical description
-of thermals in a stratified domain. In section \ref{sec:experiment}, we describe 
-the experiments conducted in this work. In section \ref{sec:results}, we compare the results
-of our experiments to the theory developed in section \ref{sec:theory}. Finally, in section
-\ref{sec:discussion}, we discuss what our results imply for the entropy rain hypothesis.
+In section \ref{sec:theory}, we develop a theoretical description of thermals in a stratified domain. 
+In section \ref{sec:experiment}, we describe the experiments conducted in this work. 
+In section \ref{sec:results}, we compare the results of our experiments to the theory developed in section \ref{sec:theory}. 
+Finally, in section \ref{sec:discussion}, we discuss what our results imply for the entropy rain hypothesis.
 
@@
 \subsection{Phenomenological description of thermal evolution}
-We show pictorally the evolution of a cold thermal from rest in 
-Fig.~\ref{fig:evolution_colormeshes}. In Fig.~\ref{fig:evolution_colormeshes}a,
-the evolution of a thermal in a weakly stratified domain with
-$n_\rho = 0.5$ density scale heights is shown. In Fig.~\ref{fig:evolution_colormeshes}b,
-the evolution of a thermal in an appreciably stratified domain with
-$n_\rho = 3$ density scale heights is shown. While the initial conditions are
-identical in both domains (spherical specific entropy perturbations of the
-same magnitude whose diameters are 5\% of the domain depth), and while in both cases
-the thermal quickly evolves into a propagating buoyant vortex ring, we find that the
-$n_\rho = 0.5$ case entrains and grows with depth, similarly to the Boussinesq regime.
-On the other hand, the $n_\rho = 3$ case has a radius which remains approximately constant
-over time, and it reaches the bottom of the domain in many fewer nondimensional freefall
-time units.
+We show pictorally the evolution of a cold thermal from rest in Fig.~\ref{fig:evolution_colormeshes}. 
+In Fig.~\ref{fig:evolution_colormeshes}a, the evolution of a thermal in a weakly stratified domain with $n_\rho = 0.5$ density scale heights is shown. 
+In Fig.~\ref{fig:evolution_colormeshes}b, the evolution of a thermal in an appreciably stratified domain with $n_\rho = 3$ density scale heights is shown. 
+While the initial conditions are identical in both domains (spherical specific entropy perturbations of the same magnitude whose diameters are 5\% of the domain depth), and while in both cases the thermal quickly evolves into a propagating buoyant vortex ring, we find that the $n_\rho = 0.5$ case entrains and grows with depth, similarly to the Boussinesq regime.
+On the other hand, the $n_\rho = 3$ case has a radius which remains approximately constant over time, and it reaches the bottom of the domain in many fewer nondimensional freefall time units.
 
-In the following sections, we will use a description of the impulse and momentum of these
-thermals, as determined by their buoyant nature, to describe the evolution of their depth
-and radii with time.
+In the following sections, we will use a description of the impulse and momentum of these thermals, as determined by their buoyant nature, to describe the evolution of their depth and radii with time.
 
@@
     \includegraphics[width=\columnwidth]{evolution_colormeshes.png}
-    \caption{The evolution of $\rho S_1 r^3$, or the total entropy weighted by
-	the cube of the thermal radius, is shown for two thermals. On the left is
-	a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights and 
-	on the right is a thermal in a strongly stratified domain with $n_\rho = 3$.
-	While both start with precisely the same initial condition, the case with low stratification
-	expands with depth like the boussinesq case, whereas the strongly stratified thermal
-	compresses with depth.
+    \caption{
+	The evolution of $\rho S_1 r^3$, or the total entropy weighted by the cube of the thermal radius, is shown for two thermals. 
+	On the left is a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights and on the right is a thermal in a strongly stratified domain with $n_\rho = 3$.
+	While both start with precisely the same initial condition, the case with low stratification expands with depth like the boussinesq case, whereas the strongly stratified thermal compresses with depth.
     \label{fig:evolution_colormeshes} }
@@
 \subsection{Evolution of momentum and impulse}
-The evolution of thermals as buoyant vortex rings has been well described in
-the unstratified, Boussinesq limit for decades 
-\citep[see e.g.][for a description and sources]{lecoanet&jeevanjee2018}.
-Here we lay out a description of the momentum and
-impulse of the thermal which will later be used 
-to describe thermal properties like radii and depth vs. time.
+The evolution of thermals as buoyant vortex rings has been well described in the unstratified, Boussinesq limit for decades \citep[see e.g.][for a description and sources]{lecoanet&jeevanjee2018}.
+Here we lay out a description of the momentum and impulse of the thermal which will later be used to describe thermal properties like radii and depth vs. time.
 
-In this work, we study an ideal gas and 
-focus on the ideal, low Mach number regime in an adiabatically
-stratified atmosphere. In this regime, a linearized equation of state describes
-the thermodynamics well, and the fully compressible Euler momentum equation
-takes the form \citep{brown&all2012},
+In this work, we study an ideal gas and focus on the ideal, low Mach number regime in an adiabatically stratified atmosphere. 
+In this regime, a linearized equation of state describes the thermodynamics well, and the fully compressible Euler momentum equation takes the form \citep{brown&all2012},
 \begin{equation}
@@
 \end{equation}
-where $\bm{u}$ is the velocity, $\varpi = P_1 / \rho_0$ is the reduced pressure,
-$S = c_V\ln T - R\ln\rho$ is the specific entropy, and thermodynamics are broken
-down into background (subscript 0) and fluctuating (subscript 1) components.
-In this work we find it instructive to examine the full momentum, and so multiplying
-this equation by the density, we obtain,
+where $\bm{u}$ is the velocity, $\varpi = P_1 / \rho_0$ is the reduced pressure, $S = c_V\ln T - R\ln\rho$ is the specific entropy, and thermodynamics are broken down into background (subscript 0) and fluctuating (subscript 1) components.
+In this work we find it instructive to examine the full momentum, and so multiplying this equation by the density, we obtain,
 \begin{equation}
@@
 \end{equation}
-Hereafter we will define the Lagrangian derivative,
-$D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$, and we acknowledge that 
-the Langrangian derivative commutes with a volume integral such that
+Hereafter we will define the Lagrangian derivative, $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$, and we acknowledge that the Langrangian derivative commutes with a volume integral such that
 \begin{equation*}
@@
 where the volume-integrated momentum is defined $\bm{M} \equiv \int_{\mathcal{V}}\rho\bm{u} dV$.
-At this point we will make the assumption of a plane-parallel atmosphere in which the gravity
-is constant, $\bm{g} = -g\hat{z}$, and note that the z-component of the volume-integrated
-momentum evolves according to
+At this point we will make the assumption of a plane-parallel atmosphere in which the gravity is constant, $\bm{g} = -g\hat{z}$, and note that the z-component of the volume-integrated momentum evolves according to
 \begin{equation}
@@
 \end{equation}
-as in the absence of viscosity and detrainment, this is a conserved quantity during
-thermal evolution (REFERENCE FIGURE). Furthermore, in the Boussinesq limit, the
-work of \citet{tarshish&all2018} shows that pressure terms reduce the efficacy of
-the buoyancy in changing the momentum by effectively reducing the buoyant acceleration
-by some factor $\beta \sim 0.5$. As a result, we can approximate the growth of a thermal's
-momentum according to
+as in the absence of viscosity and detrainment, this is a conserved quantity during thermal evolution (REFERENCE FIGURE). 
+Furthermore, in the Boussinesq limit, the work of \citet{tarshish&all2018} shows that pressure terms reduce the efficacy of the buoyancy in changing the momentum by effectively reducing the buoyant acceleration by some factor $\beta \sim 0.5$.
+As a result, we can approximate the growth of a thermal's momentum according to
 \begin{equation}
@@
 
-After describing the growth of the thermal's integrated momentum with time, we turn
-our attention to th ehydrodynamic impulse, which in the stratified limit is defined
+After describing the growth of the thermal's integrated momentum with time, we turn our attention to the hydrodynamic impulse, which in the stratified limit is defined
 \citep{shivamoggi2010},
@@
 \end{equation}
-where $\bm{x}$ is the position vector. Impulse is equivalent to the time-integrated
-work acting on the fluid resulting in the current fluid motion. 
+where $\bm{x}$ is the position vector. 
+Impulse is equivalent to the time-integrated work acting on the fluid resulting in the current fluid motion. 
 Per \citet{shivamoggi2010}, changes in the impulse can be expressed as
@@
 \end{equation*}
-where, importantly, the \emph{eulerian} derivative of the momentum is inside of the volume
-integral here. Under the proper specification of boundary conditions, 
-the integral term is zero, and the vertical impulse of a thermal thus straightforwardly
-changes in time as
+where, importantly, the \emph{eulerian} derivative of the momentum is inside of the volume integral here. 
+Under the proper specification of boundary conditions, the integral term is zero, and the vertical impulse of a thermal thus straightforwardly changes in time as
 \begin{equation}
@@
 \end{equation}
-We have thus retrieved the two findings on which our theory of thermal evolution
-will be built: \emph{both the impulse and momentum experience constant changes in
-time determined by the buoyant nature of the thermal}.
+We have thus retrieved the two findings on which our theory of thermal evolution will be built: \emph{both the impulse and momentum experience constant changes in time determined by the buoyant nature of the thermal}.
 
@@
     \includegraphics[width=\columnwidth]{constants.png}
-    \caption{Plotted are time traces for three quantities which we assume to be constant
-	in our thermal theory. In (a) and (b), the circulation and buoyancy, divided by their
-	maxima, are plotted vs. depth. We see that with increasing stratification, there is marginally
-	more detrainment of both of these quantities, but to first order they are constant over the
-	evolution of the thermal. In (c) the constant $f = V/r^3$ is plotted; after significant
-	noise during the development of the vortex ring, this quantity remains relatively constant, 
-	and increasingly approaches a constant with depth.
+    \caption{
+	Plotted are time traces for three quantities which we assume to be constant in our thermal theory. 
+	In (a) and (b), the circulation and buoyancy, divided by their maxima, are plotted vs. depth. 
+	We see that with increasing stratification, there is marginally more detrainment of both of these quantities, but to first order they are constant over the	evolution of the thermal. 
+	In (c) the constant $f = V/r^3$ is plotted; after significant noise during the development of the vortex ring, this quantity remains relatively constant, and increasingly approaches a constant with depth.
     \label{fig:constants} }
@@
 
-We first note, as in Fig.~\ref{fig:constants}a, that the buoyancy in our thermals
-is not necessarily perfectly constant in time, and that effects like detrainment result
-in a minor reduction of the buoyant signature of our thermals. We thus express the
-buoyancy in terms of two constants,
+We first note, as in Fig.~\ref{fig:constants}a, that the buoyancy in our thermals is not necessarily perfectly constant in time, and that effects like detrainment result in a minor reduction of the buoyant signature of our thermals.
+We thus express the buoyancy in terms of two constants,
 \begin{equation}
@@
 \end{equation}
-where $B_0$ is the initial buoyancy of the thermal, and $\chi$ is a constant of
-O(1) which represents this detrainment. We then integrating 
-Eqn.~\ref{eqn:change_in_impulse} in time,
+where $B_0$ is the initial buoyancy of the thermal, and $\chi$ is a constant of O(1) which represents this detrainment. 
+We then integrating Eqn.~\ref{eqn:change_in_impulse} in time,
 \begin{equation*}
@@
 \end{equation*}
-In the low-Mach number limit in which changes in density from the background are negligible,
-the impulse of a vortex ring can be approximated as
+In the low-Mach number limit in which changes in density from the background are negligible, the impulse of a vortex ring can be approximated as
 \begin{equation*}
@@
 \end{equation*}
-where $r$ is the radius of the thermal from its axis
-of symmetry to the maxima of its buoyant signature, and
-$\Gamma_0 = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the integrated circulation
-in a cross-section of the vortex ring. We take $\Gamma_0$ to be constant, which is
-a decent assumption in our experiments, see Fig.~\ref{fig:constants}b.
+where $r$ is the radius of the thermal from its axis of symmetry to the maxima of its buoyant signature, and $\Gamma_0 = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the integrated circulation in a cross-section of the vortex ring.
+We take $\Gamma_0$ to be constant, which is a decent assumption in our experiments, see Fig.~\ref{fig:constants}b.
 Combining these two expressions, we retrieve our first result,
@@
 \end{equation}
-In the Boussinesq limit where $\rho \rightarrow \text{constant}$, 
-we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime by
-\citet{lecoanet&jeevanjee2018}. We find that the inclusion of stratification adds the
-additional complexity of $r \propto \rho^{-1/2}$, such that downward-propogating 
-vortex rings (as studied here) will entrain less than boussinesq thermals,
-and upward-propogating rings will entrain more. In the absence of buoyancy ($B = 0$),
-this result aligns with the prediction for purely horizontal compression noted by
-\citet{brandenburg2016} of $r^2 \propto \rho^{-1}$.
+In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime by \citet{lecoanet&jeevanjee2018}. 
+We find that the inclusion of stratification adds the additional complexity of $r \propto \rho^{-1/2}$, such that downward-propogating vortex rings (as studied here) will entrain less than boussinesq thermals, and upward-propogating rings will entrain more.
+In the absence of buoyancy ($B = 0$), this result aligns with the prediction for purely horizontal compression noted by \citet{brandenburg2016} of $r^2 \propto \rho^{-1}$.
 
@@
 \end{equation*}
-For the proper choice of vertical velocity, $w_{\text{th}}$, and volume, $\mathcal{V}$, the
-momentum can be expressed precisely as 
+For the proper choice of vertical velocity, $w_{\text{th}}$, and volume, $\mathcal{V}$, the momentum can be expressed precisely as 
 \begin{equation*}
@@
 \end{equation*}
-and the volume can be approximated as $\mathcal{V} = f r^3$, where $f$ is a parameter
-which we take to be constant. This assumption is perhaps not as perfect as the
-assumptions of constant $B_0$ or $\Gamma_0$ (see Fig.~\ref{fig:constants}c), but
-it is nevertheless not a bad assumption. Combining our approximate expressions,
-and inserting our theoretical description of $r$ (Eqn.~\ref{eqn:r_theory}),
-we retrieve
+and the volume can be approximated as $\mathcal{V} = f r^3$, where $f$ is a parameter which we take to be constant. 
+This assumption is perhaps not as perfect as the assumptions of constant $B_0$ or $\Gamma_0$ (see Fig.~\ref{fig:constants}c), but it is nevertheless not a bad assumption. 
+Combining our approximate expressions, and inserting our theoretical description of $r$ (Eqn.~\ref{eqn:r_theory}), we retrieve
 \begin{equation}
@@
 \end{equation}
-Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and making the
-assumption that the vortex ring starts at a ``virtual origin'' (CITE) at $t = 0$ where
-it has no impulse or momentum ($I_0 = M_0 = 0$), an integrable expression for the evolution
-of thermal position over time can be retrieved,
+Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and making the assumption that the vortex ring starts at a ``virtual origin'' (CITE) at $t = 0$ where it has no impulse or momentum ($I_0 = M_0 = 0$), an integrable expression for the evolution of thermal position over time can be retrieved,
 \begin{equation}
@@
 \end{equation}
-If the atmospheric stratification in which the thermal is falling is known, this
-result can be integrated with $\rho(z_{\text{th}})$ plugged in in order to
-find the position of the thermal as a function of time. We leave this result
-general for now, and will integrate it using the polytropic stratification used in
-our simulations at the end of section \ref{sec:experiment}.
+If the atmospheric stratification in which the thermal is falling is known, this result can be integrated with $\rho(z_{\text{th}})$ plugged in in order to find the position of the thermal as a function of time.
+We leave this result general for now, and will integrate it using the polytropic stratification used in our simulations at the end of section \ref{sec:experiment}.
 
@@
 \subsection{Anelastic Simulations}
-In this work, we primarily study the evolution of 2D, azimuthally symmetric, anelastic
-thermals in cylindrical coordinates. 
-We later verify that select simulations produce the same results as 3D fully compressible
-simulations in cartesian domains (see sec. REF). 
+In this work, we primarily study the evolution of 2D, azimuthally symmetric, anelastic thermals in cylindrical coordinates. 
+We later verify that select simulations produce the same results as 3D fully compressible simulations in cartesian domains (see sec. REF). 
 The LBR anelastic equations are \citep{lecoanet&all2014},
@@
 \end{gather}
-where terms with tildes are dimensional, and where
-$D/D\td{t} = \partial/\partial \td{t} + \td{\bm{u}}\cdot\td{\grad}$. In our azimuthally symetric
-domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have
-no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$. 
+where terms with tildes are dimensional, and where $D/D\td{t} = \partial/\partial \td{t} + \td{\bm{u}}\cdot\td{\grad}$. 
+In our azimuthally symetric domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$.
 Under this approximation, the components of the stress tensor are
@@
 \end{equation}
-Furthermore, we assume that the dynamic viscosity, $\mu = \rho_0 \nu$, and the
-thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform throughout the domain and
-constant in time.
+Furthermore, we assume that the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform throughout the domain and constant in time.
 The diffusivities $\nu$ and $\chi$ therefore scale inversely with the density.
 
-We nondimensionalize these equations in the same manner as in
-\citet{lecoanet&jeevanjee2018} such that
-the length scale is the diameter of the initial thermal perturbation
-and the velocity scale is the freefall velocity. The timescale is thus
-the freefall crossing time of this unit length. Mathematically,
+We nondimensionalize these equations in the same manner as in \citet{lecoanet&jeevanjee2018} such that the length scale is the diameter of the initial thermal perturbation and the velocity scale is the freefall velocity.
+The timescale is thus the freefall crossing time of this unit length. 
+Mathematically,
 \begin{equation}
@@
 \end{equation}
-As the diffusivities scale with depth, Re$_{\text{ff}}$ is specified at the
-thermal's initial depth.
+As the diffusivities scale with depth, Re$_{\text{ff}}$ is specified at the thermal's initial depth.
 The resulting equations are,
@@
 \subsection{Atmosphere \& Initial conditions}
-We study an ideal gas whose equation of state is $P = \rho T$ and whose stratification
-is a perfectly adiabatic polytrope,
+We study an ideal gas whose equation of state is $P = \rho T$ and whose stratification is a perfectly adiabatic polytrope,
 \begin{gather}
@@
 \end{gather}
-where $m_{\text{ad}} = (\gamma-1)^{-1}$, and the adiabatic temperature 
-gradient in these nondimensional atmospheres is set with $g = m_{\text{ad}} + 1$
-and $\tilde{L}_{\text{th}} = (e^{n_\rho/m_{\text{ad}}} - 1)/L_z$, where
-$n_\rho$ is the number of density scale heights spanned by the atmosphere
-and $L_z = 20$ is the nondimensional depth of the atmosphere in units of
-thermal diameters.
+where $m_{\text{ad}} = (\gamma-1)^{-1}$, and the adiabatic temperature gradient in these nondimensional atmospheres is set with $g = m_{\text{ad}} + 1$ and $\tilde{L}_{\text{th}} = (e^{n_\rho/m_{\text{ad}}} - 1)/L_z$, where $n_\rho$ is the number of density scale heights spanned by the atmosphere and $L_z = 20$ is the nondimensional depth of the atmosphere in units of thermal diameters.
 
@@
 where $A = 1$ for our scaled equations.
-Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3r_{\text{th}}$,
-with the thermal radius set as $r_{th} = 0.5$, and a smoothing width, $\delta = 0.1$.
+Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3r_{\text{th}}$, with the thermal radius set as $r_{th} = 0.5$, and a smoothing width, $\delta = 0.1$.
 
 \subsection{Fully Compressible Simulations}
-In order to verify the validity of our 2D Anelastic simulations, we evolve select
-thermals according to the 3D Navier Stokes equations in a cartesian domain. We use
-the $(T, \ln\rho)$ formulation of the equations in which we have previously studied fully compressible
-convection at low and high Mach number \citep{lecoanet&all2014, anders&brown2017},
+In order to verify the validity of our 2D Anelastic simulations, we evolve select thermals according to the 3D Navier Stokes equations in a cartesian domain. 
+We use the $(T, \ln\rho)$ formulation of the equations in which we have previously studied fully compressible convection at low and high Mach number \citep{lecoanet&all2014, anders&brown2017},
 \begin{gather}
@@
 \end{equation}
-These equations are nondimensionalized on the temperature gradient length scale such that
-$\grad_{\text{ad}} = -1$ and the nondimensional timescale is the sound crossing time of that
-unit length at the top of the domain.
+These equations are nondimensionalized on the temperature gradient length scale such that $\grad_{\text{ad}} = -1$ and the nondimensional timescale is the sound crossing time of that unit length at the top of the domain.
 
-In setting the specific entropy, $S = c_V \ln T - R^{-1}\ln\rho$, to an equivalent condition
-to that specified in  Eqn.~\ref{eqn:thermal_IC}, we note that it is essential that the
-initial perturbation be in pressure equilibrium. The set of initial conditions that achieves this
-is
+In setting the specific entropy, $S = c_V \ln T - R^{-1}\ln\rho$, to an equivalent condition to that specified in  Eqn.~\ref{eqn:thermal_IC}, we note that it is essential that the initial perturbation be in pressure equilibrium.
+The set of initial conditions that achieves this is
 \begin{equation}
@@
 \end{equation}
-We specify the magnitude of the initial entropy perturbations as 
-$A = \epsilon = 10^{-4}$, such that the mach number of the resultant thermal is O($10^{-2}$) or less.
+We specify the magnitude of the initial entropy perturbations as $A = \epsilon = 10^{-4}$, such that the mach number of the resultant thermal is O($10^{-2}$) or less.
 
 The depth of the atmosphere in these fully compressible domains is set to $L_z = e^{n_\rho/m_{ad}} - 1$.
-In order to compare results from these
-simulations to our Anelastic thermal simulations, we rescale all outputs in post-processing
-by a length scale factor of $\ell = 20/L_z$, a timescales factor of  $\tau = \sqrt{\ell \epsilon}$,
-and a specific entropy scaling of $s = \epsilon^{-1}$.
+In order to compare results from these simulations to our Anelastic thermal simulations, we rescale all outputs in post-processing by a length scale factor of $\ell = 20/L_z$, a timescales factor of  $\tau = \sqrt{\ell \epsilon}$, and a specific entropy scaling of $s = \epsilon^{-1}$.
 
 \subsection{Numerics}
-We evolve our simulations forward in time using the 
-Dedalus\footnote{\url{http://dedalus-project.org/}} 
-pseudospectral framework \citep{burns&all2016} to time-evolve
-our equations. For our 2D simulations, we use 
-using an implicit-explicit (IMEX), third-order, four-stage
-Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997},
-and for our 3D simulations we use the second order
-semi-implicit backward differentiation formulation
-SBDF2 \citep{wang&ruuth2008}.
+We evolve our simulations forward in time using the  Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \citep{burns&all2016} to time-evolve our equations. 
+For our 2D simulations, we use using an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997}, and for our 3D simulations we use the second order semi-implicit backward differentiation formulation SBDF2 \citep{wang&ruuth2008}.
 
-Our 3D simulations are decomponsed on Fourier bases in the horizontal
-directions ($x, y \in [-L_r, L_r]$) and Chebyshev bases vertically
-($z \in [0, L_z]$) with impenetrable, stress free, fixed-temperature
-boundary conditions at the upper and lower boundaries 
-($T_1 = w = \partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
-Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and
-Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of
-$\partial_r S_1 = w = (\grad\times\bm{u})_{\phi} = 0$ at $r = L_r$.
+Our 3D simulations are decomponsed on Fourier bases in the horizontal directions ($x, y \in [-L_r, L_r]$) and Chebyshev bases vertically ($z \in [0, L_z]$) with impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries ($T_1 = w = \partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
+Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of $\partial_r S_1 = w = (\grad\times\bm{u})_{\phi} = 0$ at $r = L_r$.
 
 \subsection{Solution for thermal evolution in a Polytrope}
-Now that the atmospheric density is specific, we can 
-find an explicit solution for Eqn.~\ref{eqn:dz_theory} to compare
-to the results of our simulations. As temperature and height are
-linearly related in our atmospheres, we find it instructive to use
-temperature as a integration parameter.
-We note that, $\rho = T^{m_{ad}}$ and
-$dT = (\grad_{\text{ad}}) dz_{th}$, such that we must solve
+Now that the atmospheric density is specific, we can find an explicit solution for Eqn.~\ref{eqn:dz_theory} to compare to the results of our simulations. 
+As temperature and height are linearly related in our atmospheres, we find it instructive to use temperature as a integration parameter.
+We note that, $\rho = T^{m_{ad}}$ and $dT = (\grad_{\text{ad}}) dz_{th}$, such that we must solve 
 \begin{equation}
@@
 \end{equation}
-defining $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma^3/(\chi B)}$
-and $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and 
-ssuming that $m_{\text{ad}} < 2$ (which is valid for our case of $m_{\text{ad}} = 1.5$
-studied here) we find that
+defining $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma^3/(\chi B)}$ and $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and assuming that $m_{\text{ad}} < 2$ (which is valid for our case of $m_{\text{ad}} = 1.5$ studied here) we find that
 \begin{equation}
@@
 \end{equation}
-In the limit of large stratification, we thus find that $T_{\text{th}} \propto t^2$ for
-our case of $\alpha = 4$. The temperature can be straightforwardly converted to height
-by a rearrangement of Eqn.~\ref{eqn:polytrope},
+In the limit of large stratification, we thus find that $T_{\text{th}} \propto t^2$ for our case of $\alpha = 4$. 
+The temperature can be straightforwardly converted to height by a rearrangement of Eqn.~\ref{eqn:polytrope},
 \begin{equation}
@@
 \begin{enumerate}
-\item $T_0$ and $t_{\text{off}}$, the temperature of the thermal's virtual origin, and
-the time before the simulation's $t = 0$ at which the thermal was located at its virtual origin,
+\item $T_0$ and $t_{\text{off}}$, the temperature of the thermal's virtual origin, and the time before the simulation's $t = 0$ at which the thermal was located at its virtual origin,
 \item $B_0$ and $\Gamma$, the measurable buoyancy and circulation of the vortex ring, and
-\item $f$, $\chi$, and $\beta$, fitting parameters which describe the nature of the vortex
-ring's evolution.
+\item $f$, $\chi$, and $\beta$, fitting parameters which describe the nature of the vortex ring's evolution.
 \end{enumerate}
-The measured values of these parameters for the cases studied in this paper are presented
-in table \ref{table:parameters}.
+The measured values of these parameters for the cases studied in this paper are presented in table \ref{table:parameters}.
 
@@
 \enddata																																															
-\tablecomments{ Values from fully compressible simulations have been rescaled
-in post-processing for direct comparison with 2D anelastic cases}
+\tablecomments{ Values from fully compressible simulations have been rescaled in post-processing for direct comparison with 2D anelastic cases}
 \end{deluxetable*}
@@
     \includegraphics[width=\columnwidth]{results_panels_d_v_t.png}
-    \caption{Shown are the measured depths of thermals as a function of time for all 2D
-	Anelastic and 3D Fully compressible simulations conducted in this work. Overplotted
-	is the theoretical prediction for depth as a function of time.
+    \caption{
+	Shown are the measured depths of thermals as a function of time for all 2D Anelastic and 3D Fully compressible simulations conducted in this work. 
+	Overplotted is the theoretical prediction for depth as a function of time.
     \label{fig:results_d_v_t} }
@@
     \includegraphics[width=\columnwidth]{results_panels_vs_depth.png}
-    \caption{Shown are (a) the measured radii of thermals as a function of depth and
-	(b) the measured thermal velocities as a function of depth for all 2D
-	Anelastic and 3D Fully compressible simulations conducted in this work. Overplotted
-	are the predictions from theory.
+    \caption{
+	Shown are (a) the measured radii of thermals as a function of depth and (b) the measured thermal velocities as a function of depth for all 2D Anelastic and 3D Fully compressible simulations conducted in this work.
+	Overplotted are the predictions from theory.
     \label{fig:results_vs_depth} }
@@
 
-In Fig. \ref{fig:results_d_v_t}, we show the measured depth $d_{\text{th}} = L_z - z_{\text{th}}$
-of the thermal as a function of time for low and high stratification. 
-At very low stratification
-(e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths,
-and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$. As the stratification
-increases, 
-the thermal begins to transit the domain more quickly and approaches the limit of 
-$d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_T}. The
-theoretical fits for depth from the prediction of Eqn.~\ref{eqn:theory_T} are plotted over
-the measured data and show remarkable agreement.
+In Fig. \ref{fig:results_d_v_t}, we show the measured depth $d_{\text{th}} = L_z - z_{\text{th}}$ of the thermal as a function of time for low and high stratification. 
+At very low stratification (e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
+As the stratification increases, the thermal begins to transit the domain more quickly and approaches the limit of $d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_T}. 
+The theoretical fits for depth from the prediction of Eqn.~\ref{eqn:theory_T} are plotted over the measured data and show remarkable agreement.
 
-In Fig.~\ref{fig:results_vs_depth}a, we plot the measured thermal radius vs. depth, with the
-theoretical predictions of Eqns.~\ref{eqn:r_theory} \& \ref{eqn:theory_T} plotted as lines
-over the data. In the low stratification limit, the radius of the thermal grows linearly with
-depth, $r \propto d$, aligning with the Boussinesq limit shown in \citet{lecoanet&jeevanjee2018} 
-This growth of the thermal is the result of entrainment of environmental fluid and
-results an an accompany decceleration like $w \propto d^{-1}$ in the Boussinesq limit, 
-as is shown in Fig.~\ref{fig:results_vs_depth}b.
-However, as stratification increases, the thermal entrains less environmental fluid and
-expands less, eventually even contracting with depth in the high-stratification limit. 
+In Fig.~\ref{fig:results_vs_depth}a, we plot the measured thermal radius vs. depth, with the theoretical predictions of Eqns.~\ref{eqn:r_theory} \& \ref{eqn:theory_T} plotted as lines over the data. 
+In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, aligning with the Boussinesq limit shown in \citet{lecoanet&jeevanjee2018}.
+This growth of the thermal is the result of entrainment of environmental fluid and results an an accompany decceleration like $w \propto d^{-1}$ in the Boussinesq limit, as is shown in Fig.~\ref{fig:results_vs_depth}b.
+However, as stratification increases, the thermal entrains less environmental fluid and expands less, eventually even contracting with depth in the high-stratification limit. 
 This lessened entrainment is, unsurprisingly, accompanied by greater acceleration of the thermal.
-As in the case of depth vs. time, the overplotted theoretical predictions show excellent
-agreement with the measured data.
+As in the case of depth vs. time, the overplotted theoretical predictions show excellent agreement with the measured data.
 
@@
 \begin{enumerate}
-\item A low-stratification ``stalling'' regime, in which the thermal entrains environmental
-fluid and slows down, acting much like the Boussinesq regime, and
-\item A high-stratification ``falling'' regime, in which the thermal falls fast enough
-that compression due to the atmospheric stratification results in minimal entrainment and
-the thermal accelerates as it falls deeper into the atmosphere.
+\item A low-stratification ``stalling'' regime, in which the thermal entrains environmental fluid and slows down, acting much like the Boussinesq regime, and
+\item A high-stratification ``falling'' regime, in which the thermal falls fast enough that compression due to the atmospheric stratification results in minimal entrainment and the thermal accelerates as it falls deeper into the atmosphere.
 \end{enumerate}
-However, we note that both of these regimes could result in interesting problems for the
-entropy rain hypothesis. If solar convection were comprised of thermals in the stalling regime,
-it is unlikely that such elements would ever make it to the base of the solar convection zone, 
-stalling much closer to the solar surface and depositing their entropy signature there -- possibly
-agreeing with the hypothesis of supergranulation as the largest buoyantly driven scale of
-solar motion. On the other hand, if solar convection is comprised of thermals in the falling
-regime, then it is possible that as these thermals compress and accelerate, diffusive effects
-and potentially viscous heating could become important. We discuss these possibilities further
-in section \ref{sec:discussion}
+However, we note that both of these regimes could result in interesting problems for the entropy rain hypothesis. 
+If solar convection were comprised of thermals in the stalling regime, it is unlikely that such elements would ever make it to the base of the solar convection zone, stalling much closer to the solar surface and depositing their entropy signature there -- possibly agreeing with the hypothesis of supergranulation as the largest buoyantly driven scale of solar motion.
+On the other hand, if solar convection is comprised of thermals in the falling regime, then it is possible that as these thermals compress and accelerate, diffusive effects and potentially viscous heating could become important.
+We discuss these possibilities further in section \ref{sec:discussion}
 
@@
     \includegraphics[width=\textwidth]{diff_AN_FC.png}
-    \caption{Measured values of (a) depth vs. time and (c) radius vs. depth are plotted
-	for both the 2D anelastic and 3D fully compressible simulations. The fractional
-	difference between anelastic and fully compressible results are respectively shown
-	in (b) and (d).
+    \caption{
+	Measured values of (a) depth vs. time and (c) radius vs. depth are plotted for both the 2D anelastic and 3D fully compressible simulations. 
+	The fractional difference between anelastic and fully compressible results are respectively shown in (b) and (d).
     \label{fig:diff} }
@@
 
-In Fig.~\ref{fig:diff}, we display in more detail a comparison of our 2D Anelastic and
-3D Fully Compressible cases. In Fig.~\ref{fig:diff}a, depth vs time is shown, and the
-fractional difference between FC and AN cases is shown in Fig.~\ref{fig:diff}b.
-Differences between the two cases are $\leq 2$\% for all times, with greater error towards
-the end of the simulations as the FC simulations begin to interact with the impenetrable
-boundary at the bottom of their simulation domains.  In Fig.~\ref{fig:diff}c, radius
-vs. depth is shown, and the fractional difference between FC and AN cases is shown in
-Fig.~\ref{fig:diff}d. Aside from the very end of the simulation when the FC boundary conditions
-begin to matter, there is remarkable agreement between the two cases, with $< 1$\% differences
-between the two cases after early times in which the thermal is still developing into a vortex
-ring.
+In Fig.~\ref{fig:diff}, we display in more detail a comparison of our 2D Anelastic and 3D Fully Compressible cases. 
+In Fig.~\ref{fig:diff}a, depth vs time is shown, and the fractional difference between FC and AN cases is shown in Fig.~\ref{fig:diff}b.
+Differences between the two cases are $\leq 2$\% for all times, with greater error towards the end of the simulations as the FC simulations begin to interact with the impenetrable boundary at the bottom of their simulation domains.
+In Fig.~\ref{fig:diff}c, radius vs. depth is shown, and the fractional difference between FC and AN cases is shown in Fig.~\ref{fig:diff}d. 
+Aside from the very end of the simulation when the FC boundary conditions begin to matter, there is remarkable agreement between the two cases, with $< 1$\% differences between the two cases after early times in which the thermal is still developing into a vortex ring.
 
-This close agreement between low Mach number Fully Compressible simulations and Anelastic
-simulations parallels the agreement between the equation sets seen in \citet{lecoanet&all2014},
-and gives us confidence in our anelastic results at higher levels of stratification, where
-the 2D simulations are much more numerically feasible than the 3D fully compressible simulations.
+This close agreement between low Mach number Fully Compressible simulations and Anelastic simulations parallels the agreement between the equation sets seen in \citet{lecoanet&all2014}, and gives us confidence in our anelastic results at higher levels of stratification, where the 2D simulations are much more numerically feasible than the 3D fully compressible simulations.
 
@@
 \label{sec:discussion}
-In this work we have extended the theory of the evolution of buoyant thermals into the
-low-Mach number, stratified regime and have shown that that theory has remarkable agreement
-with the results of both Anelastic and Fully compressible simulations.
+In this work we have extended the theory of the evolution of buoyant thermals into the low-Mach number, stratified regime and have shown that that theory has remarkable agreement with the results of both Anelastic and Fully compressible simulations.
 
@@
 \begin{enumerate}
-\item speculation about extensions to the solar regime. Do things on the sun shrink
-to the point where they viscously dissipate? Do they stall?
+\item speculation about extensions to the solar regime. Do things on the sun shrink to the point where they viscously dissipate? Do they stall?
 \item Talk about what would happen if we were to study up-thermals.
-\item Extensions, and we trust that these results should hold in the regime of solar convection
-where things are turbulent.
+\item Extensions, and we trust that these results should hold in the regime of solar convection where things are turbulent.
 \end{enumerate}
@@
 \begin{acknowledgements}
-This work was supported by NASA Headquarters under the NASA Earth and Space
-Science Fellowship Program -- Grant 80NSSC18K1199.
+This work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
 This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
-Computations were conducted 
-with support by the NASA High End Computing (HEC) Program through the NASA 
-Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
-with allocation GID s1647.
+Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA  Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s1647.
 \end{acknowledgements}
@@
 \label{appendix:tracking}
-We use a thermal tracking algorithm very similar to the one used in 
-\citet{lecoanet&jeevanjee2018} and inspired by the work of 
-\citet{romps&all2015}.
+We use a thermal tracking algorithm very similar to the one used in  \citet{lecoanet&jeevanjee2018} and inspired by the work of \citet{romps&all2015}.
 
-We begin by measuring the thermal's height versus
-time. To do so, we average the domain's entropy profile in radius and azimuth
-to create an average profile of entropy with height, and then assume that the
-thermal's vortex core is located at the entropy minima of each of those profiles.
-We numerically differentiate these found values of height vs. time using
-(insert numerical differentiation technique here) and then calculate the streamfunction of
-the velocity field as in \citet{romps&all2015},
+We begin by measuring the thermal's height versus time. 
+To do so, we average the domain's entropy profile in radius and azimuth to create an average profile of entropy with height, and then assume that the thermal's vortex core is located at the entropy minima of each of those profiles.
+We numerically differentiate these found values of height vs.
+time using (insert numerical differentiation technique here) and then calculate the streamfunction of the velocity field as in \citet{romps&all2015},
 \begin{equation}
@@
 \end{equation}
-with the boundary condition that $\psi = 0$ at $r = 0$. The contour defined by $\psi = 0$
-from this solution is taken to be the outline of the thermal, and the volume of the thermal
-is taken to be the volume radially inward from that contour.
+with the boundary condition that $\psi = 0$ at $r = 0$.
+The contour defined by $\psi = 0$ from this solution is taken to be the outline of the thermal, and the volume of the thermal is taken to be the volume radially inward from that contour.
 

### 2019-05-22 tex/stratified_thermals.tex
Many paper improvements: * Added an abstract * Rearranged numerous out-of-place sections * Got rid of unnecessary nondimensionalization language; nondimensionalized FC equations. * Cleaned up tables a bit.

@@
 \begin{abstract}
+``Entropy rain,'' or the downard propagation of low entropy fluid, has been hypothesized as a dominant mechanism for carrying the solar luminosity in light of the recent Solar Convective Conundrum.
+One possible dynamical manifestation of these ``raindrops'' is that of dense, propagating vortex rings, referred to as ``thermals'' in the context of Earth's atmosphere.
+In this work, we develop an analytical theory describing entrainment in dense, antibuoyant vortex rings in stratified atmospheres.
+We show that this theory describes the evolution of laminar, axisymmetric thermals in highly stratified atmospheres and into the boussinesq limit.
+We discuss what the evolution of these thermals implies for the entropy rain hypothesis.
 \end{abstract}
@@
 
-If entropy rain does evolve into downward propagating buoyant vortex rings, it is important to understand how buoyancy effects the filling factor of these basic convective elements. 
-In the context of Earth's atmosphere, so-called ``thermals'' are thought to be the nucleus of cloud formation. 
-Thermals are buoyant areas of fluid which evolve into propagating buoyant vortex rings, and their evolution in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently have been studied through Direct Numerical Simulation (DNS) in the laminar and turbulent regime \citep{lecoanet&jeevanjee2018}.
+If entropy rain does evolve into downward propagating, dense, anti-buoyant vortex rings, it is important to understand how the filling factor of these basic convective elements is affected by their entropy signature.
+In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the nucleus of cloud formation. 
+While atmospheric, cloud-forming thermals always rise, the term is also used for the reverse, falling process and the evolution of thermals in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently have been studied through Direct Numerical Simulation (DNS) in the laminar and turbulent regime \citep{lecoanet&jeevanjee2018}.
 One fundamental result of these studies of thermals is that they experience a large degree of entrainment: their size expands with height and their propagation velocity slows despite their buoyant nature.
@@
 \subsection{Phenomenological description of thermal evolution}
-We show pictorally the evolution of a cold thermal from rest in Fig.~\ref{fig:evolution_colormeshes}. 
+We show pictorally the evolution of cold thermalss from rest in Fig.~\ref{fig:evolution_colormeshes} for two different domains which span a different number of density scale heights ($n_\rho$). 
 In Fig.~\ref{fig:evolution_colormeshes}a, the evolution of a thermal in a weakly stratified domain with $n_\rho = 0.5$ density scale heights is shown. 
 In Fig.~\ref{fig:evolution_colormeshes}b, the evolution of a thermal in an appreciably stratified domain with $n_\rho = 3$ density scale heights is shown. 
-While the initial conditions are identical in both domains (spherical specific entropy perturbations of the same magnitude whose diameters are 5\% of the domain depth), and while in both cases the thermal quickly evolves into a propagating buoyant vortex ring, we find that the $n_\rho = 0.5$ case entrains and grows with depth, similarly to the Boussinesq regime.
-On the other hand, the $n_\rho = 3$ case has a radius which remains approximately constant over time, and it reaches the bottom of the domain in many fewer nondimensional freefall time units.
+In both cases, the thermal's initial conditions are spherical, dense, low entropy perturbations of equal magnitude whose diameters are 5\% of the domain depth.
+This dense sphere spins up into an axisymmetric vortex ring, and the vertical cross section through this vortex ring shows two circular vorticity \& entropy minima.
+We find that the $n_\rho = 0.5$ case entrains and grows with depth, similarly to the Boussinesq regime.
+On the other hand, the $n_\rho = 3$ case has a radius which remains approximately constant over time.
+The goal of this paper is to understand the evolution of the thermal in the vortex ring stage.
+All of the thermals studied in this work are laminar, similar to the Hill vortices studied by \citet{brandenburg2016}, but \citet{lecoanet&jeevanjee2018} showed that laminar theory describes the evolution of turbulent thermals well.
+We reserve studies of turbulent thermals in stratified domains for future work.
 
@@
     \caption{
-	The evolution of $\rho S_1 r^3$, or the total entropy weighted by the cube of the thermal radius, is shown for two thermals. 
+	The evolution of $\rho S_1 r^3$, the mass-weighted entropy scaled by the thermal volume, is shown for two thermals. 
 	On the left is a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights and on the right is a thermal in a strongly stratified domain with $n_\rho = 3$.
@@
 \end{equation}
-Hereafter we will define the Lagrangian derivative, $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$, and we acknowledge that the Langrangian derivative commutes with a volume integral such that
+Hereafter we will define the total derivative, $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$, and we acknowledge that the Langrangian derivative commutes with a volume integral such that
 \begin{equation*}
-\frac{D}{Dt}\int_{\mathcal{V}} f dV = \int_{\mathcal{V}} \left[\frac{Df}{Dt} + f(\DivU)\right]dV.
+\frac{d}{dt}\int_{\mathcal{V}} f dV = \int_{\mathcal{V}} \left[\frac{Df}{Dt} + f(\DivU)\right]dV,
 \end{equation*}
+assuming that the volume $\mathcal{V}$ is advected with the fluid.
 Volume-integrating Eqn.~\ref{eqn:rho_euler_momentum}, we thus find
 \begin{equation}
-\frac{D\bm{M}}{Dt} = \int_{\mathcal{V}}\left(-\rho\grad\varpi - \rho\frac{S_1}{c_P}\bm{g}\right)dV,
+\frac{d\bm{M}}{dt} = \int_{\mathcal{V}}\left(-\rho\grad\varpi - \rho\frac{S_1}{c_P}\bm{g}\right)dV,
 \label{eqn:int_momentum_eqn}
@@
 \begin{equation}
-\frac{D M_z}{Dt} = \int_{\mathcal{V}}\left( -\rho\frac{\partial \varpi}{\partial z} + \rho g \frac{S_1}{c_P} \right)dV.
+\frac{d M_z}{dt} = \int_{\mathcal{V}}\left( -\rho\frac{\partial \varpi}{\partial z} + \rho g \frac{S_1}{c_P} \right)dV.
 \label{eqn:Mz_definition}
@@
 \begin{equation}
-\frac{D M_z}{Dt} \approx \beta B.
+\frac{d M_z}{dt} \approx \beta B.
 \label{eqn:theory_momentum}
@@
 \begin{equation*}
-\frac{D\bm{I}}{D t} = \int_{\mathcal{V}}\frac{\partial(\rho\bm{u})}{\partial t}dV
+\frac{d\bm{I}}{d t} = \int_{\mathcal{V}}\frac{\partial(\rho\bm{u})}{\partial t}dV
 = B\hat{z} - \int_{\mathcal{V}}\left[\rho\grad\varpi + \Div{\rho\bm{u}\bm{u}}\right]dV ,
 \end{equation*}
-where, importantly, the \emph{eulerian} derivative of the momentum is inside of the volume integral here. 
+where, importantly, the \emph{eulerian} time derivative of the momentum is inside of the volume integral here. 
 Under the proper specification of boundary conditions, the integral term is zero, and the vertical impulse of a thermal thus straightforwardly changes in time as
 \begin{equation}
-\frac{D I_z}{D t} = B.
+\frac{d I_z}{d t} = B.
 \label{eqn:change_in_impulse}
@@
 We have thus retrieved the two findings on which our theory of thermal evolution will be built: \emph{both the impulse and momentum experience constant changes in time determined by the buoyant nature of the thermal}.
+
+In the low-Mach number limit in which changes in density from the background are negligible, and in the limit of a thin-core vortex ring, the impulse of a vortex ring can be approximated as
+\begin{equation}
+I_z \approx \pi \rho r^2 \Gamma,
+\label{eqn:impulse_approx}
+\end{equation}
+where $r$ is the radius of the thermal from its axis of symmetry to the maxima of its buoyant signature, and $\Gamma = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the integrated circulation in a cross-section of the vortex ring.
+Through integration of the momentum equation, it can be shown that in the absence of viscous effects, changes in circulation in an axisymmetric vortex ring are
+\begin{equation}
+\frac{d\Gamma}{dt} = \oint_{\mathcal{C}} g \frac{S_1}{c_P}\hat{z} \cdot d\bm{x},
+\label{eqn:circulation}
+\end{equation}
+where $\mathcal{C}$ is the contour around the area $\mathcal{A}$ in which the circulation is contained and $d\bm{x}$ is the line integral element around that contour.
+For the case of a vortex core in which the entropic signature is contained tightly in the core, as in Fig.~\ref{fig:evolution_colormeshes}, any contour which is drawn around the vortex core should conserve circulation in the absence of viscosity.
 
@@
 
+After spinning up, we assume that the thermal is characterized by a constant buoyant signature, $B_0$, and constant circulation, $\Gamma_0$.
+While these thermals began as initial spherical perturbations, they can be modeled as vortex rings which evolved from a ``virtual origin'' at which they had no radius. 
+From this virtual origin, the vortex ring's momentum and impulse grow to a value of $M_0$ and $I_0$ at time $t = 0$ when the true thermal is released from rest.
+
 We first note, as in Fig.~\ref{fig:constants}a, that the buoyancy in our thermals is not necessarily perfectly constant in time, and that effects like detrainment result in a minor reduction of the buoyant signature of our thermals.
-We thus express the buoyancy in terms of two constants,
+We thus express the buoyancy as 
 \begin{equation}
@@
 \end{equation}
-where $B_0$ is the initial buoyancy of the thermal, and $\chi$ is a constant of O(1) which represents this detrainment. 
-We then integrating Eqn.~\ref{eqn:change_in_impulse} in time,
+where $\chi$ is a constant of O(1) which represents this detrainment. 
+We then integrate Eqn.~\ref{eqn:change_in_impulse} in time,
 \begin{equation*}
 I_z = \chi B_0 t + I_0.
+\label{eqn:impulse_line}
 \end{equation*}
-In the low-Mach number limit in which changes in density from the background are negligible, the impulse of a vortex ring can be approximated as
-\begin{equation*}
-I_z \approx \pi \rho r^2 \Gamma_0,
-\end{equation*}
-where $r$ is the radius of the thermal from its axis of symmetry to the maxima of its buoyant signature, and $\Gamma_0 = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the integrated circulation in a cross-section of the vortex ring.
-We take $\Gamma_0$ to be constant, which is a decent assumption in our experiments, see Fig.~\ref{fig:constants}b.
-Combining these two expressions, we retrieve our first result,
+
+Following Eqn.~\ref{eqn:circulation}, we take $\Gamma_0$ to be constant, which is a decent assumption in our numerical experiments, see Fig.~\ref{fig:constants}b.
+Combining Eqns.~\ref{eqn:impulse_line} and \ref{eqn:impulse_approx}, we retrieve our first result,
 \begin{equation}
@@
 
+\subsection{Solution for thermal evolution in a Polytrope}
+Throughout this work we will study a polytrope, as is specified later in Eqn.~\ref{eqn:polytrope}.
+Integrating Eqn.~\ref{eqn:dz_theory} with this specific density stratification, we find
+\begin{equation}
+z_{\text{th}} = \grad_{\text{ad}}^{-1}\left[\left(\frac{2C}{ \alpha } \sqrt{t + t_{\text{off}}} + T_0^{1/\alpha}  \right)^{\alpha} - 1\right] + L_z,
+\label{eqn:theory_z}
+\end{equation}
+where $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma^3/(\chi B)}$, the temperature at the virtual origin is $T_0 = 1 + \grad_{\text{ad}}(z_0 - L_z)$, $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and assuming that the polytropic index is $m_{\text{ad}} < 2$ (which is valid for our case of $m_{\text{ad}} = 1.5$ studied here).
+In the limit of large stratification, we thus find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
+
+The thermal is initialized as a uniform sphere of dense fluid, and it quickly spins up into a vortex ring. 
+While we do not attempt to model the spin-up phase in this paper, it can be parameterized by the buoyancy $B_0$, circulation $\Gamma$, as well as the virtual origin $z_0$, and temporal offset $t_off$ which are the height and time a which the vortex ring would have had zero radius in the absence of a spin-up phase.
+Our theory also involves the volumetric aspect ratio of the thermal $f$, the detrainment fraction $\chi$, and the effective buoyancy $\beta$. 
+These appear to be constant or only weakly dependent on the stratification for the thermals we have simulated.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{gather}
-\td{\grad}\cdot\td{\bm{u}} = -\td{w}\partial_{\tilde{z}} \ln\rho_0 
-\label{eqn:AN_continuity_full}\\
-\frac{D \td{\bm{u}}}{D \td{t}} = -\td{\grad} \td{\varpi} + g\frac{\td{S_1}}{c_P}\hat{z} + \frac{1}{\rho_0}\td{\grad}\cdot\left(\mu\td{\lilstressT}\right)
-\label{eqn:AN_momentum_full}\\
-\frac{D \td{S_1}}{D\td{t}} = \frac{1}{\rho c_P}\td{\grad}\cdot\left(\kappa T_0 \td{\grad} \td{S_1}\right) + \frac{\mu}{\rho_0 T_0}\td{\sigma_{ij}}\partial_{\td{x_i}}\td{u_j}
-\label{eqn:AN_energy_full}.
-\end{gather}
-where terms with tildes are dimensional, and where $D/D\td{t} = \partial/\partial \td{t} + \td{\bm{u}}\cdot\td{\grad}$. 
-In our azimuthally symetric domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$.
-Under this approximation, the components of the stress tensor are
-\begin{equation}
-\begin{split}
-&\td{\sigma}_{rr} = 2\frac{\partial \td{u_r}}{\partial \td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,
-\td{\sigma}_{\phi\phi} = 2\frac{\td{u_r}}{\td{r}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}}, \\
-&\td{\sigma}_{zz}       = 2\frac{\partial \td{w}}{\partial \td{z}} - \frac{2}{3}\td{\grad}\cdot\td{\bm{u}},\,\,\,\,\,\,\,
-\td{\sigma}_{rz}     = \td{\sigma}_{zr} = \frac{\partial \td{w}}{\partial \td{r}} + \frac{\partial \td{u_r}}{\partial \td{z}}, \\
-&\td{\sigma}_{r\phi}  = \td{\sigma}_{\phi r}  
- = \td{\sigma}_{\phi z} = \td{\sigma}_{z \phi}  = 0,\qquad
-\end{split}
-\end{equation}
-Furthermore, we assume that the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform throughout the domain and constant in time.
-The diffusivities $\nu$ and $\chi$ therefore scale inversely with the density.
-
-We nondimensionalize these equations in the same manner as in \citet{lecoanet&jeevanjee2018} such that the length scale is the diameter of the initial thermal perturbation and the velocity scale is the freefall velocity.
-The timescale is thus the freefall crossing time of this unit length. 
-Mathematically,
-\begin{equation}
-\begin{split}
-\td{\grad}\rightarrow(\td{L}_{th}^{-1})\grad, \qquad&
-\td{S}_1 \rightarrow(\Delta\td{S})S_1,\\
-\td{\bm{u}} \rightarrow (\td{u}_{th})\bm{u}, \qquad&
-\td{\varpi} \rightarrow (\td{u}_{th}^2)\varpi,\\
-\partial_{\tilde{t}} \rightarrow (\td{u}_{th}/\td{L}_{th})\partial_t,\qquad&
-\end{split}
-\end{equation}
-with
-\begin{equation}
-\tilde{u}_{th}^2 = \frac{g \tilde{L}_{th} \Delta \tilde{s}}{c_P}, \qquad
-\text{Re}_{\text{ff}} = \frac{\tilde{u}_{th} \tilde{L}_{th}}{\nu}, \qquad
-\text{Pr}_{\text{ff}} = \frac{\tilde{u}_{th} \tilde{L}_{th}}{\chi}.
-\end{equation}
-As the diffusivities scale with depth, Re$_{\text{ff}}$ is specified at the thermal's initial depth.
-The resulting equations are,
-\begin{gather}
 \DivU = -w \partial_z \ln\rho_0, \\
@@
 - \grad \varpi + S_1\hat{z} &
-+ \frac{1}{\text{Re}_{\text{ff}}}\left[\grad^2 \bm{u} + \frac{1}{3}\grad(\DivU)\right] 
++ \frac{1}{\rho_0\text{Re}}\left[\grad^2 \bm{u} + \frac{1}{3}\grad(\DivU)\right] 
 \end{split}\\
@@
 \partial_t S_1 + \bm{u}\cdot\grad S_1 =& \\
-\frac{1}{\text{Re}_{\text{ff}}}\left(\frac{1}{\text{Pr}_{\text{ff}}\rho_0c_P }\right.&[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\\
+\frac{1}{\text{Re}}\left(\frac{1}{\text{Pr}\rho_0c_P }\right.&[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\\
 &+ \left.\frac{-(\grad_{\text{ad}})}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right),
@@
 \end{gather}
-where $\grad_{\text{ad}} \equiv \tilde{L}_{\text{th}} \frac{g}{c_P}$.
+where $\grad_{\text{ad}} \equiv g(e^{n_\rho/m_{\text{ad}}} - 1)/(L_z c_P)$ and $\lilstressT$ is the viscous stress tensor in units of inverse time.
+In our azimuthally symetric domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$.
+
+These equations have been nondimensionalized in the same manner as in \citet{lecoanet&jeevanjee2018} such that the length scale is the diameter of the initial thermal perturbation and the velocity scale is the freefall velocity.
+The timescale is thus the freefall crossing time of this unit length. 
+These atmospheres are fully specific in terms of the Reynolds number and Prandtl number,
+\begin{equation}
+\text{Re} = \frac{u_{th} L_{th}}{\nu}, \qquad
+\text{Pr} = \frac{u_{th} L_{th}}{\chi}, \qquad
+u_{th}^2 = \frac{g L_{th} \Delta s}{c_P},
+\end{equation}
+where $u_{th}$ is the freefall velocity, $L_{th}$ is the thermal length scale, and
+$\Delta s$ is the magnitude of the specific entropy signature of the thermal.
+
+We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform and constant in time.
+The diffusivities $\nu$ and $\chi$ therefore scale inversely with the density.
+As the diffusivities scale with depth, Re is specified at the thermal's initial depth.
+All simulations conducted in this work use a value of Re = 600 and $\mbox{\text{Pr} = 1}$.
 
@@
 \begin{gather}
-\frac{D \ln\rho}{Dt} + \DivU = 0 \\
-\frac{D \bm{u}}{D t} = -\grad T - T\grad\ln\rho - g\hat{z} + \frac{1}{\rho}\grad\cdot\left(\mu\lilstressT\right) \\
-\frac{D T}{Dt} + (\gamma-1)T\DivU  = \frac{1}{\rho c_V}\grad\cdot\left(\kappa \grad T\right) + \frac{\mu}{\rho c_V}\sigma_{ij}\partial_{x_i}u_j.
+\frac{\partial \ln\rho_1}{\partial t} + \epsilon^{-1}\left(\bm{u}\cdot\grad\ln\rho_0 + \DivU\right) = -\bm{u}\cdot\grad\ln\rho_1, \\
+\begin{split}
+\frac{\partial \bm{u}}{\partial t}  +\grad T_1 + T_1\grad\ln\rho_0 + T_0\grad\ln\rho_1  =\\
+- \epsilon T_1\grad\ln\rho_1 + \frac{1}{\rho\text{Re}}\left[\grad^2\bm{u} + \frac{1}{3}\grad(\DivU)\right]
+\end{split} \\
+\begin{split}
+\frac{\partial T_1}{\partial t} + \epsilon^{-1}\left[\bm{u}\cdot\grad T_0 + (\gamma-1)T_0\DivU\right] = \\
+-\left[\bm{u}\cdot\grad T_1 + (\gamma-1)T_1\DivU\right] + \frac{1}{\rho c_V\text{Re}}\left[\frac{1}{\text{Pr}}\grad^2 T_1 + \sigma_{ij}\partial_{x_i}u_j\right].
+\end{split}
 \end{gather}
-where the viscous stress tensor is defined as
-\begin{equation}
-\sigma_{ij} = \left(\partial_{x_i}u_j + \partial_{x_j}u_i - \frac{2}{3}\delta_{ij}\grad\cdot\bm{u}\right).
-\end{equation}
-These equations are nondimensionalized on the temperature gradient length scale such that $\grad_{\text{ad}} = -1$ and the nondimensional timescale is the sound crossing time of that unit length at the top of the domain.
+These equations have been nondimensionalized on the same length and timescales as the anelastic equations, use the same atmospheric profiles and assumptions, and we have explicitly assumed that the background atmosphere ($T_0, \ln\rho_0$) is in hydrostatic and thermal equilibrium in the writing of these equations.
+The new parameter $\epsilon = u_{th}^2$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows, and we use $\epsilon = 10^{-4}$ in this work.
 
-In setting the specific entropy, $S = c_V \ln T - R^{-1}\ln\rho$, to an equivalent condition to that specified in  Eqn.~\ref{eqn:thermal_IC}, we note that it is essential that the initial perturbation be in pressure equilibrium.
+In setting the specific entropy to an equivalent condition to that specified in Eqn.~\ref{eqn:thermal_IC}, we note that it is essential that the initial perturbation be in pressure equilibrium. 
 The set of initial conditions that achieves this is
@@
 \end{equation}
-We specify the magnitude of the initial entropy perturbations as $A = \epsilon = 10^{-4}$, such that the mach number of the resultant thermal is O($10^{-2}$) or less.
-
-The depth of the atmosphere in these fully compressible domains is set to $L_z = e^{n_\rho/m_{ad}} - 1$.
-In order to compare results from these simulations to our Anelastic thermal simulations, we rescale all outputs in post-processing by a length scale factor of $\ell = 20/L_z$, a timescales factor of  $\tau = \sqrt{\ell \epsilon}$, and a specific entropy scaling of $s = \epsilon^{-1}$.
 
@@
 Our 3D simulations are decomponsed on Fourier bases in the horizontal directions ($x, y \in [-L_r, L_r]$) and Chebyshev bases vertically ($z \in [0, L_z]$) with impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries ($T_1 = w = \partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
-Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of $\partial_r S_1 = w = (\grad\times\bm{u})_{\phi} = 0$ at $r = L_r$.
+Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of $\partial_r S_1 = u_r = w = 0$ at $r = L_r$.
 
-\subsection{Solution for thermal evolution in a Polytrope}
-Now that the atmospheric density is specific, we can find an explicit solution for Eqn.~\ref{eqn:dz_theory} to compare to the results of our simulations. 
-As temperature and height are linearly related in our atmospheres, we find it instructive to use temperature as a integration parameter.
-We note that, $\rho = T^{m_{ad}}$ and $dT = (\grad_{\text{ad}}) dz_{th}$, such that we must solve 
-\begin{equation}
-\int_{T_0}^{T_{\text{th}}} T^{-m_{ad}/2} dT 
-= \left(\frac{\beta(\pi\Gamma)^{3/2}\grad_{\text{ad}}}{f(\chi B)^{1/2}}\right)
-\int_{0}^{t + t_{\text{off}}} t^{-1/2} dt.
-\end{equation}
-defining $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma^3/(\chi B)}$ and $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and assuming that $m_{\text{ad}} < 2$ (which is valid for our case of $m_{\text{ad}} = 1.5$ studied here) we find that
-\begin{equation}
-T_{\text{th}} = \left(\frac{2C}{ \alpha } \sqrt{t + t_{\text{off}}} + T_0^{1/\alpha}  \right)^{\alpha}.
-\label{eqn:theory_T}
-\end{equation}
-In the limit of large stratification, we thus find that $T_{\text{th}} \propto t^2$ for our case of $\alpha = 4$. 
-The temperature can be straightforwardly converted to height by a rearrangement of Eqn.~\ref{eqn:polytrope},
-\begin{equation}
-z_{\text{th}} = (T_{\text{th}} - 1)/\grad_{\text{ad}} + L_z
-\end{equation}
-The thermal is thus described in terms of seven total parameters:
-\begin{enumerate}
-\item $T_0$ and $t_{\text{off}}$, the temperature of the thermal's virtual origin, and the time before the simulation's $t = 0$ at which the thermal was located at its virtual origin,
-\item $B_0$ and $\Gamma$, the measurable buoyancy and circulation of the vortex ring, and
-\item $f$, $\chi$, and $\beta$, fitting parameters which describe the nature of the vortex ring's evolution.
-\end{enumerate}
+As a result of our theory being largely derived in the anelastic, axisymmetric limit, we have chosen to focus the bulk of our attention on our 2D, axisymmetric anelastic simulations.
+Furthermore, the 2D nature of these simulations allows us to much more feasibly study high density stratifications using fewer computational resources.
+The 3D fully compressible simulations serve primarily as a verification of the anelastic results in the low Mach number regime in which the anelastic constraint is not explicitly true, and in the 3D case where axisymmetry is not baked into the equations.
+
+While natural processes are very turbulent, we have chosen to study the evolution of laminar thermals here. 
+\citet{lecoanet&jeevanjee2018} showed for an ensemble of laminar and turbulent thermals that the measured entrainment of the evolved vortex rings in the turbulent case is well described by laminar theory.
+As we are not aware of a developed laminar theory in the stratified regime in the literature, like the one developed here, we have restricted the simulations in this work to the laminar regime in order to test our new theory in the regime where it should be transparent to verify its validity.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% RESULTS SECTION
+\section{Results}
+\label{sec:results}
 The measured values of these parameters for the cases studied in this paper are presented in table \ref{table:parameters}.
 
-\begin{deluxetable*}{c c c c c c c c c}
+\begin{deluxetable*}{c c c c c c c c}
 \tabletypesize{\footnotesize}
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$\grad_{\text{ad}}$} & \colhead{$T_0$} & \colhead{$t_{\text{off}}$} & \colhead{$B$} & \colhead{$\Gamma$} & \colhead{$f$} & \colhead{$\chi$} & \colhead{$\beta$}	}	
+\colhead{$n_\rho$} & \colhead{$T_0$} & \colhead{$t_{\text{off}}$} & \colhead{$B$} & \colhead{$\Gamma$} & \colhead{$f$} & \colhead{$\chi$} & \colhead{$\beta$}	}	
 \startdata																																															
-\multicolumn{9}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	& $3.45 \times 10^{-3}$		& 0.985	& 0.166	& -0.547 & -2.17 & 7.01	& 1.04	& 0.499	\\
-0.5 	& $1.98 \times 10^{-2}$		& 0.918	& 0.704	& -0.568 & -2.12 & 7.04	& 0.976	& 0.490	\\
-1	 	& $4.74 \times 10^{-2}$		& 0.827	& 1.09 	& -0.601 & -2.05 & 7.07	& 0.915	& 0.480	\\
-2	 	& $0.140$             		& 0.677	& 1.26	& -0.712 & -1.89 & 7.08	& 0.841 & 0.456	\\
-3	 	& $0.319$             		& 0.619	& 1.01	& -0.946 & -1.73 & 7.08	& 0.808	& 0.436	\\
-4	 	& $0.667$             		& 0.698	& 0.622	& -1.47	 & -1.59 & 7.10	& 0.793	& 0.422	\\
-5	 	& $1.352$             		&			& 			&	 &	&	&	&	\\
-\multicolumn{9}{l}{\textbf{3D Fully Compressible Simulations}}\\    
-0.5 	& 	$1.98 \times 10^{-2}$	& 0.924	& 0.583	& -0.568 & -2.12 & 6.66	& 0.978	& 0.452	\\
-1	 	& 	$4.74 \times 10^{-2}$	& 0.832	& 1.26	& -0.601 & -2.05 & 6.88	& 0.902	& 0.454	\\
-2	 	& 	$0.140$             	& 0.666	& 1.53	& -0.711 & -1.89 & 7.08	& 0.822	& 0.450	\\
+\multicolumn{8}{l}{\textbf{2D Anelastic Simulations}}\\
+0.1 	&  0.985	& 0.166	& -0.547 & -2.17 & 7.01	& 1.04	& 0.499	\\
+0.5 	&  0.918	& 0.704	& -0.568 & -2.12 & 7.04	& 0.976	& 0.490	\\
+1	 	&  0.827	& 1.09 	& -0.601 & -2.05 & 7.07	& 0.915	& 0.480	\\
+2	 	&  0.677	& 1.26	& -0.712 & -1.89 & 7.08	& 0.841 & 0.456	\\
+3	 	&  0.619	& 1.01	& -0.946 & -1.73 & 7.08	& 0.808	& 0.436	\\
+4	 	&  0.698	& 0.622	& -1.47	 & -1.59 & 7.10	& 0.793	& 0.422	\\
+5	 	& 			& 			&	 &	&	&	&	\\
+\multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations}}\\    
+0.5 	&  0.924	& 0.583	& -0.568 & -2.12 & 6.66	& 0.978	& 0.452	\\
+1	 	&  0.832	& 1.26	& -0.601 & -2.05 & 6.88	& 0.902	& 0.454	\\
+2	 	&  0.666	& 1.53	& -0.711 & -1.89 & 7.08	& 0.822	& 0.450	\\
 \enddata																																															
@@
 \end{deluxetable*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% RESULTS SECTION
-\section{Results}
-\label{sec:results}
 
@@
 At very low stratification (e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
-As the stratification increases, the thermal begins to transit the domain more quickly and approaches the limit of $d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_T}. 
-The theoretical fits for depth from the prediction of Eqn.~\ref{eqn:theory_T} are plotted over the measured data and show remarkable agreement.
+As the stratification increases, the thermal begins to transit the domain more quickly and approaches the limit of $d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_z}. 
+The theoretical fits for depth from the prediction of Eqn.~\ref{eqn:theory_z} are plotted over the measured data and show remarkable agreement.
 
-In Fig.~\ref{fig:results_vs_depth}a, we plot the measured thermal radius vs. depth, with the theoretical predictions of Eqns.~\ref{eqn:r_theory} \& \ref{eqn:theory_T} plotted as lines over the data. 
+In Fig.~\ref{fig:results_vs_depth}a, we plot the measured thermal radius vs. depth, with the theoretical predictions of Eqns.~\ref{eqn:r_theory} \& \ref{eqn:theory_z} plotted as lines over the data. 
 In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, aligning with the Boussinesq limit shown in \citet{lecoanet&jeevanjee2018}.
@@
 \end{enumerate}
-However, we note that both of these regimes could result in interesting problems for the entropy rain hypothesis. 
-If solar convection were comprised of thermals in the stalling regime, it is unlikely that such elements would ever make it to the base of the solar convection zone, stalling much closer to the solar surface and depositing their entropy signature there -- possibly agreeing with the hypothesis of supergranulation as the largest buoyantly driven scale of solar motion.
-On the other hand, if solar convection is comprised of thermals in the falling regime, then it is possible that as these thermals compress and accelerate, diffusive effects and potentially viscous heating could become important.
-We discuss these possibilities further in section \ref{sec:discussion}
 
@@
 In this work we have extended the theory of the evolution of buoyant thermals into the low-Mach number, stratified regime and have shown that that theory has remarkable agreement with the results of both Anelastic and Fully compressible simulations.
+
+However, we note that both the falling and stalling regimes observed here could result in interesting problems for the entropy rain hypothesis. 
+If solar convection were comprised of thermals in the stalling regime, it is unlikely that such elements would ever make it to the base of the solar convection zone, stalling much closer to the solar surface and depositing their entropy signature there -- possibly agreeing with the hypothesis of supergranulation as the largest buoyantly driven scale of solar motion.
+On the other hand, if solar convection is comprised of thermals in the falling regime, then it is possible that as these thermals compress and accelerate, diffusive effects and potentially viscous heating could become important.
+We discuss these possibilities further in section \ref{sec:discussion}
 
@@
 \multicolumn{6}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	& 	7				&	512			& 512			& 49 	&	0.1	\\
-0.5 	& 	7				&	512			& 512			& 42.5 	&	0.1	\\
-1	 	& 	5				&	512			& 512			& 38 	&	0.1	\\
-2	 	& 	5				&	512			& 512			& 31.75	&	0.1	\\
-3	 	& 	5				&	1024		& 1024			& 27.25	&	0.1	\\
-4	 	& 	5				&	1024		& 1024			& 25 	&	0.075	\\
-5	 	& 	2.4				&	1024		& 1024			& 22.8 	&	0.05	\\
+0.1 	& 	5				&	128			& 512			& 49 	&	0.2	\\
+0.5 	& 	5				&	128			& 512			& 42.5 	&	0.2	\\
+1	 	& 	5				&	128			& 512			& 38 	&	0.2	\\
+2	 	& 	5				&	128			& 512			& 31.75	&	0.2	\\
+3	 	& 	5				&	256			& 512			& 27.25	&	0.15	\\
+4	 	& 	5				&	256			& 512			& 25 	&	0.1	\\
+5	 	& 	5				&	256			& 512			& 22.8 	&	0.05	\\
 \multicolumn{6}{l}{\textbf{3D Fully Compressible Simulations}}\\

### 2019-05-22 code/AN_2D_thermal.py
Many 2D code improvements: * Better boundary condition specification * Better nz == 0 specification * cleaned up run scripts

@@ -118,7 +118,7 @@ r_basis = de.Chebyshev('r', nr, interval=(0, Lr), dealias=3/2)
 domain = de.Domain([z_basis, r_basis], grid_dtype=np.float64)
 
 problem = de.IVP(domain, variables=['u', 'w', 'ur', 'wr', 'S1', 'S1r', 'p'])
-problem.meta['u', 'w', 'S1r', 'p']['r']['dirichlet'] = True
+problem.meta['u', 'ur', 'w', 'wr', 'S1', 'S1r', 'p']['r']['dirichlet'] = True
 problem.parameters['u_phi'] = problem.parameters['u_phir'] = 0
 
 problem.parameters['pi']         = np.pi
@@ -134,6 +134,7 @@ problem.parameters['Pr']         = Pr
 problem.parameters['Lnondim']    = -grad_T_ad #scaling factor from unscaled polytropes -- for viscous heating term.
 
 problem.substitutions['T']            = '(1 + grad_T_ad*(z - Lz))'
+problem.substitutions['ln_rho0']      = '(m_ad*log(T))'              
 problem.substitutions['T0']           = '(T)'
 problem.substitutions['rho0']         = '((T)**(m_ad))'              
 problem.substitutions['ln_rho0_z']    = '(m_ad*grad_T_ad/T)'         
@@ -157,10 +158,9 @@ problem.substitutions['UdotGradU_phi']      = '(UdotGrad(u_phi, u_phir) - u_phi*
 problem.substitutions['Lap(A, Ar)']         = '(Ar/r + dr(Ar) + dz(dz(A)))'
 problem.substitutions['Lap_phi(A, Ar)']     = '(Lap(A, Ar) - A/r**2)'
 problem.substitutions['Lap_r(A, Ar)']       = '(Lap(A, Ar) - A/r**2)'
-problem.substitutions['DivU_true']          = '(u/r + ur + dz(w))'
-problem.substitutions['DivU']               = '(DivU_true)'
+problem.substitutions['DivU']               = '(u/r + ur + dz(w))'
 problem.substitutions['DivUr']              = '(ur/r - u/r**2 + dr(ur) + dz(wr))'
-problem.substitutions['DivUz']              = '(-1)*(ln_rho0_z*dz(w) + w*ln_rho0_zz)'
+problem.substitutions['DivUz']              = '(-1)*(ln_rho0_z*dz(w) + w*ln_rho0_zz)' #This isn't stable as a natural dz(DivU)
 
[…]

### 2019-05-22 code/join_data.py

@@ -32,6 +32,7 @@ logger.info("joining data from Dedalus run {:s}".format(data_dir))
 if args['--data_type'] is not None:
     data_types=[args['--data_type']]
 else:
+#    data_types = ['slices', 'profiles']
     data_types = ['final_checkpoint', 'checkpoint', 'volumes', 'profiles', 'slices', 'scalars']
 
 for data_type in data_types:

### 2019-05-22 code/plotting/overview_fig.py

@@ -78,10 +78,10 @@ nrho_001_r_no_buoy = theory_r(times, 0, -1/2, nrho_001[3], nrho_001[-2], rho_f=i
 ind_001 = nrho_001_d[nrho_001_d > 2][0] == nrho_001_d
 ind_3 = nrho_3_d[nrho_3_d > 2][0] == nrho_3_d
 plt.plot(nrho_001_d, (nrho_001_d/nrho_001_d[ind_001])**2, c='black', lw=0.5)
-ax.text(2.5, 5, r'$f \propto d^2$', fontsize=10)
+ax.text(2.5, 5, r'$f \propto d^2\,\mathrm{(Boussinesq, LJ19)}$', fontsize=10)
 plt.plot(nrho_3_d, (nrho_3_r/nrho_3_r[ind_3])**2, c='k', lw=1.5)
-plt.plot(nrho_3_d, (nrho_3_r_no_buoy/nrho_3_r_no_buoy[ind_3])**2, c='black', lw=0.5, dashes=(4,1))
-ax.text(2.5, 1.5e-1, r'$f \propto \rho^{-1}$', fontsize=10)
+plt.plot(nrho_3_d, (nrho_3_r_no_buoy/nrho_3_r_no_buoy[ind_3])**2, c='black', lw=0.5)
+ax.text(2.5, 1.5e-1, r'$f \propto \rho^{-1}\,\mathrm{(Horizontal compression, B16)}$', fontsize=10)
 plt.yscale('log')
 plt.ylabel(r'$f = r^2$')
 plt.xlabel('Depth')

### 2019-05-23 tex/stratified_thermals.tex
figure updates, sketched out discussion section

@@
 %% EXPERIMENT SECTION
-\section{Experiment} 
+\section{Numerical Experiment} 
 \label{sec:experiment}
@@
 \begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{results_panels_d_v_t.png}
+    \includegraphics[width=\columnwidth]{results_panels.png}
     \caption{
@@
 \begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{results_panels_vs_depth.png}
+    \includegraphics[width=\columnwidth]{diff_AN_FC.png}
     \caption{
-	Shown are (a) the measured radii of thermals as a function of depth and (b) the measured thermal velocities as a function of depth for all 2D Anelastic and 3D Fully compressible simulations conducted in this work.
-	Overplotted are the predictions from theory.
-    \label{fig:results_vs_depth} }
+	Measured values of (a) depth vs. time and (c) radius vs. depth are plotted for both the 2D anelastic and 3D fully compressible simulations. 
+	The fractional difference between anelastic and fully compressible results are respectively shown in (b) and (d).
+    \label{fig:diff} }
 \end{figure}
@@
 
-These results suggest that there are two regimes of downflowing thermal behavior:
-\begin{enumerate}
-\item A low-stratification ``stalling'' regime, in which the thermal entrains environmental fluid and slows down, acting much like the Boussinesq regime, and
-\item A high-stratification ``falling'' regime, in which the thermal falls fast enough that compression due to the atmospheric stratification results in minimal entrainment and the thermal accelerates as it falls deeper into the atmosphere.
-\end{enumerate}
-
 \subsection{Verification of 2D Anelastic approximation}
-\begin{figure*}[t!]
-    \includegraphics[width=\textwidth]{diff_AN_FC.png}
-    \caption{
-	Measured values of (a) depth vs. time and (c) radius vs. depth are plotted for both the 2D anelastic and 3D fully compressible simulations. 
-	The fractional difference between anelastic and fully compressible results are respectively shown in (b) and (d).
-    \label{fig:diff} }
-\end{figure*}
-
 In Fig.~\ref{fig:diff}, we display in more detail a comparison of our 2D Anelastic and 3D Fully Compressible cases. 
@@
 %% CONCLUSION SECTION
-\section{Discussion}
+\section{Conclusion \& Discussion}
 \label{sec:discussion}
-In this work we have extended the theory of the evolution of buoyant thermals into the low-Mach number, stratified regime and have shown that that theory has remarkable agreement with the results of both Anelastic and Fully compressible simulations.
+In this paper we extended the theory of thermal entrainment to include stratification, and showed that theory predicts that dense thermals will experience less entrainment than boussinesq thermals due to increasing atmospheric density with depth.
+We performed 2D anelastic simulations of thermal evolution for varying degrees of stratification and showed that our parameterized theory describes the evolution of thermals in these systems remarkably well.
+Furthermore, we verified the validity of our anelastic simulations with select 3D fully compressible simulations of thermal evolution.
+
+We note that the evolution of dense thermals in stratified domain is complex, and neither the assumption of horizontal compression \citep[as in e.g.][]{brandenburg2016} or the evolution of thermals in the Boussinesq regime fully describes the behavior of these events fully.
+Rather, results fall somewhere in between, and theory and simulations suggest that there are two regimes of downflowing thermal behavior:
+\begin{enumerate}
+\item A low-stratification ``stalling'' regime, in which the thermal entrains environmental fluid and slows down, acting much like the Boussinesq regime, and
+\item A high-stratification ``falling'' regime, in which the thermal falls fast enough that compression due to the atmospheric stratification results in minimal entrainment and the thermal accelerates as it falls deeper into the atmosphere.
+\end{enumerate}
 
 However, we note that both the falling and stalling regimes observed here could result in interesting problems for the entropy rain hypothesis. 
-If solar convection were comprised of thermals in the stalling regime, it is unlikely that such elements would ever make it to the base of the solar convection zone, stalling much closer to the solar surface and depositing their entropy signature there -- possibly agreeing with the hypothesis of supergranulation as the largest buoyantly driven scale of solar motion.
-On the other hand, if solar convection is comprised of thermals in the falling regime, then it is possible that as these thermals compress and accelerate, diffusive effects and potentially viscous heating could become important.
-We discuss these possibilities further in section \ref{sec:discussion}
+If solar convection were comprised of thermals in the stalling regime, it is unlikely that such elements would ever make it to the base of the solar convection zone.
+Rather, we expect that they would stall closer to the solar surface and deposit their entropy signature there. 
+This could be seen as agreeing with the hypothesis of supergranulation as the largest buoyantly driven scale of solar motion.
 
-We should have some discussion on these topics:
-\begin{enumerate}
-\item speculation about extensions to the solar regime. Do things on the sun shrink to the point where they viscously dissipate? Do they stall?
-\item Talk about what would happen if we were to study up-thermals.
-\item Extensions, and we trust that these results should hold in the regime of solar convection where things are turbulent.
-\end{enumerate}
+On the other hand, if solar convection is comprised of thermals in the falling regime, then it is not out of the question for solar surface elements to reach deep into the Sun.
+While vortex rings in the falling regime would theoretically be able to reach the bottom of the solar convection zone, the compression effects that occur as they shrink could cause problems.
+For example, it is possible that these thermals could shrink to the point where conductivity becomes important, or as their length scales decrease and velocities increase, viscous heating could become an important effect and essentially erase the buoyant signature of these entropy rain droplets.
+
+In Fig.~\ref{fig:discussion}, we extrapolate the results of our simulations to solar convection.
+For each simulation performed, we show the behavior of our thermals if they were to fall the first $n_\rho = 10$ density scale heights of the solar convection zone, rather than the few that we were able to simulate here.
+We see blahblahblah.
 
@@
 To do so, we average the domain's entropy profile in radius and azimuth to create an average profile of entropy with height, and then assume that the thermal's vortex core is located at the entropy minima of each of those profiles.
-We numerically differentiate these found values of height vs.
-time using (insert numerical differentiation technique here) and then calculate the streamfunction of the velocity field as in \citet{romps&all2015},
+We numerically differentiate these found values of height vs. time using (insert numerical differentiation technique here) to get the velocity of the bulk of the thermal, $w_{\text{th}}$.
+We then calculate the streamfunction of the velocity field as in \citet{romps&all2015},
 \begin{equation}
@@
 with the boundary condition that $\psi = 0$ at $r = 0$. 
-The contour defined by $\psi = 0$ from this solution is taken to be the outline of the thermal, and the volume of the thermal is taken to be the volume radially inward from that contour.
+The contour defined by $\psi = 0$ from this solution is taken to be the outline of the thermal, and the volume of the thermal is taken to be the volume contained in that contour.
 

### 2019-05-24 tex/stratified_thermals.tex
some text improvements

@@
 
+\defcitealias{lecoanet&jeevanjee2018}{LJ19}
+\newcommand{\LJ}{\citetalias{lecoanet&jeevanjee2018}}
+
 \begin{document}
@@
 Recent observations of solar convection have revealed a convective conundrum.
-Power spectra have revealed weaker flows than anticipated at large length scales \citep{hanasoge&all2012, greer&all2015}, calling into question the existence of so-called ``giant cells'' driven by deep convection which would manifest as powerful, large-scale motions at the solar surface.
+Power spectra of horizontal velocities show weaker flows than anticipated at large length scales \citep{hanasoge&all2012, greer&all2015}.
+These obserations cast doubt on the existence of ``giant cells'' driven by deep convection which should manifest as powerful, large-scale motions at the solar surface and throughout the solar convection zone.
 This discrepancy between theory and observations has called into question our fundamental understanding of convection, sparking numerous targeted investigations the nature of convection in the Sun  \citep{featherstone&hindman2016, omara&all2016, cossette&rast2016, kapyla&all2017, hotta2017}.
 
-\cite{spruit1997} hypothesized that convective motions may be driven entirely by cool downflows at the surface of the Sun, and \citet{brandenburg2016} expanded upon this ``entropy rain'' hypothesis. 
+\cite{spruit1997} hypothesized that convective motions in the Sun may be driven entirely by cooling at the solar surface, and \citet{brandenburg2016} expanded upon this ``entropy rain'' hypothesis. 
 Brandenburg's work includes a careful expansion of mixing length theory to incorporate flux contributions from nonlocal convective motions, and handles this theory in a horizontally-averaged sense.
-He includes some discussion of possible flow morphologies which could be manifestations of this entropy rain, and even includes some brief simulations of propogating Hill vortices. 
-However, these simulations and discussions did not include include a fundamental piece of entropy rain: it is buoyant, and has an entropy deviation from the background atmosphere.
+He includes some discussion of possible flow morphologies which could be manifestations of this entropy rain, and even includes some brief simulations of propagating Hill vortices. 
+However, these simulations and discussions did not include include a fundamental piece of entropy rain: its entropic signature deviates from the background atmosphere.
+Entropy rain is dense, and the effects of antibuoyant forces will modify its dynamics.
 
-If entropy rain does evolve into downward propagating, dense, anti-buoyant vortex rings, it is important to understand how the filling factor of these basic convective elements is affected by their entropy signature.
+If entropy rain does evolve into downward propagating, dense vortex rings, it is important to understand how the filling factor of these basic convective elements is affected by their entropy signature.
 In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the nucleus of cloud formation. 
-While atmospheric, cloud-forming thermals always rise, the term is also used for the reverse, falling process and the evolution of thermals in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently have been studied through Direct Numerical Simulation (DNS) in the laminar and turbulent regime \citep{lecoanet&jeevanjee2018}.
-One fundamental result of these studies of thermals is that they experience a large degree of entrainment: their size expands with height and their propagation velocity slows despite their buoyant nature.
+Atmospheric cloud-forming thermals always rise, but the term is also used for the reverse, falling process.
+The evolution of thermals in the Boussinesq limit has been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently have been studied through Direct Numerical Simulation (DNS) in the laminar and turbulent regime \citep{lecoanet&jeevanjee2018}.
+One fundamental result of these studies of thermals is that they experience a large degree of entrainment characterized by radial expansion and decceleration of propagation velocity.
 However, we do not know of a study in which the propagation of these thermals, and thus the nature of their entrainment, is affected by a significant atmospheric stratification.
@@
     \caption{
-	We have plotted the evolution of the filling factor, or radius squared, of a buoyant vortex ring with depth (the $n_\rho = 3$ case examined later in this work). 
-	Overplotted in a thin solid line is the prediction for filling factor growth in the Boussinesq case, and in the thin dashed line is plotted the prediction for pure horizontal compression, as in \citet{brandenburg2016}.
+	The evolution of the filling factor, or radius squared, of a buoyant vortex ring with depth is shown in an atmosphere which spans three density scale heights (the $n_\rho = 3$ case examined later in this work).
+	Overplotted in thin solid lines are the predictions for filling factor growth in the Boussinesq case (as in \LJ) and the prediction for pure horizontal compression (as in \citet{brandenburg2016}).
     \label{fig:overview} }
@@
 
-In the absence of buoyantly-induced entrainment, \citet{brandenburg2016} suggests that the filling factor, $f$, of vortex rings should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression.
+In the absence of buoyantly-induced entrainment, \citet{brandenburg2016} suggests that the filling factor, $f$, of convective elements should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression.
 On the other hand, the filling factor of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth propagated.
-These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true propagation of a thermal in an appreciably stratified environment.
+These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true propagation of a numerically simulated thermal in an appreciably stratified environment.
 
-In this work, we extend the study of \citet{lecoanet&jeevanjee2018} to study the propagation of low-Mach number, cold thermals in stratified domains. 
+In this paper, we extend the study of \citet{lecoanet&jeevanjee2018} (hereafter \LJ) to study the propagation of low-Mach number, cold thermals in stratified domains. 
 We are specifically interested in how buoyant entrainment affects the scaling of the thermal radius, or filling factor, with depth. 
 If buoyant entrainment is a dominant effect, it is possible that entropy rain would simply grow too large and stall before reaching the bottom of the solar convection zone.
-On the other hand, if the compression effects suggested by \citet{brandenburg2016} are the dominant effect, then it is possible that these thermals could propagate to the bottom of the solar
-convection zone, or potentially shrink to a sufficiently small size where thermal dissipation is significant.
+On the other hand, if the compression effects suggested by \citet{brandenburg2016} are the dominant effect, then it is possible that these thermals could propagate to the bottom of the solar convection zone, and perhaps could be the nucleus of entropy rain.
 
 In section \ref{sec:theory}, we develop a theoretical description of thermals in a stratified domain. 
-In section \ref{sec:experiment}, we describe the experiments conducted in this work. 
-In section \ref{sec:results}, we compare the results of our experiments to the theory developed in section \ref{sec:theory}. 
+In section \ref{sec:experiment}, we describe the numerical experiments conducted in this work. 
+In section \ref{sec:results}, we compare our theory and simulation results. 
 Finally, in section \ref{sec:discussion}, we discuss what our results imply for the entropy rain hypothesis.
@@
 \subsection{Phenomenological description of thermal evolution}
-We show pictorally the evolution of cold thermalss from rest in Fig.~\ref{fig:evolution_colormeshes} for two different domains which span a different number of density scale heights ($n_\rho$). 
-In Fig.~\ref{fig:evolution_colormeshes}a, the evolution of a thermal in a weakly stratified domain with $n_\rho = 0.5$ density scale heights is shown. 
-In Fig.~\ref{fig:evolution_colormeshes}b, the evolution of a thermal in an appreciably stratified domain with $n_\rho = 3$ density scale heights is shown. 
+We show pictorally the evolution of cold thermals from rest in Fig.~\ref{fig:evolution_colormeshes} for two different domains which span a different number of density scale heights ($n_\rho$). 
+In Fig.~\ref{fig:evolution_colormeshes}a, the evolution of a thermal in a weakly stratified domain with $n_\rho = 0.5$ is shown. 
+In Fig.~\ref{fig:evolution_colormeshes}b, the evolution of a thermal in an appreciably stratified domain with $n_\rho = 3$ is shown. 
 In both cases, the thermal's initial conditions are spherical, dense, low entropy perturbations of equal magnitude whose diameters are 5\% of the domain depth.
-This dense sphere spins up into an axisymmetric vortex ring, and the vertical cross section through this vortex ring shows two circular vorticity \& entropy minima.
-We find that the $n_\rho = 0.5$ case entrains and grows with depth, similarly to the Boussinesq regime.
+This dense sphere spins up into an axisymmetric vortex ring, and the vertical cross section through this vortex ring shows two circular vorticity and entropy minima.
+We find that the $n_\rho = 0.5$ case entrains and grows with depth similarly to thermal behavior in the Boussinesq regime.
 On the other hand, the $n_\rho = 3$ case has a radius which remains approximately constant over time.
+
 The goal of this paper is to understand the evolution of the thermal in the vortex ring stage.
-All of the thermals studied in this work are laminar, similar to the Hill vortices studied by \citet{brandenburg2016}, but \citet{lecoanet&jeevanjee2018} showed that laminar theory describes the evolution of turbulent thermals well.
-We reserve studies of turbulent thermals in stratified domains for future work.
+All of the thermals studied in this work are laminar, similar to the Hill vortices studied by \citet{brandenburg2016}.
+Fortunately, \LJ\, showed that laminar theory describes the evolution of turbulent thermals well.
+As a result, we reserve studies of turbulent thermals in stratified domains for future work.
 
-In the following sections, we will use a description of the impulse and momentum of these thermals, as determined by their buoyant nature, to describe the evolution of their depth and radii with time.
+In the following sections, we will use a description of the impulse and momentum of dense vortex rings to describe the evolution of their depth and radii with time.
 
@@
 In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime by \citet{lecoanet&jeevanjee2018}. 
-We find that the inclusion of stratification adds the additional complexity of $r \propto \rho^{-1/2}$, such that downward-propogating vortex rings (as studied here) will entrain less than boussinesq thermals, and upward-propogating rings will entrain more.
+We find that the inclusion of stratification adds the additional complexity of $r \propto \rho^{-1/2}$, such that downward-propagating vortex rings (as studied here) will entrain less than boussinesq thermals, and upward-propagating rings will entrain more.
 In the absence of buoyancy ($B = 0$), this result aligns with the prediction for purely horizontal compression noted by \citet{brandenburg2016} of $r^2 \propto \rho^{-1}$.

### 2019-05-24 tex/stratified_thermals.tex
draft 2

@@
 \subsection{Evolution of momentum and impulse}
-The evolution of thermals as buoyant vortex rings has been well described in the unstratified, Boussinesq limit for decades \citep[see e.g.][for a description and sources]{lecoanet&jeevanjee2018}.
-Here we lay out a description of the momentum and impulse of the thermal which will later be used to describe thermal properties like radii and depth vs. time.
+The evolution of thermals as buoyant vortex rings has been well described in the unstratified, Boussinesq limit for decades (see e.g. \LJ\,for a description and references).
+While many descriptions of vortex rings assume that they evolve in a self-similar state, we will lay out a description of the momentum and impulse of the thermal and show how these quantities control the evolution of the vortex ring.
 
-In this work, we study an ideal gas and focus on the ideal, low Mach number regime in an adiabatically stratified atmosphere. 
+We study a fluid characterized by an ideal gas equation of state and focus on the ideal, low Mach number regime in an adiabatically stratified atmosphere. 
 In this regime, a linearized equation of state describes the thermodynamics well, and the fully compressible Euler momentum equation takes the form \citep{brown&all2012},
@@
 where $\bm{u}$ is the velocity, $\varpi = P_1 / \rho_0$ is the reduced pressure, $S = c_V\ln T - R\ln\rho$ is the specific entropy, and thermodynamics are broken down into background (subscript 0) and fluctuating (subscript 1) components.
-In this work we find it instructive to examine the full momentum, and so multiplying this equation by the density, we obtain,
+In this limit where the linearized equation of state is valid, $S_1 \approx c_V T_1/T_0 - R \rho_1/\rho_0$.
+In this work we find it instructive to examine the full momentum, and so multiplying this equation by the full density, we obtain,
 \begin{equation}
@@
 \end{equation}
-Hereafter we will define the total derivative, $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$, and we acknowledge that the Langrangian derivative commutes with a volume integral such that
+Hereafter we will define the total derivative, $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$, and we acknowledge that the Langrangian derivative commutes with a volume integral according to 
 \begin{equation*}
@@
 \end{equation*}
-assuming that the volume $\mathcal{V}$ is advected with the fluid.
+for a volume, $\mathcal{V}$, which is advected with the fluid.
 Volume-integrating Eqn.~\ref{eqn:rho_euler_momentum}, we thus find
@@
 \end{equation}
-At this point, we find it useful to define the total buoyancy,
+At this stage, it is useful to define the total buoyancy,
 \begin{equation}
@@
 \end{equation}
-as in the absence of viscosity and detrainment, this is a conserved quantity during thermal evolution (REFERENCE FIGURE). 
+as in the absence of viscosity and detrainment, this is a conserved quantity during thermal evolution (see e.g., Fig.~\ref{fig:constants}a). 
 Furthermore, in the Boussinesq limit, the work of \citet{tarshish&all2018} shows that pressure terms reduce the efficacy of the buoyancy in changing the momentum by effectively reducing the buoyant acceleration by some factor $\beta \sim 0.5$.
-As a result, we can approximate the growth of a thermal's momentum according to
+As a result, we approximate the growth of a thermal's vertical momentum according to
 \begin{equation}
@@
 
-After describing the growth of the thermal's integrated momentum with time, we turn our attention to the hydrodynamic impulse, which in the stratified limit is defined
-\citep{shivamoggi2010},
+We now turn our attention to the hydrodynamic impulse, which in the stratified limit can be expressed as \citep{shivamoggi2010},
 \begin{equation}
@@
 where $\bm{x}$ is the position vector. 
-Impulse is equivalent to the time-integrated work acting on the fluid resulting in the current fluid motion. 
+The hydrodynamic impulse is the time-integrated work which has acted on the fluid to result in the current fluid motion. 
 Per \citet{shivamoggi2010}, changes in the impulse can be expressed as
@@
 where, importantly, the \emph{eulerian} time derivative of the momentum is inside of the volume integral here. 
-Under the proper specification of boundary conditions, the integral term is zero, and the vertical impulse of a thermal thus straightforwardly changes in time as
+Under the proper specification of volumetric boundaries, the integral term is zero, and the vertical impulse of a thermal thus straightforwardly changes in time as
 \begin{equation}
@@
 \end{equation}
-where $r$ is the radius of the thermal from its axis of symmetry to the maxima of its buoyant signature, and $\Gamma = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the integrated circulation in a cross-section of the vortex ring.
-Through integration of the momentum equation, it can be shown that in the absence of viscous effects, changes in circulation in an axisymmetric vortex ring are
+where $r$ is the radius of the thermal from its axis of symmetry to the maxima of its buoyant signature, and $\Gamma = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the circulation in a cross-section of the vortex ring.
+Integrating the momentum equation in the absence of viscous effects shows that changes in circulation in an axisymmetric vortex ring are
 \begin{equation}
@@
 For the case of a vortex core in which the entropic signature is contained tightly in the core, as in Fig.~\ref{fig:evolution_colormeshes}, any contour which is drawn around the vortex core should conserve circulation in the absence of viscosity.
+As a result, we will treat the circulation of a developed vortex ring as a conserved quantity.
 
@@
     \caption{
-	Plotted are time traces for three quantities which we assume to be constant in our thermal theory. 
-	In (a) and (b), the circulation and buoyancy, divided by their maxima, are plotted vs. depth. 
-	We see that with increasing stratification, there is marginally more detrainment of both of these quantities, but to first order they are constant over the	evolution of the thermal. 
-	In (c) the constant $f = V/r^3$ is plotted; after significant noise during the development of the vortex ring, this quantity remains relatively constant, and increasingly approaches a constant with depth.
+	Evolution traces are shown for  three quantities which we assume to be constant in our parameterized thermal theory. 
+	The circulation (a) and buoyancy (b), divided by their parameterized value for each case (see Table \ref{table:parameters}), are plotted vs. depth. 
+	We see that with increasing stratification, there is marginally more detrainment of both of these quantities, but to first order they are constant over the	thermal's transit time. 
+	In (c) the volumetric constant $f$ is shown; after significant noise during the development of the vortex ring, this quantity settles toward a value of O(7) throughout the thermal's transit.
     \label{fig:constants} }
@@
 After spinning up, we assume that the thermal is characterized by a constant buoyant signature, $B_0$, and constant circulation, $\Gamma_0$.
-While these thermals began as initial spherical perturbations, they can be modeled as vortex rings which evolved from a ``virtual origin'' at which they had no radius. 
+While these thermals began as initial spherical perturbations, they can be modeled as having always been vortex rings which evolved from a ``virtual origin'' where the vortex ring is characterized by having a radius of zero.
 From this virtual origin, the vortex ring's momentum and impulse grow to a value of $M_0$ and $I_0$ at time $t = 0$ when the true thermal is released from rest.
@@
 I_z = \chi B_0 t + I_0.
-\label{eqn:impulse_line}
 \end{equation*}
 
-Following Eqn.~\ref{eqn:circulation}, we take $\Gamma_0$ to be constant, which is a decent assumption in our numerical experiments, see Fig.~\ref{fig:constants}b.
-Combining Eqns.~\ref{eqn:impulse_line} and \ref{eqn:impulse_approx}, we retrieve our first result,
+Combining this result with Eqn.~\ref{eqn:impulse_approx}, we retrieve our first result,
 \begin{equation}
@@
 \end{equation}
-In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime by \citet{lecoanet&jeevanjee2018}. 
+Following Eqn.~\ref{eqn:circulation}, and taking $\Gamma_0$ to be constant (which is a decent assumption in our numerical experiments, as in Fig.~\ref{fig:constants}b), we find that the radius grows with time but this growth is damped by increasing atmospheric density.
+In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime in \LJ. 
 We find that the inclusion of stratification adds the additional complexity of $r \propto \rho^{-1/2}$, such that downward-propagating vortex rings (as studied here) will entrain less than boussinesq thermals, and upward-propagating rings will entrain more.
@@
 
-The momentum can likewise be integrated like the impulse,
+The momentum can likewise be simply integrated,
 \begin{equation*}
@@
 \end{equation*}
-For the proper choice of vertical velocity, $w_{\text{th}}$, and volume, $\mathcal{V}$, the momentum can be expressed precisely as 
+For the proper choice of vertical velocity, $w_{\text{th}}$, and volume, $\mathcal{V}$, the momentum is also precisely 
 \begin{equation*}
-M_z = \rho \mathcal{V} w_{\text{th}},
+M_z = \rho \mathcal{V} w_{\text{th}}.
 \end{equation*}
-and the volume can be approximated as $\mathcal{V} = f r^3$, where $f$ is a parameter which we take to be constant. 
+We approximate the volume as $\mathcal{V} = f r^3$, where $f$ is a parameter which we take to be constant. 
 This assumption is perhaps not as perfect as the assumptions of constant $B_0$ or $\Gamma_0$ (see Fig.~\ref{fig:constants}c), but it is nevertheless not a bad assumption. 
-Combining our approximate expressions, and inserting our theoretical description of $r$ (Eqn.~\ref{eqn:r_theory}), we retrieve
+Combining our approximate expressions, and using our theoretical description of $r$ (Eqn.~\ref{eqn:r_theory}), we retrieve
 \begin{equation}
@@
 \end{equation}
-Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and making the assumption that the vortex ring starts at a ``virtual origin'' (CITE) at $t = 0$ where it has no impulse or momentum ($I_0 = M_0 = 0$), an integrable expression for the evolution of thermal position over time can be retrieved,
+Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and making the assumption that the vortex ring is at the virtual origin at $t = 0$ so that $I_0 = M_0 = 0$, an integrable expression for the evolution of thermal position over time can be retrieved,
 \begin{equation}
@@
 \end{equation}
-If the atmospheric stratification in which the thermal is falling is known, this result can be integrated with $\rho(z_{\text{th}})$ plugged in in order to find the position of the thermal as a function of time.
-We leave this result general for now, and will integrate it using the polytropic stratification used in our simulations at the end of section \ref{sec:experiment}.
+If the atmospheric stratification in which the thermal is falling is known, this result can be integrated with the known profile of $\rho(z_{\text{th}})$ in order to find the position of the thermal as a function of time.
+We leave this result general for now, and will integrate it using the polytropic stratification used in our simulations in the next section.
 
 \subsection{Solution for thermal evolution in a Polytrope}
-Throughout this work we will study a polytrope, as is specified later in Eqn.~\ref{eqn:polytrope}.
-Integrating Eqn.~\ref{eqn:dz_theory} with this specific density stratification, we find
+In this work, we study an ideal gas whose equation of state is $P = \rho T$ and whose stratification is a perfectly adiabatic polytrope,
+\begin{gather}
+T_0 = 1 + (\grad_{\text{ad}})(z - L_z), \\
+\rho_0 = T_0^{\,m_{\text{ad}}},
+\label{eqn:polytrope}
+\end{gather}
+where $m_{\text{ad}} = (\gamma-1)^{-1}$, and where the adiabatic temperature gradient in our nondimensional systems (see section \ref{sec:experiment}) is $\grad_{\text{ad}} \equiv g(e^{n_\rho/m_{\text{ad}}} - 1)/(L_z c_P)$, with $g = m_{\text{ad}} + 1$ and $L_z = 20$ is the nondimensional depth of the atmosphere in units of thermal diameters.
+
+Integrating Eqn.~\ref{eqn:dz_theory} under this polytropic density stratification and assuming $m_{\text{ad}} < 2$, we find
 \begin{equation}
@@
 \end{equation}
-where $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma^3/(\chi B)}$, the temperature at the virtual origin is $T_0 = 1 + \grad_{\text{ad}}(z_0 - L_z)$, $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and assuming that the polytropic index is $m_{\text{ad}} < 2$ (which is valid for our case of $m_{\text{ad}} = 1.5$ studied here).
-In the limit of large stratification, we thus find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
+where $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma^3/(\chi B)}$ and the temperature at the virtual origin is $T_0 = 1 + \grad_{\text{ad}}(z_0 - L_z)$.
+The virtual origin is located at $z = z_0$ and $t = -t_{\text{off}}$ in simulation units, which are the height and time a which the vortex ring would have had zero radius in the absence of a spin-up phase.
+The constant $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
 
 The thermal is initialized as a uniform sphere of dense fluid, and it quickly spins up into a vortex ring. 
-While we do not attempt to model the spin-up phase in this paper, it can be parameterized by the buoyancy $B_0$, circulation $\Gamma$, as well as the virtual origin $z_0$, and temporal offset $t_off$ which are the height and time a which the vortex ring would have had zero radius in the absence of a spin-up phase.
+While we do not attempt to model the spin-up phase in this paper, it can be parameterized by the buoyancy $B_0$, circulation $\Gamma_0$, as well as the virtual origin $z_0$, and temporal offset $t_{\text{off}}$.
 Our theory also involves the volumetric aspect ratio of the thermal $f$, the detrainment fraction $\chi$, and the effective buoyancy $\beta$. 
@@
 \label{sec:experiment}
+%In this work, we primarily study the evolution of 2D, azimuthally symmetric, anelastic thermals in cylindrical coordinates. 
+As a result of our theory being largely derived in the anelastic, axisymmetric limit, we have chosen to focus the bulk of our attention on our 2D, axisymmetric anelastic simulations.
+We choose to focus on 2D simulations, as they allow us to more easily study high density stratifications using highly reproducible simulations whose computational expense is low.
+We verify that select anelastic simulations produce the same results as 3D fully compressible simulations in cartesian domains.
+
+While natural processes are very turbulent, we have chosen to study the evolution of laminar thermals here. 
+As we are not aware of a developed laminar theory in the stratified regime in the literature, like the one developed here, it is useful to restrict our study to the laminar case to determine the validity of our theory.
+Furthermore, \LJ\, showed in the Boussinesq limit that the measured entrainment of turbulent thermal vortex rings is well described by laminar theory, and we have no reason to believe that result should not hold for the stratified case.
+As a result, we leave studies of turbulent thermals to future work.
 
 \subsection{Anelastic Simulations}
-In this work, we primarily study the evolution of 2D, azimuthally symmetric, anelastic thermals in cylindrical coordinates. 
-We later verify that select simulations produce the same results as 3D fully compressible simulations in cartesian domains (see sec. REF). 
 The LBR anelastic equations are \citep{lecoanet&all2014},
@@
 \end{gather}
-where $\grad_{\text{ad}} \equiv g(e^{n_\rho/m_{\text{ad}}} - 1)/(L_z c_P)$ and $\lilstressT$ is the viscous stress tensor in units of inverse time.
+where $\lilstressT$ is the viscous stress tensor in units of inverse time.
 In our azimuthally symetric domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$.
@@
 The timescale is thus the freefall crossing time of this unit length. 
-These atmospheres are fully specific in terms of the Reynolds number and Prandtl number,
+These equations are then fully specified in terms of the Reynolds number and Prandtl number,
 \begin{equation}
-\text{Re} = \frac{u_{th} L_{th}}{\nu}, \qquad
-\text{Pr} = \frac{u_{th} L_{th}}{\chi}, \qquad
-u_{th}^2 = \frac{g L_{th} \Delta s}{c_P},
+\text{Re} = \frac{ u_{\text{th}} L_{\text{th}}}{\nu}, \qquad
+\text{Pr} = \frac{ u_{\text{th}} L_{\text{th}}}{\chi}, \qquad
+u_{\text{th}}^2 = \frac{g L_{\text{th}} \Delta s}{c_P},
 \end{equation}
-where $u_{th}$ is the freefall velocity, $L_{th}$ is the thermal length scale, and
+where $u_{\text{th}}$ is the freefall velocity, $L_{th}$ is the thermal length scale, and
 $\Delta s$ is the magnitude of the specific entropy signature of the thermal.
@@
 
-\subsection{Atmosphere \& Initial conditions}
-We study an ideal gas whose equation of state is $P = \rho T$ and whose stratification is a perfectly adiabatic polytrope,
-\begin{gather}
-T_0 = 1 + (\grad_{\text{ad}})(z - L_z) \\
-\rho_0 = T_0^{\,m_{\text{ad}}},
-\label{eqn:polytrope}
-\end{gather}
-where $m_{\text{ad}} = (\gamma-1)^{-1}$, and the adiabatic temperature gradient in these nondimensional atmospheres is set with $g = m_{\text{ad}} + 1$ and $\tilde{L}_{\text{th}} = (e^{n_\rho/m_{\text{ad}}} - 1)/L_z$, where $n_\rho$ is the number of density scale heights spanned by the atmosphere and $L_z = 20$ is the nondimensional depth of the atmosphere in units of thermal diameters.
-
+\subsection{Initial conditions}
 To initialize the simulation, we specify a spherical initial specific entropy perturbation,
 \begin{equation}
-S_1 = - \frac{A}{2}\left[1 - \text{erf}\left(\frac{r' - r_{th}}{\delta}\right)\right],
+S_1 = - \frac{1}{2}\left[1 - \text{erf}\left(\frac{r' - r_{\text{th}}}{\delta}\right)\right].
 \label{eqn:thermal_IC}
 \end{equation}
-where $A = 1$ for our scaled equations.
-Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3r_{\text{th}}$, with the thermal radius set as $r_{th} = 0.5$, and a smoothing width, $\delta = 0.1$.
+Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3r_{\text{th}}$, with the thermal radius set as $r_{\text{th}} = 0.5$, and a smoothing width, $\delta = 0.1$.
+As mentioned previously, Re = 600 and Pr = 1 are specified at the thermal's initial depth, $z = z_0$.
 
@@
 \begin{equation}
-\ln\rho_1 = S_1/c_P, \qquad T_1 = T_0(e^{-\ln\rho_1} - 1).
+\ln\rho_1 = S_1/c_P, \qquad T_1 = T_0(e^{-\epsilon\ln\rho_1} - 1)/\epsilon.
 \end{equation}
@@
 \subsection{Numerics}
-We evolve our simulations forward in time using the  Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \citep{burns&all2016} to time-evolve our equations. 
-For our 2D simulations, we use using an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997}, and for our 3D simulations we use the second order semi-implicit backward differentiation formulation SBDF2 \citep{wang&ruuth2008}.
+We evolve our simulations forward in time using the  Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \citep{burns&all2016} [CITE THE METHODS PAPER]. 
+For our 2D simulations, we use using an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997}, and for our 3D simulations we use the second-order semi-implicit backward differentiation formulation SBDF2 \citep{wang&ruuth2008}.
 
-Our 3D simulations are decomponsed on Fourier bases in the horizontal directions ($x, y \in [-L_r, L_r]$) and Chebyshev bases vertically ($z \in [0, L_z]$) with impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries ($T_1 = w = \partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
-Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of $\partial_r S_1 = u_r = w = 0$ at $r = L_r$.
+Our 3D simulations are decomposed on Fourier bases in the horizontal directions ($x, y \in [-L_r, L_r]$) and Chebyshev bases vertically ($z \in [0, L_z]$) with impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries ($T_1 = w = \partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
+Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of $\partial_r S_1 = w = (\grad\times\bm{u})_\phi = 0$ at $r = L_r$.
 
-As a result of our theory being largely derived in the anelastic, axisymmetric limit, we have chosen to focus the bulk of our attention on our 2D, axisymmetric anelastic simulations.
-Furthermore, the 2D nature of these simulations allows us to much more feasibly study high density stratifications using fewer computational resources.
-The 3D fully compressible simulations serve primarily as a verification of the anelastic results in the low Mach number regime in which the anelastic constraint is not explicitly true, and in the 3D case where axisymmetry is not baked into the equations.
-
-While natural processes are very turbulent, we have chosen to study the evolution of laminar thermals here. 
-\citet{lecoanet&jeevanjee2018} showed for an ensemble of laminar and turbulent thermals that the measured entrainment of the evolved vortex rings in the turbulent case is well described by laminar theory.
-As we are not aware of a developed laminar theory in the stratified regime in the literature, like the one developed here, we have restricted the simulations in this work to the laminar regime in order to test our new theory in the regime where it should be transparent to verify its validity.
+All of the code used to perform the simulations in this work can be found online in the supplementary materials in a Zenodo repository (CREATE AND CITE REPO).
 
@@
 \label{sec:results}
-The measured values of these parameters for the cases studied in this paper are presented in table \ref{table:parameters}.
+The measured values of each of the parameters described in section \ref{sec:theory} for each of our simulations  \ref{sec:theory} for each of our simulations  \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
+As anticipated, $\beta$ is O(0.5) and $\chi$ is O(1), with both decreasing slightly in value with increasing stratification, which is perhaps unsurprising in light of Fig.~\ref{fig:constants}.
+In all cases, the buoyancy $B_0$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
+In our nondimensional units, we also find that the circulation is O(-2) for each of our cases, and decreases with increasing stratification (and decreasing vortex size).
 
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$T_0$} & \colhead{$t_{\text{off}}$} & \colhead{$B$} & \colhead{$\Gamma$} & \colhead{$f$} & \colhead{$\chi$} & \colhead{$\beta$}	}	
+\colhead{$n_\rho$} & \colhead{$T_0$} & \colhead{$t_{\text{off}}$} & \colhead{$B_0$} & \colhead{$\Gamma_0$} & \colhead{$f$} & \colhead{$\chi$} & \colhead{$\beta$}	}	
 \startdata																																															
@@
 \enddata																																															
-\tablecomments{ Values from fully compressible simulations have been rescaled in post-processing for direct comparison with 2D anelastic cases}
+\tablecomments{ }
 \end{deluxetable*}
@@
     \caption{
-	Shown are the measured depths of thermals as a function of time for all 2D Anelastic and 3D Fully compressible simulations conducted in this work. 
-	Overplotted is the theoretical prediction for depth as a function of time.
-    \label{fig:results_d_v_t} }
+	The measured depths of thermals as a function of time for all 2D Anelastic and 3D Fully compressible simulations conducted in this work are shown in (a).
+	The corresponding thermal velocities as a function of depth are shown in (b)
+	Overplotted in a thin solid line for each case are our theoretical predictions from section \ref{sec:theory} given the parameters in table \ref{table:parameters}.
+    \label{fig:results_panels} }
 \end{figure}
@@
     \caption{
-	Measured values of (a) depth vs. time and (c) radius vs. depth are plotted for both the 2D anelastic and 3D fully compressible simulations. 
-	The fractional difference between anelastic and fully compressible results are respectively shown in (b) and (d).
+	Measured values of radius vs. depth are plotted for both the 2D anelastic and 3D fully compressible simulations in (a). 
+	For completeness, we also include the cases in which we only studied the 2D anelastic simulations.
+	For the cases in which only the anelastic equations were solved, the theory is overplotted in a thin solid line, and similar agreement between simulations and theory is found for the cases where both equations sets were used.
+	The fractional difference between anelastic and fully compressible results are shown in (b).
     \label{fig:diff} }
@@
 
-In Fig. \ref{fig:results_d_v_t}, we show the measured depth $d_{\text{th}} = L_z - z_{\text{th}}$ of the thermal as a function of time for low and high stratification. 
+In Fig. \ref{fig:results_panels}a, we show the measured depth $d_{\text{th}} = L_z - z_{\text{th}}$ of the thermal as a function of time for low and high stratification. 
 At very low stratification (e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
@@
 
-In Fig.~\ref{fig:results_vs_depth}a, we plot the measured thermal radius vs. depth, with the theoretical predictions of Eqns.~\ref{eqn:r_theory} \& \ref{eqn:theory_z} plotted as lines over the data. 
+In Fig.~\ref{fig:results_panels}b, we show the corresponding thermal velocity as a function of depth with the theory overplotted again.
+As anticipated, low density ($n_\rho = 0.1$) thermals deccelerate with depth.
+We find that with increasing stratification, this decceleration stops and sufficiently stratified runs ($n_\rho \geq 3$) experience acceleration of the thermal.
+
+In Fig.~\ref{fig:diff}a, we display measured thermal radius vs. depth, with a detailed comparison of our 2D Anelastic and 3D Fully Compressible cases. 
 In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, aligning with the Boussinesq limit shown in \citet{lecoanet&jeevanjee2018}.
-This growth of the thermal is the result of entrainment of environmental fluid and results an an accompany decceleration like $w \propto d^{-1}$ in the Boussinesq limit, as is shown in Fig.~\ref{fig:results_vs_depth}b.
-However, as stratification increases, the thermal entrains less environmental fluid and expands less, eventually even contracting with depth in the high-stratification limit. 
-This lessened entrainment is, unsurprisingly, accompanied by greater acceleration of the thermal.
-As in the case of depth vs. time, the overplotted theoretical predictions show excellent agreement with the measured data.
+This growth of the thermal is the result of entrainment of environmental fluid and accompanies decceleration like $w \propto d^{-1}$ in the Boussinesq limit, as is shown in Fig.~\ref{fig:results_panels}b.
+However, as stratification increases, the thermal entrainment of environmental fluid decreases and it experiences less expansion.
+In the limit of large stratification ($n_\rho \geq 3$), thermals begin contracting with depth.
+This lessened entrainment is, unsurprisingly, accompanied by greater acceleration of the thermal (Fig.~\ref{fig:results_panels}).
 
-\subsection{Verification of 2D Anelastic approximation}
-In Fig.~\ref{fig:diff}, we display in more detail a comparison of our 2D Anelastic and 3D Fully Compressible cases. 
-In Fig.~\ref{fig:diff}a, depth vs time is shown, and the fractional difference between FC and AN cases is shown in Fig.~\ref{fig:diff}b.
-Differences between the two cases are $\leq 2$\% for all times, with greater error towards the end of the simulations as the FC simulations begin to interact with the impenetrable boundary at the bottom of their simulation domains.
-In Fig.~\ref{fig:diff}c, radius vs. depth is shown, and the fractional difference between FC and AN cases is shown in Fig.~\ref{fig:diff}d. 
-Aside from the very end of the simulation when the FC boundary conditions begin to matter, there is remarkable agreement between the two cases, with $< 1$\% differences between the two cases after early times in which the thermal is still developing into a vortex ring.
-
-This close agreement between low Mach number Fully Compressible simulations and Anelastic simulations parallels the agreement between the equation sets seen in \citet{lecoanet&all2014}, and gives us confidence in our anelastic results at higher levels of stratification, where the 2D simulations are much more numerically feasible than the 3D fully compressible simulations.
+In Fig.~\ref{fig:diff}b, the fractional difference in radius vs. depth between 3D FC and 2D AN cases is shown for the $n_\rho = [0.5, 1, 2]$ cases studied here. 
+Aside from early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the impenetrable boundary at the bottom of the domain, the 2D anelastic and 3D fully compressible simulations agree surprisingly well.
+We find differences in the radius of less than 1\% throughout the bulk of the thermal evolution for the cases studied here.
+This gives us confidence that our high stratification anelastic simulations are producing reliable results.
+Furthermore, this close agreement between low Mach number Fully Compressible simulations and Anelastic simulations parallels the agreement between the equation sets seen in \citet{lecoanet&all2014}.
 
@@
 \label{sec:discussion}
-In this paper we extended the theory of thermal entrainment to include stratification, and showed that theory predicts that dense thermals will experience less entrainment than boussinesq thermals due to increasing atmospheric density with depth.
+In this paper we developed a simple theory of the evolution of buoyant (or dense) vortex rings in stratified atmospheres.
+We showed that this theory predicts that dense thermals will experience less entrainment than boussinesq thermals due to increasing atmospheric density with depth.
 We performed 2D anelastic simulations of thermal evolution for varying degrees of stratification and showed that our parameterized theory describes the evolution of thermals in these systems remarkably well.
-Furthermore, we verified the validity of our anelastic simulations with select 3D fully compressible simulations of thermal evolution.
+Furthermore, we verified the validity of our anelastic simulations with select 3D fully compressible simulations of thermal evolution and found agreement to under 1\%.
 
-We note that the evolution of dense thermals in stratified domain is complex, and neither the assumption of horizontal compression \citep[as in e.g.][]{brandenburg2016} or the evolution of thermals in the Boussinesq regime fully describes the behavior of these events fully.
+We note that the evolution of dense thermals in stratified domains is complex, and neither the assumption of horizontal compression \citep[as in e.g.][]{brandenburg2016} or the evolution of thermals in the Boussinesq regime (as in \LJ) fully describes the behavior of these events fully.
 Rather, results fall somewhere in between, and theory and simulations suggest that there are two regimes of downflowing thermal behavior:
@@
 \appendix
+\section{Thermal Radius and Height measurements}
+\label{appendix:radius}
+Throughout this work, we frequently report the thermal's radius or its depth.
+We measure the thermal's radius and height as the radius from the axis of symmetry and the height from the bottom of the domain at which the thermal's vortex core is located.
+To measure this, we locate the maxima of the entropy.
+To find the entropy maxima vertically, we integrate $\int\rho S_1 r dr$ in our Dedalus domain, then use the spectral data of that profile to sample it on a 4096 point grid vertically, and we take the location of the minima on that grid to be the thermal height.
+To find the entropy maxima horizontally, we integrate $int \rho S_1 dz$ in our Dedalus domain, then sample the spectral data onto a 2048-point radial grid, and take the minima of that profile to be the radius of the thermal.
+In order to find the thermal's velocity as a function of time, we use a five-point stencil to differentiate the thermal's depth, $d$,
+$$
+w_{\text{th}}(t) = \frac{d }{dt}d_{\text{th}}(t) = \frac{-d_{\text{th}}(x + 2\Delta t) + 8d_{\text{th}}(t + \Delta t) - 8 d_{\text{th}}(t - \Delta t) + d_{\text{th}}(t - 2\Delta t)}{12\Delta t}
+$$
+
 \section{Thermal Tracking}

### 2019-05-24 code/AN_2D_thermal.py
lots of small improvements to 2D thermal code

@@ -113,13 +113,12 @@ logger.info('saving files in {:s}'.format(data_dir))
 #####################
 # Dedalus simulation
 #####################
-z_basis = de.Fourier('z', nz, interval=(0, Lz), dealias=3/2)
+z_basis = de.Fourier(  'z', nz, interval=(0, Lz), dealias=3/2)
 r_basis = de.Chebyshev('r', nr, interval=(0, Lr), dealias=3/2)
 domain = de.Domain([z_basis, r_basis], grid_dtype=np.float64)
 
 problem = de.IVP(domain, variables=['u', 'w', 'ur', 'wr', 'S1', 'S1r', 'p'])
 problem.meta['u', 'ur', 'w', 'wr', 'S1', 'S1r', 'p']['r']['dirichlet'] = True
-problem.parameters['u_phi'] = problem.parameters['u_phir'] = 0
 
 problem.parameters['pi']         = np.pi
 problem.parameters['Lz']         = Lz
@@ -136,14 +135,22 @@ problem.parameters['Lnondim']    = -grad_T_ad #scaling factor from unscaled poly
 problem.substitutions['T']            = '(1 + grad_T_ad*(z - Lz))'
 problem.substitutions['ln_rho0']      = '(m_ad*log(T))'              
 problem.substitutions['T0']           = '(T)'
-problem.substitutions['rho0']         = '((T)**(m_ad))'              
+problem.substitutions['rho0']         = '(T**m_ad)'              
 problem.substitutions['ln_rho0_z']    = '(m_ad*grad_T_ad/T)'         
+problem.substitutions['ln_rho0_z_less_top']    = '(m_ad*grad_T_ad*(1/T - 1))'         
 problem.substitutions['ln_rho0_zz']   = '(-m_ad*grad_T_ad**2/T**2)'  
 problem.substitutions['ln_T0_z']      = '(grad_T_ad/T)'              
+problem.substitutions['T_bot']        = '(1 - grad_T_ad*Lz)'              
+problem.substitutions['rho_bot']      = '(T_bot**m_ad)'              
+problem.substitutions['ln_rho0_z_top']    = '(m_ad*grad_T_ad)'         
+problem.substitutions['ln_rho0_z_bot']    = '(m_ad*grad_T_ad/T_bot)'         
[…]

### 2019-05-24 code/logic/post_processing.py

@@ -65,7 +65,7 @@ class DedalusIntegrator():
     """
     A simple class for post-processing thermal data
     """
-    def __init__(self, nr, nz, Lr, Lz, *args, r_cheby=False, **kwargs):
+    def __init__(self, nr, nz, Lr, Lz, *args, r_cheby=False, twoD=False, **kwargs):
         """
         Initialize the domain. Sets up a 2D (z, r) grid, with chebyshev
         decomposition in the z-direction and fourier decomposition in the r-direction.
@@ -81,8 +81,9 @@ class DedalusIntegrator():
         """
         self.Lz, self.Lr = Lz, Lr
         if r_cheby:
+            bounds = (0, Lz)
             self.r_basis = de.Chebyshev('r', nr, interval=(0,Lr))
-            self.z_basis = de.Fourier('z', nz, interval=(0, Lz))
+            self.z_basis = de.Fourier('z', nz, interval=bounds)
             self.domain = de.Domain([self.z_basis, self.r_basis], grid_dtype=np.float64)
             self.r              = self.domain.grid(1)
             self.z              = self.domain.grid(0)
@@ -260,6 +261,7 @@ class ThermalPostProcessor():
             s1  = f['tasks']['S1'].value * self.s_factor
             w   = f['tasks']['w'].value  * self.L_factor/self.t_factor
             u   = f['tasks']['u'].value  * self.L_factor/self.t_factor
+#            V   = f['tasks']['p'].value  
             V   = f['tasks']['V'].value  / self.t_factor
             r   = f['scales']['r']['1.0'].value * self.L_factor 
             z   = f['scales']['z']['1.0'].value * self.L_factor 
@@ -304,7 +306,7 @@ class ThermalPostProcessor():
             r, z, rr, zz, s1, w, u, V = self.read_file(fn)
 
             if filenum == 0:
-                integrator = DedalusIntegrator(len(r), len(z), self.Lr, self.Lz, self.grad_T_ad, self.m_ad, r_cheby=True)
+                integrator = DedalusIntegrator(len(r), len(z), self.Lr, self.Lz, self.grad_T_ad, self.m_ad, r_cheby=True, twoD=self.twoD)
                 count           = 0
                 contours        = np.zeros((len(self.times), len(z)))
                 radius = np.zeros_like(self.times)
@@ -575,7 +577,7 @@ class ThermalPostProcessor():
                 r, z, rr, zz, s1, w, u, V = self.read_file(fn)
 
[…]

### 2019-05-24 code/plotting/constants.py

@@ -1,5 +1,11 @@
 import matplotlib
 matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import numpy as np
@@ -7,7 +13,7 @@ import h5py
 
 aspect = [0.35, 0.35, 0.25, 0.25, 0.25, 0.25]
 CASES = [0.1, 0.5, 1, 2, 3, 4]
-ROOT_DIR='../good_2D_runs/'
+ROOT_DIR='../weird_form_good_2D_runs/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
 height, width = 4, 3.25 
@@ -26,7 +32,7 @@ fig = plt.figure(figsize=(width, height))
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 cax = plt.subplot(gs.new_subplotspec(*((0, 0), 50, 1000)))
 
-norm = matplotlib.colors.Normalize(vmin=1, vmax=len(DIRS))
+norm = matplotlib.colors.Normalize(vmin=0, vmax=len(DIRS))
 sm   = plt.cm.ScalarMappable(cmap='viridis_r', norm=norm)
 sm.set_array([])
 
@@ -39,36 +45,41 @@ for i, direc in enumerate(DIRS):
     r, d     = f['vortex_radius'].value, 20 - f['vortex_height'].value
     f.close()
 
+
+    fit_f = h5py.File('{:s}/thermal_analysis/fit_file.h5'.format(direc), 'r')
+    Gamma0, B0 = fit_f['Gamma0'].value, fit_f['B0'].value
+    fit_f.close()
+
     color = sm.to_rgba(i+1)
[…]

### 2019-05-24 code/plotting/diff_AN_FC.py

@@ -1,19 +1,33 @@
 import matplotlib
 matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import numpy as np
 import h5py
 
+NRUNS=6
+
+
+
 aspect = [0.35, 0.25, 0.25]
 CASES = [0.5, 1, 2]
-TOFF  = [0.704, 1.09, 1.26]
-ROOT_DIR='../good_2D_runs/'
+ROOT_DIR='../weird_form_good_2D_runs/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
+
+aspect_2D = [0.35, 0.25, 0.25]
+CASES_2D = [0.1, 3, 4]
+color_dir = [1, 5, 6]
+DIRS_2D=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES_2D, aspect_2D)] 
 
 CASES_3D = [0.5, 1, 2]
 AR_3D    = [0.5, 0.4, 0.35]
-TOFF_3D  = [0.583, 1.26, 1.53]
 THREED_DIR = '../good_3D_runs/'
 DIRS_3D=['{:s}FC_3D_thermal_Re6e2_Pr1_eps1.00e-4_nrho{}_aspect{}/'.format(THREED_DIR,nrho, ar) for nrho, ar in zip(CASES_3D, AR_3D)] 
 dict_3D = {}
@@ -21,27 +35,37 @@ for i in range(len(CASES_3D)):
     dict_3D[CASES_3D[i]] = DIRS_3D[i]
 
 
-height, width = 2.5, 6.5 
+height, width = 2.5, 3.25 
 
 gs = gridspec.GridSpec(1000, 1000)
[…]

### 2019-05-24 code/plotting/evolution_colormeshes.py

@@ -1,7 +1,14 @@
 import matplotlib
 matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
+from scipy.interpolate import interp1d
 import numpy as np
 import h5py
 
@@ -55,6 +62,7 @@ for i, ax in enumerate(axs):
         if i == 0 and j == 0:
             bar = plt.colorbar(c, cax=cax, orientation='horizontal')
             cax.xaxis.set_ticks_position('top')
+            bar.set_label(r'$\rho S_1 r^3$', labelpad=-38)
         x_max = 5
         if j == len(dirs[i])-2:
             max_contours = contours.max(axis=1)
@@ -69,13 +77,16 @@ for i, ax in enumerate(axs):
             zs_contours = [z.flatten()[ind] for ind in max_contours_args]
             ax.plot(max_contours, zs_contours, c='k', lw=0.25)
             ax.plot(-max_contours, zs_contours, c='k', lw=0.25)
-
-            for j in range(4):
-                base = int((j+1)*np.floor(len(max_contours-2)/5))
-                dx = max_contours[base + 2] - max_contours[base]
-                dy =  zs_contours[base + 2] - zs_contours[base]
-                ax.arrow( max_contours[base], zs_contours[base],   dx,  dy, shape='full', lw=0, length_includes_head=True, head_width=0.25, color='black')
-                ax.arrow(-max_contours[base], zs_contours[base], -(dx), dy, shape='full', lw=0, length_includes_head=True, head_width=0.25, color='black')
+           
+            contour_f = interp1d(zs_contours, max_contours)
+            heights = [17, 14, 11, 8, 5, 2]
+            dy = -0.5
+            for h in heights:
+                this_r = contour_f(h)
+                next_r = contour_f(h+dy)
+                dx = next_r-this_r
[…]

### 2019-05-24 code/plotting/overview_fig.py

@@ -1,5 +1,11 @@
 import matplotlib
 matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import numpy as np
@@ -78,15 +84,17 @@ nrho_001_r_no_buoy = theory_r(times, 0, -1/2, nrho_001[3], nrho_001[-2], rho_f=i
 ind_001 = nrho_001_d[nrho_001_d > 2][0] == nrho_001_d
 ind_3 = nrho_3_d[nrho_3_d > 2][0] == nrho_3_d
 plt.plot(nrho_001_d, (nrho_001_d/nrho_001_d[ind_001])**2, c='black', lw=0.5)
-ax.text(2.5, 5, r'$f \propto d^2\,\mathrm{(Boussinesq, LJ19)}$', fontsize=10)
 plt.plot(nrho_3_d, (nrho_3_r/nrho_3_r[ind_3])**2, c='k', lw=1.5)
 plt.plot(nrho_3_d, (nrho_3_r_no_buoy/nrho_3_r_no_buoy[ind_3])**2, c='black', lw=0.5)
-ax.text(2.5, 1.5e-1, r'$f \propto \rho^{-1}\,\mathrm{(Horizontal compression, B16)}$', fontsize=10)
 plt.yscale('log')
 plt.ylabel(r'$f = r^2$')
 plt.xlabel('Depth')
 plt.xlim(2, 20)
+plt.ylim(5e-2, 1e2)
 
 
+ax.text(14, 52, r'$f \propto d^2\,\mathrm{(LJ19)}$', rotation=12)
+ax.text(11.5, 1.2, r'$\mathrm{simulation}\,(n_\rho=3)$', rotation=-2)
+ax.text(14, 2.2e-1, r'$f \propto \rho^{-1}\,\mathrm{(B16)}$', rotation=-7)
 
 fig.savefig('overview_fig.png', dpi=300, bbox_inches='tight')

### 2019-05-24 code/plotting/results_panels.py

@@ -1,5 +1,11 @@
 import matplotlib
 matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import numpy as np
@@ -7,7 +13,7 @@ import h5py
 
 aspect = [0.35, 0.35, 0.25, 0.25, 0.25, 0.25]
 CASES = [0.1, 0.5, 1, 2, 3, 4]
-ROOT_DIR='../good_2D_runs/'
+ROOT_DIR='../weird_form_good_2D_runs/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
 CASES_3D = [0.5, 1, 2]
@@ -18,106 +24,66 @@ dict_3D = {}
 for i in range(len(CASES_3D)):
     dict_3D[CASES_3D[i]] = DIRS_3D[i]
 
-
 height, width = 2.5, 3.25 
 
 gs = gridspec.GridSpec(1000, 1000)
-fig = plt.figure(figsize=(width, height))
-ax  = plt.subplot(gs.new_subplotspec((100, 0), 900, 1000))
-cax = plt.subplot(gs.new_subplotspec((0,   0), 100, 1000))
+fig = plt.figure(figsize=(width, height*2))
+cax = plt.subplot(gs.new_subplotspec((30,   0), 50, 1000))
+ax1 = plt.subplot(gs.new_subplotspec((100,  0), 380, 1000))
+ax2 = plt.subplot(gs.new_subplotspec((620,  0), 380, 1000))
 
-norm = matplotlib.colors.Normalize(vmin=1, vmax=len(CASES))
+norm = matplotlib.colors.Normalize(vmin=0, vmax=len(CASES))
 sm   = plt.cm.ScalarMappable(cmap='viridis_r', norm=norm)
 sm.set_array([])
 
[…]

### 2019-05-28 code/AN_2D_thermal.py
minor changes to align code with paper version

@@ -6,12 +6,6 @@ on a freefall velocity scale with the length scale set by the diameter of the th
 This code must be used with a version of Dedalus after commit  0128fa0 by Keaton Burns 
 on 2019-02-21, such that the problem.add_equation() function has the 'tau' keyword.
 
-A 'Buoyancy time' is the freefall timescale if the length were set as the domain depth,
-rather than the thermal depth. In our nondimensional units, if the domain depth is
-Lz, t_b = sqrt(Lz), and in general it takes ~12 buoyancy times for a "boussinesq" thermal
-to cross the domain (e.g., n_rho = 0.01), whereas more stratified thermals take less time
-(e.g., at n_rho = 2, it takes about 7 buoyancy times to cross the domain).
-
 Usage:
     AN_2D_thermal.py [options]
 
@@ -23,7 +17,7 @@ Options:
     --nr=<n>              Number of r coefficients [default: 128]
 
     --wall_hours=<t>      Number of wall hours to run for max [default: 7.5]
-    --run_time_buoy=<rt>  Number of buoyancy times to run for [default: 10.0]
+    --run_time_buoy=<rt>  Number of buoyancy times to run for [default: 60]
 
     --aspect=<a>          Domain runs from [0, Lr], with Lr = aspect*Lz [default: 0.25]
     --label=<l>           an optional string at the end of the output directory for easy identification
@@ -33,8 +27,8 @@ Options:
     --Lz=<L>              The depth of the domain, in thermal diameters [default: 20]
 
     --chi_nu              If true, use a constant diffusivity (rather than constant dynamic diffusivity) eqn formulation
-    --safety=<s>          Safety factor base [default: 0.08]
-    --out_cadence=<o>     Time cadence of output saves in buoyancy times [default: 0.08]  
+    --safety=<s>          Safety factor base [default: 0.1]
+    --out_cadence=<o>     Time cadence of output saves in buoyancy times [default: 0.35]  
 
     --restart=<file>      Name of file to restart from, if starting from checkpoint
 
@@ -79,7 +73,6 @@ Cp        = gamma*m_ad
 Cv        = Cp/gamma
[…]

### 2019-05-28 code/logic/post_processing.py

@@ -925,8 +925,8 @@ class ThermalPostProcessor():
                     cax.set_xticklabels(['', r'$\pm{:.2e}$'.format(maxv), ''])
                     cax.xaxis.set_ticks_position('none')
                     cax.set_title(title)
-#                    ax.set_xlim(0, 0.25*self.Lz)
-#                    ax.set_ylim(0, self.Lz)
+                    ax.set_xlim(0, 0.25*self.Lz)
+                    ax.set_ylim(0, self.Lz)
                     ax.axhline(z_cb[count-1], lw=0.5, c='k', ls='--')
                     ax.scatter(radius[count-1], height[count-1], color='black', s=2)
                     ax.plot(contour[good_contour], z[good_contour], c='k', lw=0.5)

### 2019-05-28 code/plotting/constants.py

@@ -11,9 +11,12 @@ import matplotlib.gridspec as gridspec
 import numpy as np
 import h5py
 
-aspect = [0.35, 0.35, 0.25, 0.25, 0.25, 0.25]
-CASES = [0.1, 0.5, 1, 2, 3, 4]
-ROOT_DIR='../weird_form_good_2D_runs/'
+#aspect = [0.35, 0.35, 0.25, 0.25, 0.25, 0.25]
+#CASES = [0.1, 0.5, 1, 2, 3, 4]
+#ROOT_DIR='../weird_form_good_2D_runs/'
+aspect = [0.25, 0.25, 0.25, 0.25, 0.25, 0.25, 0.2, 0.25]
+CASES = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
+ROOT_DIR='../good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
 height, width = 4, 3.25 
@@ -32,7 +35,7 @@ fig = plt.figure(figsize=(width, height))
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 cax = plt.subplot(gs.new_subplotspec(*((0, 0), 50, 1000)))
 
-norm = matplotlib.colors.Normalize(vmin=0, vmax=len(DIRS))
+norm = matplotlib.colors.Normalize(vmin=0.8, vmax=len(DIRS))
 sm   = plt.cm.ScalarMappable(cmap='viridis_r', norm=norm)
 sm.set_array([])
 

### 2019-05-28 code/plotting/diff_AN_FC.py

@@ -12,18 +12,16 @@ import matplotlib.gridspec as gridspec
 import numpy as np
 import h5py
 
-NRUNS=6
+NRUNS=8
 
-
-
-aspect = [0.35, 0.25, 0.25]
+aspect = [0.25, 0.25, 0.25]
 CASES = [0.5, 1, 2]
-ROOT_DIR='../weird_form_good_2D_runs/'
+ROOT_DIR='../good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
-aspect_2D = [0.35, 0.25, 0.25]
-CASES_2D = [0.1, 3, 4]
-color_dir = [1, 5, 6]
+aspect_2D = [0.25, 0.25, 0.25, 0.2, 0.25]
+CASES_2D = [0.1, 3, 4, 5, 6]
+color_dir = [1, 5, 6, 7, 8]
 DIRS_2D=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES_2D, aspect_2D)] 
 
 CASES_3D = [0.5, 1, 2]
@@ -52,7 +50,7 @@ fig = plt.figure(figsize=(width, height))
 axs = [plt.subplot(gs.new_subplotspec(*args)) for args in subplots]
 cax = plt.subplot(gs.new_subplotspec((0,   0), 50, 1000))
 
-norm = matplotlib.colors.Normalize(vmin=0, vmax=NRUNS)
+norm = matplotlib.colors.Normalize(vmin=0.8, vmax=NRUNS)
 sm   = plt.cm.ScalarMappable(cmap='viridis_r', norm=norm)
 sm.set_array([])
 

### 2019-05-28 code/plotting/evolution_colormeshes.py

@@ -12,8 +12,8 @@ from scipy.interpolate import interp1d
 import numpy as np
 import h5py
 
-dirs = [    ('../may03/AN_2D_thermal_nrho0.5_Re6e2_Pr1_aspect0.25_Lz20', (1, 0), (2, 18), (5, 17)) ,
-            ('../may03/AN_2D_thermal_nrho3_Re6e2_Pr1_aspect0.25_Lz20' , (1,0), (2, 12),  (4, 5))]
+dirs = [    ('../good_2D_runs/z_bot_zero/AN_2D_thermal_nrho0.5_Re6e2_Pr1_aspect0.25_Lz20', (1, 0), (2, 18), (5, 17)) ,
+            ('../good_2D_runs/z_bot_zero/AN_2D_thermal_nrho3_Re6e2_Pr1_aspect0.25_Lz20' , (1,0), (2, 12),  (4, 5))]
 
 
 gs = gridspec.GridSpec(1000, 1000)
@@ -33,6 +33,7 @@ for i, ax in enumerate(axs):
         print('opening file ', this_dir, filenum, imgnum)
         f  = h5py.File('{:s}/slices/slices_s{}.h5'.format(this_dir, filenum), 'r')
         cf = h5py.File('{:s}/thermal_analysis/contour_file.h5'.format(this_dir), 'r')
+        ff = h5py.File('{:s}/thermal_analysis/final_outputs.h5'.format(this_dir), 'r')
 
         r = f['scales']['r']['1.0'].value
         z = f['scales']['z']['1.0'].value
@@ -45,12 +46,14 @@ for i, ax in enumerate(axs):
 
         contour = cf['contours'].value[20*(filenum-1)+imgnum,:]
         contours = cf['contours'].value 
+        heights  = 20 - ff['d_measured'].value
 
         if j > 0:
             rho *= np.max(contour)**3
         
         field = f['tasks']['S1'].value[imgnum,:]
         f.close()
+        ff.close()
         cf.close()
 
         minval = -1 
@@ -66,18 +69,13 @@ for i, ax in enumerate(axs):
         x_max = 5
         if j == len(dirs[i])-2:
             max_contours = contours.max(axis=1)
-            max_contours = max_contours
-            max_contours_args = contours.argmax(axis=1)
             good_a = (max_contours > 0)
-            last = np.diff(max_contours_args).argmax()
-            good_a[last:] = False
 
             max_contours = max_contours[good_a]
-            max_contours_args = max_contours_args[good_a]
[…]

### 2019-05-28 code/plotting/results_panels.py

@@ -11,9 +11,12 @@ import matplotlib.gridspec as gridspec
 import numpy as np
 import h5py
 
-aspect = [0.35, 0.35, 0.25, 0.25, 0.25, 0.25]
-CASES = [0.1, 0.5, 1, 2, 3, 4]
-ROOT_DIR='../weird_form_good_2D_runs/'
+#aspect = [0.35, 0.35, 0.25, 0.25, 0.25, 0.25]
+#CASES = [0.1, 0.5, 1, 2, 3, 4]
+#ROOT_DIR='../weird_form_good_2D_runs/'
+aspect = [0.25, 0.25, 0.25, 0.25, 0.25, 0.25, 0.2, 0.25]
+CASES = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
+ROOT_DIR='../good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
 CASES_3D = [0.5, 1, 2]
@@ -32,7 +35,7 @@ cax = plt.subplot(gs.new_subplotspec((30,   0), 50, 1000))
 ax1 = plt.subplot(gs.new_subplotspec((100,  0), 380, 1000))
 ax2 = plt.subplot(gs.new_subplotspec((620,  0), 380, 1000))
 
-norm = matplotlib.colors.Normalize(vmin=0, vmax=len(CASES))
+norm = matplotlib.colors.Normalize(vmin=0.8, vmax=len(CASES))
 sm   = plt.cm.ScalarMappable(cmap='viridis_r', norm=norm)
 sm.set_array([])
 
@@ -70,7 +73,7 @@ for i, direc in enumerate(DIRS):
             ax.set_xlabel('Time')
         elif j == 1:
             ax.set_xlim(0, 20)
-            ax.set_ylim(0.2, 1)
+            ax.set_ylim(0.2, 1.15)
             ax.set_yticks((0.5, 1))
             ax.set_ylabel('|w|')
             ax.set_xlabel('Depth')

### 2019-05-28 tex/stratified_thermals.tex
adds in nrho=5, nrho=6 data

@@
 4	 	&  0.698	& 0.622	& -1.47	 & -1.59 & 7.10	& 0.793	& 0.422	\\
-5	 	& 			& 			&	 &	&	&	&	\\
+5	 	&  0.963	& 0.327	& -2.70	 & -1.49 & 7.15	& 0.786	& 0.414	\\
+6	 	&  1.57 	& 0.064	& -5.73	 & -1.43 & 7.16	& 0.787	& 0.408	\\
 \multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations}}\\    
@@
 
+For details on how measurements of thermal properties are conducted in our simulations, we refer the reader to appendix \ref{appendix:measurements}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \appendix
-\section{Thermal Radius and Height measurements}
-\label{appendix:radius}
+\section{Thermal Measurements}
+\label{appendix:measurements}
 Throughout this work, we frequently report the thermal's radius or its depth.
@@
 
+Integral quantities, such as the circulation, $\Gamma$, the buoyancy, $B$, and the volume, $\mathcal{V}$ require us to first determine what fraction of the domain constitutes the thermal.
+To do so, we use the thermal tracking algorithm described in appendix \ref{appendix:tracking} to determine the radial contour that outlines the thermal as a function of height, $\mathcal{C}$.
+We then use this contour to find our integral quantities,
+\begin{equation}
+\Gamma = \int_0^{\mathcal{C}}\int_0^{L_z} (\grad\times\bm{u})_\phi dz dr, \qquad
+B      = \int_0^{\mathcal{C}}\int_0^{L_z} \rho S_1 dz dr, \qquad
+\mathcal{V} = \int_0^{\mathcal{C}}\int_0^{L_z} 1\,dz dr.
+\end{equation}
+
 \section{Thermal Tracking}
 \label{appendix:tracking}
-We use a thermal tracking algorithm very similar to the one used in  \citet{lecoanet&jeevanjee2018} and inspired by the work of \citet{romps&all2015}.
-
-We begin by measuring the thermal's height versus time. 
-To do so, we average the domain's entropy profile in radius and azimuth to create an average profile of entropy with height, and then assume that the thermal's vortex core is located at the entropy minima of each of those profiles.
-We numerically differentiate these found values of height vs. time using (insert numerical differentiation technique here) to get the velocity of the bulk of the thermal, $w_{\text{th}}$.
+We use a thermal tracking algorithm very similar to the one used in  \citet{lecoanet&jeevanjee2018} and inspired by the work of \citet{romps&all2015} in order to determine the full extent of the thermal, as pictured by the elliptical outlines in Fig.~\ref{fig:evolution_colormeshes}
+We begin by measuring the thermal's velocity versus time, $w_{\text{th}}$, as described in appendix \ref{appendix:measurements}. 
 We then calculate the streamfunction of the velocity field as in \citet{romps&all2015},
@@
 with the boundary condition that $\psi = 0$ at $r = 0$. 
-The contour defined by $\psi = 0$ from this solution is taken to be the outline of the thermal, and the volume of the thermal is taken to be the volume contained in that contour.
+The contour defined by $\psi = 0$ from this solution is taken to be the contour bounding the thermal, $\mathcal{C}$.
 
@@
 \label{appendix:table}
+Information regarding the simulation resolution and CFL safety factor for each of the simulations presented in this work is contained in table \ref{table:simulation_info}.
+The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository CITE.
 
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$L_r$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
+\colhead{$n_\rho$} & \colhead{$L_r$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{\text{evolution}}$} & \colhead{safety}	}	
 \startdata																																															
 \multicolumn{6}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	& 	5				&	128			& 512			& 49 	&	0.2	\\
-0.5 	& 	5				&	128			& 512			& 42.5 	&	0.2	\\
-1	 	& 	5				&	128			& 512			& 38 	&	0.2	\\
-2	 	& 	5				&	128			& 512			& 31.75	&	0.2	\\
-3	 	& 	5				&	256			& 512			& 27.25	&	0.15	\\
-4	 	& 	5				&	256			& 512			& 25 	&	0.1	\\
-5	 	& 	5				&	256			& 512			& 22.8 	&	0.05	\\
+0.1 	& 	5				&	128			& 512			& 50 	&	0.6	\\
+0.5 	& 	5				&	128			& 512			& 45 	&	0.6	\\
+1	 	& 	5				&	128			& 512			& 41 	&	0.6	\\
+2	 	& 	5				&	256			& 1024			& 34	&	0.4	\\
+3	 	& 	5				&	256			& 1024			& 29	&	0.4	\\
+4	 	& 	5				&	256			& 1024			& 26 	&	0.3	\\
+5	 	& 	5				&	256			& 1536			& 25 	&	0.14	\\
+6	 	& 	5				&	256			& 1536			& 23 	&	0.08	\\
 \multicolumn{6}{l}{\textbf{3D Fully Compressible Simulations}}\\
-0.5 	& 	5				&	256			& 512			& 42.5 		&	0.8	\\
-1	 	& 	4				&	256			& 512			& 38 	 	&	0.8	\\
-2	 	& 	3.5				&	256			& 1536			& 31.75 	&	0.8	\\
+0.5 	& 	5				&	256			& 512			& 42.5 		&	0.2	\\
+1	 	& 	4				&	256			& 512			& 38 	 	&	0.2	\\
+2	 	& 	3.5				&	256			& 1536			& 31.75 	&	0.2	\\
 \enddata																																															

### 2019-05-29 tex/stratified_thermals.tex
Abstract.

@@
 \begin{abstract}
-``Entropy rain,'' or the downard propagation of low entropy fluid, has been hypothesized as a dominant mechanism for carrying the solar luminosity in light of the recent Solar Convective Conundrum.
-One possible dynamical manifestation of these ``raindrops'' is that of dense, propagating vortex rings, referred to as ``thermals'' in the context of Earth's atmosphere.
-In this work, we develop an analytical theory describing entrainment in dense, antibuoyant vortex rings in stratified atmospheres.
-We show that this theory describes the evolution of laminar, axisymmetric thermals in highly stratified atmospheres and into the boussinesq limit.
-We discuss what the evolution of these thermals implies for the entropy rain hypothesis.
+% first sentence should state the solar convective conundrum.
+Something like: Historically, the sun's luminosity was thought to be carried by large-scale convective flows, but recent observations show no such flow exists.
+% second paragraph should introduce entropy rain, e.g.: In place of large-scale flows, some have suggested the solar luminosity may be transported by small ``droplets'' of rapidly falling, low entropy fluid
+This ``entropy rain'' would propagate as dense vortex rings, analogous to rising buoyant ``thermals'' in the Earth's atmosphere.
+In this work, we develop an analytical theory describing the evolution of dense, negatively buoyant thermals.
+We verify the theory with 2D and 3D simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
+We discuss what the evolution of these thermals implies for the entropy rain hypothesis. % should replace this with a summary of the implications
 \end{abstract}

### 2019-05-29 tex/stratified_thermals.tex
cleans up manuscript per suggestions from Daniel + cleans up code some

@@
 \begin{abstract}
-% first sentence should state the solar convective conundrum.
-Something like: Historically, the sun's luminosity was thought to be carried by large-scale convective flows, but recent observations show no such flow exists.
-% second paragraph should introduce entropy rain, e.g.: In place of large-scale flows, some have suggested the solar luminosity may be transported by small ``droplets'' of rapidly falling, low entropy fluid
+Historically, large-scale convective flows called ``giant cells'' were thought to transport the Sun's luminosity from deep in the solar convection zone, but recent observations show no such flow exists.
+In place of large-scale flows, some authors have suggested the solar luminosity may instead be transported by small ``droplets'' of rapidly falling, low entropy fluid.
 This ``entropy rain'' would propagate as dense vortex rings, analogous to rising buoyant ``thermals'' in the Earth's atmosphere.
@@
 We verify the theory with 2D and 3D simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
-We discuss what the evolution of these thermals implies for the entropy rain hypothesis. % should replace this with a summary of the implications
+Our results suggest that entropy rain driven at the surface of the Sun could fall into two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
+We briefly discuss difficulties for the entropy rain hypothesis in both of these regimes.
 \end{abstract}
@@
 However, these simulations and discussions did not include include a fundamental piece of entropy rain: its entropic signature deviates from the background atmosphere.
-Entropy rain is dense, and the effects of antibuoyant forces will modify its dynamics.
+Entropy rain is dense, and the effects of buoyancy forces will modify its dynamics.
 
@@
 	We see that with increasing stratification, there is marginally more detrainment of both of these quantities, but to first order they are constant over the	thermal's transit time. 
-	In (c) the volumetric constant $f$ is shown; after significant noise during the development of the vortex ring, this quantity settles toward a value of O(7) throughout the thermal's transit.
+	In (c) the volumetric constant $f$ is shown; after significant noise during the development of the vortex ring, this quantity settles toward a value of $\mathcal{O}(7)$ throughout the thermal's transit.
     \label{fig:constants} }
@@
 \end{equation}
-where $\chi$ is a constant of O(1) which represents this detrainment. 
+where $\chi$ is a constant of $\mathcal{O}$(1) which represents this detrainment. 
 We then integrate Eqn.~\ref{eqn:change_in_impulse} in time,
@@
 If the atmospheric stratification in which the thermal is falling is known, this result can be integrated with the known profile of $\rho(z_{\text{th}})$ in order to find the position of the thermal as a function of time.
-We leave this result general for now, and will integrate it using the polytropic stratification used in our simulations in the next section.
+
+To summarize, we have modeled the evolved thermal as a \emph{thin-core, axisymmetric} vortex ring which is evolving in a plane-parallel, adiabatic atmosphere, and have assumed that the motions are low Mach number such that a linearized equation of state describes the thermal well.
+We have assumed that viscous and conductive effects are small and can be neglected, such that the total density-weighted specific entropy in the thermal is a conserved quantity.
+We assume that vortex ring's circulation is constant, that the thermal's volume is spheroidal, and that the effects of pressure and detrainment on impulse and momentum can be parameterized as constants.
+Under these assumptions, we arrived at Eqn.~\ref{eqn:dz_theory}, which we leave in its general form here, and which we will integrate using the polytropic stratification used in our simulations in the next section.
 
@@
 
-\subsection{Initial conditions}
-To initialize the simulation, we specify a spherical initial specific entropy perturbation,
-\begin{equation}
-S_1 = - \frac{1}{2}\left[1 - \text{erf}\left(\frac{r' - r_{\text{th}}}{\delta}\right)\right].
-\label{eqn:thermal_IC}
-\end{equation}
-Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3r_{\text{th}}$, with the thermal radius set as $r_{\text{th}} = 0.5$, and a smoothing width, $\delta = 0.1$.
-As mentioned previously, Re = 600 and Pr = 1 are specified at the thermal's initial depth, $z = z_0$.
-
 \subsection{Fully Compressible Simulations}
@@
 
+\subsection{Initial conditions}
+To initialize the simulation, we specify a spherical initial specific entropy perturbation,
+\begin{equation}
+S_1 = - \frac{1}{2}\left[1 - \text{erf}\left(\frac{r' - r_{\text{th}}}{\delta}\right)\right].
+\label{eqn:thermal_IC}
+\end{equation}
+Here, $r' = \sqrt{r^2 + (z - z_0)^2}$, where $z_0 = L_z - 3r_{\text{th}}$, with the thermal radius set as $r_{\text{th}} = 0.5$, and a smoothing width, $\delta = 0.1$.
+As mentioned previously, Re = 600 and Pr = 1 are specified at the thermal's initial depth, $z = z_0$.
+
 \subsection{Numerics}
-We evolve our simulations forward in time using the  Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \citep{burns&all2016} [CITE THE METHODS PAPER]. 
+We evolve our simulations forward in time using the  Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \citep{burns&all2016, burns&all2019}. 
 For our 2D simulations, we use using an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997}, and for our 3D simulations we use the second-order semi-implicit backward differentiation formulation SBDF2 \citep{wang&ruuth2008}.
@@
 Our 3D simulations are decomposed on Fourier bases in the horizontal directions ($x, y \in [-L_r, L_r]$) and Chebyshev bases vertically ($z \in [0, L_z]$) with impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries ($T_1 = w = \partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
-Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of $\partial_r S_1 = w = (\grad\times\bm{u})_\phi = 0$ at $r = L_r$.
+Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of $\partial_r S_1 = w = (\grad\times\bm{u})_\phi = 0$ at $r = L_r$ and $u = \partial_r(w) = \partial_r(S_1) = 0$ at $r = 0$.
 
@@
 \label{sec:results}
+\begin{figure}[t!]
+    \includegraphics[width=\columnwidth]{results_panels.png}
+    \caption{
+	The measured depths of thermals as a function of time for all 2D Anelastic and 3D Fully compressible simulations conducted in this work are shown in (a).
+	The corresponding thermal velocities as a function of depth are shown in (b)
+	Overplotted in a thin solid line for each case are our theoretical predictions from section \ref{sec:theory} given the parameters in table \ref{table:parameters}.
+    \label{fig:results_panels} }
+\end{figure}
+
+\begin{figure}[t!]
+    \includegraphics[width=\columnwidth]{diff_AN_FC.png}
+    \caption{
+	Measured values of radius vs. depth are plotted for both the 2D anelastic and 3D fully compressible simulations in (a). 
+	For completeness, we also include the cases in which we only studied the 2D anelastic simulations.
+	For the cases in which only the anelastic equations were solved, the theory is overplotted in a thin solid line, and similar agreement between simulations and theory is found for the cases where both equations sets were used.
+	The fractional difference between anelastic and fully compressible results are shown in (b).
+    \label{fig:diff} }
+\end{figure}
+
+In Fig. \ref{fig:results_panels}a, we show the measured depth $d_{\text{th}} = L_z - z_{\text{th}}$ of the thermal as a function of time for low and high stratification. 
+At very low stratification (e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
+As the stratification increases, the thermal begins to transit the domain more quickly and approaches the limit of $d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_z}. 
+The theoretical fits for depth from the prediction of Eqn.~\ref{eqn:theory_z} are plotted over the measured data.
+Unsurprisingly, the theoretical fits are poor for early times when the thermal is spinning up from its initial spherical state into the vortex ring state.
+Once the thermal is spun up into a vortex ring, the theory shows remarkable agreement with the measured data.
+
+In Fig.~\ref{fig:results_panels}b, we show the corresponding thermal velocity as a function of depth with the theory overplotted again.
+As anticipated, low density ($n_\rho = 0.1$) thermals deccelerate with depth.
+We find that with increasing stratification, this decceleration stops and sufficiently stratified runs ($n_\rho \geq 3$) experience acceleration of the thermal.
+
+In Fig.~\ref{fig:diff}a, we display measured thermal radius vs. depth, with a detailed comparison of our 2D Anelastic and 3D Fully Compressible cases. 
+In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, aligning with the Boussinesq limit shown in \citet{lecoanet&jeevanjee2018}.
+This growth of the thermal is the result of entrainment of environmental fluid and accompanies decceleration like $w \propto d^{-1}$ in the Boussinesq limit, as is shown in Fig.~\ref{fig:results_panels}b.
+However, as stratification increases, the thermal entrainment of environmental fluid decreases and it experiences less expansion.
+In the limit of large stratification ($n_\rho \geq 3$), thermals begin contracting with depth.
+This lessened entrainment is, unsurprisingly, accompanied by greater acceleration of the thermal (Fig.~\ref{fig:results_panels}).
+
+In Fig.~\ref{fig:diff}b, the fractional difference in radius vs. depth between 3D FC and 2D AN cases is shown for the $n_\rho = [0.5, 1, 2]$ cases studied here. 
+Aside from early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the impenetrable boundary at the bottom of the domain, the 2D anelastic and 3D fully compressible simulations agree surprisingly well.
+We find differences in the radius of less than 1\% throughout the bulk of the thermal evolution for the cases studied here.
+This gives us confidence that our high stratification anelastic simulations are producing reliable results.
+Furthermore, this close agreement between low Mach number Fully Compressible simulations and Anelastic simulations parallels the agreement between the equation sets seen in \citet{lecoanet&all2014}.
+
 The measured values of each of the parameters described in section \ref{sec:theory} for each of our simulations  \ref{sec:theory} for each of our simulations  \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
-As anticipated, $\beta$ is O(0.5) and $\chi$ is O(1), with both decreasing slightly in value with increasing stratification, which is perhaps unsurprising in light of Fig.~\ref{fig:constants}.
+As anticipated, $\beta$ is $\mathcal{O}$(0.5) and $\chi$ is $\mathcal{0}$(1), with both decreasing slightly in value with increasing stratification, which is perhaps unsurprising in light of Fig.~\ref{fig:constants}.
 In all cases, the buoyancy $B_0$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
-In our nondimensional units, we also find that the circulation is O(-2) for each of our cases, and decreases with increasing stratification (and decreasing vortex size).
+In our nondimensional units, we also find that the circulation is $\mathcal{0}$(-2) for each of our cases, and decreases with increasing stratification (and decreasing vortex size).
 
@@
 
-\begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{results_panels.png}
-    \caption{
-	The measured depths of thermals as a function of time for all 2D Anelastic and 3D Fully compressible simulations conducted in this work are shown in (a).
-	The corresponding thermal velocities as a function of depth are shown in (b)
-	Overplotted in a thin solid line for each case are our theoretical predictions from section \ref{sec:theory} given the parameters in table \ref{table:parameters}.
-    \label{fig:results_panels} }
-\end{figure}
-
-\begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{diff_AN_FC.png}
-    \caption{
-	Measured values of radius vs. depth are plotted for both the 2D anelastic and 3D fully compressible simulations in (a). 
-	For completeness, we also include the cases in which we only studied the 2D anelastic simulations.
-	For the cases in which only the anelastic equations were solved, the theory is overplotted in a thin solid line, and similar agreement between simulations and theory is found for the cases where both equations sets were used.
-	The fractional difference between anelastic and fully compressible results are shown in (b).
-    \label{fig:diff} }
-\end{figure}
-
-In Fig. \ref{fig:results_panels}a, we show the measured depth $d_{\text{th}} = L_z - z_{\text{th}}$ of the thermal as a function of time for low and high stratification. 
-At very low stratification (e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
-As the stratification increases, the thermal begins to transit the domain more quickly and approaches the limit of $d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_z}. 
-The theoretical fits for depth from the prediction of Eqn.~\ref{eqn:theory_z} are plotted over the measured data and show remarkable agreement.
-
-In Fig.~\ref{fig:results_panels}b, we show the corresponding thermal velocity as a function of depth with the theory overplotted again.
-As anticipated, low density ($n_\rho = 0.1$) thermals deccelerate with depth.
-We find that with increasing stratification, this decceleration stops and sufficiently stratified runs ($n_\rho \geq 3$) experience acceleration of the thermal.
-
-In Fig.~\ref{fig:diff}a, we display measured thermal radius vs. depth, with a detailed comparison of our 2D Anelastic and 3D Fully Compressible cases. 
-In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, aligning with the Boussinesq limit shown in \citet{lecoanet&jeevanjee2018}.
-This growth of the thermal is the result of entrainment of environmental fluid and accompanies decceleration like $w \propto d^{-1}$ in the Boussinesq limit, as is shown in Fig.~\ref{fig:results_panels}b.
-However, as stratification increases, the thermal entrainment of environmental fluid decreases and it experiences less expansion.
-In the limit of large stratification ($n_\rho \geq 3$), thermals begin contracting with depth.
-This lessened entrainment is, unsurprisingly, accompanied by greater acceleration of the thermal (Fig.~\ref{fig:results_panels}).
-
-In Fig.~\ref{fig:diff}b, the fractional difference in radius vs. depth between 3D FC and 2D AN cases is shown for the $n_\rho = [0.5, 1, 2]$ cases studied here. 
-Aside from early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the impenetrable boundary at the bottom of the domain, the 2D anelastic and 3D fully compressible simulations agree surprisingly well.
-We find differences in the radius of less than 1\% throughout the bulk of the thermal evolution for the cases studied here.
-This gives us confidence that our high stratification anelastic simulations are producing reliable results.
-Furthermore, this close agreement between low Mach number Fully Compressible simulations and Anelastic simulations parallels the agreement between the equation sets seen in \citet{lecoanet&all2014}.
-
-For details on how measurements of thermal properties are conducted in our simulations, we refer the reader to appendix \ref{appendix:measurements}.
+Throughout this section, the thermal's depth and radius refer respectively to the atmospheric depth and the radius from the axis of symmetry at which the vortex ring's entropy minimum is located.
+The velocity is simply the derivative with respect to time of that measured depth.
+For specifics on how these measurements are conducted in our simulations, we refer the reader to appendix \ref{appendix:measurements}.
 
@@
 \Gamma = \int_0^{\mathcal{C}}\int_0^{L_z} (\grad\times\bm{u})_\phi dz dr, \qquad
-B      = \int_0^{\mathcal{C}}\int_0^{L_z} \rho S_1 dz dr, \qquad
-\mathcal{V} = \int_0^{\mathcal{C}}\int_0^{L_z} 1\,dz dr.
+B      = 2\pi \int_0^{\mathcal{C}}\int_0^{L_z} \rho S_1 r dz dr, \qquad
+\mathcal{V} = 2\pi \int_0^{\mathcal{C}}\int_0^{L_z} 1\,r dz dr.
 \end{equation}
@@
 
-\bibliography{../tex/biblio.bib}
+\bibliography{biblio.bib}
 

### 2019-05-29 code/AN_2D_thermal.py

@@ -70,13 +70,13 @@ Lz          = float(args['--Lz'])
 gamma     = 5./3                         #adiabatic index
 m_ad      = 1/(gamma-1)
 Cp        = gamma*m_ad
-Cv        = Cp/gamma
 grad_T_ad = -(np.exp(n_rho/m_ad) - 1)/Lz #adiabatic temperature gradient
-g         = (1 + m_ad) #* -grad_T_ad     #gravity
+g         = (1 + m_ad)                   #gravity
+logger.info('Creating polytrope with grad_T_ad: {:.4e}, g: {:.4e}'.format(grad_T_ad, g))
 
 Lr        = aspect*Lz
-radius    = 0.5       #Thermal radius, by definition, in nondimensionalization
-delta_r   = radius/5  #Thermal smoothing width
+radius    = 0.5       
+delta_r   = radius/5  
 
 #(r0, z0) is the midpoint of the (spherical) thermal
 r0        = 0
@@ -86,8 +86,6 @@ z0        = Lz - 3*radius
 # is the freefall Re at the height of the initial thermal
 if kappa_mu:
     Re /= (1 + grad_T_ad*(z0 - Lz))**m_ad
-
-logger.info('Creating polytrope with grad_T_ad: {:.4e}, g: {:.4e}'.format(grad_T_ad, g))
 
 ###################
 # Set up output dir
@@ -106,6 +104,8 @@ logger.info('saving files in {:s}'.format(data_dir))
 #####################
 # Dedalus simulation
 #####################
+# z-domain extends to -5 so that measurements can be made around z=0 
+#  before thermal gets to edge of periodic domain.
 z_basis = de.Fourier(  'z', nz, interval=(-5, Lz), dealias=3/2)
 r_basis = de.Chebyshev('r', nr, interval=(0, Lr), dealias=3/2)
 domain = de.Domain([z_basis, r_basis], grid_dtype=np.float64)
@@ -118,28 +118,19 @@ problem.parameters['Lz']         = Lz
 problem.parameters['Lr']         = Lr
 problem.parameters['m_ad']       = m_ad
 problem.parameters['Cp']         = Cp
-problem.parameters['Cv']         = Cv
 problem.parameters['grad_T_ad']  = grad_T_ad
-problem.parameters['g']          = g
[…]

### 2019-05-29 code/logic/post_processing.py

@@ -261,7 +261,6 @@ class ThermalPostProcessor():
             s1  = f['tasks']['S1'].value * self.s_factor
             w   = f['tasks']['w'].value  * self.L_factor/self.t_factor
             u   = f['tasks']['u'].value  * self.L_factor/self.t_factor
-#            V   = f['tasks']['p'].value  
             V   = f['tasks']['V'].value  / self.t_factor
             r   = f['scales']['r']['1.0'].value * self.L_factor 
             z   = f['scales']['z']['1.0'].value * self.L_factor 
@@ -354,145 +353,6 @@ class ThermalPostProcessor():
                 output_file['z']                = z
                 output_file['contours']         = contours
                 output_file.close()
-
-
-
-#    def fit_w_cb(self, iterative=False):
-#        """
-#        Fit thermal bulk velocity (cloud bottom, 'cb') according to the
-#        developed theory of stratified thermal evolution.
-#
-#        Output information from the fit is stored in root_dir/out_dir/fit_file.h5
-#
-#        Inputs:
-#        -------
-#        iterative   : bool, optional
-#            If True, use output from a previous fit to get this fit.
-#        """
-#        c_f = h5py.File('{:s}/z_cb_file.h5'.format(self.full_out_dir), 'r')
-#        z_cb = c_f['z_cb'].value
-#        cb_T = 1 + self.grad_T_ad*(z_cb - self.Lz)
-#        z = c_f['z'].value
-#        vortex_height = c_f['vortex_height'].value
-#        vortex_radius = c_f['vortex_radius'].value
-#        vortex_rho    = c_f['vortex_rho'].value
-#        vortex_T      = c_f['vortex_T'].value
-#        circ          = c_f['circ'].value
-#        B             = c_f['B'].value
-#        momentum      = c_f['momentum'].value
-#        c_f.close()
-#
-#
-#        fit_t = self.get_good_times(z_cb, L_max=0.6, L_min=0.15)
-#
-#        #Estimates
-#        B_est = np.mean(B[fit_t])
-#        circ_est = np.mean(circ[fit_t])
-#
-#        circ0 = circ[fit_t][0]
-#        I    = 2*np.pi*vortex_rho[fit_t] * vortex_radius[fit_t]**2 * circ_est
[…]

### 2019-05-29 code/FC_3D_thermal.py
some cleanup of 3D code & run scripts

@@ -20,7 +20,7 @@ Options:
     --mesh=<mesh>                        Processor mesh
 
     --run_time=<run_time>                Run time, in hours [default: 7.5]
-    --run_time_buoy=<run_time_buoy>      Run time, in buoyancy times
+    --run_time_buoy=<run_time_buoy>      Run time, in buoyancy times [default: 50]
 
     --restart=<restart_file>             Restart from checkpoint
 
@@ -28,7 +28,7 @@ Options:
 
     --label=<label>                      Additional label for run output directory
     --join                               If flagged, join files at end of run
-    --out_cadence=<cadence>              Fraction of a buoyancy time on which to output [default: 0.08]                    
+    --out_cadence=<cadence>              Fraction of a buoyancy time on which to output [default: 0.35]                    
 
     --chi_nu                             If flagged, do chi/nu formulation
 
@@ -52,11 +52,11 @@ from dedalus.extras import flow_tools
 from dedalus.tools  import post
 
 from logic.checkpointing import Checkpoint
-from logic.output import *
-from logic.domains import *
-from logic.atmospheres import *
-from logic.equations import *
-from logic.thermal import *
+from logic.output import initialize_output
+from logic.domains import DedalusDomain
+from logic.atmospheres import Polytrope
+from logic.equations import KappaMuFCE, ChiNuFCE
+from logic.thermal import Thermal
 
 logger = logging.getLogger(__name__)
 checkpoint_min = 30
@@ -118,58 +118,29 @@ if mpi4py.MPI.COMM_WORLD.rank == 0:
 
 nx = int(args['--nx'])
 ny = int(args['--ny'])
-nz = args['--nz']
-if ',' in nz:
-    nz = [int(n) for n in nz.split(',')]
-    tot_nz = np.sum(nz)
-#    if n_rho > 2:
-#        L_top = np.exp(2/m) - 1
-#    else:
-    L_top = 0.1*Lz + 2*radius
-    L_bot = Lz - L_top
-    Lz_domain = [L_bot, L_top]
-else:
-    nz = int(nz)
-    tot_nz = nz
-    Lz_domain = Lz
-
-
-
-
+nz = int(args['--nz'])
 mesh = args['--mesh']
[…]

### 2019-05-29 code/logic/equations.py

@@ -171,18 +171,11 @@ class KappaMuFCE(FullyCompressibleEquations):
     set based on kappa and mu, not chi and nu.
     """
 
-    def __init__(self, de_domain, atmosphere, A=0.5, B=0.5, *args, **kwargs):
+    def __init__(self, de_domain, atmosphere, *args, **kwargs):
         """
         Construct the atmosphere.  See parent class init for some input defns.
-
-        Parameters
-        ----------
-        A, B   : Floats
-            Used in approximating rho^{-1} = (A/T0 + B/T0**2) to reduce bandwidth.
         """
         super(KappaMuFCE, self).__init__(de_domain, atmosphere, *args, **kwargs)
-        self.problem.parameters['A'] = A
-        self.problem.parameters['B'] = B
 
     def _set_diffusion_subs(self, viscous_heating=True):
         """
@@ -308,7 +301,7 @@ class ChiNuFCE(FullyCompressibleEquations):
 
         self.problem.substitutions['L_thermal']    = self.linear_thermal_diff
         self.problem.substitutions['R_thermal']    = self.nonlinear_thermal_diff
-        self.problem.parameters['source_terms'] = 0
+        self.problem.parameters['source_terms'] = 0 #Assumes thermal equilibrium of background state.
 #        self.source                   = " (Cv_inv*( chi*(T0_zz + ln_rho0_z*T0_z) + chi_z*T0_z) )"
 #        self.problem.substitutions['source_terms'] = self.source
 

### 2019-05-29 code/logic/post_processing.py

@@ -81,7 +81,10 @@ class DedalusIntegrator():
         """
         self.Lz, self.Lr = Lz, Lr
         if r_cheby:
-            bounds = (0, Lz)
+            if twoD:
+                bounds = (-5, Lz)
+            else:
+                bounds = (0, Lz)
             self.r_basis = de.Chebyshev('r', nr, interval=(0,Lr))
             self.z_basis = de.Fourier('z', nz, interval=bounds)
             self.domain = de.Domain([self.z_basis, self.r_basis], grid_dtype=np.float64)

### 2019-05-29 code/plotting/constants.py

@@ -67,8 +67,8 @@ axs[2].set_ylim(0.8, 2)
 for i in (0, 1, 2):
     axs[i].set_xlim(2, 20)
 axs[2].set_ylabel('w')
-axs[0].set_ylabel(r'$\Gamma/\Gamma_{0}$')
-axs[1].set_ylabel(r'$B/B_{0}$')
+axs[0].set_ylabel(r'$\Gamma/\Gamma_{\mathrm{th}}$')
+axs[1].set_ylabel(r'$B/B_{\mathrm{th}}$')
 axs[2].set_ylabel(r'$f/7$')
 axs[2].set_xlabel('Depth')
 

### 2019-05-29 code/plotting/diff_AN_FC.py

@@ -19,9 +19,9 @@ CASES = [0.5, 1, 2]
 ROOT_DIR='../good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
-aspect_2D = [0.25, 0.25, 0.25, 0.2, 0.25]
-CASES_2D = [0.1, 3, 4, 5, 6]
-color_dir = [1, 5, 6, 7, 8]
+aspect_2D = [0.25, 0.25, 0.25, 0.25, 0.25, 0.25, 0.2, 0.25]
+CASES_2D = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
+color_dir = [1, 2, 3, 4, 5, 6, 7, 8]
 DIRS_2D=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES_2D, aspect_2D)] 
 
 CASES_3D = [0.5, 1, 2]
@@ -77,7 +77,7 @@ for i, direc in enumerate(DIRS):
     color = sm.to_rgba(i+2)
     x2, y2, x3, y3 = d, r, d3, r3
     l = np.min((len(y2), len(y3)))
-    axs[0].plot(x2[:l], y2[:l], marker='o', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.8), markerfacecolor=(*color[:-1], 0.2), markeredgewidth=0.5)
+#    axs[0].plot(x2[:l], y2[:l], marker='o', lw=0, markersize=3, markeredgecolor=(*color[:-1], 0.8), markerfacecolor=(*color[:-1], 0.2), markeredgewidth=0.5)
     axs[0].plot(x3[:l], y3[:l], marker='+', lw=0, markersize=2, markeredgecolor='k', markerfacecolor='k', markeredgewidth=0.5)
 
     axs[1].axhline(1e-2, c='k', lw=0.25)
@@ -93,27 +93,31 @@ for i, direc in enumerate(DIRS):
     axs[1].set_ylim(1e-3, 1e-1)
     axs[1].set_xlim(x2.min(), x2.max())
 
-axs[0].set_ylim(0.1, 2)
[…]

### 2019-05-29 code/plotting/evolution_colormeshes.py

@@ -69,14 +69,15 @@ for i, ax in enumerate(axs):
         x_max = 5
         if j == len(dirs[i])-2:
             max_contours = contours.max(axis=1)
-            good_a = (max_contours > 0)
+            good_a = (max_contours > 0)*(heights <= 14)
+            good_a[2] = True
 
             max_contours = max_contours[good_a]
             zs_contours = heights[good_a]
-            ax.plot( max_contours[:-1], zs_contours[:-1], c='k', lw=0.25)
-            ax.plot(-max_contours[:-1], zs_contours[:-1], c='k', lw=0.25)
-          
-            contour_f = interp1d(zs_contours, max_contours)
+            contour_f = interp1d(zs_contours, max_contours, bounds_error=False, fill_value='extrapolate')
+            ax.plot( contour_f(zs_contours[:-1]), zs_contours[:-1], c='k', lw=0.25)
+            ax.plot(-contour_f(zs_contours[:-1]), zs_contours[:-1], c='k', lw=0.25)
+         
             heights = [17, 14, 11, 8, 5, 2]
             dy = -0.5
             for h in heights:

### 2019-05-29 tex/stratified_thermals.tex
small mechanical or clarification changes. Renames some parameterization constants.

@@
 Power spectra of horizontal velocities show weaker flows than anticipated at large length scales \citep{hanasoge&all2012, greer&all2015}.
-These obserations cast doubt on the existence of ``giant cells'' driven by deep convection which should manifest as powerful, large-scale motions at the solar surface and throughout the solar convection zone.
+These observations cast doubt on the existence of ``giant cells'' driven by deep convection which should manifest as powerful, large-scale motions at the solar surface and throughout the solar convection zone.
 This discrepancy between theory and observations has called into question our fundamental understanding of convection, sparking numerous targeted investigations the nature of convection in the Sun  \citep{featherstone&hindman2016, omara&all2016, cossette&rast2016, kapyla&all2017, hotta2017}.
@@
 
-If entropy rain does evolve into downward propagating, dense vortex rings, it is important to understand how the filling factor of these basic convective elements is affected by their entropy signature.
+If entropy rain does evolve into downward propagating, dense vortex rings, it is important to understand how the filling factor of these basic convective elements is affected by their negative buoyancy.
 In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the nucleus of cloud formation. 
@@
 \subsection{Evolution of momentum and impulse}
-The evolution of thermals as buoyant vortex rings has been well described in the unstratified, Boussinesq limit for decades (see e.g. \LJ\,for a description and references).
+The evolution of thermals as buoyant vortex rings has been well described in the unstratified, Boussinesq limit for decades (see e.g.,~\LJ\,for a description and references).
 While many descriptions of vortex rings assume that they evolve in a self-similar state, we will lay out a description of the momentum and impulse of the thermal and show how these quantities control the evolution of the vortex ring.
@@
 where $r$ is the radius of the thermal from its axis of symmetry to the maxima of its buoyant signature, and $\Gamma = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the circulation in a cross-section of the vortex ring.
-Integrating the momentum equation in the absence of viscous effects shows that changes in circulation in an axisymmetric vortex ring are
+Integrating Eqn.~\ref{eqn:euler_momentum} reveals that changes in circulation can be calculated as
 \begin{equation}
@@
 
-After spinning up, we assume that the thermal is characterized by a constant buoyant signature, $B_0$, and constant circulation, $\Gamma_0$.
+After spinning up, we assume that the thermal is characterized by a constant buoyant signature, $B_{\text{th}}$, and constant circulation, $\Gamma_{\text{th}}$.
 While these thermals began as initial spherical perturbations, they can be modeled as having always been vortex rings which evolved from a ``virtual origin'' where the vortex ring is characterized by having a radius of zero.
@@
 \begin{equation}
-B \approx \chi B_0,
+B \approx \chi B_{\text{th}},
 \end{equation}
@@
 \begin{equation*}
-I_z = \chi B_0 t + I_0.
+I_z = \chi B_{\text{th}} t + I_0.
 \end{equation*}
@@
 \begin{equation}
-r = \sqrt{\frac{\chi B_0 t + I_0}{\pi\rho\Gamma_0}}.
+r = \sqrt{\frac{\chi B_{\text{th}} t + I_0}{\pi\rho\Gamma_{\text{th}}}}.
 \label{eqn:r_theory}
 \end{equation}
-Following Eqn.~\ref{eqn:circulation}, and taking $\Gamma_0$ to be constant (which is a decent assumption in our numerical experiments, as in Fig.~\ref{fig:constants}b), we find that the radius grows with time but this growth is damped by increasing atmospheric density.
+Following Eqn.~\ref{eqn:circulation} and taking $\Gamma_{\text{th}}$ to be constant (which is a decent assumption in our numerical experiments, as in Fig.~\ref{fig:constants}b), we find that the radius grows with time but this growth is damped by increasing atmospheric density.
 In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime in \LJ. 
@@
 \begin{equation*}
-M_z = \beta\chi B_0 t + M_0.
+M_z = \beta\chi B_{\text{th}} t + M_0.
 \end{equation*}
@@
 We approximate the volume as $\mathcal{V} = f r^3$, where $f$ is a parameter which we take to be constant. 
-This assumption is perhaps not as perfect as the assumptions of constant $B_0$ or $\Gamma_0$ (see Fig.~\ref{fig:constants}c), but it is nevertheless not a bad assumption. 
+This assumption is perhaps not as perfect as the assumptions of constant $B_{\text{th}}$ or $\Gamma_{\text{th}}$ (see Fig.~\ref{fig:constants}c), but it is nevertheless not a bad assumption. 
 Combining our approximate expressions, and using our theoretical description of $r$ (Eqn.~\ref{eqn:r_theory}), we retrieve
 \begin{equation}
-\rho^{-1/2} w_{\text{th}} = \left(\frac{(\pi \Gamma)^{3/2}}{f}\right)\frac{\beta\chi B_0 t + M_0}{(\chi B_0 t + I_0)^{3/2}}.
+\rho^{-1/2} w_{\text{th}} = \left(\frac{(\pi \Gamma_{\text{th}})^{3/2}}{f}\right)\frac{\beta\chi B_{\text{th}} t + M_0}{(\chi B_{\text{th}} t + I_0)^{3/2}}.
 \end{equation}
@@
 \frac{dz_{\text{th}}}{\rho(z_{\text{th}})^{1/2}} =
-\left(\frac{\beta(\pi\Gamma)^{3/2}}{f(\chi B_0)^{1/2}}\right)\frac{dt}{t^{1/2}}
+\left(\frac{\beta(\pi\Gamma_{\text{th}})^{3/2}}{f(\chi B_{\text{th}})^{1/2}}\right)\frac{dt}{t^{1/2}}.
 \label{eqn:dz_theory}
@@
 \subsection{Solution for thermal evolution in a Polytrope}
-In this work, we study an ideal gas whose equation of state is $P = \rho T$ and whose stratification is a perfectly adiabatic polytrope,
+In this work, we study an ideal gas with an adiabatic index of $\gamma = 5/3$, whose equation of state is $P = \rho T$, and whose stratification is a perfectly adiabatic polytrope,
 \begin{gather}
@@
 where $m_{\text{ad}} = (\gamma-1)^{-1}$, and where the adiabatic temperature gradient in our nondimensional systems (see section \ref{sec:experiment}) is $\grad_{\text{ad}} \equiv g(e^{n_\rho/m_{\text{ad}}} - 1)/(L_z c_P)$, with $g = m_{\text{ad}} + 1$ and $L_z = 20$ is the nondimensional depth of the atmosphere in units of thermal diameters.
+All thermodynamic quantities are nondimensionalized such that $\rho_0 = T_0 = 1$ at $z = L_z$.
 
@@
 \begin{equation}
-z_{\text{th}} = \grad_{\text{ad}}^{-1}\left[\left(\frac{2C}{ \alpha } \sqrt{t + t_{\text{off}}} + T_0^{1/\alpha}  \right)^{\alpha} - 1\right] + L_z,
+z_{\text{th}} = \grad_{\text{ad}}^{-1}\left[\left(\frac{2C}{ \alpha } \sqrt{t + t_{\text{off}}} + T_{\text{th},0}^{1/\alpha}  \right)^{\alpha} - 1\right] + L_z,
 \label{eqn:theory_z}
 \end{equation}
-where $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma^3/(\chi B)}$ and the temperature at the virtual origin is $T_0 = 1 + \grad_{\text{ad}}(z_0 - L_z)$.
-The virtual origin is located at $z = z_0$ and $t = -t_{\text{off}}$ in simulation units, which are the height and time a which the vortex ring would have had zero radius in the absence of a spin-up phase.
+where $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma_{\text{th}}^3/(\chi B_{\text{th}})}$ and the temperature at the virtual origin is $T_{\text{th},0} = 1 + \grad_{\text{ad}}(z_{\text{th},0} - L_z)$.
+The virtual origin is located at $z = z_0$ and $t = -t_{\text{off}}$ in simulation units, which are the height and time at which the vortex ring would have had zero radius in the absence of a spin-up phase.
 The constant $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
@@
 The thermal is initialized as a uniform sphere of dense fluid, and it quickly spins up into a vortex ring. 
-While we do not attempt to model the spin-up phase in this paper, it can be parameterized by the buoyancy $B_0$, circulation $\Gamma_0$, as well as the virtual origin $z_0$, and temporal offset $t_{\text{off}}$.
+While we do not attempt to model the spin-up phase in this paper, it can be parameterized by the buoyancy $B_{\text{th}}$, circulation $\Gamma_{\text{th}}$, as well as the virtual origin $z_{\text{th,0}}$, and temporal offset $t_{\text{off}}$.
 Our theory also involves the volumetric aspect ratio of the thermal $f$, the detrainment fraction $\chi$, and the effective buoyancy $\beta$. 
@@
 where $\lilstressT$ is the viscous stress tensor in units of inverse time.
-In our azimuthally symetric domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$.
+In our azimuthally symetric, cylindrical domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$.
 
-These equations have been nondimensionalized in the same manner as in \citet{lecoanet&jeevanjee2018} such that the length scale is the diameter of the initial thermal perturbation and the velocity scale is the freefall velocity.
+These equations have been nondimensionalized in the same manner as in \LJ\, such that the length scale is the diameter of the initial thermal perturbation and the velocity scale is the freefall velocity.
 The timescale is thus the freefall crossing time of this unit length. 
@@
 We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform and constant in time.
+We make this choice as the mass-weighted diffusivities, $\mu$ and $\kappa$, appear in the density-weighted momentum and entropy equations, and we find the density-weighted entropy and momentum to be key quantities in our thermal theory.
 The diffusivities $\nu$ and $\chi$ therefore scale inversely with the density.
@@
 \end{gather}
-These equations have been nondimensionalized on the same length and timescales as the anelastic equations, use the same atmospheric profiles and assumptions, and we have explicitly assumed that the background atmosphere ($T_0, \ln\rho_0$) is in hydrostatic and thermal equilibrium in the writing of these equations.
-The new parameter $\epsilon = u_{th}^2$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows, and we use $\epsilon = 10^{-4}$ in this work.
+These equations have been nondimensionalized on the same length and time scales as the anelastic equations, use the same atmospheric profiles and assumptions, and we have explicitly assumed that the background atmosphere ($T_0, \ln\rho_0$) is in hydrostatic and thermal equilibrium in the writing of these equations.
+The new parameter $\epsilon = u_{\text{th}}^2$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows, and we use $\epsilon = 10^{-4}$ in this work.
 
@@
 \begin{equation}
-S_1 = - \frac{1}{2}\left[1 - \text{erf}\left(\frac{r' - r_{\text{th}}}{\delta}\right)\right].
+S_1 = \frac{1}{2}\left[\text{erf}\left(\frac{r' - r_{\text{th}}}{\delta}\right) - 1\right].
 \label{eqn:thermal_IC}
@@
 
-In Fig.~\ref{fig:diff}a, we display measured thermal radius vs. depth, with a detailed comparison of our 2D Anelastic and 3D Fully Compressible cases. 
-In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, aligning with the Boussinesq limit shown in \citet{lecoanet&jeevanjee2018}.
+In Fig.~\ref{fig:diff}a, we display measured thermal radius vs. depth, with a point-by-point comparison of our 2D Anelastic and 3D Fully Compressible cases. 
+In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, aligning with the Boussinesq limit shown in \LJ.
 This growth of the thermal is the result of entrainment of environmental fluid and accompanies decceleration like $w \propto d^{-1}$ in the Boussinesq limit, as is shown in Fig.~\ref{fig:results_panels}b.
@@
 
-In Fig.~\ref{fig:diff}b, the fractional difference in radius vs. depth between 3D FC and 2D AN cases is shown for the $n_\rho = [0.5, 1, 2]$ cases studied here. 
-Aside from early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the impenetrable boundary at the bottom of the domain, the 2D anelastic and 3D fully compressible simulations agree surprisingly well.
+In Fig.~\ref{fig:diff}b, the fractional difference in radius vs. depth between 3D fully compressible and 2D anelastic cases is shown for the $n_\rho = [0.5, 1, 2]$ cases studied here. 
+Aside from early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the impenetrable boundary at the bottom of the domain, the 2D anelastic and 3D fully compressible simulations agree well.
 We find differences in the radius of less than 1\% throughout the bulk of the thermal evolution for the cases studied here.
@@
 
-The measured values of each of the parameters described in section \ref{sec:theory} for each of our simulations  \ref{sec:theory} for each of our simulations  \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
-As anticipated, $\beta$ is $\mathcal{O}$(0.5) and $\chi$ is $\mathcal{0}$(1), with both decreasing slightly in value with increasing stratification, which is perhaps unsurprising in light of Fig.~\ref{fig:constants}.
-In all cases, the buoyancy $B_0$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
-In our nondimensional units, we also find that the circulation is $\mathcal{0}$(-2) for each of our cases, and decreases with increasing stratification (and decreasing vortex size).
+The measured values of each of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
+As anticipated, $\beta$ is $\mathcal{O}$(0.5) and $\chi$ is $\mathcal{O}$(1), with both decreasing slightly in value with increasing stratification, which is perhaps unsurprising in light of Fig.~\ref{fig:constants}.
+In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
+In our nondimensional units, we also find that the circulation is $\mathcal{O}$(-2) for each of our cases, and decreases with increasing stratification (and decreasing vortex size).
 
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$T_0$} & \colhead{$t_{\text{off}}$} & \colhead{$B_0$} & \colhead{$\Gamma_0$} & \colhead{$f$} & \colhead{$\chi$} & \colhead{$\beta$}	}	
+\colhead{$n_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$f$} & \colhead{$\chi$} & \colhead{$\beta$}	}	
 \startdata																																															
 \multicolumn{8}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	&  0.985	& 0.166	& -0.547 & -2.17 & 7.01	& 1.04	& 0.499	\\
-0.5 	&  0.918	& 0.704	& -0.568 & -2.12 & 7.04	& 0.976	& 0.490	\\
-1	 	&  0.827	& 1.09 	& -0.601 & -2.05 & 7.07	& 0.915	& 0.480	\\
-2	 	&  0.677	& 1.26	& -0.712 & -1.89 & 7.08	& 0.841 & 0.456	\\
-3	 	&  0.619	& 1.01	& -0.946 & -1.73 & 7.08	& 0.808	& 0.436	\\
-4	 	&  0.698	& 0.622	& -1.47	 & -1.59 & 7.10	& 0.793	& 0.422	\\
-5	 	&  0.963	& 0.327	& -2.70	 & -1.49 & 7.15	& 0.786	& 0.414	\\
-6	 	&  1.57 	& 0.064	& -5.73	 & -1.43 & 7.16	& 0.787	& 0.408	\\
+0.1 	&  24.4 	& 0.166	& -0.547 & -2.17 & 7.01	& 1.04	& 0.499	\\
+0.5 	&  24.1 	& 0.704	& -0.568 & -2.12 & 7.04	& 0.976	& 0.490	\\
+1	 	&  23.7 	& 1.09 	& -0.601 & -2.05 & 7.07	& 0.915	& 0.480	\\
+2	 	&  22.3 	& 1.26	& -0.712 & -1.89 & 7.08	& 0.841 & 0.456	\\
+3	 	&  21.2 	& 1.01	& -0.946 & -1.73 & 7.08	& 0.808	& 0.436	\\
+4	 	&  20.5 	& 0.622	& -1.47	 & -1.59 & 7.10	& 0.793	& 0.422	\\
+5	 	&  20	    & 0.327	& -2.70	 & -1.49 & 7.15	& 0.786	& 0.414	\\
+6	 	&  19.8 	& 0.064	& -5.73	 & -1.43 & 7.16	& 0.787	& 0.408	\\
 \multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations}}\\    
-0.5 	&  0.924	& 0.583	& -0.568 & -2.12 & 6.66	& 0.978	& 0.452	\\
-1	 	&  0.832	& 1.26	& -0.601 & -2.05 & 6.88	& 0.902	& 0.454	\\
-2	 	&  0.666	& 1.53	& -0.711 & -1.89 & 7.08	& 0.822	& 0.450	\\
+0.5 	&  23.8 	& 0.583	& -0.568 & -2.12 & 6.66	& 0.978	& 0.452	\\
+1	 	&  23.5 	& 1.26	& -0.601 & -2.05 & 6.88	& 0.902	& 0.454	\\
+2	 	&  22.4 	& 1.53	& -0.711 & -1.89 & 7.08	& 0.822	& 0.450	\\
 \enddata																																															
@@
 \label{sec:discussion}
-In this paper we developed a simple theory of the evolution of buoyant (or dense) vortex rings in stratified atmospheres.
+In this paper we developed a simple theory of the evolution of negatively buoyant vortex rings in stratified atmospheres.
 We showed that this theory predicts that dense thermals will experience less entrainment than boussinesq thermals due to increasing atmospheric density with depth.
@@
 
-We note that the evolution of dense thermals in stratified domains is complex, and neither the assumption of horizontal compression \citep[as in e.g.][]{brandenburg2016} or the evolution of thermals in the Boussinesq regime (as in \LJ) fully describes the behavior of these events fully.
+We note that the evolution of dense thermals in stratified domains is complex, and neither the assumption of horizontal compression \citep[as in e.g.,][]{brandenburg2016} or the evolution of thermals in the Boussinesq regime (as in \LJ) fully describes the behavior of these events fully.
 Rather, results fall somewhere in between, and theory and simulations suggest that there are two regimes of downflowing thermal behavior:
@@
 B      = 2\pi \int_0^{\mathcal{C}}\int_0^{L_z} \rho S_1 r dz dr, \qquad
-\mathcal{V} = 2\pi \int_0^{\mathcal{C}}\int_0^{L_z} 1\,r dz dr.
+\mathcal{V} = 2\pi \int_0^{\mathcal{C}}\int_0^{L_z}r dz dr.
 \end{equation}

### 2019-05-30 tex/stratified_thermals.tex
Edits to abstract & intro.

@@
 \usepackage{color}
-\newcommand{\gv}[1]{{\color{blue} #1}}
+\newcommand{\dl}[1]{{\color{blue} #1}}
 
@@
 \begin{abstract}
-Historically, large-scale convective flows called ``giant cells'' were thought to transport the Sun's luminosity from deep in the solar convection zone, but recent observations show no such flow exists.
-In place of large-scale flows, some authors have suggested the solar luminosity may instead be transported by small ``droplets'' of rapidly falling, low entropy fluid.
-This ``entropy rain'' would propagate as dense vortex rings, analogous to rising buoyant ``thermals'' in the Earth's atmosphere.
+Large-scale convective flows called giant cells were once thought to transport the Sun's luminosity in the solar convection zone, but recent observations have called their existence into question.
+In place of large-scale flows, some authors have suggested the solar luminosity may instead be transported by small droplets of rapidly falling, low entropy fluid.
+This ``entropy rain'' would propagate as dense vortex rings, analogous to rising buoyant thermals in the Earth's atmosphere.
 In this work, we develop an analytical theory describing the evolution of dense, negatively buoyant thermals.
@@
 Our results suggest that entropy rain driven at the surface of the Sun could fall into two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
-We briefly discuss difficulties for the entropy rain hypothesis in both of these regimes.
+We briefly discuss difficulties for the entropy rain hypothesis in both of these regimes. \dl{This last sentence could be clarified, but I don't know what we're trying to say here}
 \end{abstract}
@@
 Power spectra of horizontal velocities show weaker flows than anticipated at large length scales \citep{hanasoge&all2012, greer&all2015}.
-These observations cast doubt on the existence of ``giant cells'' driven by deep convection which should manifest as powerful, large-scale motions at the solar surface and throughout the solar convection zone.
-This discrepancy between theory and observations has called into question our fundamental understanding of convection, sparking numerous targeted investigations the nature of convection in the Sun  \citep{featherstone&hindman2016, omara&all2016, cossette&rast2016, kapyla&all2017, hotta2017}.
+These observations cast doubt on the existence of giant cells driven by deep convection which should manifest as powerful, large-scale motions at the solar surface. 
+This discrepancy between theory and observations has called into question our fundamental understanding of convection, sparking numerous targeted investigations into the nature of solar convection  \citep{featherstone&hindman2016, omara&all2016, cossette&rast2016, kapyla&all2017, hotta2017}.
 
-\cite{spruit1997} hypothesized that convective motions in the Sun may be driven entirely by cooling at the solar surface, and \citet{brandenburg2016} expanded upon this ``entropy rain'' hypothesis. 
-Brandenburg's work includes a careful expansion of mixing length theory to incorporate flux contributions from nonlocal convective motions, and handles this theory in a horizontally-averaged sense.
-He includes some discussion of possible flow morphologies which could be manifestations of this entropy rain, and even includes some brief simulations of propagating Hill vortices. 
-However, these simulations and discussions did not include include a fundamental piece of entropy rain: its entropic signature deviates from the background atmosphere.
-Entropy rain is dense, and the effects of buoyancy forces will modify its dynamics.
+Rather than appealing to giant cells, \cite{spruit1997} hypothesized that convective motions in the Sun may be primarily driven by cooling in narrow downflow lanes at the solar surface.
+\citet{brandenburg2016} incorporated this ``entropy rain'' concept into a non-local mixing length theory, and suggested the entropy rain could take the form of propagating vortex rings. 
+However, \citet{brandenburg2016} does not include a fundamental aspect of entropy rain: it has lower entropy than the background atmosphere.
+Entropy rain is dense, and buoyancy forces will modify its dynamics.
 
-If entropy rain does evolve into downward propagating, dense vortex rings, it is important to understand how the filling factor of these basic convective elements is affected by their negative buoyancy.
-In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the nucleus of cloud formation. 
-Atmospheric cloud-forming thermals always rise, but the term is also used for the reverse, falling process.
-The evolution of thermals in the Boussinesq limit has been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently have been studied through Direct Numerical Simulation (DNS) in the laminar and turbulent regime \citep{lecoanet&jeevanjee2018}.
-One fundamental result of these studies of thermals is that they experience a large degree of entrainment characterized by radial expansion and decceleration of propagation velocity.
-However, we do not know of a study in which the propagation of these thermals, and thus the nature of their entrainment, is affected by a significant atmospheric stratification.
+It is important to understand how the filling factor of these basic convective elements is affected by their negative buoyancy. 
+In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be basic unit of convection \citep[e.g.,][]{romps2015}. 
+Atmospheric thermals are buoyant and rise, but the term is also used for dense, falling fluid.
+We thus study the entropy rain hypothesis by investigating the evolution of individual dense thermals.
+
+Thermals in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently through Direct Numerical Simulation (DNS) \citep{lecoanet&jeevanjee2018}.
+These studies find that thermals expand radially and decelerate as they propagate.
+Such an expansion may prevent entropy rain from reaching the bottom of the solar convection.
+However, this work does not include the effects of density stratification.
 
@@
     \caption{
-	The evolution of the filling factor, or radius squared, of a buoyant vortex ring with depth is shown in an atmosphere which spans three density scale heights (the $n_\rho = 3$ case examined later in this work).
-	Overplotted in thin solid lines are the predictions for filling factor growth in the Boussinesq case (as in \LJ) and the prediction for pure horizontal compression (as in \citet{brandenburg2016}).
+	The filling factor of a dense thermal as a function of depth in an atmosphere which spans three density scale heights (the $n_\rho = 3$ case examined later in this work). 
+	Thin solid lines are the predictions for filling factor growth for the Boussinesq case (\LJ) and for pure horizontal compression \citep{brandenburg2016}.
     \label{fig:overview} }
@@
 
-In the absence of buoyantly-induced entrainment, \citet{brandenburg2016} suggests that the filling factor, $f$, of convective elements should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression.
-On the other hand, the filling factor of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth propagated.
-These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true propagation of a numerically simulated thermal in an appreciably stratified environment.
+Ignoring entropy variations, \citet{brandenburg2016} suggests the filling fraction $f$ of entropy rain should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression.
+On the other hand, the filling factor of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth of the thermal.
+These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true propagation of a numerically simulated dense thermal including both entropy variations and density stratification.
 
-In this paper, we extend the study of \citet{lecoanet&jeevanjee2018} (hereafter \LJ) to study the propagation of low-Mach number, cold thermals in stratified domains. 
-We are specifically interested in how buoyant entrainment affects the scaling of the thermal radius, or filling factor, with depth. 
-If buoyant entrainment is a dominant effect, it is possible that entropy rain would simply grow too large and stall before reaching the bottom of the solar convection zone.
-On the other hand, if the compression effects suggested by \citet{brandenburg2016} are the dominant effect, then it is possible that these thermals could propagate to the bottom of the solar convection zone, and perhaps could be the nucleus of entropy rain.
+In this paper, we extend \citet{lecoanet&jeevanjee2018} (hereafter \LJ) to study the propagation of low-Mach number, low-entropy thermals in stratified domains. 
+We are specifically interested in how the buoyancy force affects the scaling of the thermal radius, or filling factor, with depth. 
+If buoyancy dominant, it is possible that entropy rain would simply grow too large and stall before reaching the bottom of the solar convection zone.
+On the other hand, if the compression effects of \citet{brandenburg2016} are dominant, then these thermals could propagate to the bottom of the solar convection zone, validating the entropy rain picture.
 

### 2019-05-30 tex/stratified_thermals.tex
Section 2. Lots of changes to 2.2

@@
 \subsection{Phenomenological description of thermal evolution}
-We show pictorally the evolution of cold thermals from rest in Fig.~\ref{fig:evolution_colormeshes} for two different domains which span a different number of density scale heights ($n_\rho$). 
-In Fig.~\ref{fig:evolution_colormeshes}a, the evolution of a thermal in a weakly stratified domain with $n_\rho = 0.5$ is shown. 
-In Fig.~\ref{fig:evolution_colormeshes}b, the evolution of a thermal in an appreciably stratified domain with $n_\rho = 3$ is shown. 
-In both cases, the thermal's initial conditions are spherical, dense, low entropy perturbations of equal magnitude whose diameters are 5\% of the domain depth.
-This dense sphere spins up into an axisymmetric vortex ring, and the vertical cross section through this vortex ring shows two circular vorticity and entropy minima.
-We find that the $n_\rho = 0.5$ case entrains and grows with depth similarly to thermal behavior in the Boussinesq regime.
-On the other hand, the $n_\rho = 3$ case has a radius which remains approximately constant over time.
+Fig.~\ref{fig:evolution_colormeshes} depicts the descent of 3D cold thermals released from rest in domains which span a different number of density scale heights ($n_\rho$).
+The left panel shows a weakly stratified domain with $n_\rho=0.5$, whereas the right panel shows a strongly stratified domain with $n_\rho=3$.
+In both cases, the thermal is initialized with a spherical negative entropy perturbation, which a diameter of 5\% of the domain depth.
+This dense sphere spins up into an axisymmetric vortex ring, and the vertical cross section through this vortex ring shows two circular vorticity and entropy extrema.
+In the $n_\rho = 0.5$ simulation, the thermal grows with depth, similar to thermals in the Boussinesq regime.
+On the other hand, in the $n_\rho = 3$ simulation, the thermal's radius remains approximately constant.
 
@@
 All of the thermals studied in this work are laminar, similar to the Hill vortices studied by \citet{brandenburg2016}.
-Fortunately, \LJ\, showed that laminar theory describes the evolution of turbulent thermals well.
-As a result, we reserve studies of turbulent thermals in stratified domains for future work.
+Crucially, \LJ\, showed little difference between the evolution of laminar and turbulent thermals in the Boussinesq limit.
+As a result, we leave studies of turbulent thermals in stratified domains for future work.
 
-In the following sections, we will use a description of the impulse and momentum of dense vortex rings to describe the evolution of their depth and radii with time.
+In the following sections, we will use the impulse of dense vortex rings derive their depth and radii with time.
 
@@
     \caption{
-	The evolution of $\rho S_1 r^3$, the mass-weighted entropy scaled by the thermal volume, is shown for two thermals. 
-	On the left is a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights and on the right is a thermal in a strongly stratified domain with $n_\rho = 3$.
-	While both start with precisely the same initial condition, the case with low stratification expands with depth like the boussinesq case, whereas the strongly stratified thermal compresses with depth.
+	The mass-weighted entropy perturbation, $\rho S_1 r^3$, for two thermals. 
+	(left) a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights; (right) a thermal in a strongly stratified domain with $n_\rho = 3$.
+	While both start with precisely the same initial condition, the thermal in low stratification expands with depth, whereas the thermal in strong stratification compresses with depth.
     \label{fig:evolution_colormeshes} }
@@
 
-\subsection{Evolution of momentum and impulse}
-The evolution of thermals as buoyant vortex rings has been well described in the unstratified, Boussinesq limit for decades (see e.g.,~\LJ\,for a description and references).
-While many descriptions of vortex rings assume that they evolve in a self-similar state, we will lay out a description of the momentum and impulse of the thermal and show how these quantities control the evolution of the vortex ring.
+\subsection{Impulse}
 
-We study a fluid characterized by an ideal gas equation of state and focus on the ideal, low Mach number regime in an adiabatically stratified atmosphere. 
-In this regime, a linearized equation of state describes the thermodynamics well, and the fully compressible Euler momentum equation takes the form \citep{brown&all2012},
-\begin{equation}
-\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} = 
--\grad\varpi - \frac{S_1}{c_P}\bm{g},
-\label{eqn:euler_momentum}
-\end{equation}
-where $\bm{u}$ is the velocity, $\varpi = P_1 / \rho_0$ is the reduced pressure, $S = c_V\ln T - R\ln\rho$ is the specific entropy, and thermodynamics are broken down into background (subscript 0) and fluctuating (subscript 1) components.
-In this limit where the linearized equation of state is valid, $S_1 \approx c_V T_1/T_0 - R \rho_1/\rho_0$.
-In this work we find it instructive to examine the full momentum, and so multiplying this equation by the full density, we obtain,
-\begin{equation}
-\frac{\partial (\rho\bm{u})}{\partial t} + \bm{u}\cdot\grad(\rho\bm{u}) + \rho\bm{u}(\DivU)
-= -\rho\grad\varpi - \rho\frac{S_1}{c_P}\bm{g}.
-\label{eqn:rho_euler_momentum}
-\end{equation}
-Hereafter we will define the total derivative, $D/Dt \equiv \partial/\partial t + \bm{u}\cdot\grad$, and we acknowledge that the Langrangian derivative commutes with a volume integral according to 
-\begin{equation*}
-\frac{d}{dt}\int_{\mathcal{V}} f dV = \int_{\mathcal{V}} \left[\frac{Df}{Dt} + f(\DivU)\right]dV,
-\end{equation*}
-for a volume, $\mathcal{V}$, which is advected with the fluid.
-Volume-integrating Eqn.~\ref{eqn:rho_euler_momentum}, we thus find
-\begin{equation}
-\frac{d\bm{M}}{dt} = \int_{\mathcal{V}}\left(-\rho\grad\varpi - \rho\frac{S_1}{c_P}\bm{g}\right)dV,
-\label{eqn:int_momentum_eqn}
-\end{equation}
-where the volume-integrated momentum is defined $\bm{M} \equiv \int_{\mathcal{V}}\rho\bm{u} dV$.
-At this point we will make the assumption of a plane-parallel atmosphere in which the gravity is constant, $\bm{g} = -g\hat{z}$, and note that the z-component of the volume-integrated momentum evolves according to
-\begin{equation}
-\frac{d M_z}{dt} = \int_{\mathcal{V}}\left( -\rho\frac{\partial \varpi}{\partial z} + \rho g \frac{S_1}{c_P} \right)dV.
-\label{eqn:Mz_definition}
-\end{equation}
-At this stage, it is useful to define the total buoyancy,
-\begin{equation}
-B \equiv \int_{\mathcal{V}} \rho\, S_1\, \frac{g}{c_P}\, dV,
-\label{eqn:tot_buoyancy}
-\end{equation}
-as in the absence of viscosity and detrainment, this is a conserved quantity during thermal evolution (see e.g., Fig.~\ref{fig:constants}a). 
-Furthermore, in the Boussinesq limit, the work of \citet{tarshish&all2018} shows that pressure terms reduce the efficacy of the buoyancy in changing the momentum by effectively reducing the buoyant acceleration by some factor $\beta \sim 0.5$.
-As a result, we approximate the growth of a thermal's vertical momentum according to
-\begin{equation}
-\frac{d M_z}{dt} \approx \beta B.
-\label{eqn:theory_momentum}
-\end{equation}
+The evolution of thermals in the Boussinesq limit has been understood for decades (see e.g.,~\LJ\, for a description and references).
+While many theoretical descriptions rely on self-similarity arguments, we will show how the impulse of a thermal controls its evolution.
 
-We now turn our attention to the hydrodynamic impulse, which in the stratified limit can be expressed as \citep{shivamoggi2010},
+The hydrodynamic impulse is defined as \citep{shivamoggi2010},
 \begin{equation}
@@
 where $\bm{x}$ is the position vector. 
-The hydrodynamic impulse is the time-integrated work which has acted on the fluid to result in the current fluid motion. 
-Per \citet{shivamoggi2010}, changes in the impulse can be expressed as
+The impulse is the time-integrated work which has acted on the fluid to result in the current fluid motion.
+It is thus unaffected by internal forces (e.g., pressure or viscous).
+Upon integration by parts, it is obvious that the impulse encompasses the momentum of the fluid within the volume $\mathcal{V}$.
+However, one can also show that the surface terms correspond to the momentum outside the volume $\mathcal{V}$ \citep[e.g.][]{Akhmetov2009}.
+A thermal with volume $\mathcal{V}$, density $\rho$, and translating with velocity $w_{\text{th}} \hat{z}$ thus has an impulse \dl{note that 1+beta is the inverse of your old beta}
+\begin{equation}\label{eqn:momentum}
+I_z = (1+\beta) \rho \mathcal{V} w_{\text{th}},
+\end{equation}
+where $\beta$ is due to the ``virtual mass effect'' in which the thermal drags environment air along with it \citep{tarshish&all2018}.
+
+We now restrict our study to an ideal gas in the low Mach-number regime, in an adiabatic background.
+Due to rapid pressure equilibration in for low Mach-number flows, we can approximate \dl{Don't know if this is actually a good idea...}
 \begin{equation*}
-\frac{d\bm{I}}{d t} = \int_{\mathcal{V}}\frac{\partial(\rho\bm{u})}{\partial t}dV
-= B\hat{z} - \int_{\mathcal{V}}\left[\rho\grad\varpi + \Div{\rho\bm{u}\bm{u}}\right]dV ,
+\frac{\rho_1}{\rho_0} \approx \frac{S_1}{c_P},
 \end{equation*}
-where, importantly, the \emph{eulerian} time derivative of the momentum is inside of the volume integral here. 
-Under the proper specification of volumetric boundaries, the integral term is zero, and the vertical impulse of a thermal thus straightforwardly changes in time as
+where $S_1$ is the specific entropy perturbation and $c_P$ is the specific heat at constant pressure; thermodynamic variables are decomposed into background (subscript 0) and fluctuating (subscript 1) components.
+
+The rate of change of change of the impulse is
+\begin{equation*}
+\frac{d\bm{I}}{d t} = \int_\mathcal{V} \rho_1 \bm{g} dV,
+\end{equation*}
+because the surface terms completely cancel.
+It is useful to define the buoyancy perturbation,
+\begin{equation}
+B \equiv \int_{\mathcal{V}} \rho\, S_1\, \frac{g}{c_P}\, dV.
+\label{eqn:tot_buoyancy}
+\end{equation}
+such that
 \begin{equation}
@@
 \end{equation}
-We have thus retrieved the two findings on which our theory of thermal evolution will be built: \emph{both the impulse and momentum experience constant changes in time determined by the buoyant nature of the thermal}.
 
-In the low-Mach number limit in which changes in density from the background are negligible, and in the limit of a thin-core vortex ring, the impulse of a vortex ring can be approximated as
+In the limit of a low Mach-number, thin-core vortex ring, the impulse can be approximated as
 \begin{equation}
@@
 \end{equation}
-where $r$ is the radius of the thermal from its axis of symmetry to the maxima of its buoyant signature, and $\Gamma = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the circulation in a cross-section of the vortex ring.
-Integrating Eqn.~\ref{eqn:euler_momentum} reveals that changes in circulation can be calculated as
+where $r$ is the radius of the thermal from its axis of symmetry to its vorticity maximum, and $\Gamma = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the circulation in a cross-section of the vortex ring.
+The circulation can change due to baroclinic torques,
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{C}$ is the contour around the area $\mathcal{A}$ in which the circulation is contained and $d\bm{x}$ is the line integral element around that contour.
-For the case of a vortex core in which the entropic signature is contained tightly in the core, as in Fig.~\ref{fig:evolution_colormeshes}, any contour which is drawn around the vortex core should conserve circulation in the absence of viscosity.
-As a result, we will treat the circulation of a developed vortex ring as a conserved quantity.
+where $\mathcal{C}=\partial \mathcal{A}$ is the contour around the thermal's vorticity.
+For the case of a vortex core in which the entropy perturbation is contained tightly in the core, as in Fig.~\ref{fig:evolution_colormeshes}, a contour can be drawn for which $S_1\approx0$.
+Thus, there are no net baroclinic torques, and we will treat the circulation of a developed vortex ring as a conserved quantity.
 
-\subsection{Parameterized description of thermal evolution}
+\subsection{Model of thermal evolution}
 \begin{figure}[t!]
@@
     \caption{
-	Evolution traces are shown for  three quantities which we assume to be constant in our parameterized thermal theory. 
-	The circulation (a) and buoyancy (b), divided by their parameterized value for each case (see Table \ref{table:parameters}), are plotted vs. depth. 
-	We see that with increasing stratification, there is marginally more detrainment of both of these quantities, but to first order they are constant over the	thermal's transit time. 
-	In (c) the volumetric constant $f$ is shown; after significant noise during the development of the vortex ring, this quantity settles toward a value of $\mathcal{O}(7)$ throughout the thermal's transit.
+	Evolution of circulation, buoyancy perturbation, and volume factor in thermal simulations.
+	All are nearly constant after an initial spin-up phase.
+	With increasing stratification, we see marginally more detrainment (middle panel).
+	The volume factor can be approximated to be $\mathcal{O}(7)$ for all of our simulations.
     \label{fig:constants} }
@@
 
-After spinning up, we assume that the thermal is characterized by a constant buoyant signature, $B_{\text{th}}$, and constant circulation, $\Gamma_{\text{th}}$.
-While these thermals began as initial spherical perturbations, they can be modeled as having always been vortex rings which evolved from a ``virtual origin'' where the vortex ring is characterized by having a radius of zero.
-From this virtual origin, the vortex ring's momentum and impulse grow to a value of $M_0$ and $I_0$ at time $t = 0$ when the true thermal is released from rest.
+After spinning up, we assume that the thermal has a negative buoyancy, $B_{\text{th}}$, and circulation, $\Gamma_{\text{th}}$.
+While these thermals began as initial spherical perturbations, they act like vortex rings which evolved from a ``virtual origin'' where the vortex ring had zero radius.
+From this virtual origin, the vortex ring's impulse grows $I_0$ at time $t = 0$ when the true thermal is released from rest.
 
-We first note, as in Fig.~\ref{fig:constants}a, that the buoyancy in our thermals is not necessarily perfectly constant in time, and that effects like detrainment result in a minor reduction of the buoyant signature of our thermals.
-We thus express the buoyancy as 
+We find the thermal undergoes weak detrainment, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}a).
+We thus express the negative buoyancy as 
 \begin{equation}
@@
 where $\chi$ is a constant of $\mathcal{O}$(1) which represents this detrainment. 
-We then integrate Eqn.~\ref{eqn:change_in_impulse} in time,
+We then integrate Eqn.~\ref{eqn:change_in_impulse},
 \begin{equation*}
@@
 
-Combining this result with Eqn.~\ref{eqn:impulse_approx}, we retrieve our first result,
+Combining this with Eqn.~\ref{eqn:impulse_approx}, we retrieve our first main result,
 \begin{equation}
@@
 \end{equation}
-Following Eqn.~\ref{eqn:circulation} and taking $\Gamma_{\text{th}}$ to be constant (which is a decent assumption in our numerical experiments, as in Fig.~\ref{fig:constants}b), we find that the radius grows with time but this growth is damped by increasing atmospheric density.
-In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in the Boussinesq regime in \LJ. 
-We find that the inclusion of stratification adds the additional complexity of $r \propto \rho^{-1/2}$, such that downward-propagating vortex rings (as studied here) will entrain less than boussinesq thermals, and upward-propagating rings will entrain more.
-In the absence of buoyancy ($B = 0$), this result aligns with the prediction for purely horizontal compression noted by \citet{brandenburg2016} of $r^2 \propto \rho^{-1}$.
+Recall there are no net baroclinic torques, so stays $\Gamma_{\text{th}}$ nearly constant (Fig.~\ref{fig:constants}b).
+In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in \LJ.
+In the limit of strong stratification, $r \propto \rho^{-1/2}$. 
+In the absence of buoyancy ($B_{\text{th}} = 0$), this corresponds to purely horizontal compression, with $r^2 \propto \rho^{-1}$ \citep{brandenburg2016}.
 
-The momentum can likewise be simply integrated,
-\begin{equation*}
-M_z = \beta\chi B_{\text{th}} t + M_0.
-\end{equation*}
-For the proper choice of vertical velocity, $w_{\text{th}}$, and volume, $\mathcal{V}$, the momentum is also precisely 
-\begin{equation*}
-M_z = \rho \mathcal{V} w_{\text{th}}.
-\end{equation*}
+To solve for the vertical evolution of the thermal, we can use equation~\ref{eqn:momentum}.
 We approximate the volume as $\mathcal{V} = f r^3$, where $f$ is a parameter which we take to be constant.
-This assumption is perhaps not as perfect as the assumptions of constant $B_{\text{th}}$ or $\Gamma_{\text{th}}$ (see Fig.~\ref{fig:constants}c), but it is nevertheless not a bad assumption. 
-Combining our approximate expressions, and using our theoretical description of $r$ (Eqn.~\ref{eqn:r_theory}), we retrieve
+We find \dl{fix this equation}
 \begin{equation}
-\rho^{-1/2} w_{\text{th}} = \left(\frac{(\pi \Gamma_{\text{th}})^{3/2}}{f}\right)\frac{\beta\chi B_{\text{th}} t + M_0}{(\chi B_{\text{th}} t + I_0)^{3/2}}.
+\rho^{-1/2} w_{\text{th}} = \left(\frac{(\pi \Gamma_{\text{th}})^{3/2}}{f}\right)\frac{\beta\chi B_{\text{th}} t + I_0}{(\chi B_{\text{th}} t + I_0)^{3/2}}.
 \end{equation}
-Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and making the assumption that the vortex ring is at the virtual origin at $t = 0$ so that $I_0 = M_0 = 0$, an integrable expression for the evolution of thermal position over time can be retrieved,
+Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and assuming $I_0$ is small so can be neglected, we have \dl{fix this equation}
 \begin{equation}
@@
 \end{equation}
-If the atmospheric stratification in which the thermal is falling is known, this result can be integrated with the known profile of $\rho(z_{\text{th}})$ in order to find the position of the thermal as a function of time.
+This can be easily integrated given an atmospheric stratification $\rho(z)$.
 
@@
 We have assumed that viscous and conductive effects are small and can be neglected, such that the total density-weighted specific entropy in the thermal is a conserved quantity.
-We assume that vortex ring's circulation is constant, that the thermal's volume is spheroidal, and that the effects of pressure and detrainment on impulse and momentum can be parameterized as constants.
-Under these assumptions, we arrived at Eqn.~\ref{eqn:dz_theory}, which we leave in its general form here, and which we will integrate using the polytropic stratification used in our simulations in the next section.
+We assume the thermal's volume is spheroidal, and that the virtual mass effect and detrainment can be parameterized as constants.
+Under these assumptions, we arrive at Eqn.~\ref{eqn:dz_theory}.
 
-\subsection{Solution for thermal evolution in a Polytrope}
-In this work, we study an ideal gas with an adiabatic index of $\gamma = 5/3$, whose equation of state is $P = \rho T$, and whose stratification is a perfectly adiabatic polytrope,
+\subsection{Solution polytrope atmospheres}
+In this work, we study an ideal gas with an adiabatic index of $\gamma = 5/3$.
+An adiabatic polytrope satisfies
 \begin{gather}
@@
 \end{gather}
-where $m_{\text{ad}} = (\gamma-1)^{-1}$, and where the adiabatic temperature gradient in our nondimensional systems (see section \ref{sec:experiment}) is $\grad_{\text{ad}} \equiv g(e^{n_\rho/m_{\text{ad}}} - 1)/(L_z c_P)$, with $g = m_{\text{ad}} + 1$ and $L_z = 20$ is the nondimensional depth of the atmosphere in units of thermal diameters.
+where $m_{\text{ad}} = (\gamma-1)^{-1}$.
 All thermodynamic quantities are nondimensionalized such that $\rho_0 = T_0 = 1$ at $z = L_z$.
 
-Integrating Eqn.~\ref{eqn:dz_theory} under this polytropic density stratification and assuming $m_{\text{ad}} < 2$, we find
+Integrating Eqn.~\ref{eqn:dz_theory} under this polytropic density stratification, we find
 \begin{equation}
@@
 where $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma_{\text{th}}^3/(\chi B_{\text{th}})}$ and the temperature at the virtual origin is $T_{\text{th},0} = 1 + \grad_{\text{ad}}(z_{\text{th},0} - L_z)$.
-The virtual origin is located at $z = z_0$ and $t = -t_{\text{off}}$ in simulation units, which are the height and time at which the vortex ring would have had zero radius in the absence of a spin-up phase.
+The thermal is at the virtual origin, $z=z_0$, at time $t=-t_{\text{off}}$.
 The constant $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
 
-The thermal is initialized as a uniform sphere of dense fluid, and it quickly spins up into a vortex ring. 
+In our simulations, the thermal is initialized as a uniform sphere of dense fluid but it quickly spins up into a vortex ring. 
 While we do not attempt to model the spin-up phase in this paper, it can be parameterized by the buoyancy $B_{\text{th}}$, circulation $\Gamma_{\text{th}}$, as well as the virtual origin $z_{\text{th,0}}$, and temporal offset $t_{\text{off}}$.

### 2019-05-30 tex/stratified_thermals.tex
Minor changes to section 2.

@@
 \end{equation}
-where $\beta$ is due to the ``virtual mass effect'' in which the thermal drags environment air along with it \citep{tarshish&all2018}.
+where $\beta$ is due to the ``virtual mass effect'' from the environmental fluid moving together with the thermal \citep{tarshish&all2018}.
 
@@
 While these thermals began as initial spherical perturbations, they act like vortex rings which evolved from a ``virtual origin'' where the vortex ring had zero radius.
-From this virtual origin, the vortex ring's impulse grows $I_0$ at time $t = 0$ when the true thermal is released from rest.
+From this virtual origin, the vortex ring's impulse would have been $I_0$ at time $t = 0$ when the true thermal is released from rest.
 
-We find the thermal undergoes weak detrainment, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}a).
-We thus express the negative buoyancy as 
+We find the thermal undergoes weak detrainment, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}b).
+We thus express the buoyancy perturbation as 
 \begin{equation}
@@
 \end{equation}
-Recall there are no net baroclinic torques, so stays $\Gamma_{\text{th}}$ nearly constant (Fig.~\ref{fig:constants}b).
+Recall there are no net baroclinic torques, so stays $\Gamma_{\text{th}}$ nearly constant (Fig.~\ref{fig:constants}a).
 In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in \LJ.
-In the limit of strong stratification, $r \propto \rho^{-1/2}$. 
-In the absence of buoyancy ($B_{\text{th}} = 0$), this corresponds to purely horizontal compression, with $r^2 \propto \rho^{-1}$ \citep{brandenburg2016}.
+In the limit of strong stratification, $r \propto \rho^{-1/2}$, corresponding to purely horizontal compression, with $r^2 \propto \rho^{-1}$ \citep{brandenburg2016}.
 
@@
 \end{equation}
-Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and assuming $I_0$ is small so can be neglected, we have \dl{fix this equation}
+Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and assuming $I_0$ is small, we have \dl{fix this equation}
 \begin{equation}
@@
 
-To summarize, we have modeled the evolved thermal as a \emph{thin-core, axisymmetric} vortex ring which is evolving in a plane-parallel, adiabatic atmosphere, and have assumed that the motions are low Mach number such that a linearized equation of state describes the thermal well.
-We have assumed that viscous and conductive effects are small and can be neglected, such that the total density-weighted specific entropy in the thermal is a conserved quantity.
-We assume the thermal's volume is spheroidal, and that the virtual mass effect and detrainment can be parameterized as constants.
-Under these assumptions, we arrive at Eqn.~\ref{eqn:dz_theory}.
+To summarize, we model thermals as thin-core vortex rings.
+The vortex ring is parameterized by its buoyancy perturbation and circulation, which are assumed to be nearly constant after spin-up.
+The impulse increases in magnitude due to buoyancy forces (Eqn.~\ref{eqn:change_in_impulse}), and allows us to relate the size of the vortex ring (Eqn.~\ref{eqn:impulse_approx}) to the momentum of the thermal and its ambient fluid (Eqn.~\ref{eqn:momentum}).
+Assuming the thermals' volume is spheroidal and that the virtual mass effect and detrainment can be parameterized as constants, we arrive at Eqn.~\ref{eqn:dz_theory}.
 

### 2019-05-30 tex/stratified_thermals.tex
Section 3 edits.

@@
 Our theory also involves the volumetric aspect ratio of the thermal $f$, the detrainment fraction $\chi$, and the effective buoyancy $\beta$. 
-These appear to be constant or only weakly dependent on the stratification for the thermals we have simulated.
+These appear to be only weakly dependent on the stratification for the thermals we have simulated.
 
@@
 \label{sec:experiment}
-%In this work, we primarily study the evolution of 2D, azimuthally symmetric, anelastic thermals in cylindrical coordinates. 
-As a result of our theory being largely derived in the anelastic, axisymmetric limit, we have chosen to focus the bulk of our attention on our 2D, axisymmetric anelastic simulations.
-We choose to focus on 2D simulations, as they allow us to more easily study high density stratifications using highly reproducible simulations whose computational expense is low.
-We verify that select anelastic simulations produce the same results as 3D fully compressible simulations in cartesian domains.
+To test our theory, we run a series of simulations of the 3D fully compressible equations, as well as 2D simulations of the anelastic equations.
+We verify the 3D and 2D simulations produce the same results when run with the same parameters.
+Because 2D simulations are less computationally expensive, we cover a broader parameter regime.
 
-While natural processes are very turbulent, we have chosen to study the evolution of laminar thermals here. 
-As we are not aware of a developed laminar theory in the stratified regime in the literature, like the one developed here, it is useful to restrict our study to the laminar case to determine the validity of our theory.
-Furthermore, \LJ\, showed in the Boussinesq limit that the measured entrainment of turbulent thermal vortex rings is well described by laminar theory, and we have no reason to believe that result should not hold for the stratified case.
-As a result, we leave studies of turbulent thermals to future work.
+While solar convection is very turbulent, we restrict our study to laminar thermals. 
+In the Boussinesq limit, \LJ\, showed the evolution of turbulent vortex rings is well described by laminar theory; we expect this will also hold in the stratified case.
+In future work, we will apply this laminar theory to turbulent thermals with density stratification, which necessitates 3D simulations.
 
-\subsection{Anelastic Simulations}
+\subsection{2D Anelastic Simulations}
 The LBR anelastic equations are \citep{lecoanet&all2014},
@@
 where $\lilstressT$ is the viscous stress tensor in units of inverse time.
-In our azimuthally symetric, cylindrical domain, we assume that $\partial_\phi = 0$; as the initial conditions of our simulations are at rest and have no azimuthal velocity, $u_\phi$, we explicitly impose that $u_\phi = 0$; therefore $\bm{u} = u_r \hat{r} + w\hat{z}$.
+We solve these equations in cylindrical geometry, assuming axisymmetry.
 
-These equations have been nondimensionalized in the same manner as in \LJ\, such that the length scale is the diameter of the initial thermal perturbation and the velocity scale is the freefall velocity.
-The timescale is thus the freefall crossing time of this unit length. 
+Following \LJ\,, we non-dimensionalize the equations with the initial diameter of the thermal and its freefall velocity.
 These equations are then fully specified in terms of the Reynolds number and Prandtl number,
@@
 $\Delta s$ is the magnitude of the specific entropy signature of the thermal.
+The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{n_\rho/m_{\text{ad}}}-1)/(L_z c_P)$, where $L_z$ is the height of the domain.
 
@@
 
-\subsection{Fully Compressible Simulations}
-In order to verify the validity of our 2D Anelastic simulations, we evolve select thermals according to the 3D Navier Stokes equations in a cartesian domain. 
-We use the $(T, \ln\rho)$ formulation of the equations in which we have previously studied fully compressible convection at low and high Mach number \citep{lecoanet&all2014, anders&brown2017},
+\subsection{3D Fully Compressible Simulations}
+In order to verify our 2D anelastic simulations, we also simulate thermals with the 3D Navier Stokes equations. 
+We use the $(T, \ln\rho)$ formulation of the equations \citep{lecoanet&all2014, anders&brown2017},
 \begin{gather}
@@
 \end{gather}
-These equations have been nondimensionalized on the same length and time scales as the anelastic equations, use the same atmospheric profiles and assumptions, and we have explicitly assumed that the background atmosphere ($T_0, \ln\rho_0$) is in hydrostatic and thermal equilibrium in the writing of these equations.
-The new parameter $\epsilon = u_{\text{th}}^2$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows, and we use $\epsilon = 10^{-4}$ in this work.
-
-In setting the specific entropy to an equivalent condition to that specified in Eqn.~\ref{eqn:thermal_IC}, we note that it is essential that the initial perturbation be in pressure equilibrium. 
-The set of initial conditions that achieves this is
-\begin{equation}
-\ln\rho_1 = S_1/c_P, \qquad T_1 = T_0(e^{-\epsilon\ln\rho_1} - 1)/\epsilon.
-\end{equation}
+These equations are non-dimensionalized in the same way as the anelastic equations, and use the same background atmosphere.
+The new parameter $\epsilon = u_{\text{th}}^2$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows; we use $\epsilon = 10^{-4}$ in this work.
 
 \subsection{Initial conditions}
-To initialize the simulation, we specify a spherical initial specific entropy perturbation,
+The simulations is initialized with a spherical specific entropy perturbation,
 \begin{equation}
@@
 
+For the fully compressible simulations, we must also specify the density perturbation $\rho_1$.
+We pick perturbations that are in pressure equilibrium,
+\begin{equation}
+\ln\rho_1 = S_1/c_P, \qquad T_1 = T_0(e^{-\epsilon\ln\rho_1} - 1)/\epsilon.
+\end{equation}
+
 \subsection{Numerics}
-We evolve our simulations forward in time using the  Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \citep{burns&all2016, burns&all2019}. 
-For our 2D simulations, we use using an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997}, and for our 3D simulations we use the second-order semi-implicit backward differentiation formulation SBDF2 \citep{wang&ruuth2008}.
+We simulate the thermals using the  Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \citep{burns&all2016, burns&all2019}.
+The 2D simulations use using an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997}, and the 3D simulations use the second-order semi-implicit backward differentiation formulation SBDF2 \citep{wang&ruuth2008}.
 
-Our 3D simulations are decomposed on Fourier bases in the horizontal directions ($x, y \in [-L_r, L_r]$) and Chebyshev bases vertically ($z \in [0, L_z]$) with impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries ($T_1 = w = \partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).
-Our 2D simulations are decomposed on a Fourier $(z \in [0, L_z])$ and Chebyshev $(r \in [0, L_r])$ domain, with boundary conditions of $\partial_r S_1 = w = (\grad\times\bm{u})_\phi = 0$ at $r = L_r$ and $u = \partial_r(w) = \partial_r(S_1) = 0$ at $r = 0$.
+The 2D simulation domain is the direct product of a Fourier basis $(z \in [0, L_z])$ and a Chebyshev basis $(r \in [0, L_r])$.
+The boundary conditions are $\partial_r S_1 = w = (\grad\times\bm{u})_\phi = 0$ at $r = L_r$, and the regularity of the equations automatically impose $u = \partial_r(w) = \partial_r(S_1) = 0$ at $r = 0$.
+The 3D simulation domain is the direct product of Fourier bases in the horizontal directions ($x, y \in [-L_r, L_r]$) and a Chebyshev basis ($z \in [0, L_z]$).
+We impose impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries.
 

### 2019-05-30 tex/stratified_thermals.tex
Edits to section 4.

@@
 An adiabatic polytrope satisfies
-\begin{gather}
+\begin{gather}\label{eqn:T0}
 T_0 = 1 + (\grad_{\text{ad}})(z - L_z), \\
@@
 where $m_{\text{ad}} = (\gamma-1)^{-1}$.
-All thermodynamic quantities are nondimensionalized such that $\rho_0 = T_0 = 1$ at $z = L_z$.
+All thermodynamic quantities are nondimensionalized such that $\rho_0 = T_0 = 1$ at $z = L_z$, the top of the domain.
 
@@
 $\Delta s$ is the magnitude of the specific entropy signature of the thermal.
-The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{n_\rho/m_{\text{ad}}}-1)/(L_z c_P)$, where $L_z$ is the height of the domain.
+
+The background density and temperature are given by Eqs.~\ref{eqn:T0} \& \ref{eqn:polytrope}.
+The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{n_\rho/m_{\text{ad}}}-1)/(L_z c_P)$, where $L_z=20$ is the height of the domain.
 
@@
     \caption{
-	The measured depths of thermals as a function of time for all 2D Anelastic and 3D Fully compressible simulations conducted in this work are shown in (a).
-	The corresponding thermal velocities as a function of depth are shown in (b)
-	Overplotted in a thin solid line for each case are our theoretical predictions from section \ref{sec:theory} given the parameters in table \ref{table:parameters}.
+	(a) The thermal depth as a function of time for the 2D anelastic and 3D fully compressible simulations.
+	(b) The corresponding thermal velocities as a function of depth.
+	Theoretical predictions from section \ref{sec:theory} are plotted in thin solid lines for each case (see parameters in table \ref{table:parameters}).
     \label{fig:results_panels} }
@@
     \caption{
-	Measured values of radius vs. depth are plotted for both the 2D anelastic and 3D fully compressible simulations in (a). 
-	For completeness, we also include the cases in which we only studied the 2D anelastic simulations.
-	For the cases in which only the anelastic equations were solved, the theory is overplotted in a thin solid line, and similar agreement between simulations and theory is found for the cases where both equations sets were used.
-	The fractional difference between anelastic and fully compressible results are shown in (b).
+	(a) Thermal radius as a function of depth are plotted for the 2D anelastic and 3D fully compressible simulations.
+	Theoretical predictions from section \ref{sec:theory} are plotted in thin solid lines.
+	(b) The fractional difference between anelastic and fully compressible simulations.
     \label{fig:diff} }
@@
 
-In Fig. \ref{fig:results_panels}a, we show the measured depth $d_{\text{th}} = L_z - z_{\text{th}}$ of the thermal as a function of time for low and high stratification. 
+To compare to the model, we must measure the thermal's depth and radius.
+We define the thermal's depth and radius using the thermal's entropy minimum.
+For specifics on how these measurements are conducted in our simulations, we refer the reader to appendix \ref{appendix:measurements}.
+
+In Fig. \ref{fig:results_panels}a, we show the depth $d_{\text{th}} = L_z - z_{\text{th}}$ of the thermal as a function of time for simulations with different stratifications. 
 At very low stratification (e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
-As the stratification increases, the thermal begins to transit the domain more quickly and approaches the limit of $d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_z}. 
+As the stratification increases, the thermal transits the domain more quickly and approaches the limit of $d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_z}. 
 The theoretical fits for depth from the prediction of Eqn.~\ref{eqn:theory_z} are plotted over the measured data.
-Unsurprisingly, the theoretical fits are poor for early times when the thermal is spinning up from its initial spherical state into the vortex ring state.
-Once the thermal is spun up into a vortex ring, the theory shows remarkable agreement with the measured data.
+The theoretical fits are poor at early times when the thermal is spinning up from its initial spherical state into the vortex ring state.
+Once the thermal is spun up into a vortex ring, the theory shows remarkable agreement with the data.
 
-In Fig.~\ref{fig:results_panels}b, we show the corresponding thermal velocity as a function of depth with the theory overplotted again.
-As anticipated, low density ($n_\rho = 0.1$) thermals deccelerate with depth.
-We find that with increasing stratification, this decceleration stops and sufficiently stratified runs ($n_\rho \geq 3$) experience acceleration of the thermal.
+In Fig.~\ref{fig:results_panels}b, we show the corresponding thermal velocity as a function of depth.
+Low density ($n_\rho = 0.1$) thermals decelerate with depth.
+With increasing stratification, this deceleration stops and sufficiently stratified runs ($n_\rho \geq 3$) experience acceleration.
 
-In Fig.~\ref{fig:diff}a, we display measured thermal radius vs. depth, with a point-by-point comparison of our 2D Anelastic and 3D Fully Compressible cases. 
-In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, aligning with the Boussinesq limit shown in \LJ.
-This growth of the thermal is the result of entrainment of environmental fluid and accompanies decceleration like $w \propto d^{-1}$ in the Boussinesq limit, as is shown in Fig.~\ref{fig:results_panels}b.
+Fig.~\ref{fig:diff}a plots the thermal radius as a function of depth.
+In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, as is the case in the Boussinesq limit (\LJ).
+The growth of the thermal is due to entrainment of environmental fluid, which causes the thermal to decelerate like $w \propto d^{-1}$, as is shown in Fig.~\ref{fig:results_panels}b.
 However, as stratification increases, the thermal entrainment of environmental fluid decreases and it experiences less expansion.
-In the limit of large stratification ($n_\rho \geq 3$), thermals begin contracting with depth.
-This lessened entrainment is, unsurprisingly, accompanied by greater acceleration of the thermal (Fig.~\ref{fig:results_panels}).
+In the limit of large stratification ($n_\rho \geq 3$), thermals contract with depth, and the thermals accelerate as they fall.
 
-In Fig.~\ref{fig:diff}b, the fractional difference in radius vs. depth between 3D fully compressible and 2D anelastic cases is shown for the $n_\rho = [0.5, 1, 2]$ cases studied here. 
-Aside from early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the impenetrable boundary at the bottom of the domain, the 2D anelastic and 3D fully compressible simulations agree well.
-We find differences in the radius of less than 1\% throughout the bulk of the thermal evolution for the cases studied here.
+Finally, we quantify the excellent agreement between the 2D anelastic and 3D fully compressible simulations in Fig.~\ref{fig:diff}b.
+We ran simulations in both models for $n_\rho = [0.5, 1, 2]$.
+There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the simulations begin interacting with the bottom of the domain.
+Outside these times, we find differences in the radius of less than 1\%.
 This gives us confidence that our high stratification anelastic simulations are producing reliable results.
-Furthermore, this close agreement between low Mach number Fully Compressible simulations and Anelastic simulations parallels the agreement between the equation sets seen in \citet{lecoanet&all2014}.
+\citet{lecoanet&all2014} also found close agreement between low Mach-number anelastic and fully compressible simulations.
 
-The measured values of each of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
-As anticipated, $\beta$ is $\mathcal{O}$(0.5) and $\chi$ is $\mathcal{O}$(1), with both decreasing slightly in value with increasing stratification, which is perhaps unsurprising in light of Fig.~\ref{fig:constants}.
+The values of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
+As anticipated, $\beta$ is $\mathcal{O}$(0.5) and $\chi$ is $\mathcal{O}$(1), with both decreasing slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
 In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
-In our nondimensional units, we also find that the circulation is $\mathcal{O}$(-2) for each of our cases, and decreases with increasing stratification (and decreasing vortex size).
+We also find that the non-dimensional circulation is $\mathcal{O}$(-2) for each of our cases, and decreases with increasing stratification.
 
@@
 \end{deluxetable*}
-
-Throughout this section, the thermal's depth and radius refer respectively to the atmospheric depth and the radius from the axis of symmetry at which the vortex ring's entropy minimum is located.
-The velocity is simply the derivative with respect to time of that measured depth.
-For specifics on how these measurements are conducted in our simulations, we refer the reader to appendix \ref{appendix:measurements}.
 

### 2019-05-31 tex/stratified_thermals.tex
some changes to notations and updates to table 1 with new formulation

@@
 However, one can also show that the surface terms correspond to the momentum outside the volume $\mathcal{V}$ \citep[e.g.][]{Akhmetov2009}.
-A thermal with volume $\mathcal{V}$, density $\rho$, and translating with velocity $w_{\text{th}} \hat{z}$ thus has an impulse \dl{note that 1+beta is the inverse of your old beta}
+A thermal with volume $\mathcal{V}$, density $\rho$, and translating with velocity $w_{\text{th}} \hat{z}$ thus has an impulse
 \begin{equation}\label{eqn:momentum}
-I_z = (1+\beta) \rho \mathcal{V} w_{\text{th}},
+I_z = (1+k) \rho \mathcal{V} w_{\text{th}},
 \end{equation}
-where $\beta$ is due to the ``virtual mass effect'' from the environmental fluid moving together with the thermal \citep{tarshish&all2018}.
+where $k$ is due to the ``virtual mass effect'' from the environmental fluid moving together with the thermal \citep{tarshish&all2018}.
 
@@
 Due to rapid pressure equilibration in for low Mach-number flows, we can approximate \dl{Don't know if this is actually a good idea...}
+%Need to do test of pomega magnitude, or see if this eqn is pretty true.
 \begin{equation*}
@@
 To solve for the vertical evolution of the thermal, we can use equation~\ref{eqn:momentum}.
-We approximate the volume as $\mathcal{V} = f r^3$, where $f$ is a parameter which we take to be constant.
-We find \dl{fix this equation}
+We approximate the volume as $\mathcal{V} = m r^3$, where $m$ is a parameter which we take to be constant.
+We find
 \begin{equation}
-\rho^{-1/2} w_{\text{th}} = \left(\frac{(\pi \Gamma_{\text{th}})^{3/2}}{f}\right)\frac{\beta\chi B_{\text{th}} t + I_0}{(\chi B_{\text{th}} t + I_0)^{3/2}}.
+\rho^{-1/2} w_{\text{th}} = \left(\frac{(\pi \Gamma_{\text{th}})^{3/2}}{(1 + k) m}\right)(\chi B_{\text{th}} t + I_0)^{-1/2}.
 \end{equation}
-Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and assuming $I_0$ is small, we have \dl{fix this equation}
+Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and assuming $I_0$ is small, we have
 \begin{equation}
 \frac{dz_{\text{th}}}{\rho(z_{\text{th}})^{1/2}} =
-\left(\frac{\beta(\pi\Gamma_{\text{th}})^{3/2}}{f(\chi B_{\text{th}})^{1/2}}\right)\frac{dt}{t^{1/2}}.
+\left(\frac{(\pi\Gamma_{\text{th}})^{3/2}}{m(1 + k)(\chi B_{\text{th}})^{1/2}}\right)\frac{dt}{t^{1/2}}.
 \label{eqn:dz_theory}
@@
 \end{equation}
-where $C \equiv \beta \pi^{3/2} \grad_{\text{ad}} / f \sqrt{\Gamma_{\text{th}}^3/(\chi B_{\text{th}})}$ and the temperature at the virtual origin is $T_{\text{th},0} = 1 + \grad_{\text{ad}}(z_{\text{th},0} - L_z)$.
+where $C \equiv \pi^{3/2} \grad_{\text{ad}} / (1 + k) / m \sqrt{\Gamma_{\text{th}}^3/(\chi B_{\text{th}})}$ and the temperature at the virtual origin is $T_{\text{th},0} = 1 + \grad_{\text{ad}}(z_{\text{th},0} - L_z)$.
 The thermal is at the virtual origin, $z=z_0$, at time $t=-t_{\text{off}}$.
@@
 While we do not attempt to model the spin-up phase in this paper, it can be parameterized by the buoyancy $B_{\text{th}}$, circulation $\Gamma_{\text{th}}$, as well as the virtual origin $z_{\text{th,0}}$, and temporal offset $t_{\text{off}}$.
-Our theory also involves the volumetric aspect ratio of the thermal $f$, the detrainment fraction $\chi$, and the effective buoyancy $\beta$. 
+Our theory also involves the volumetric aspect ratio of the thermal $f$, the detrainment fraction $\chi$, and the effective buoyancy $k$. 
 These appear to be only weakly dependent on the stratification for the thermals we have simulated.
@@
 The values of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
-As anticipated, $\beta$ is $\mathcal{O}$(0.5) and $\chi$ is $\mathcal{O}$(1), with both decreasing slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
+As anticipated, $k$ is $\mathcal{O}$(0.5) and $\chi$ is $\mathcal{O}$(1), with both decreasing slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
 In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$f$} & \colhead{$\chi$} & \colhead{$\beta$}	}	
+\colhead{$n_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$m$} & \colhead{$\chi$} & \colhead{$k$}	}	
 \startdata																																															
 \multicolumn{8}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	&  24.4 	& 0.166	& -0.547 & -2.17 & 7.01	& 1.04	& 0.499	\\
-0.5 	&  24.1 	& 0.704	& -0.568 & -2.12 & 7.04	& 0.976	& 0.490	\\
-1	 	&  23.7 	& 1.09 	& -0.601 & -2.05 & 7.07	& 0.915	& 0.480	\\
-2	 	&  22.3 	& 1.26	& -0.712 & -1.89 & 7.08	& 0.841 & 0.456	\\
-3	 	&  21.2 	& 1.01	& -0.946 & -1.73 & 7.08	& 0.808	& 0.436	\\
-4	 	&  20.5 	& 0.622	& -1.47	 & -1.59 & 7.10	& 0.793	& 0.422	\\
-5	 	&  20	    & 0.327	& -2.70	 & -1.49 & 7.15	& 0.786	& 0.414	\\
-6	 	&  19.8 	& 0.064	& -5.73	 & -1.43 & 7.16	& 0.787	& 0.408	\\
+0.1 	&  24.6 	& 0.144	& -0.548 & -2.17 & 8.05	& 1.04	& 0.732	\\
+0.5 	&  24.2 	& 0.695	& -0.569 & -2.12 & 8.34	& 0.977	& 0.715	\\
+1	 	&  23.7 	& 1.11 	& -0.602 & -2.05 & 8.65	& 0.915	& 0.703	\\
+2	 	&  22.3 	& 1.27	& -0.713 & -1.89 & 9.23	& 0.842 & 0.682	\\
+3	 	&  21.2 	& 1.01	& -0.947 & -1.73 & 9.81	& 0.807	& 0.654	\\
+4	 	&  20.5 	& 0.615	& -1.47	 & -1.59 & 10.2	& 0.794	& 0.642	\\
+5	 	&  20.0	    & 0.425	& -2.70	 & -1.49 & 10.7	& 0.781	& 0.609	\\
+6	 	&  19.8 	& 0.041	& -5.73	 & -1.43 & 10.8	& 0.787	& 0.616	\\
 \multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations}}\\    
-0.5 	&  23.8 	& 0.583	& -0.568 & -2.12 & 6.66	& 0.978	& 0.452	\\
-1	 	&  23.5 	& 1.26	& -0.601 & -2.05 & 6.88	& 0.902	& 0.454	\\
-2	 	&  22.4 	& 1.53	& -0.711 & -1.89 & 7.08	& 0.822	& 0.450	\\
+0.5 	&  23.8 	& 0.583	& -0.568 & -2.12 & 	& 0.978	& 	\\
+1	 	&  23.5 	& 1.26	& -0.601 & -2.05 & 	& 0.902	& 	\\
+2	 	&  22.4 	& 1.53	& -0.711 & -1.89 & 	& 0.822	& 	\\
 \enddata																																															
@@
 We see blahblahblah.
+%Does thermal conduct away its buoyancy? If so, we're left with Axel's case
+%What radius does it have when it's at the bottom?
 
@@
 To find the entropy maxima vertically, we integrate $\int\rho S_1 r dr$ in our Dedalus domain, then use the spectral data of that profile to sample it on a 4096 point grid vertically, and we take the location of the minima on that grid to be the thermal height.
-To find the entropy maxima horizontally, we integrate $int \rho S_1 dz$ in our Dedalus domain, then sample the spectral data onto a 2048-point radial grid, and take the minima of that profile to be the radius of the thermal.
+To find the entropy maxima horizontally, we integrate $\int \rho S_1 dz$ in our Dedalus domain, then sample the spectral data onto a 2048-point radial grid, and take the minima of that profile to be the radius of the thermal.
 In order to find the thermal's velocity as a function of time, we use a five-point stencil to differentiate the thermal's depth, $d$,

### 2019-06-01 code/logic/post_processing.py
updated fit

@@ -40,7 +40,7 @@ def linear_fit(x, a, b):
 
 def theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=-1):
     """ The constant in stratified thermals theory """
-    return (beta * grad_T_ad * Gamma0 * np.pi**(3./2) / f) * np.sqrt(Gamma0/(B0 * chi))
+    return (grad_T_ad * Gamma0 * np.pi**(3./2) / f / (1 + beta)) * np.sqrt(Gamma0/(B0 * chi))
 
 def theory_r(t, B0, Gamma0, chi, t_off, rho_f=None):
     """ The temperature profile (vs time) from stratified thermals theory """

### 2019-06-01 code/plotting/constants.py

@@ -1,11 +1,14 @@
 import matplotlib
 matplotlib.use('Agg')
 matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+#matplotlib.rcParams['text.usetex'] = True
 matplotlib.rcParams['mathtext.fontset'] = 'custom'
 matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
 matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
 matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
-matplotlib.rcParams.update({'font.size': 9})
+#matplotlib.rcParams['mathtext.cal'] = 'DejaVu Sans:caligraphic'
+#matplotlib.rcParams['mathtext.fallback_to_cm'] = True 
+#matplotlib.rcParams.update({'font.size': 9})
 import matplotlib.pyplot as plt
 import matplotlib.gridspec as gridspec
 import numpy as np
@@ -14,9 +17,9 @@ import h5py
 #aspect = [0.35, 0.35, 0.25, 0.25, 0.25, 0.25]
 #CASES = [0.1, 0.5, 1, 2, 3, 4]
 #ROOT_DIR='../weird_form_good_2D_runs/'
-aspect = [0.25, 0.25, 0.25, 0.25, 0.25, 0.25, 0.2, 0.25]
+aspect = [0.25, 0.25, 0.25, 0.25, 0.25, 0.25, 0.25, 0.25]
 CASES = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
-ROOT_DIR='../good_2D_runs/z_bot_zero/'
+ROOT_DIR='../'#good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
 height, width = 4, 3.25 
@@ -50,26 +53,26 @@ for i, direc in enumerate(DIRS):
 
 
     fit_f = h5py.File('{:s}/thermal_analysis/fit_file.h5'.format(direc), 'r')
-    Gamma0, B0 = fit_f['Gamma0'].value, fit_f['B0'].value
+    Gamma0, B0, f0 = fit_f['Gamma0'].value, fit_f['B0'].value, fit_f['f'].value
[…]

### 2019-06-03 tex/stratified_thermals.tex
some plotting changes, etc.

@@
 
-In Fig.~\ref{fig:discussion}, we extrapolate the results of our simulations to solar convection.
-For each simulation performed, we show the behavior of our thermals if they were to fall the first $n_\rho = 10$ density scale heights of the solar convection zone, rather than the few that we were able to simulate here.
-We see blahblahblah.
+We now make an attempt to roughly estimate what simulation regime presented here would correspond to dynamics of thermals on the Sun.
+We estimate that thermal diameters would be roughly the width of solar downflows, or $0.1$ Mm.
+Using the VAL atmosphere of \citet{avrett&loeser2008}, we estimate the solar surface to have a temperature of $T_0 = 6000$ K, a density of $1.74 \times 10^{-7}$ g/cm$^3$, a sound speed of $c_s = 9.5 \times 10^5$ cm/s, and the average density of the thermal's initial depth is $\bar{\rho} = 1.17\rho_0$.
+Estimating that solar downflows have a temperature deviation of $T_1 = -500$ K \citep{borrero&bellotrubio2002}, the nondimensional entropy signature of solar downflows is $S_1/c_p \sim \gamma^{-1}\ln(1 + T1/T0) = -5.22 \times 10^{-2}$.
+Estimating solar surface gravity as $g = 2.74 \times 10^4$ cm/s$^2$, the buoyancy of such a thermal is $\tilde{B} = (4\pi/3) (L/2)^3\bar{\rho}g (S_1/c_p) = -1.52 \times 10^{17}$ g cm$^4$/s$^2$.
+Nondimensionalizing this by $N = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = np.sqrt{S_1/c_P} c_s$, we find $B = \tilde{B}/N = -3.57$, which lies between the $n_\rho = 5$ and $n_\rho = 6$ simulations we studied here.
+We assume therefore that the dynamics of such thermals in the Sun can be described as being bracketed in the range $B/2$ and $2B$.
+Interpolating and extrapolating the data in Table \ref{table:parameters}, we calculate theoretical predictions for how thermals with these buoyancies would evolve in the solar convection zone.
+
+We plot these estimates of thermal evolution in the solar convection zone in Fig.
+\ref{fig:thermal_sun_comparison}, using a simple solar interior model calculated using MESA \citep{paxton&all2011} to map the density profiles of our simulation domains onto the density profiles of the Sun.
+In Fig.
+\ref{fig:thermal_sun_comparison}a\&b, we respectively show the evolution of these thermals' radii and velocities inside of the Sun -- on both ends of our estimate window, the thermal is in the falling regime and experiences compression of its radius with corresponding increases in velocity.
+In Fig.
+\ref{fig:thermal_sun_comparison}c, we use the solar diffusivity models shown in \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r^2$) and the thermal freefall timescale over 1 Mm ($\tau_{\text{ff}} = (1\,\text{Mm})/w_{\text{th}}$), and we plot the ratio of these two timescales over the thermal's evolution.
+Throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
+We find a fractional diffusion rate over the thermal's transit of the solar convection zone of $\int_{R_\odot}^{0.7 R_\odot} \tau_\kappa^{-1} dR/w_{th} = 6.55\times 10^{-3}$ for the $B/2$ estimate, and $1.57 \times 10^{-3}$ for the $2B$ estimate.
+In either case, we estimate that the thermal loses less than 1\% of its entropic signature due to diffusion alone.
+We also estimate the amount of entropy that the thermal should lose due to viscous heating as $\int_{R_\odot}^{0.7 R_\odot} \nu w_{th}^2 / (r^2 \rho T c_P) dr / w_{th}$, and after normalizing by $S_1/c_p$, we find that the thermal generates $\mathcal{O}(10^{-4}-10^{-5})$ of its initial entropic signature.
+
+\begin{figure}[t!]
+    \includegraphics[width=\columnwidth]{thermal_sun_comparison.png}
+    \caption{
+    \label{fig:thermal_sun_comparison} }
+\end{figure}
+
 %Does thermal conduct away its buoyancy? If so, we're left with Axel's case

### 2019-06-03 code/plotting/evolution_colormeshes.py

@@ -1,7 +1,7 @@
 import matplotlib
 matplotlib.use('Agg')
 matplotlib.rcParams['font.family'] = 'DejaVu Serif'
-matplotlib.rcParams['mathtext.fontset'] = 'custom'
+#matplotlib.rcParams['mathtext.fontset'] = 'custom'
 matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
 matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
 matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
@@ -12,8 +12,8 @@ from scipy.interpolate import interp1d
 import numpy as np
 import h5py
 
-dirs = [    ('../good_2D_runs/z_bot_zero/AN_2D_thermal_nrho0.5_Re6e2_Pr1_aspect0.25_Lz20', (1, 0), (2, 18), (5, 17)) ,
-            ('../good_2D_runs/z_bot_zero/AN_2D_thermal_nrho3_Re6e2_Pr1_aspect0.25_Lz20' , (1,0), (2, 12),  (4, 5))]
+dirs = [    ('../AN_2D_thermal_nrho0.5_Re6e2_Pr1_aspect0.25_Lz20', (1, 0), (2, 18), (5, 17)) ,
+            ('../AN_2D_thermal_nrho3_Re6e2_Pr1_aspect0.25_Lz20' , (1,0), (2, 12),  (4, 5))]
 
 
 gs = gridspec.GridSpec(1000, 1000)
@@ -28,35 +28,52 @@ cax = plt.subplot(gs.new_subplotspec( (50, 50),    50, 950 ))
 plot_count = 0
 for i, ax in enumerate(axs):
     this_dir = dirs[i][0]
+    if i == 0:
+        B = -0.568
+    else:
+        B = -0.946
     for j, info in enumerate(dirs[i][1:]):
+
         filenum, imgnum = info
         print('opening file ', this_dir, filenum, imgnum)
         f  = h5py.File('{:s}/slices/slices_s{}.h5'.format(this_dir, filenum), 'r')
         cf = h5py.File('{:s}/thermal_analysis/contour_file.h5'.format(this_dir), 'r')
         ff = h5py.File('{:s}/thermal_analysis/final_outputs.h5'.format(this_dir), 'r')
+        pf = h5py.File('{:s}/thermal_analysis/post_analysis.h5'.format(this_dir), 'r')
 
[…]

### 2019-06-03 code/plotting/thermal_sun_comparison.py

@@ -1,0 +1,221 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+
+cm2Mm = 1e-8 #Mm / cm
+Rsun2cm = 6.957e10 #cm / Rsun
+Rsun2Mm = 6.957e2 #Mm / Rsun
+
+def theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=-1):
+    """ The constant in stratified thermals theory """
+    return (grad_T_ad * Gamma0 * np.pi**(3./2) / f / (1 + beta)) * np.sqrt(Gamma0/(B0 * chi))
+
+def theory_r(t, B0, Gamma0, chi, t_off, rho_f=None):
+    """ The temperature profile (vs time) from stratified thermals theory """
+    r = np.sqrt(chi*B0*(t + t_off)/np.pi/Gamma0)
+    if rho_f is None:
+        return r
+    return r/np.sqrt(rho_f(t))
+
+def theory_T(t, B0, Gamma0, f, chi, beta, t_off, T0, grad_T_ad=-1, m_ad=1.5):
+    """ The temperature profile (vs time) from stratified thermals theory """
+    C0 = theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=grad_T_ad)
+    Tpow = 1 - (m_ad/2)
+    return (2*Tpow*C0*np.sqrt(t + t_off) + T0**(Tpow))**(1./Tpow)
+
+def theory_dT_dt(t, B0, Gamma0, f, chi, beta, t_off, T0, grad_T_ad=-1, m_ad=1.5):
+    """ The temperature derivative (vs time) from stratified thermals theory """
+    C0 = theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=grad_T_ad)
+    this_T = theory_T(t, B0, Gamma0, f, chi, beta, t_off, T0, grad_T_ad=grad_T_ad, m_ad=m_ad)
+    return C0*this_T**(m_ad/2)/np.sqrt(t + t_off)
+
+def read_solar_profiles():
+    mesa_data = np.genfromtxt('sun_4.5gyr.data', skip_header=6, usecols=(2, 4)) #logR (in Rsun units), logRho (g/cm^3)
+    mesa_data = 10**(mesa_data)
+    radius    = mesa_data[:,0]*Rsun2Mm
[…]

### 2019-06-03 tex/stratified_thermals.tex
full rough paper

--- 2019-05-31 tex/stratified_thermals.tex
@@
 Our results suggest that entropy rain driven at the surface of the Sun could fall into two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
-We briefly discuss difficulties for the entropy rain hypothesis in both of these regimes. \dl{This last sentence could be clarified, but I don't know what we're trying to say here}
+We estimate that solar downflows should be in the falling regime, but should remain large enough to shield their entropic signature until they reach the base of the solar convective zone.
 \end{abstract}
@@
 %% THEORY SECTION
-\section{Theory}
+\section{Model of thermal evolution}
 \label{sec:theory}
@@
 T_0 = 1 + (\grad_{\text{ad}})(z - L_z), \\
-\rho_0 = T_0^{\,m_{\text{ad}}},
+\rho_0 = T_0^{\,n_{\text{ad}}},
 \label{eqn:polytrope}
 \end{gather}
-where $m_{\text{ad}} = (\gamma-1)^{-1}$.
+where $n_{\text{ad}} = (\gamma-1)^{-1}$.
 All thermodynamic quantities are nondimensionalized such that $\rho_0 = T_0 = 1$ at $z = L_z$, the top of the domain.
@@
 The thermal is at the virtual origin, $z=z_0$, at time $t=-t_{\text{off}}$.
-The constant $\alpha^{-1} = 1 - m_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
+The constant $\alpha^{-1} = 1 - n_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
 
@@
 %% EXPERIMENT SECTION
-\section{Numerical Experiment} 
+\section{Simulation setup} 
 \label{sec:experiment}
@@
 The background density and temperature are given by Eqs.~\ref{eqn:T0} \& \ref{eqn:polytrope}.
-The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{n_\rho/m_{\text{ad}}}-1)/(L_z c_P)$, where $L_z=20$ is the height of the domain.
+The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{n_\rho/n_{\text{ad}}}-1)/(L_z c_P)$, where $L_z=20$ is the height of the domain.
 
@@
 
-The 2D simulation domain is the direct product of a Fourier basis $(z \in [0, L_z])$ and a Chebyshev basis $(r \in [0, L_r])$.
+The 2D simulation domain is the direct product of a Fourier basis $(z \in [-L_z/4, L_z])$ and a Chebyshev basis $(r \in [0, L_r])$.
 The boundary conditions are $\partial_r S_1 = w = (\grad\times\bm{u})_\phi = 0$ at $r = L_r$, and the regularity of the equations automatically impose $u = \partial_r(w) = \partial_r(S_1) = 0$ at $r = 0$.
@@
 We impose impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries.
+In all of our simulations we specify $L_z = 20$ and $L_r = 5$.
+We extend our 2D simulation domains to $z = -L_z/4$ because those simulations are vertically periodic.
+This extension allows us to study the full transit of the thermal above $z = 0$ and terminate the simulation before it begins to wrap through the bottom of the periodic domain.
 
@@
 %% RESULTS SECTION
-\section{Results}
+\section{Model verification}
 \label{sec:results}
@@
 \multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations}}\\    
-0.5 	&  23.8 	& 0.583	& -0.568 & -2.12 & 	& 0.978	& 	\\
-1	 	&  23.5 	& 1.26	& -0.601 & -2.05 & 	& 0.902	& 	\\
-2	 	&  22.4 	& 1.53	& -0.711 & -1.89 & 	& 0.822	& 	\\
+0.1 	&  23.4 	& -0.337& -0.547 & -2.17 & 8.98	& 1.06	& 0.636	\\
+0.5 	&  23.8 	& 0.572	& -0.568 & -2.12 & 8.79	& 0.978	& 0.678	\\
+1	 	&  23.6 	& 1.15	& -0.601 & -2.05 & 8.87	& 0.907	& 0.689	\\
+2	 	&  22.9 	& 2.88	& -0.699 & -1.89 & 9.24	& 0.776	& 0.706	\\
 \enddata																																															
@@
 %% CONCLUSION SECTION
-\section{Conclusion \& Discussion}
+\section{Discussion \& Conclusion}
 \label{sec:discussion}
@@
 However, we note that both the falling and stalling regimes observed here could result in interesting problems for the entropy rain hypothesis. 
-If solar convection were comprised of thermals in the stalling regime, it is unlikely that such elements would ever make it to the base of the solar convection zone.
-Rather, we expect that they would stall closer to the solar surface and deposit their entropy signature there. 
-This could be seen as agreeing with the hypothesis of supergranulation as the largest buoyantly driven scale of solar motion.
+If solar convection were comprised of thermals in the stalling regime, such convective elements would grow enormously in size and slow down very close to the solar surface.
+In a perfectly quiescent atmosphere, these very slow, very large convective elements would propagate to the base of the convection zone over enormous timescales, but their large length scales would likely shield them from any dissipative effects.
+However, the solar convection zone is highly turbulent, and we expect that any large, coherent, and slowly propagating structures would be torn apart by turbulent motions.
 
 On the other hand, if solar convection is comprised of thermals in the falling regime, then it is not out of the question for solar surface elements to reach deep into the Sun.
-While vortex rings in the falling regime would theoretically be able to reach the bottom of the solar convection zone, the compression effects that occur as they shrink could cause problems.
-For example, it is possible that these thermals could shrink to the point where conductivity becomes important, or as their length scales decrease and velocities increase, viscous heating could become an important effect and essentially erase the buoyant signature of these entropy rain droplets.
+Such vortex rings in the falling regime would theoretically be able to reach the bottom of the solar convection zone, and the effects of buoyancy which counteract some of the natural compressional effects of the atmosphere, could shield the thermal from dissipative effects.
+In this absence of this buoyant expansion, we anticipate that falling vortices in the solar convection zone would shrink to the point where conductivity could become important.
+However, due to the presence of buoyant entrainment, thermals in nature are likely shielded from conductive effects.
 
-In Fig.~\ref{fig:discussion}, we extrapolate the results of our simulations to solar convection.
-For each simulation performed, we show the behavior of our thermals if they were to fall the first $n_\rho = 10$ density scale heights of the solar convection zone, rather than the few that we were able to simulate here.
-We see blahblahblah.
+In order to determine what behavioral regime thermals would occupy in the Sun, we will now estimate which of the simulations presented in this work could most accurately describe entropy rain in the Sun.
+We estimate that thermal diameters would be roughly the width of solar downflows, or $L = 0.1$ Mm.
+Using the VAL atmosphere of \citet{avrett&loeser2008}, we estimate the solar surface to have a temperature of $T_0 = 6000$ K, a density of $\rho_0 = 1.74 \times 10^{-7}$ g/cm$^3$, a sound speed of $c_s = 9.5 \times 10^5$ cm/s, and the average density over the radial extent of the thermal is $\bar{\rho} = 1.17\rho_0$.
+Estimating that solar downflows have a temperature deviation of $T_1 = -500$ K \citep{borrero&bellotrubio2002}, the nondimensional entropy signature of solar downflows is $S_1/c_p \sim \gamma^{-1}\ln(1 + T_1/T_0) = -5.22 \times 10^{-2}$.
+Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$, the buoyancy of such a thermal is $\tilde{B} \approx (4\pi/3) (L/2)^3\bar{\rho}g (S_1/c_p) = -1.52 \times 10^{17}$ g cm$^4$/s$^2$.
+Nondimensionalizing this by $N = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B = \tilde{B}/N = -3.57$, which lies between the $n_\rho = 5$ and $n_\rho = 6$ simulations we studied here.
+
+We assume that our estimate for $B$ could be off by a factor of two, and thus bracket the behavior of solar thermals as having $[B_\ell, B_u] = 0.5B, 2B$.
+Interpolating and extrapolating the data in Table \ref{table:parameters}, we calculate theoretical predictions for how thermals with these buoyancies would evolve in the solar convection zone.
+We plot these estimates of thermal evolution in the solar convection zone in Fig.
+\ref{fig:thermal_sun_comparison}, using a simple solar interior model calculated using MESA \citep{paxton&all2011} to map the density profiles of our simulation domains onto the density profile of the Sun.
+In Fig. \ref{fig:thermal_sun_comparison}a\&b, we respectively show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
+We use the solar diffusivity models shown in \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r^2$) and the thermal freefall timescale over 1 Mm ($\tau_{\text{ff}} = (1\,\text{Mm})/w_{\text{th}}$).
+In Fig. \ref{fig:thermal_sun_comparison}c, we plot the ratio of these two timescales over the thermal's evolution.
+
+In general, we find that our entire estimated window for our thermals exists in the falling regime and these thermals experience radial compression with corresponding increases in velocity.
+Furthermore, throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
+We find a fractional diffusion rate over the thermal's transit of the solar convection zone of $\int_{R_\odot}^{0.7 R_\odot} \tau_\kappa^{-1} dR/w_{th} = [6.55, 1.57]\times 10^{-3}$ for $[B_\ell, B_u]$.
+In other words, throughout our bracketing interval, we estimate that the thermal loses less than 1\% of its entropic signature to diffusion.
+We similarly estimate the amount of entropy that the thermal should lose due to viscous heating as $(S_1/c_p)^{-1}\int_{R_\odot}^{0.7 R_\odot} \nu w_{th}^2 / (r^2 \rho T c_P) dr / w_{th} = [1.17, 0.17] \times 10^{-4}$ for $[B_\ell, B_u]$.
+
+``Entropy rain'' is the hypothesis that narrow downflows can transport the luminosity of the Sun via enthalpy fluxes.
+If the rain's entropy diffuses away before it hits the bottom, then it cannot transport the flux.
+We find that with our more accurate model for thermal propagation, the thermal maintains its entropy all the way to the base of the convection zone, and entropy rain is a possible mechanism for transporting the solar luminosity.
+
+\begin{figure}[t!]
+    \includegraphics[width=\columnwidth]{thermal_sun_comparison.png}
+    \caption{
+	(a) Bounds on the evolution of the radii of entropy rain in the Sun are shown and compared to what the radii would be under purely horizontal compression.
+	(b) The velocities of the thermals in the estimated boundaries are shown. 
+	(c) The estimated ratio of the thermal diffusion timescale of the thermals normalized by the thermal's freefall timescale over 1 Mm is shown.
+	Diffusivities are calculated using the realistic solar-like diffusion profiles of \citet{brown2011}.
+    \label{fig:thermal_sun_comparison} }
+\end{figure}
+
 %Does thermal conduct away its buoyancy? If so, we're left with Axel's case
@@
 
-\begin{deluxetable*}{c c c c c c}
+\begin{deluxetable*}{c c c c c }
 \tabletypesize{\footnotesize}
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$L_r$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{\text{evolution}}$} & \colhead{safety}	}	
+\colhead{$n_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{\text{evolution}}$} & \colhead{safety}	}	
 \startdata																																															
-\multicolumn{6}{l}{\textbf{2D Anelastic Simulations}}\\
-0.1 	& 	5				&	128			& 512			& 50 	&	0.6	\\
-0.5 	& 	5				&	128			& 512			& 45 	&	0.6	\\
-1	 	& 	5				&	128			& 512			& 41 	&	0.6	\\
-2	 	& 	5				&	256			& 1024			& 34	&	0.4	\\
-3	 	& 	5				&	256			& 1024			& 29	&	0.4	\\
-4	 	& 	5				&	256			& 1024			& 26 	&	0.3	\\
-5	 	& 	5				&	256			& 1536			& 25 	&	0.14	\\
-6	 	& 	5				&	256			& 1536			& 23 	&	0.08	\\
-\multicolumn{6}{l}{\textbf{3D Fully Compressible Simulations}}\\
-0.5 	& 	5				&	256			& 512			& 42.5 		&	0.2	\\
-1	 	& 	4				&	256			& 512			& 38 	 	&	0.2	\\
-2	 	& 	3.5				&	256			& 1536			& 31.75 	&	0.2	\\
+\multicolumn{5}{l}{\textbf{2D Anelastic Simulations}}\\
+0.1 	& 		128			& 512			& 50 	&	0.6	\\
+0.5 	& 		128			& 512			& 45 	&	0.6	\\
+1	 	& 		128			& 512			& 41 	&	0.6	\\
+2	 	& 		128			& 1024			& 34	&	0.4	\\
+3	 	& 		192			& 1024			& 29	&	0.4	\\
+4	 	& 		256			& 1024			& 26 	&	0.3	\\
+5	 	& 		256			& 1536			& 25 	&	0.14	\\
+6	 	& 		256			& 1536			& 23 	&	0.08	\\
+\multicolumn{5}{l}{\textbf{3D Fully Compressible Simulations}}\\
+0.1 	& 		256			& 512			& 50 		&	0.15	\\
+0.5 	& 		256			& 512			& 45 		&	0.15	\\
+1	 	& 		256			& 512			& 41	 	&	0.15	\\
+2	 	& 		256			& 1536			& 34    	&	0.1	\\
 \enddata																																															

### 2019-06-03 code/plotting/thermal_sun_comparison.py

@@ -160,10 +160,14 @@ for i in range(2):
     solar_radii.append(rho2r(rho_outs[i]*(rho_top/rho_outs[i][0])))
     plt.plot(solar_radii[i]/(Rsun2Mm), r_outs[i]*(L/2/r_outs[i][0]), c='k', lw=0.5*(i+1))
 
+plt.plot(solar_radii[0]/(Rsun2Mm), (L/2)/(rho_outs[0]/rho_outs[0][0])**(1./2), c='k', lw=2)
+ax.text(0.69, 8e-5, r'$r \propto \rho^{-1/2}$')
+ax.text(0.69, 7e-3, 'thermals')
+
 #Make plot pretty
 plt.xlim(0.68, 0.995)
 plt.yscale('log')
-plt.ylim(1e-3, 1e-1)
+plt.ylim(1e-5, 1e-1)
 plt.ylabel('radius (Mm)')
 
 ax = fig.add_subplot(3,1,2)

### 2019-06-04 tex/stratified_thermals.tex
conclusion rework, table captions, appendices updates

@@
 \begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{evolution_colormeshes.png}
+    \includegraphics[width=\columnwidth]{evolution_colormeshes.pdf}
     \caption{
-	The mass-weighted entropy perturbation, $\rho S_1 r^3$, for two thermals. 
-	(left) a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights; (right) a thermal in a strongly stratified domain with $n_\rho = 3$.
+	Entropy perturbations, scaled by density and thermal volume, are shown.
+	For visualization purposes in the evolved state, $\mathcal{V}$ is an approximation of the volume of the torus that the entropy occupies rather than the full thermal ellipsoidal volume.
+	(a) A thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights; (b) a thermal in a strongly stratified domain with $n_\rho = 3$.
 	While both start with precisely the same initial condition, the thermal in low stratification expands with depth, whereas the thermal in strong stratification compresses with depth.
@@
 
-The values of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
-As anticipated, $k$ is $\mathcal{O}$(0.5) and $\chi$ is $\mathcal{O}$(1), with both decreasing slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
-In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
-We also find that the non-dimensional circulation is $\mathcal{O}$(-2) for each of our cases, and decreases with increasing stratification.
-
 \begin{deluxetable*}{c c c c c c c c}
@@
 \enddata																																															
-\tablecomments{ }
+\tablecomments{ 
+Parameters presented in this table are best fits to simulation output data in the range $z = [0.1 L_z, 0.65 L_z]$.
+Above this range, the thermal is still spinning up from initial conditions; below this range, 3D cases are heavily interacting with the bottom boundary.}
 \end{deluxetable*}
 
+The values of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
+As anticipated, $\chi$ is $\mathcal{O}$(1) and decreases slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
+In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
+We also find that the non-dimensional circulation is $\mathcal{O}$(-2) for each of our cases, and decreases with increasing stratification.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% CONCLUSION SECTION
-\section{Discussion \& Conclusion}
-\label{sec:discussion}
-In this paper we developed a simple theory of the evolution of negatively buoyant vortex rings in stratified atmospheres.
-We showed that this theory predicts that dense thermals will experience less entrainment than boussinesq thermals due to increasing atmospheric density with depth.
-We performed 2D anelastic simulations of thermal evolution for varying degrees of stratification and showed that our parameterized theory describes the evolution of thermals in these systems remarkably well.
-Furthermore, we verified the validity of our anelastic simulations with select 3D fully compressible simulations of thermal evolution and found agreement to under 1\%.
-
-We note that the evolution of dense thermals in stratified domains is complex, and neither the assumption of horizontal compression \citep[as in e.g.,][]{brandenburg2016} or the evolution of thermals in the Boussinesq regime (as in \LJ) fully describes the behavior of these events fully.
+%% SOLAR EXTENSION SECTION
+\section{Implications for entropy rain hypothesis}
+\label{sec:implications}
+Our theory shows that the evolution of dense thermals in stratified domains is complex.
+Neither the assumption of pure compression \citep[as in e.g.,][]{brandenburg2016} nor the evolution of thermals in the Boussinesq regime (\LJ) fully describes thermal behavior.
 Rather, results fall somewhere in between, and theory and simulations suggest that there are two regimes of downflowing thermal behavior:
@@
 \item A low-stratification ``stalling'' regime, in which the thermal entrains environmental fluid and slows down, acting much like the Boussinesq regime, and
-\item A high-stratification ``falling'' regime, in which the thermal falls fast enough that compression due to the atmospheric stratification results in minimal entrainment and the thermal accelerates as it falls deeper into the atmosphere.
+\item A high-stratification ``falling'' regime, in which the thermal falls sufficiently fast that atmospheric compression dominates over entrainment and the thermal accelerates as it falls deeper into the atmosphere.
 \end{enumerate}
+We note that both of these regimes could have interesting implications for the entropy rain hypothesis.
 
-However, we note that both the falling and stalling regimes observed here could result in interesting problems for the entropy rain hypothesis. 
-If solar convection were comprised of thermals in the stalling regime, such convective elements would grow enormously in size and slow down very close to the solar surface.
-In a perfectly quiescent atmosphere, these very slow, very large convective elements would propagate to the base of the convection zone over enormous timescales, but their large length scales would likely shield them from any dissipative effects.
-However, the solar convection zone is highly turbulent, and we expect that any large, coherent, and slowly propagating structures would be torn apart by turbulent motions.
+If the nucleus of solar convection were thermals in the stalling regime, convective elements would grow enormously in size and slow down very close to the solar surface.
+In a perfectly quiescent atmosphere, these slow, large convective elements would eventually propagate to the base of the convection zone over long timescales.
+In fact, their large length scales would likely help shield them from any dissipative effects despite their low velocities.
+However, the solar convection zone is highly turbulent, and we expect that a more likely outcome for such large, coherent, and slowly propagating structures is that they would be torn apart by turbulent motions.
 
-On the other hand, if solar convection is comprised of thermals in the falling regime, then it is not out of the question for solar surface elements to reach deep into the Sun.
-Such vortex rings in the falling regime would theoretically be able to reach the bottom of the solar convection zone, and the effects of buoyancy which counteract some of the natural compressional effects of the atmosphere, could shield the thermal from dissipative effects.
-In this absence of this buoyant expansion, we anticipate that falling vortices in the solar convection zone would shrink to the point where conductivity could become important.
-However, due to the presence of buoyant entrainment, thermals in nature are likely shielded from conductive effects.
+On the other hand, if solar convection is comprised of thermals in the falling regime, then it is likely that solar surface elements would reach deep into the Sun.
+Neglecting buoyancy, we expect that downward propagating vortex rings in the solar convection zone would likely compress to sizes on which conductivity could become important.
+Our theory of thermals suggests that, instead, buoyancy counteracts some of the compressional effects of stratification, and could help convective elements maintain coherency as they cross the solar convection zone.
 
-In order to determine what behavioral regime thermals would occupy in the Sun, we will now estimate which of the simulations presented in this work could most accurately describe entropy rain in the Sun.
-We estimate that thermal diameters would be roughly the width of solar downflows, or $L = 0.1$ Mm.
-Using the VAL atmosphere of \citet{avrett&loeser2008}, we estimate the solar surface to have a temperature of $T_0 = 6000$ K, a density of $\rho_0 = 1.74 \times 10^{-7}$ g/cm$^3$, a sound speed of $c_s = 9.5 \times 10^5$ cm/s, and the average density over the radial extent of the thermal is $\bar{\rho} = 1.17\rho_0$.
-Estimating that solar downflows have a temperature deviation of $T_1 = -500$ K \citep{borrero&bellotrubio2002}, the nondimensional entropy signature of solar downflows is $S_1/c_p \sim \gamma^{-1}\ln(1 + T_1/T_0) = -5.22 \times 10^{-2}$.
-Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$, the buoyancy of such a thermal is $\tilde{B} \approx (4\pi/3) (L/2)^3\bar{\rho}g (S_1/c_p) = -1.52 \times 10^{17}$ g cm$^4$/s$^2$.
-Nondimensionalizing this by $N = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B = \tilde{B}/N = -3.57$, which lies between the $n_\rho = 5$ and $n_\rho = 6$ simulations we studied here.
-
-We assume that our estimate for $B$ could be off by a factor of two, and thus bracket the behavior of solar thermals as having $[B_\ell, B_u] = 0.5B, 2B$.
-Interpolating and extrapolating the data in Table \ref{table:parameters}, we calculate theoretical predictions for how thermals with these buoyancies would evolve in the solar convection zone.
-We plot these estimates of thermal evolution in the solar convection zone in Fig.
-\ref{fig:thermal_sun_comparison}, using a simple solar interior model calculated using MESA \citep{paxton&all2011} to map the density profiles of our simulation domains onto the density profile of the Sun.
-In Fig. \ref{fig:thermal_sun_comparison}a\&b, we respectively show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
-We use the solar diffusivity models shown in \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r^2$) and the thermal freefall timescale over 1 Mm ($\tau_{\text{ff}} = (1\,\text{Mm})/w_{\text{th}}$).
-In Fig. \ref{fig:thermal_sun_comparison}c, we plot the ratio of these two timescales over the thermal's evolution.
-
-In general, we find that our entire estimated window for our thermals exists in the falling regime and these thermals experience radial compression with corresponding increases in velocity.
-Furthermore, throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
-We find a fractional diffusion rate over the thermal's transit of the solar convection zone of $\int_{R_\odot}^{0.7 R_\odot} \tau_\kappa^{-1} dR/w_{th} = [6.55, 1.57]\times 10^{-3}$ for $[B_\ell, B_u]$.
-In other words, throughout our bracketing interval, we estimate that the thermal loses less than 1\% of its entropic signature to diffusion.
-We similarly estimate the amount of entropy that the thermal should lose due to viscous heating as $(S_1/c_p)^{-1}\int_{R_\odot}^{0.7 R_\odot} \nu w_{th}^2 / (r^2 \rho T c_P) dr / w_{th} = [1.17, 0.17] \times 10^{-4}$ for $[B_\ell, B_u]$.
-
-``Entropy rain'' is the hypothesis that narrow downflows can transport the luminosity of the Sun via enthalpy fluxes.
-If the rain's entropy diffuses away before it hits the bottom, then it cannot transport the flux.
-We find that with our more accurate model for thermal propagation, the thermal maintains its entropy all the way to the base of the convection zone, and entropy rain is a possible mechanism for transporting the solar luminosity.
+We now estimate what the behavior of thermals in the Sun would be based on the simulations presented in this work.
+To do so, we will approximate the dimensional buoyancy perturbation of Eqn.~\ref{eqn:tot_buoyancy} as $\tilde{B} = \rho \mathcal{V} g (S_1/c_p)$, and calculate this quantity for thermals launched from the solar photosphere, assuming that solar downflow lanes quickly break up into thermals.
+Using the VAL atmospheric data of \citet{avrett&loeser2008}, we estimate the solar surface to have a temperature of $T_0 \approx 6000$ K, a density of $\rho_0 \approx 1.74 \times 10^{-7}$ g/cm$^3$, and a sound speed of $c_s = 9.5 \times 10^5$ cm/s.
+We estimate that thermal diameters would be roughly the width of downflow lanes ($L_{\text{th}} = 0.1$ Mm), and the average atmospheric density over the first $L_{\text{th}}$ of the solar interior is $\bar{\rho} = 1.17\rho_0$.
+Estimating downflows to have a temperature deviation of $T_1 = -500$ K \citep{borrero&bellotrubio2002}, the nondimensional entropy signature of solar downflows is $S_1/c_p \sim \gamma^{-1}\ln(1 + T_1/T_0) = -5.22 \times 10^{-2}$.
+Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$, the buoyancy of a spherical thermal is 
+$$
+\tilde{B} \approx \bar{\rho}\left[\frac{4\pi}{3} \left(\frac{L}{2}\right)^3\right] g \frac{S_1}{c_P} = -1.52 \times 10^{17} \text{g cm}^4/\text{s}^2.
+$$
+Nondimensionalizing this by $N = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B = \tilde{B}/N = -3.57$, which lies between the $n_\rho = 5$ and $n_\rho = 6$ simulations we studied here (see table \ref{table:parameters}).
 
 \begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{thermal_sun_comparison.png}
+    \includegraphics[width=\columnwidth]{thermal_sun_comparison.pdf}
     \caption{
@@
 
-%Does thermal conduct away its buoyancy? If so, we're left with Axel's case
-%What radius does it have when it's at the bottom?
+Due to the numerous assumptions made in calculating $B$, we assume this estimate is only accurate to within a factor of two, and thus study thermals in the interval $[B_\ell, B_u] = 0.5B, 2B$.
+Interpolating and extrapolating the data in Table \ref{table:parameters}, we use Eqns.~\ref{eqn:r_theory} \& \ref{eqn:theory_z} to calculate theoretical predictions for how thermals with these buoyancies would evolve over extended atmospheres like the solar convection zone.
+Using a simple solar interior model calculated using MESA \citep{paxton&all2011} to map the density profiles of our simulation domains onto the density profile of the Sun, we plot the evolution of thermals in our estimated interval in Fig.
+\ref{fig:thermal_sun_comparison}.
+In Fig. \ref{fig:thermal_sun_comparison}a\&b, we respectively show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
+We use the solar diffusivity models shown in \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r^2$) and the thermal freefall timescale over 1 Mm ($\tau_{\text{ff}} = [1\,\text{Mm}]/w_{\text{th}}$).
+In Fig. \ref{fig:thermal_sun_comparison}c, we plot the ratio of these two timescales over the thermal's evolution.
 
+We find that our estimated bracket for solar thermal behavior is in the falling regime.
+These thermals experience radial compression with corresponding increases in velocity, but experience much less compression than a naive approximation based on the density stratification would suggest.
+Furthermore, throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
+We find a fractional diffusion rate over the thermal's transit of the solar convection zone of 
+$$
+\int_{R_\odot}^{0.7 R_\odot} \tau_\kappa^{-1} \frac{dR}{w_{th}} = [6.55, 1.57]\times 10^{-3}\,\text{for}\,[B_\ell, B_u].
+$$
+We similarly estimate the amount of entropy that the thermal should lose due to viscous heating as 
+$$
+\frac{1}{(S_1)}\int_{R_\odot}^{0.7 R_\odot} \nu \frac{1}{\rho T}\frac{w_{th}^2}{r^2}\frac{dr}{w_{th}} = [1.17, 0.17] \times 10^{-4}\,\text{for}\,[B_\ell, B_u].
+$$
+In other words, throughout our bracketing interval, we estimate that the thermal loses less than 1\% of its entropic signature to diffusion, and approximately 0.01\% of its signature due to viscous heating.
+These estimates suggest that entropy rain in the form of thermals could feasibly transport the solar luminosity.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% CONCLUSION SECTION
+\section{Summary \& Conclusion}
+\label{sec:discussion}
+In this paper we developed a simple theory of the evolution of negatively buoyant vortex rings in stratified atmospheres.
+We showed that this theory predicts that dense thermals will experience less entrainment than boussinesq thermals due to increasing atmospheric density with depth.
+Similarly, we showed that these thermals experience less compression than would be expected due to pure atmosphreic compression of a neutral vortex ring.
+We performed 2D anelastic simulations of thermal evolution for varying degrees of stratification and showed that our parameterized theory describes the evolution of thermals in these systems remarkably well.
+Furthermore, we verified the validity of our anelastic simulations with select 3D fully compressible simulations of thermal evolution and found agreement to under 1\%.
+We noted that the evolution of dense thermals in stratified domains is complex, but can be classified into a near-Boussinesq ``stalling'' and a high-stratification ``falling'' regime.
+An estimate of the entropic nature of solar downflows suggests that thermals launched from the solar surface would exhibit behavior in the falling regime.
+
+The ``Entropy rain'' hypothesis states that narrow downflows can transport the luminosity of the Sun via enthalpy fluxes.
+If the rain stalls near the surface or its entropy diffuses away before it hits the bottom, then it cannot transport the flux.
+We find that with our more accurate model for thermal propagation, solar thermals should maintain their entropy all the way to the base of the convection zone, and entropy rain is a possible mechanism for transporting the solar luminosity.
+
+$\,$\newline$\,$
 \begin{acknowledgements}
@@
 Throughout this work, we frequently report the thermal's radius or its depth.
-We measure the thermal's radius and height as the radius from the axis of symmetry and the height from the bottom of the domain at which the thermal's vortex core is located.
-To measure this, we locate the maxima of the entropy.
-To find the entropy maxima vertically, we integrate $\int\rho S_1 r dr$ in our Dedalus domain, then use the spectral data of that profile to sample it on a 4096 point grid vertically, and we take the location of the minima on that grid to be the thermal height.
-To find the entropy maxima horizontally, we integrate $\int \rho S_1 dz$ in our Dedalus domain, then sample the spectral data onto a 2048-point radial grid, and take the minima of that profile to be the radius of the thermal.
+We measure the thermal's radius and height as the radius from the axis of symmetry and the height above $z = 0$ at which the thermal's vortex core is located.
+We assume that the vortex core is located at the thermal's entropy minima.
+To find the entropy minima vertically, we integrate $\int\rho S_1 r dr$ in our Dedalus domain, then use the spectral data of that profile to sample it on a 4096-point vertical grid; we take the location of the minima on that grid to be the thermal height.
+To find the entropy minima horizontally, we integrate $\int \rho S_1 dz$ in our Dedalus domain, then sample the spectral data onto a 2048-point radial grid, and take the minima of that profile to be the radius of the thermal.
 In order to find the thermal's velocity as a function of time, we use a five-point stencil to differentiate the thermal's depth, $d$,
@@
 \begin{equation}
-\Gamma = \int_0^{\mathcal{C}}\int_0^{L_z} (\grad\times\bm{u})_\phi dz dr, \qquad
-B      = 2\pi \int_0^{\mathcal{C}}\int_0^{L_z} \rho S_1 r dz dr, \qquad
-\mathcal{V} = 2\pi \int_0^{\mathcal{C}}\int_0^{L_z}r dz dr.
+\Gamma = \int_0^{L_z}\int_0^{\mathcal{C}} (\grad\times\bm{u})_\phi dr\,dz, \qquad
+B      = 2\pi \int_0^{L_z}\int_0^{\mathcal{C}} \rho S_1 r dr\,dz, \qquad
+\mathcal{V} = 2\pi \int_0^{L_z}\int_0^{\mathcal{C}}r dr\,dz.
 \end{equation}
 
-\section{Thermal Tracking}
+\section{Thermal Tracking Algorithm}
 \label{appendix:tracking}
-We use a thermal tracking algorithm very similar to the one used in  \citet{lecoanet&jeevanjee2018} and inspired by the work of \citet{romps&all2015} in order to determine the full extent of the thermal, as pictured by the elliptical outlines in Fig.~\ref{fig:evolution_colormeshes}
+We use a thermal tracking algorithm very similar to the one used in  \citet{lecoanet&jeevanjee2018} and inspired by the work of \citet{romps&all2015} in order to determine the full extent of the thermal, as pictured by the elliptical outlines in Fig.~\ref{fig:evolution_colormeshes}.
 We begin by measuring the thermal's velocity versus time, $w_{\text{th}}$, as described in appendix \ref{appendix:measurements}. 
-We then calculate the streamfunction of the velocity field as in \citet{romps&all2015},
+We calculate the streamfunction of the velocity field as in \citet{romps&all2015},
 \begin{equation}
 \frac{\partial \psi}{\partial r} = 2\pi \rho r (w - w_{\text{th}}),
+\label{eqn:thermal_tracker}
 \end{equation}
-with the boundary condition that $\psi = 0$ at $r = 0$. 
+using vertical velocity data, $w$, in a 2D domain which radially spans $r = [0, L_r]$ and vertically spans the same depth as the simulation domain.
+For our 2D simulations, this is simply the output of the simulations.
+For our 3D simulations, we assume that the vortex ring is azimuthally symmetric, and it is thus fine to use the vertical velocity data in the $y = 0$ plane at values of $x \geq 0$.
+We solve Eqn.~\ref{eqn:thermal_tracker} with the boundary condition that $\psi = 0$ at $r = 0$. 
 The contour defined by $\psi = 0$ from this solution is taken to be the contour bounding the thermal, $\mathcal{C}$.
@@
 \label{appendix:table}
-Information regarding the simulation resolution and CFL safety factor for each of the simulations presented in this work is contained in table \ref{table:simulation_info}.
+Information regarding the simulation resolution, evolution time, and CFL safety factor for each of the simulations presented in this work is contained in table \ref{table:simulation_info}.
 The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository CITE.
@@
 \tablecomments{
+The density stratification in density scale heights, $n_\rho$, is used throughout this work and can be easily seen in numerous figures.
+Our 2D sims have a simulation coefficient resolution of nr x nz, and our 3D sims have a coefficient resolution of nx x ny x nz.
+We evolve our simulations from initial conditions until $t_{\text{evolution}}$ dimensionless freefall times have passed.
+We use a CFL to determine the appropriate size of our timestep at each timestep in our simulation, and the CFL safety factor decreases with increasing stratification.
+Our 2D sims use the RK443 timestepper and our 3D sims use the SBDF2 timestepper, resulting in vastly different safety factor sizes in 2D and 3D.
 }

### 2019-06-04 code/plotting/evolution_colormeshes.py

@@ -64,16 +64,21 @@ for i, ax in enumerate(axs):
 
         print(np.max(contour))
         if j > 0:
-            rho *= this_volume/np.abs(B)#np.pi * this_r**3 /np.abs(B)
+            if i == 0:
+                #Estimate of torus volume
+                rho *= 2*np.pi**2 * this_r**3 / 4**2 /np.abs(B)
+            else:
+                rho *= 2*np.pi**2 * this_r**3 / 3**2 /np.abs(B)
+#            rho *= this_volume/np.abs(B)
         else:
-            rho *= 5*(4./3)*np.pi*(0.5)**3/ np.abs(B)
+            rho *= (4./3)*np.pi*(0.5)**3/ np.abs(B)
         
         field = f['tasks']['S1'].value[imgnum,:]
         f.close()
         ff.close()
         cf.close()
 
-        minval = -5
+        minval = -1
         breaks = len(dirs[i]) - 1
         good   = (zz > (breaks-1-j)/breaks * 20)*(zz <= (breaks-j)/breaks * 20)
         z_shape = np.sum((z > (breaks-1-j)/breaks * 20)*(z <= (breaks-j)/breaks * 20))
@@ -81,6 +86,7 @@ for i, ax in enumerate(axs):
         c = ax.pcolormesh(-rr[good].reshape(z_shape, len(r)), zz[good].reshape(z_shape, len(r)), (rho*field)[good].reshape(z_shape, len(r)), cmap='Blues_r', rasterized=True, vmin=minval, vmax=0)
         if i == 0 and j == 0:
             bar = plt.colorbar(c, cax=cax, orientation='horizontal')
+            bar.solids.set_rasterized(True)
             cax.xaxis.set_ticks_position('top')
             bar.set_label(r'$\frac{\rho S_1 \mathcal{V}}{B_{\mathrm{th}}}$', labelpad=-38)
         x_max = 5
@@ -120,13 +126,16 @@ for i, ax in enumerate(axs):
             ax.set_xlim(-x_max, x_max)
             ax.set_yticklabels([])
             ax.set_xticks((0, x_max))
-            ax.text(-0.97*x_max, 18.7, r'$n_\rho = 3$', size=9)
+            ax.text(-0.97*x_max, 18.5, r'$n_\rho = 3$', size=9)
+            ax.text(-4.7, 0.3, 'b', fontsize=12)
         else:
[…]

### 2019-06-04 code/plotting/thermal_sun_comparison.py

@@ -147,12 +147,13 @@ for Buoy in (B_nondim/2, 2*B_nondim):
 
 fig = plt.figure(figsize=(3.25, 6))
 ax = fig.add_subplot(3,1,1)
+axs = [ax]
 
 #Plot radius grey band
 x_values = rho_outs[0]*(rho_top/rho_outs[0][0])
 upper_y_values = r_outs[0]*(L/2/r_outs[0][0])
 lower_y_values = interp1d(rho_outs[1]*(rho_top/rho_outs[1][0]), r_outs[1]*(L/2/r_outs[1][0]))(x_values)
-plt.fill_between(rho2r(x_values)/(Rsun2Mm), lower_y_values, upper_y_values, color='black', alpha=0.4)
+plt.fill_between(rho2r(x_values)/(Rsun2Mm), lower_y_values, upper_y_values, color='black', alpha=0.4, rasterized=True)
 
 #plot actual radius measurements
 solar_radii = []
@@ -168,14 +169,15 @@ ax.text(0.69, 7e-3, 'thermals')
 plt.xlim(0.68, 0.995)
 plt.yscale('log')
 plt.ylim(1e-5, 1e-1)
-plt.ylabel('radius (Mm)')
+plt.ylabel(r'$r_{\mathrm{th}}$ (Mm)')
 
 ax = fig.add_subplot(3,1,2)
+axs += [ax]
 #Plot radius grey band
 x_values = solar_radii[0] 
 upper_y_values = w_outs[0]*(u_th/w_outs[0][0])
 lower_y_values = interp1d(solar_radii[1], w_outs[1]*(u_th/w_outs[1][0]))(x_values)
-plt.fill_between(x_values/(Rsun2Mm), lower_y_values, upper_y_values, color='black', alpha=0.4)
+plt.fill_between(x_values/(Rsun2Mm), lower_y_values, upper_y_values, color='black', alpha=0.4, rasterized=True)
 
 #plot actual velocity measurements
 for i in range(2):
@@ -185,10 +187,11 @@ for i in range(2):
 plt.xlim(0.68, 0.995)
 plt.ylim(1e-3, 1e-1)
 plt.yscale('log')
-plt.ylabel('velocity (Mm/s)')
+plt.ylabel(r'$w_{\mathrm{th}}$ (Mm/s)')
 
 
 ax = fig.add_subplot(3,1,3)
+axs += [ax]
 
 #Plot grey band
 tau_ratios = []
[…]

### 2019-06-04 tex/stratified_thermals.tex
proofreads sections 1-4 a bit, adds a bunch of .pdfs for figures

@@
 In place of large-scale flows, some authors have suggested the solar luminosity may instead be transported by small droplets of rapidly falling, low entropy fluid.
-This ``entropy rain'' would propagate as dense vortex rings, analogous to rising buoyant thermals in the Earth's atmosphere.
+This ``entropy rain'' could propagate as dense vortex rings, analogous to rising buoyant thermals in the Earth's atmosphere.
 In this work, we develop an analytical theory describing the evolution of dense, negatively buoyant thermals.
@@
 Our results suggest that entropy rain driven at the surface of the Sun could fall into two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
-We estimate that solar downflows should be in the falling regime, but should remain large enough to shield their entropic signature until they reach the base of the solar convective zone.
+We estimate that solar downflows should be in the falling regime and should remain large enough to shield their entropic signature from diffusive effects until they reach the base of the solar convective zone.
 \end{abstract}
@@
 \citet{brandenburg2016} incorporated this ``entropy rain'' concept into a non-local mixing length theory, and suggested the entropy rain could take the form of propagating vortex rings. 
-However, \citet{brandenburg2016} does not include a fundamental aspect of entropy rain: it has lower entropy than the background atmosphere.
+However, the vortex rings described by \citet{brandenburg2016} do not include a fundamental aspect of entropy rain: it has lower entropy than the background atmosphere.
 Entropy rain is dense, and buoyancy forces will modify its dynamics.
 
-It is important to understand how the filling factor of these basic convective elements is affected by their negative buoyancy. 
-In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be basic unit of convection \citep[e.g.,][]{romps2015}. 
+It is important to understand how the filling fraction of these basic convective elements is affected by their negative buoyancy. 
+In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the basic unit of convection \citep[e.g.,][]{romps2015}. 
 Atmospheric thermals are buoyant and rise, but the term is also used for dense, falling fluid.
@@
 
-Thermals in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently through Direct Numerical Simulation (DNS) \citep{lecoanet&jeevanjee2018}.
+Thermals in the Boussinesq limit have been well studied in the laboratory for decades \citep[see e.g.][]{morton&all1956, scorer1957}, and more recently through Direct Numerical Simulation \citep[DNS,][]{lecoanet&jeevanjee2018}.
 These studies find that thermals expand radially and decelerate as they propagate.
-Such an expansion may prevent entropy rain from reaching the bottom of the solar convection.
+Such an expansion may prevent entropy rain from reaching the bottom of the solar convection zone.
 However, this work does not include the effects of density stratification.
@@
     \caption{
-	The filling factor of a dense thermal as a function of depth in an atmosphere which spans three density scale heights (the $n_\rho = 3$ case examined later in this work). 
-	Thin solid lines are the predictions for filling factor growth for the Boussinesq case (\LJ) and for pure horizontal compression \citep{brandenburg2016}.
+	Shown is the filling fraction of a dense thermal as a function of depth in an atmosphere which spans three density scale heights (the $n_\rho = 3$ case examined later in this work). 
+	Thin solid lines indicate the predictions for filling fraction growth in the Boussinesq case (\LJ) and for pure horizontal compression \citep[B16,][]{brandenburg2016}.
     \label{fig:overview} }
@@
 Ignoring entropy variations, \citet{brandenburg2016} suggests the filling fraction $f$ of entropy rain should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression.
-On the other hand, the filling factor of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth of the thermal.
+On the other hand, the filling fraction of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth of the thermal.
 These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true propagation of a numerically simulated dense thermal including both entropy variations and density stratification.
@@
 In this paper, we extend \citet{lecoanet&jeevanjee2018} (hereafter \LJ) to study the propagation of low-Mach number, low-entropy thermals in stratified domains. 
-We are specifically interested in how the buoyancy force affects the scaling of the thermal radius, or filling factor, with depth. 
-If buoyancy dominant, it is possible that entropy rain would simply grow too large and stall before reaching the bottom of the solar convection zone.
+We are specifically interested in how the buoyancy force affects the scaling of the thermal radius, or filling fraction, with depth. 
+If buoyancy dominates, it is possible that entropy rain would simply grow too large and stall before reaching the bottom of the solar convection zone.
 On the other hand, if the compression effects of \citet{brandenburg2016} are dominant, then these thermals could propagate to the bottom of the solar convection zone, validating the entropy rain picture.
@@
 In section \ref{sec:results}, we compare our theory and simulation results. 
-Finally, in section \ref{sec:discussion}, we discuss what our results imply for the entropy rain hypothesis.
+In section \ref{sec:implications}, we discuss what our results imply for the entropy rain hypothesis.
+Finally, in section \ref{sec:discussion}, we summarize our findings and conclusions.
 
@@
 \subsection{Phenomenological description of thermal evolution}
-Fig.~\ref{fig:evolution_colormeshes} depicts the descent of 3D cold thermals released from rest in domains which span a different number of density scale heights ($n_\rho$).
+Fig.~\ref{fig:evolution_colormeshes} depicts the descent of 3D cold thermals released from rest in two domains which span a different number of density scale heights, $n_\rho$.
 The left panel shows a weakly stratified domain with $n_\rho=0.5$, whereas the right panel shows a strongly stratified domain with $n_\rho=3$.
-In both cases, the thermal is initialized with a spherical negative entropy perturbation, which a diameter of 5\% of the domain depth.
+In both cases, the thermal is initialized with a spherical negative entropy perturbation, with a diameter of 5\% of the domain depth.
 This dense sphere spins up into an axisymmetric vortex ring, and the vertical cross section through this vortex ring shows two circular vorticity and entropy extrema.
 In the $n_\rho = 0.5$ simulation, the thermal grows with depth, similar to thermals in the Boussinesq regime.
-On the other hand, in the $n_\rho = 3$ simulation, the thermal's radius remains approximately constant.
+On the other hand, in the $n_\rho = 3$ simulation, the thermal's radius decreases marginally with depth.
 
@@
 
-In the following sections, we will use the impulse of dense vortex rings derive their depth and radii with time.
+In the following sections, we will use the impulse of dense vortex rings to derive expressions for the evolution of their depth and radii with time.
 
@@
     \caption{
-	Entropy perturbations, scaled by density and thermal volume, are shown.
+	Entropy perturbations, scaled by density and thermal volume and normalized by the thermal's buoyancy perturbation, are shown.
 	For visualization purposes in the evolved state, $\mathcal{V}$ is an approximation of the volume of the torus that the entropy occupies rather than the full thermal ellipsoidal volume.
-	(a) A thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights; (b) a thermal in a strongly stratified domain with $n_\rho = 3$.
-	While both start with precisely the same initial condition, the thermal in low stratification expands with depth, whereas the thermal in strong stratification compresses with depth.
+	Shown are (a) a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights, and (b) a thermal in a strongly stratified domain with $n_\rho = 3$.
+	While both start with precisely the same initial condition, the thermal in low stratification expands with depth, whereas the thermal in strong stratification compresses marginally with depth.
     \label{fig:evolution_colormeshes} }
@@
 \end{equation}
-where $k$ is due to the ``virtual mass effect'' from the environmental fluid moving together with the thermal \citep{tarshish&all2018}.
+where $k$ encompasses the ``virtual mass effect'' from the environmental fluid moving together with the thermal \citep{tarshish&all2018}.
 
 We now restrict our study to an ideal gas in the low Mach-number regime, in an adiabatic background.
-Due to rapid pressure equilibration in for low Mach-number flows, we can approximate \dl{Don't know if this is actually a good idea...}
+Due to rapid pressure equilibration in low Mach-number flows, we can approximate \dl{Don't know if this is actually a good idea...}
 %Need to do test of pomega magnitude, or see if this eqn is pretty true.
@@
 \begin{equation*}
-\frac{d\bm{I}}{d t} = \int_\mathcal{V} \rho_1 \bm{g} dV,
+\frac{d\bm{I}}{d t} = \int_\mathcal{V} \rho_1\, \bm{g}\, dV,
 \end{equation*}
@@
 \end{equation}
-where $r$ is the radius of the thermal from its axis of symmetry to its vorticity maximum, and $\Gamma = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the circulation in a cross-section of the vortex ring.
+where $r$ is the radius of the thermal from its axis of symmetry to its vorticity extremum, and $\Gamma = \int_{\mathcal{A}} (\grad\times\bm{u})dA$ is the circulation in a cross-section of the vortex ring.
 The circulation can change due to baroclinic torques,
@@
     \caption{
-	Evolution of circulation, buoyancy perturbation, and volume factor in thermal simulations.
+	Evolution of buoyancy perturbation (a), circulation (b), and volume factor (c) in 2D thermal simulations.
 	All are nearly constant after an initial spin-up phase.
-	With increasing stratification, we see marginally more detrainment (middle panel).
-	The volume factor can be approximated to be $\mathcal{O}(7)$ for all of our simulations.
+	With increasing stratification, we see marginally more detrainment (a).
     \label{fig:constants} }
@@
 While these thermals began as initial spherical perturbations, they act like vortex rings which evolved from a ``virtual origin'' where the vortex ring had zero radius.
-From this virtual origin, the vortex ring's impulse would have been $I_0$ at time $t = 0$ when the true thermal is released from rest.
+We will model the thermal has having been located at its virtual origin at $t = -t_{\text{off}}$, where $t = 0$ is the time at which the true thermal was released from rest.
 
-We find the thermal undergoes weak detrainment, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}b).
+We find the thermal undergoes weak detrainment, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}a).
 We thus express the buoyancy perturbation as 
@@
 \begin{equation*}
-I_z = \chi B_{\text{th}} t + I_0.
+I_z = \chi B_{\text{th}} (t + t_{\text{off}}).
 \end{equation*}
@@
 \begin{equation}
-r = \sqrt{\frac{\chi B_{\text{th}} t + I_0}{\pi\rho\Gamma_{\text{th}}}}.
+r = \sqrt{\frac{\chi B_{\text{th}} (t + t_{\text{off}})}{\pi\rho\Gamma_{\text{th}}}}.
 \label{eqn:r_theory}
 \end{equation}
-Recall there are no net baroclinic torques, so stays $\Gamma_{\text{th}}$ nearly constant (Fig.~\ref{fig:constants}a).
+Recall there are no net baroclinic torques, so $\Gamma_{\text{th}}$ stays nearly constant (Fig.~\ref{fig:constants}b).
 In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in \LJ.
-In the limit of strong stratification, $r \propto \rho^{-1/2}$, corresponding to purely horizontal compression, with $r^2 \propto \rho^{-1}$ \citep{brandenburg2016}.
+In the limit of strong stratification, we find $r \propto \rho^{-1/2}$, corresponding to purely horizontal compression, with $r^2 \propto \rho^{-1}$ \citep{brandenburg2016}.
 
-To solve for the vertical evolution of the thermal, we can use equation~\ref{eqn:momentum}.
-We approximate the volume as $\mathcal{V} = m r^3$, where $m$ is a parameter which we take to be constant.
-We find
-\begin{equation}
-\rho^{-1/2} w_{\text{th}} = \left(\frac{(\pi \Gamma_{\text{th}})^{3/2}}{(1 + k) m}\right)(\chi B_{\text{th}} t + I_0)^{-1/2}.
-\end{equation}
-Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, and assuming $I_0$ is small, we have
+To solve for the vertical evolution of the thermal, we can use Eqn.~\ref{eqn:momentum}.
+We approximate the volume as $\mathcal{V} = m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption, as in Fig.~\ref{fig:constants}c).
+Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, we find
 \begin{equation}
 \frac{dz_{\text{th}}}{\rho(z_{\text{th}})^{1/2}} =
-\left(\frac{(\pi\Gamma_{\text{th}})^{3/2}}{m(1 + k)(\chi B_{\text{th}})^{1/2}}\right)\frac{dt}{t^{1/2}}.
+\left(\frac{(\pi\Gamma_{\text{th}})^{3/2}}{m(1 + k)(\chi B_{\text{th}})^{1/2}}\right)\frac{dt}{(t + t_{\text{off}})^{1/2}}.
 \label{eqn:dz_theory}
@@
 \end{equation}
-where $C \equiv \pi^{3/2} \grad_{\text{ad}} / (1 + k) / m \sqrt{\Gamma_{\text{th}}^3/(\chi B_{\text{th}})}$ and the temperature at the virtual origin is $T_{\text{th},0} = 1 + \grad_{\text{ad}}(z_{\text{th},0} - L_z)$.
-The thermal is at the virtual origin, $z=z_0$, at time $t=-t_{\text{off}}$.
-The constant $\alpha^{-1} = 1 - n_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
+where 
+$$
+C \equiv \frac{\grad_{\text{ad}}}{m(1 + k)} \sqrt{\frac{(\pi\Gamma_{\text{th}})^3}{\chi B_{\text{th}}}}.
+$$ 
+The thermal is at the virtual origin, $z=z_0$, at time $t=-t_{\text{off}}$, and the temperature there is $T_{\text{th},0} = 1 + \grad_{\text{ad}}(z_{\text{th},0} - L_z)$.
+We define $\alpha^{-1} \equiv 1 - n_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
 
@@
 We verify the 3D and 2D simulations produce the same results when run with the same parameters.
-Because 2D simulations are less computationally expensive, we cover a broader parameter regime.
+Because 2D simulations are less computationally expensive, we use them to cover a broader parameter regime.
 
@@
 \partial_t S_1 + \bm{u}\cdot\grad S_1 =& \\
-\frac{1}{\text{Re}}\left(\frac{1}{\text{Pr}\rho_0c_P }\right.&[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\\
+\frac{1}{\text{Re}}\left(\frac{1}{\rho_0c_P\text{Pr} }\right.&[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\\
 &+ \left.\frac{-(\grad_{\text{ad}})}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right),
@@
 \end{equation}
-where $u_{\text{th}}$ is the freefall velocity, $L_{th}$ is the thermal length scale, and
+where $u_{\text{th}}$ is the freefall velocity, $L_{\text{th}}$ is the thermal length scale, and
 $\Delta s$ is the magnitude of the specific entropy signature of the thermal.
@@
 \begin{split}
-\frac{\partial \bm{u}}{\partial t}  +\grad T_1 + T_1\grad\ln\rho_0 + T_0\grad\ln\rho_1  =\\
-- \epsilon T_1\grad\ln\rho_1 + \frac{1}{\rho\text{Re}}\left[\grad^2\bm{u} + \frac{1}{3}\grad(\DivU)\right]
+\frac{\partial \bm{u}}{\partial t}  +\grad T_1 + &T_1\grad\ln\rho_0 + T_0\grad\ln\rho_1  =\\
+- \epsilon &T_1\grad\ln\rho_1 + \frac{1}{\rho\text{Re}}\left[\grad^2\bm{u} + \frac{1}{3}\grad(\DivU)\right]
 \end{split} \\
 \begin{split}
-\frac{\partial T_1}{\partial t} + \epsilon^{-1}\left[\bm{u}\cdot\grad T_0 + (\gamma-1)T_0\DivU\right] = \\
--\left[\bm{u}\cdot\grad T_1 + (\gamma-1)T_1\DivU\right] + \frac{1}{\rho c_V\text{Re}}\left[\frac{1}{\text{Pr}}\grad^2 T_1 + \sigma_{ij}\partial_{x_i}u_j\right].
+&\frac{\partial T_1}{\partial t} + \epsilon^{-1}\left[\bm{u}\cdot\grad T_0 + (\gamma-1)T_0\DivU\right] = \\
+&-\left[\bm{u}\cdot\grad T_1 + (\gamma-1)T_1\DivU\right] + \frac{1}{\rho c_V\text{Re}}\left[\frac{1}{\text{Pr}}\grad^2 T_1 + \sigma_{ij}\partial_{x_i}u_j\right].
 \end{split}
@@
 \subsection{Initial conditions}
-The simulations is initialized with a spherical specific entropy perturbation,
+The simulations are initialized with a spherical specific entropy perturbation,
 \begin{equation}
@@
 We simulate the thermals using the  Dedalus\footnote{\url{http://dedalus-project.org/}} pseudospectral framework \citep{burns&all2016, burns&all2019}.
-The 2D simulations use using an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997}, and the 3D simulations use the second-order semi-implicit backward differentiation formulation SBDF2 \citep{wang&ruuth2008}.
+The 2D simulations use an implicit-explicit (IMEX), third-order, four-stage Runge-Kutta timestepping scheme RK443 \citep{ascher&all1997}, and the 3D simulations use the second-order semi-implicit backward differentiation formulation SBDF2 \citep{wang&ruuth2008}.
 
@@
 Finally, we quantify the excellent agreement between the 2D anelastic and 3D fully compressible simulations in Fig.~\ref{fig:diff}b.
-We ran simulations in both models for $n_\rho = [0.5, 1, 2]$.
+We ran simulations in both models for $n_\rho = [0.1, 0.5, 1, 2]$.
 There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the simulations begin interacting with the bottom of the domain.
@@
 1	 	& 		256			& 512			& 41	 	&	0.15	\\
-2	 	& 		256			& 1536			& 34    	&	0.1	\\
+2	 	& 		256			& 1024			& 34    	&	0.1	\\
 \enddata																																															

### 2019-06-04 code/plotting/thermal_sun_comparison.py

@@ -1,10 +1,19 @@
 import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
 import matplotlib.pyplot as plt
 from scipy.interpolate import interp1d
+
 
 cm2Mm = 1e-8 #Mm / cm
 Rsun2cm = 6.957e10 #cm / Rsun
 Rsun2Mm = 6.957e2 #Mm / Rsun
+
 
 def theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=-1):
     """ The constant in stratified thermals theory """
@@ -162,8 +171,8 @@ for i in range(2):
     plt.plot(solar_radii[i]/(Rsun2Mm), r_outs[i]*(L/2/r_outs[i][0]), c='k', lw=0.5*(i+1))
 
 plt.plot(solar_radii[0]/(Rsun2Mm), (L/2)/(rho_outs[0]/rho_outs[0][0])**(1./2), c='k', lw=2)
-ax.text(0.69, 8e-5, r'$r \propto \rho^{-1/2}$')
-ax.text(0.69, 7e-3, 'thermals')
+ax.text(0.69, 8e-5, r'$r \propto \rho^{-1/2}$', rotation=3)
+ax.text(0.69, 7e-3, 'thermals', rotation=2.5)
 
 #Make plot pretty
 plt.xlim(0.68, 0.995)

### 2019-06-05 tex/stratified_thermals.tex
Changes to abstract and intro.

@@
 We verify the theory with 2D and 3D simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
-Our results suggest that entropy rain driven at the surface of the Sun could fall into two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
-We estimate that solar downflows should be in the falling regime and should remain large enough to shield their entropic signature from diffusive effects until they reach the base of the solar convective zone.
+Our results show that dense thermals fall in two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
+We estimate that solar downflows are in the falling regime and maintain their entropy perturbation against diffusion until they reach the base of the convection zone.
+This suggests that entropy rain may be an effective nonlocal mechanism for transporting the solar luminosity.
 \end{abstract}
@@
 \citet{brandenburg2016} incorporated this ``entropy rain'' concept into a non-local mixing length theory, and suggested the entropy rain could take the form of propagating vortex rings.
-However, the vortex rings described by \citet{brandenburg2016} do not include a fundamental aspect of entropy rain: it has lower entropy than the background atmosphere.
+The entropy rain hypothesis assumes these small vortex rings can maintain their entropy perturbation as they traverse the entire solar convection zone.
+This allows them to transport the solar luminosity via enthalpy fluxes.
+However, the vortex rings described by \citet{brandenburg2016} do not include a fundamental aspect of entropy rain: entropy perturbations relative to the background atmosphere.
 Entropy rain is dense, and buoyancy forces will modify its dynamics.
 
-It is important to understand how the filling fraction of these basic convective elements is affected by their negative buoyancy. 
+It is important to understand how the propagation of these basic convective elements is affected by their negative buoyancy. 
 In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the basic unit of convection \citep[e.g.,][]{romps2015}. 
@@
 These studies find that thermals expand radially and decelerate as they propagate.
-Such an expansion may prevent entropy rain from reaching the bottom of the solar convection zone.
+Such a deceleration may cause the thermals to move so slowly they would diffuse away their entropy perturbation before reaching the bottom of the solar convection zone.
 However, this work does not include the effects of density stratification.
@@
 \begin{acknowledgements}
+We'd like to thank Brett McKim and Nadir Jeevanjee for discussions about thermals and the laminar entrainment picture.
 This work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
 This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
+DL is supported by Princeton Center for Theoretical Science and Lyman Spitzer Jr.~postdoctoral fellowships.
 Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA  Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s1647.

### 2019-06-05 tex/stratified_thermals.tex
Figure captions.

@@
     \caption{
-	Entropy perturbations, scaled by density and thermal volume and normalized by the thermal's buoyancy perturbation, are shown.
-	For visualization purposes in the evolved state, $\mathcal{V}$ is an approximation of the volume of the torus that the entropy occupies rather than the full thermal ellipsoidal volume.
-	Shown are (a) a thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights, and (b) a thermal in a strongly stratified domain with $n_\rho = 3$.
-	While both start with precisely the same initial condition, the thermal in low stratification expands with depth, whereas the thermal in strong stratification compresses marginally with depth.
+	Mass-weighted entropy perturbations, normalized by the thermal's buoyancy perturbation.
+	(a) thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights, and (b) thermal in a strongly stratified domain with $n_\rho = 3$.
+	While both start with precisely the same initial condition, the thermal in low stratification expands with depth, whereas the thermal in strong stratification compresses with depth.
     \label{fig:evolution_colormeshes} }
@@
 	All are nearly constant after an initial spin-up phase.
-	With increasing stratification, we see marginally more detrainment (a).
+	With increasing stratification, we see marginally more detrainment in (a).
     \label{fig:constants} }
@@
     \caption{
-	(a) Thermal radius as a function of depth are plotted for the 2D anelastic and 3D fully compressible simulations.
+	(a) Thermal radius as a function of depth for the 2D anelastic and 3D fully compressible simulations.
 	Theoretical predictions from section \ref{sec:theory} are plotted in thin solid lines.

### 2019-06-05 tex/stratified_thermals.tex
Changes to sections 5 & 6... and a few other minor changes.

@@
 While many theoretical descriptions rely on self-similarity arguments, we will show how the impulse of a thermal controls its evolution.
+This section parallels a similar analysis for the Boussinesq case, presented in McKim et al (in prep).
 
@@
 Neither the assumption of pure compression \citep[as in e.g.,][]{brandenburg2016} nor the evolution of thermals in the Boussinesq regime (\LJ) fully describes thermal behavior.
-Rather, results fall somewhere in between, and theory and simulations suggest that there are two regimes of downflowing thermal behavior:
+Rather, the results fall somewhere in between, and theory and simulations suggest that there are two regimes of downflowing thermal behavior:
 \begin{enumerate}
@@
 
-If the nucleus of solar convection were thermals in the stalling regime, convective elements would grow enormously in size and slow down very close to the solar surface.
+If the solar downflows are in the stalling regime, convective elements would grow enormously in size and slow down very close to the solar surface.
 In a perfectly quiescent atmosphere, these slow, large convective elements would eventually propagate to the base of the convection zone over long timescales.
@@
 Neglecting buoyancy, we expect that downward propagating vortex rings in the solar convection zone would likely compress to sizes on which conductivity could become important.
-Our theory of thermals suggests that, instead, buoyancy counteracts some of the compressional effects of stratification, and could help convective elements maintain coherency as they cross the solar convection zone.
+Our theory of thermals suggests that, instead, buoyancy counteracts some of the compressional effects of stratification, and could help convective elements maintain their entropy perturbation as they cross the solar convection zone.
 
-We now estimate what the behavior of thermals in the Sun would be based on the simulations presented in this work.
-To do so, we will approximate the dimensional buoyancy perturbation of Eqn.~\ref{eqn:tot_buoyancy} as $\tilde{B} = \rho \mathcal{V} g (S_1/c_p)$, and calculate this quantity for thermals launched from the solar photosphere, assuming that solar downflow lanes quickly break up into thermals.
+We now estimate the behavior of thermals in the Sun based on the simulations presented in this work.
+The thermal evolution depends on a variety of parameters (see table table:parameters).
+However, we find the only parameter which changes appreciably as we increase the stratification is the normalized buoyancy $B_\text{th}$.
+To estimate $B_\text{th}$ in the sun, we approximate the dimensional buoyancy perturbation of Eqn.~\ref{eqn:tot_buoyancy} as $\tilde{B} = \rho \mathcal{V} g (S_1/c_p)$, and calculate this quantity for thermals launched from the solar photosphere, assuming that solar downflow lanes quickly break up into thermals.
 Using the VAL atmospheric data of \citet{avrett&loeser2008}, we estimate the solar surface to have a temperature of $T_0 \approx 6000$ K, a density of $\rho_0 \approx 1.74 \times 10^{-7}$ g/cm$^3$, and a sound speed of $c_s = 9.5 \times 10^5$ cm/s.
@@
 $$
-Nondimensionalizing this by $N = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B = \tilde{B}/N = -3.57$, which lies between the $n_\rho = 5$ and $n_\rho = 6$ simulations we studied here (see table \ref{table:parameters}).
+Nondimensionalizing this by $B_0 = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B_\text{th} = \tilde{B}/B_0 = -3.57$, which lies between the $n_\rho = 5$ and $n_\rho = 6$ simulations we studied here (see table \ref{table:parameters}).
 
@@
 
-Due to the numerous assumptions made in calculating $B$, we assume this estimate is only accurate to within a factor of two, and thus study thermals in the interval $[B_\ell, B_u] = 0.5B, 2B$.
+Because solar downflows likely break up into thermals of various sizes, we will examine the fate of thermals with dimensionless buoyancy in the interval $[B_\ell, B_u] = 0.5B_\text{th}, 2B_\text{th}$.
 Interpolating and extrapolating the data in Table \ref{table:parameters}, we use Eqns.~\ref{eqn:r_theory} \& \ref{eqn:theory_z} to calculate theoretical predictions for how thermals with these buoyancies would evolve over extended atmospheres like the solar convection zone.
@@
 \ref{fig:thermal_sun_comparison}.
-In Fig. \ref{fig:thermal_sun_comparison}a\&b, we respectively show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
-We use the solar diffusivity models shown in \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r^2$) and the thermal freefall timescale over 1 Mm ($\tau_{\text{ff}} = [1\,\text{Mm}]/w_{\text{th}}$).
+In Fig. \ref{fig:thermal_sun_comparison}a\&b, we show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
+We use the solar diffusivity models of \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r^2$) and the thermal freefall timescale over 1 Mm ($\tau_{\text{ff}} = [1\,\text{Mm}]/w_{\text{th}}$).
 In Fig. \ref{fig:thermal_sun_comparison}c, we plot the ratio of these two timescales over the thermal's evolution.
 
-We find that our estimated bracket for solar thermal behavior is in the falling regime.
-These thermals experience radial compression with corresponding increases in velocity, but experience much less compression than a naive approximation based on the density stratification would suggest.
+We find that our estimated solar thermal is in the falling regime.
+These thermals experience radial compression with corresponding increases in velocity, but experience much less compression than a naive approximation based on the density stratification alone.
 Furthermore, throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
@@
 $$
-\int_{R_\odot}^{0.7 R_\odot} \tau_\kappa^{-1} \frac{dR}{w_{th}} = [6.55, 1.57]\times 10^{-3}\,\text{for}\,[B_\ell, B_u].
+\int_{R_\odot}^{0.7 R_\odot} \tau_\kappa^{-1} \frac{dr}{w_{th}} = [6.55, 1.57]\times 10^{-3}\,\text{for}\,[B_\ell, B_u].
 $$
-We similarly estimate the amount of entropy that the thermal should lose due to viscous heating as 
-$$
-\frac{1}{(S_1)}\int_{R_\odot}^{0.7 R_\odot} \nu \frac{1}{\rho T}\frac{w_{th}^2}{r^2}\frac{dr}{w_{th}} = [1.17, 0.17] \times 10^{-4}\,\text{for}\,[B_\ell, B_u].
-$$
-In other words, throughout our bracketing interval, we estimate that the thermal loses less than 1\% of its entropic signature to diffusion, and approximately 0.01\% of its signature due to viscous heating.
-These estimates suggest that entropy rain in the form of thermals could feasibly transport the solar luminosity.
+Thus, the thermal loses less than 1\% of its entropic signature to diffusion.
+These estimates suggest that entropy rain could transport the solar luminosity.
 
@@
 In this paper we developed a simple theory of the evolution of negatively buoyant vortex rings in stratified atmospheres.
-We showed that this theory predicts that dense thermals will experience less entrainment than boussinesq thermals due to increasing atmospheric density with depth.
-Similarly, we showed that these thermals experience less compression than would be expected due to pure atmosphreic compression of a neutral vortex ring.
-We performed 2D anelastic simulations of thermal evolution for varying degrees of stratification and showed that our parameterized theory describes the evolution of thermals in these systems remarkably well.
-Furthermore, we verified the validity of our anelastic simulations with select 3D fully compressible simulations of thermal evolution and found agreement to under 1\%.
-We noted that the evolution of dense thermals in stratified domains is complex, but can be classified into a near-Boussinesq ``stalling'' and a high-stratification ``falling'' regime.
-An estimate of the entropic nature of solar downflows suggests that thermals launched from the solar surface would exhibit behavior in the falling regime.
+This theory predicts that dense thermals experience less entrainment than Boussinesq thermals due to increasing atmospheric density with depth.
+Likewise, these thermals experience less compression than would be expected due to pure atmospheric compression of a neutrally buoyant vortex ring.
+We performed 2D anelastic \& 3D fully compressible simulations of thermal evolution in the laminar regime for varying degrees of stratification, and showed that our parameterized theory describes the evolution of thermals in these systems remarkably well.
+We found excellent agreement between the 2D \& 3D simulations.
+The evolution of dense thermals in stratified domains is complex, but can be classified into a near-Boussinesq ``stalling'' and a high-stratification ``falling'' regime.
+We estimate that solar downflows would fall into this latter regime.
 
-The ``Entropy rain'' hypothesis states that narrow downflows can transport the luminosity of the Sun via enthalpy fluxes.
+The ``entropy rain'' hypothesis states that narrow downflows can transport the luminosity of the Sun via enthalpy fluxes.
 If the rain stalls near the surface or its entropy diffuses away before it hits the bottom, then it cannot transport the flux.
-We find that with our more accurate model for thermal propagation, solar thermals should maintain their entropy all the way to the base of the convection zone, and entropy rain is a possible mechanism for transporting the solar luminosity.
+We find that with our more accurate model for thermal propagation, solar thermals should maintain their entropy all the way to the base of the convection zone.
+Hence, entropy rain is a possible mechanism for transporting the solar luminosity.
 
@@
 For our 2D simulations, this is simply the output of the simulations.
-For our 3D simulations, we assume that the vortex ring is azimuthally symmetric, and it is thus fine to use the vertical velocity data in the $y = 0$ plane at values of $x \geq 0$.
+For our 3D simulations, we assume that the vortex ring is azimuthally symmetric, and thus use the vertical velocity data in the $y = 0$ plane at values of $x \geq 0$.
 We solve Eqn.~\ref{eqn:thermal_tracker} with the boundary condition that $\psi = 0$ at $r = 0$. 
-The contour defined by $\psi = 0$ from this solution is taken to be the contour bounding the thermal, $\mathcal{C}$.
+The contour $\psi = 0$ is taken to be the contour bounding the thermal, $\mathcal{C}$.
 
@@
 \tablecomments{
-The density stratification in density scale heights, $n_\rho$, is used throughout this work and can be easily seen in numerous figures.
-Our 2D sims have a simulation coefficient resolution of nr x nz, and our 3D sims have a coefficient resolution of nx x ny x nz.
+Our 2D sims have spectral mode resolution of nr x nz, and our 3D sims have spectral mode resolution of nx x ny x nz.
 We evolve our simulations from initial conditions until $t_{\text{evolution}}$ dimensionless freefall times have passed.

### 2019-06-05 code/logic/post_processing.py
plotting, run scripts

@@ -265,6 +265,7 @@ class ThermalPostProcessor():
             w   = f['tasks']['w'].value  * self.L_factor/self.t_factor
             u   = f['tasks']['u'].value  * self.L_factor/self.t_factor
             V   = f['tasks']['V'].value  / self.t_factor
+            p   = f['tasks']['p'].value * (self.L_factor/self.t_factor)**2
             r   = f['scales']['r']['1.0'].value * self.L_factor 
             z   = f['scales']['z']['1.0'].value * self.L_factor 
             rr, zz = np.meshgrid(r, z)
@@ -273,6 +274,7 @@ class ThermalPostProcessor():
             w   = f['tasks']['w y mid'].value * self.L_factor/self.t_factor
             u   = f['tasks']['u y mid'].value * self.L_factor/self.t_factor
             V   = f['tasks']['vorticity y mid'].value / self.t_factor
+            p = None
             x = f['scales']['x']['1.0'].value * self.L_factor 
             r = x[x >= 0]
             r_ind = (x >= 0).flatten()
@@ -283,7 +285,7 @@ class ThermalPostProcessor():
             z  = f['scales']['z']['1.0'].value * self.L_factor 
             zz, rr = np.meshgrid(z, r)
         f.close()
-        return r, z, rr, zz, s1, w, u, V
+        return r, z, rr, zz, s1, w, u, V,p
 
 
     def calculate_contour(self, iterative=False):
@@ -305,7 +307,7 @@ class ThermalPostProcessor():
 
         for filenum, fn in enumerate(self.files):
             #Read entropy, density, velocity, vorticity
-            r, z, rr, zz, s1, w, u, V = self.read_file(fn)
+            r, z, rr, zz, s1, w, u, V, p = self.read_file(fn)
 
             if filenum == 0:
                 integrator = DedalusIntegrator(len(r), len(z), self.Lr, self.Lz, self.grad_T_ad, self.m_ad, r_cheby=True, twoD=self.twoD)
@@ -437,7 +439,7 @@ class ThermalPostProcessor():
             #First, get some basic info about the thermal
             for filenum, fn in enumerate(self.files):
                 #Read entropy, density, velocity, vorticity
-                r, z, rr, zz, s1, w, u, V = self.read_file(fn)
+                r, z, rr, zz, s1, w, u, V, p = self.read_file(fn)
 
                 if filenum == 0:
[…]

### 2019-06-05 code/plotting/constants.py

@@ -1,8 +1,7 @@
 import matplotlib
 matplotlib.use('Agg')
 matplotlib.rcParams['font.family'] = 'DejaVu Serif'
-#matplotlib.rcParams['text.usetex'] = True
-matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
 matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
 matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
 matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
@@ -60,18 +59,18 @@ for i, direc in enumerate(DIRS):
     good = S < 0.5*S.min()
     good[:10] = True
     V0 = V/r**3
-    for j, x, y in zip(range(3), (d, d, d), (Gam/Gamma0, S/B0, V0/f0)):
+    for j, x, y in zip(range(3), (d, d, d), (S/B0, Gam/Gamma0, V0/f0)):
         axs[j].plot(x[good], y[good], lw=0.75, c=color)
 
-axs[0].set_ylim(0.25, 1.1)
-axs[1].set_ylim(0.25, 1.1)
+axs[0].set_ylim(0.75, 1.1)
+axs[1].set_ylim(0.75, 1.1)
 axs[2].set_ylim(0.75, 1.1)
 
 for i in (0, 1, 2):
     axs[i].set_xlim(2, 20)
 axs[2].set_ylabel('w')
-axs[0].set_ylabel(r'$\Gamma/\Gamma_{\mathrm{th}}$')
-axs[1].set_ylabel(r'$B/B_{\mathrm{th}}$')
+axs[0].set_ylabel(r'$B/B_{\mathrm{th}}$')
+axs[1].set_ylabel(r'$\Gamma/\Gamma_{\mathrm{th}}$')
 axs[2].set_ylabel(r'$\mathcal{V}/(mr^3)$')
 axs[2].set_xlabel('Depth')
 
@@ -83,10 +82,16 @@ axs[0].tick_params(labelbottom=False)
 axs[1].tick_params(labelbottom=False)
 
 cb = plt.colorbar(sm, cax=cax, orientation='horizontal', boundaries=np.linspace(1, len(CASES)+1, len(CASES)+1)-0.5, ticks=np.arange(len(CASES)+1))
+cb.solids.set_rasterized(True)
[…]

### 2019-06-05 code/plotting/diff_AN_FC.py

@@ -1,7 +1,7 @@
 import matplotlib
 matplotlib.use('Agg')
 matplotlib.rcParams['font.family'] = 'DejaVu Serif'
-matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
 matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
 matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
 matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
@@ -12,10 +12,12 @@ import matplotlib.gridspec as gridspec
 import numpy as np
 import h5py
 
+from scipy.interpolate import interp1d
+
 NRUNS=8
 
-aspect = [0.25, 0.25, 0.25]
-CASES = [0.5, 1, 2]
+aspect = [0.25, 0.25, 0.25, 0.25]
+CASES = [0.1, 0.5, 1, 2]
 ROOT_DIR='../'#good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
@@ -24,9 +26,9 @@ CASES_2D = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
 color_dir = [1, 2, 3, 4, 5, 6, 7, 8]
 DIRS_2D=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES_2D, aspect_2D)] 
 
-CASES_3D = [0.5, 1, 2]
-AR_3D    = [0.5, 0.4, 0.35]
-THREED_DIR = '../good_3D_runs/'
+CASES_3D = [0.1, 0.5, 1, 2]
+AR_3D    = [0.5, 0.5, 0.5, 0.5]
+THREED_DIR = '../'
 DIRS_3D=['{:s}FC_3D_thermal_Re6e2_Pr1_eps1.00e-4_nrho{}_aspect{}/'.format(THREED_DIR,nrho, ar) for nrho, ar in zip(CASES_3D, AR_3D)] 
 dict_3D = {}
 for i in range(len(CASES_3D)):
[…]

### 2019-06-05 code/plotting/evolution_colormeshes.py

@@ -1,7 +1,7 @@
 import matplotlib
 matplotlib.use('Agg')
 matplotlib.rcParams['font.family'] = 'DejaVu Serif'
-#matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
 matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
 matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
 matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'

### 2019-06-05 code/plotting/results_panels.py

@@ -1,7 +1,7 @@
 import matplotlib
 matplotlib.use('Agg')
 matplotlib.rcParams['font.family'] = 'DejaVu Serif'
-matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
 matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
 matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
 matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
@@ -19,9 +19,9 @@ CASES = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
 ROOT_DIR='../'#good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
-CASES_3D = [0.5, 1, 2]
-AR_3D    = [0.5, 0.4, 0.35]
-THREED_DIR = '../good_3D_runs/'
+CASES_3D = [0.1, 0.5, 1, 2]
+AR_3D    = [0.5, 0.5, 0.5, 0.5]
+THREED_DIR = '../'
 DIRS_3D=['{:s}FC_3D_thermal_Re6e2_Pr1_eps1.00e-4_nrho{}_aspect{}/'.format(THREED_DIR,nrho, ar) for nrho, ar in zip(CASES_3D, AR_3D)] 
 dict_3D = {}
 for i in range(len(CASES_3D)):
@@ -33,7 +33,7 @@ gs = gridspec.GridSpec(1000, 1000)
 fig = plt.figure(figsize=(width, height*2))
 cax = plt.subplot(gs.new_subplotspec((30,   0), 50, 1000))
 ax1 = plt.subplot(gs.new_subplotspec((100,  0), 380, 1000))
-ax2 = plt.subplot(gs.new_subplotspec((620,  0), 380, 1000))
+ax2 = plt.subplot(gs.new_subplotspec((600,  0), 400, 1000))
 
 norm = matplotlib.colors.Normalize(vmin=0.8, vmax=len(CASES))
 sm   = plt.cm.ScalarMappable(cmap='viridis_r', norm=norm)
[…]

### 2019-06-05 code/plotting/constants.py
comments out fig labels

@@ -87,9 +87,9 @@ cax.xaxis.set_ticks_position('top')
 cax.xaxis.set_ticklabels(CASES)
 cb.set_label(r'$n_\rho$', labelpad=-35)
 
-axs[0].text(19, 1.03, 'a', fontsize=12)
-axs[1].text(19, 1.03, 'b', fontsize=12)
-axs[2].text(19, 1.03, 'c', fontsize=12)
+#axs[0].text(19, 1.03, 'a', fontsize=12)
+#axs[1].text(19, 1.03, 'b', fontsize=12)
+#axs[2].text(19, 1.03, 'c', fontsize=12)
 
 
 

### 2019-06-05 code/plotting/diff_AN_FC.py

@@ -133,8 +133,8 @@ cax.xaxis.set_ticklabels([0.1, 0.5, 1, 2, 3, 4, 5, 6])
 cb.set_label(r'$n_\rho$', labelpad=-30)
 
 
-axs[0].text(2.25, 0.21, 'a', fontsize=10)
-axs[1].text(2.25, 1.3e-4, 'b', fontsize=10)
+#axs[0].text(2.25, 0.21, 'a', fontsize=10)
+#axs[1].text(2.25, 1.3e-4, 'b', fontsize=10)
 
 
 fig.savefig('diff_AN_FC.png', dpi=300, bbox_inches='tight')

### 2019-06-05 code/plotting/evolution_colormeshes.py

@@ -127,13 +127,13 @@ for i, ax in enumerate(axs):
             ax.set_yticklabels([])
             ax.set_xticks((0, x_max))
             ax.text(-0.97*x_max, 18.5, r'$n_\rho = 3$', size=9)
-            ax.text(-4.7, 0.3, 'b', fontsize=12)
+#            ax.text(-4.7, 0.3, 'b', fontsize=12)
         else:
             ax.set_xlim(-x_max, x_max)
             ax.set_xticks((-x_max, 0, x_max))
             ax.text(-0.97*x_max, 18.5, r'$n_\rho = \frac{1}{2}$', size=9)
             ax.set_ylabel('z')
-            ax.text(-4.7, 0.3, 'a', fontsize=12)
+#            ax.text(-4.7, 0.3, 'a', fontsize=12)
         ax.set_xlabel('x')
 
 

### 2019-06-05 code/plotting/overview_fig.py

@@ -87,7 +87,7 @@ plt.plot(nrho_001_d, (nrho_001_d/nrho_001_d[ind_001])**2, c='black', lw=0.5)
 plt.plot(nrho_3_d, (nrho_3_r/nrho_3_r[ind_3])**2, c='k', lw=1.5)
 plt.plot(nrho_3_d, (nrho_3_r_no_buoy/nrho_3_r_no_buoy[ind_3])**2, c='black', lw=0.5)
 plt.yscale('log')
-plt.ylabel(r'$f = r^2$')
+plt.ylabel(r'$f = (r/r_0)^2$')
 plt.xlabel('Depth')
 plt.xlim(2, 20)
 plt.ylim(5e-2, 1e2)
@@ -98,3 +98,4 @@ ax.text(11.5, 1.2, r'$\mathrm{simulation}\,(n_\rho=3)$', rotation=-2)
 ax.text(14, 2.2e-1, r'$f \propto \rho^{-1}\,\mathrm{(B16)}$', rotation=-7)
 
 fig.savefig('overview_fig.png', dpi=300, bbox_inches='tight')
+fig.savefig('overview_fig.pdf', dpi=600, bbox_inches='tight')

### 2019-06-05 code/plotting/results_panels.py

@@ -90,8 +90,8 @@ cax.xaxis.set_ticks_position('top')
 cax.xaxis.set_ticklabels(CASES)
 cb.set_label(r'$n_\rho$', labelpad=-40)
 
-ax1.text(0.5, 18.5, 'a', fontsize=12)
-ax2.text(0.2, 0.225, 'b', fontsize=12)
+#ax1.text(0.5, 18.5, 'a', fontsize=12)
+#ax2.text(0.2, 0.225, 'b', fontsize=12)
 
 fig.savefig('results_panels.png', dpi=300, bbox_inches='tight')
 fig.savefig('results_panels.pdf', dpi=600, bbox_inches='tight')

### 2019-06-05 code/plotting/thermal_sun_comparison.py

@@ -233,9 +233,9 @@ plt.ylabel(r'$\tau_\kappa/\tau_{\mathrm{ff}}$')
 plt.xlabel(r'radius $(R_{\odot})$')
 #plt.legend(loc='best', fontsize=9, frameon=False)
 
-axs[0].text(0.685, 4e-2, 'a', fontsize=12)
-axs[1].text(0.685, 6e-2, 'b', fontsize=12)
-axs[2].text(0.685, 1.5e7, 'c', fontsize=12)
+#axs[0].text(0.685, 4e-2, 'a', fontsize=12)
+#axs[1].text(0.685, 6e-2, 'b', fontsize=12)
+#axs[2].text(0.685, 1.5e7, 'c', fontsize=12)
 
 plt.savefig('thermal_sun_comparison.png', dpi=300, bbox_inches='tight')
 plt.savefig('thermal_sun_comparison.pdf', dpi=600, bbox_inches='tight')

### 2019-06-05 code/join_data.py
cleanup for zenodo move

@@ -32,8 +32,7 @@ logger.info("joining data from Dedalus run {:s}".format(data_dir))
 if args['--data_type'] is not None:
     data_types=[args['--data_type']]
 else:
-#    data_types = ['slices', 'profiles']
-    data_types = ['final_checkpoint', 'checkpoint']#, 'volumes', 'profiles', 'slices', 'scalars']
+    data_types = ['slices', 'profiles', 'final_checkpoint', 'checkpoint', 'volumes', 'scalars']
 
 for data_type in data_types:
     logger.info("merging {}".format(data_type))

### 2019-06-05 tex/stratified_thermals.tex
Prepares repository for submission. * Minor changes to the manuscript text * Adds the stratified_thermals_code folder, which is tarred and published as supplemental materials * Small changes to figures

@@
 %% TITLE & AUTHORS
-\shorttitle{Stratified Thermals}
+\shorttitle{Entropy Rain: Thermals in Stratified Domains}
 \shortauthors{Anders et al.}
@@
 \begin{document}
-\title{Entrainment of low Mach number thermals in stratified domains}
+\title{Entropy Rain: Dilution and Compression of Thermals in Stratified Domains}
 
@@
 
-\keywords{hydrodynamics --- turbulence --- entrainment}
+\keywords{ hydrodynamics --- convection ---  Sun:interior --- Stars:interior}
 
@@
 It is important to understand how the propagation of these basic convective elements is affected by their negative buoyancy. 
-In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the basic unit of convection \citep[e.g.,][]{romps2015}. 
+In the context of Earth's atmosphere, ``thermals,'' or buoyant fluid regions which evolve into rising vortex rings, are thought to be the basic unit of convection \citep[e.g.,][]{romps&all2015}. 
 Atmospheric thermals are buoyant and rise, but the term is also used for dense, falling fluid.
@@
 Such a deceleration may cause the thermals to move so slowly they would diffuse away their entropy perturbation before reaching the bottom of the solar convection zone.
-However, this work does not include the effects of density stratification.
+However, this past work does not include the effects of density stratification.
 
@@
 On the other hand, the filling fraction of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth of the thermal.
-These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true propagation of a numerically simulated dense thermal including both entropy variations and density stratification.
+These regimes are shown in Fig.~\ref{fig:overview}, and compared to the true propagation of a numerically simulated dense thermal which includes both entropy variations and density stratification.
 
@@
 The left panel shows a weakly stratified domain with $n_\rho=0.5$, whereas the right panel shows a strongly stratified domain with $n_\rho=3$.
-In both cases, the thermal is initialized with a spherical negative entropy perturbation, with a diameter of 5\% of the domain depth.
+In both cases, the thermal is initialized with a spherical negative entropy perturbation whose diameter is 5\% of the domain depth.
 This dense sphere spins up into an axisymmetric vortex ring, and the vertical cross section through this vortex ring shows two circular vorticity and entropy extrema.
@@
 	Mass-weighted entropy perturbations, normalized by the thermal's buoyancy perturbation.
-	(a) thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights, and (b) thermal in a strongly stratified domain with $n_\rho = 3$.
+	(left) A thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights, and (right) a thermal in a strongly stratified domain with $n_\rho = 3$.
 	While both start with precisely the same initial condition, the thermal in low stratification expands with depth, whereas the thermal in strong stratification compresses with depth.
@@
 We now restrict our study to an ideal gas in the low Mach-number regime, in an adiabatic background.
-Due to rapid pressure equilibration in low Mach-number flows, we can approximate \dl{Don't know if this is actually a good idea...}
-%Need to do test of pomega magnitude, or see if this eqn is pretty true.
+Due to rapid pressure equilibration in low Mach-number flows, we can approximate 
 \begin{equation*}
-\frac{\rho_1}{\rho_0} \approx \frac{S_1}{c_P},
+\frac{\rho_1}{\rho_0} \approx -\frac{S_1}{c_P},
 \end{equation*}
@@
 
-The rate of change of change of the impulse is
+The rate of change of the impulse is
 \begin{equation*}
@@
 because the surface terms completely cancel.
-It is useful to define the buoyancy perturbation,
+Assuming $\bm{g} = -g\hat{z}$, it is useful to define the buoyancy perturbation,
 \begin{equation}
-B \equiv \int_{\mathcal{V}} \rho\, S_1\, \frac{g}{c_P}\, dV.
+B \equiv \int_{\mathcal{V}} \rho_0\, S_1\, \frac{g}{c_P}\, dV.
 \label{eqn:tot_buoyancy}
@@
 \begin{equation}
-I_z \approx \pi \rho r^2 \Gamma,
+I_z \approx \pi \rho_0 r^2 \Gamma,
 \label{eqn:impulse_approx}
@@
     \caption{
-	Evolution of buoyancy perturbation (a), circulation (b), and volume factor (c) in 2D thermal simulations.
+	Evolution of buoyancy perturbation (top), circulation (middle), and volume factor (bottom) in 2D thermal simulations.
 	All are nearly constant after an initial spin-up phase.
-	With increasing stratification, we see marginally more detrainment in (a).
+	With increasing stratification, we see marginally more detrainment in the buoyancy perturbation.
     \label{fig:constants} }
@@
 While these thermals began as initial spherical perturbations, they act like vortex rings which evolved from a ``virtual origin'' where the vortex ring had zero radius.
-We will model the thermal has having been located at its virtual origin at $t = -t_{\text{off}}$, where $t = 0$ is the time at which the true thermal was released from rest.
+We model the thermal as having been located at its virtual origin at $t = -t_{\text{off}}$, where $t = 0$ is the time at which the true thermal was released from rest.
 
-We find the thermal undergoes weak detrainment, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}a).
+We find the thermal undergoes weak detrainment, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}, top panel).
 We thus express the buoyancy perturbation as 
 \begin{equation}
-B \approx \chi B_{\text{th}},
+B \approx \eta B_{\text{th}},
 \end{equation}
-where $\chi$ is a constant of $\mathcal{O}$(1) which represents this detrainment. 
+where $\eta$ is a constant of $\mathcal{O}$(1) which represents this detrainment. 
 We then integrate Eqn.~\ref{eqn:change_in_impulse},
 \begin{equation*}
-I_z = \chi B_{\text{th}} (t + t_{\text{off}}).
+I_z = \eta B_{\text{th}} (t + t_{\text{off}}).
 \end{equation*}
@@
 \begin{equation}
-r = \sqrt{\frac{\chi B_{\text{th}} (t + t_{\text{off}})}{\pi\rho\Gamma_{\text{th}}}}.
+r = \sqrt{\frac{\eta B_{\text{th}} (t + t_{\text{off}})}{\pi\rho_0\Gamma_{\text{th}}}}.
 \label{eqn:r_theory}
 \end{equation}
-Recall there are no net baroclinic torques, so $\Gamma_{\text{th}}$ stays nearly constant (Fig.~\ref{fig:constants}b).
+Recall there are no net baroclinic torques, so $\Gamma_{\text{th}}$ stays nearly constant (Fig.~\ref{fig:constants}, middle panel).
 In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in \LJ.
@@
 To solve for the vertical evolution of the thermal, we can use Eqn.~\ref{eqn:momentum}.
-We approximate the volume as $\mathcal{V} = m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption, as in Fig.~\ref{fig:constants}c).
+We approximate the volume as $\mathcal{V} \approx m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption, as in Fig.~\ref{fig:constants}, bottom panel).
 Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, we find
@@
 \frac{dz_{\text{th}}}{\rho(z_{\text{th}})^{1/2}} =
-\left(\frac{(\pi\Gamma_{\text{th}})^{3/2}}{m(1 + k)(\chi B_{\text{th}})^{1/2}}\right)\frac{dt}{(t + t_{\text{off}})^{1/2}}.
+\left(\frac{(\pi\Gamma_{\text{th}})^{3/2}}{m(1 + k)(\eta B_{\text{th}})^{1/2}}\right)\frac{dt}{(t + t_{\text{off}})^{1/2}}.
 \label{eqn:dz_theory}
@@
 
-\subsection{Solution polytrope atmospheres}
+\subsection{Polytropic atmosphere solution}
 In this work, we study an ideal gas with an adiabatic index of $\gamma = 5/3$.
@@
 $$
-C \equiv \frac{\grad_{\text{ad}}}{m(1 + k)} \sqrt{\frac{(\pi\Gamma_{\text{th}})^3}{\chi B_{\text{th}}}}.
+C \equiv \frac{\grad_{\text{ad}}}{m(1 + k)} \sqrt{\frac{(\pi\Gamma_{\text{th}})^3}{\eta B_{\text{th}}}}.
 $$ 
@@
 While we do not attempt to model the spin-up phase in this paper, it can be parameterized by the buoyancy $B_{\text{th}}$, circulation $\Gamma_{\text{th}}$, as well as the virtual origin $z_{\text{th,0}}$, and temporal offset $t_{\text{off}}$.
-Our theory also involves the volumetric aspect ratio of the thermal $f$, the detrainment fraction $\chi$, and the effective buoyancy $k$. 
+Our theory also involves the volumetric aspect ratio of the thermal, $m$, the detrainment fraction, $\eta$, and the effective buoyancy, $k$. 
 These appear to be only weakly dependent on the stratification for the thermals we have simulated.
@@
 We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform and constant in time.
-We make this choice as the mass-weighted diffusivities, $\mu$ and $\kappa$, appear in the density-weighted momentum and entropy equations, and we find the density-weighted entropy and momentum to be key quantities in our thermal theory.
+We make this choice because $\mu$ and $\kappa$ appear in the density-weighted momentum and entropy equations, and we find the density-weighted entropy and momentum to be key quantities in our thermal theory.
 The diffusivities $\nu$ and $\chi$ therefore scale inversely with the density.
@@
 These equations are non-dimensionalized in the same way as the anelastic equations, and use the same background atmosphere.
-The new parameter $\epsilon = u_{\text{th}}^2$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows; we use $\epsilon = 10^{-4}$ in this work.
+The new parameter $\epsilon = u_{\text{th}}^2$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows analagously to the adiabatic excess in polytropic convection \citep{anders&brown2017}; we use $\epsilon = 10^{-4}$ in this work.
 
@@
 
-All of the code used to perform the simulations in this work can be found online in the supplementary materials in a Zenodo repository (CREATE AND CITE REPO).
+All of the code used to perform the simulations in this work can be found online in the supplementary materials in a Zenodo repository \citep{supp_andersetall2019}.
 
@@
     \caption{
-	(a) The thermal depth as a function of time for the 2D anelastic and 3D fully compressible simulations.
-	(b) The corresponding thermal velocities as a function of depth.
+	(top) The thermal depth as a function of time for the 2D anelastic and 3D fully compressible simulations.
+	(bottom) The corresponding thermal velocities as a function of depth.
 	Theoretical predictions from section \ref{sec:theory} are plotted in thin solid lines for each case (see parameters in table \ref{table:parameters}).
@@
     \caption{
-	(a) Thermal radius as a function of depth for the 2D anelastic and 3D fully compressible simulations.
+	(top) Thermal radius as a function of depth for the 2D anelastic and 3D fully compressible simulations.
 	Theoretical predictions from section \ref{sec:theory} are plotted in thin solid lines.
-	(b) The fractional difference between anelastic and fully compressible simulations.
+	(bottom) The fractional difference between anelastic and fully compressible simulations.
     \label{fig:diff} }
@@
 
-In Fig. \ref{fig:results_panels}a, we show the depth $d_{\text{th}} = L_z - z_{\text{th}}$ of the thermal as a function of time for simulations with different stratifications. 
+In the top panel of Fig. \ref{fig:results_panels} we show the depth, $d_{\text{th}} = L_z - z_{\text{th}}$, of the thermal as a function of time for simulations with different stratifications. 
 At very low stratification (e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
@@
 
-In Fig.~\ref{fig:results_panels}b, we show the corresponding thermal velocity as a function of depth.
+In the bottom panel of Fig.~\ref{fig:results_panels} we show the corresponding thermal velocity as a function of depth.
 Low density ($n_\rho = 0.1$) thermals decelerate with depth.
@@
 
-Fig.~\ref{fig:diff}a plots the thermal radius as a function of depth.
+The top panel of Fig.~\ref{fig:diff} plots the thermal radius as a function of depth.
 In the low stratification limit, the radius of the thermal grows linearly with depth, $r \propto d$, as is the case in the Boussinesq limit (\LJ).
-The growth of the thermal is due to entrainment of environmental fluid, which causes the thermal to decelerate like $w \propto d^{-1}$, as is shown in Fig.~\ref{fig:results_panels}b.
+The growth of the thermal is due to entrainment of environmental fluid, which causes the thermal to decelerate like $w \propto d^{-1}$, as is shown in the bottom panel of Fig.~\ref{fig:results_panels}.
 However, as stratification increases, the thermal entrainment of environmental fluid decreases and it experiences less expansion.
@@
 
-Finally, we quantify the excellent agreement between the 2D anelastic and 3D fully compressible simulations in Fig.~\ref{fig:diff}b.
+Finally, we quantify the excellent agreement between the 2D anelastic and 3D fully compressible simulations in Fig.~\ref{fig:diff}, bottom panel.
 We ran simulations in both models for $n_\rho = [0.1, 0.5, 1, 2]$.
-There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the simulations begin interacting with the bottom of the domain.
+There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the bottom of the domain.
 Outside these times, we find differences in the radius of less than 1\%.
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$m$} & \colhead{$\chi$} & \colhead{$k$}	}	
+\colhead{$n_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$m$} & \colhead{$\eta$} & \colhead{$k$}	}	
 \startdata																																															
@@
 The values of the parameters described in section \ref{sec:theory} for each of our simulations are presented in table \ref{table:parameters}.
-As anticipated, $\chi$ is $\mathcal{O}$(1) and decreases slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
+As anticipated, $\eta$ is $\mathcal{O}$(1) and decreases slightly in value with increasing stratification, consistent with Fig.~\ref{fig:constants}.
 In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
-We also find that the non-dimensional circulation is $\mathcal{O}$(-2) for each of our cases, and decreases with increasing stratification.
+We also find that the non-dimensional circulation is $\mathcal{O}$(-2) for each of our cases, and decreases in magnitude with increasing stratification.
 
@@
 We now estimate the behavior of thermals in the Sun based on the simulations presented in this work.
-The thermal evolution depends on a variety of parameters (see table table:parameters).
+The thermal evolution depends on a variety of parameters (see table \ref{table:parameters}).
 However, we find the only parameter which changes appreciably as we increase the stratification is the normalized buoyancy $B_\text{th}$.
@@
     \caption{
-	(a) Bounds on the evolution of the radii of entropy rain in the Sun are shown and compared to what the radii would be under purely horizontal compression.
-	(b) The velocities of the thermals in the estimated boundaries are shown. 
-	(c) The estimated ratio of the thermal diffusion timescale of the thermals normalized by the thermal's freefall timescale over 1 Mm is shown.
+	(top) Bounds on the evolution of the radii of entropy rain in the Sun are shown and compared to what the radii would be under purely horizontal compression.
+	(middle) The corresponding range of velocities of solar-like thermals are shown. 
+	(bottom) Shown is the estimated range of the ratio of the thermal diffusion timescale normalized by the freefall timescale over the thermal radial length scale.
 	Diffusivities are calculated using the realistic solar-like diffusion profiles of \citet{brown2011}.
@@
 \ref{fig:thermal_sun_comparison}.
-In Fig. \ref{fig:thermal_sun_comparison}a\&b, we show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
-We use the solar diffusivity models of \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r^2$) and the thermal freefall timescale over 1 Mm ($\tau_{\text{ff}} = [1\,\text{Mm}]/w_{\text{th}}$).
-In Fig. \ref{fig:thermal_sun_comparison}c, we plot the ratio of these two timescales over the thermal's evolution.
+In the top and middle panels of Fig.
+\ref{fig:thermal_sun_comparison}, we show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
+We use the solar diffusivity models of \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r_{\text{th}}^2$) and the thermal freefall timescale over its own radial length scale ($\tau_{\text{ff}} = r_{\text{th}}/w_{\text{th}}$).
+In the bottom panel of Fig. \ref{fig:thermal_sun_comparison}, we plot the ratio of these two timescales over the thermal's evolution.
 
@@
 This work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
-This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
+This work was additionally supported by NASA LWS grant NNX16AC92G and by the National Science Foundation under grant No.~1616538. 
 DL is supported by Princeton Center for Theoretical Science and Lyman Spitzer Jr.~postdoctoral fellowships.
@@
 To find the entropy minima horizontally, we integrate $\int \rho S_1 dz$ in our Dedalus domain, then sample the spectral data onto a 2048-point radial grid, and take the minima of that profile to be the radius of the thermal.
-In order to find the thermal's velocity as a function of time, we use a five-point stencil to differentiate the thermal's depth, $d$,
+For our 2D simulations, we use entropy data from the full simulation domain to perform these calculations.
+For our 3D simulations, we assume that the vortex ring is azimuthally symmetric, and thus use the entropy data in the $y = 0$ plane at radial values of $x \geq 0$.
+In order to find the thermal's velocity as a function of time, we use a five-point stencil to differentiate the thermal's depth, $d_{\text{th}}$,
 $$
@@
 
-Integral quantities, such as the circulation, $\Gamma$, the buoyancy, $B$, and the volume, $\mathcal{V}$ require us to first determine what fraction of the domain constitutes the thermal.
-To do so, we use the thermal tracking algorithm described in appendix \ref{appendix:tracking} to determine the radial contour that outlines the thermal as a function of height, $\mathcal{C}$.
+Calculating integral quantities such as the circulation, $\Gamma$, the buoyancy, $B$, and the volume, $\mathcal{V}$, require knowledge of what fraction of the domain constitutes the thermal.
+We use the thermal tracking algorithm described in appendix \ref{appendix:tracking} to determine the radial contour, $\mathcal{C}$, that outlines the thermal as a function of height.
 We then use this contour to find our integral quantities,
@@
 Information regarding the simulation resolution, evolution time, and CFL safety factor for each of the simulations presented in this work is contained in table \ref{table:simulation_info}.
-The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository CITE.
+The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository  \citep{supp_andersetall2019}.
 
@@
 We use a CFL to determine the appropriate size of our timestep at each timestep in our simulation, and the CFL safety factor decreases with increasing stratification.
-Our 2D sims use the RK443 timestepper and our 3D sims use the SBDF2 timestepper, resulting in vastly different safety factor sizes in 2D and 3D.
+Our 2D sims use the RK443 timestepper and our 3D sims use the SBDF2 timestepper, resulting in different safety factor sizes in 2D and 3D.
 }

### 2019-06-05 stratified_thermals_code/AN_2D_thermal.py

@@ -1,0 +1,292 @@
+"""
+Dedalus script for simulating a 2D, azimuthally-symmetric thermal in an adiabatic polytrope.
+Equations are LBR Anelastic, as in Brown et al. 2012 and Lecoanet et al. 2014, rescaled
+on a freefall velocity scale with the length scale set by the diameter of the thermal.
+
+This code must be used with a version of Dedalus after commit  0128fa0 by Keaton Burns 
+on 2019-02-21, such that the problem.add_equation() function has the 'tau' keyword.
+
+Usage:
+    AN_2D_thermal.py [options]
+
+Options:
+    --n_rho=<n_rho>       number of density scale heights [default: 0.5]
+    --Reynolds=<Re>       Reynolds number [default: 6e2]
+    --Prandtl=<Pr>        Prandtl number [default: 1]
+    --nz=<n>              Number of z coefficients [default: 256]
+    --nr=<n>              Number of r coefficients [default: 128]
+
+    --wall_hours=<t>      Number of wall hours to run for max [default: 7.5]
+    --run_time_buoy=<rt>  Number of buoyancy times to run for [default: 60]
+
+    --aspect=<a>          Domain runs from [0, Lr], with Lr = aspect*Lz [default: 0.25]
+    --label=<l>           an optional string at the end of the output directory for easy identification
+
+    --rk443               If flagged, timestep using RK443. Else, SBDF2.
+
+    --Lz=<L>              The depth of the domain, in thermal diameters [default: 20]
+
+    --chi_nu              If true, use a constant diffusivity (rather than constant dynamic diffusivity) eqn formulation
+    --safety=<s>          Safety factor base [default: 0.1]
+    --out_cadence=<o>     Time cadence of output saves in buoyancy times [default: 0.35]  
+
+    --restart=<file>      Name of file to restart from, if starting from checkpoint
+
+"""
+import os
+import time
+import sys
+
+import numpy as np
+from mpi4py import MPI
+from scipy.special import erf
+from dedalus import public as de
[…]

### 2019-06-05 stratified_thermals_code/FC_3D_thermal.py

@@ -1,0 +1,278 @@
+"""
+Stratified fully compressible thermals in an adibatically stratified polytrope.
+Mu and Kappa are constant with depth.
+
+Usage:
+    FC_3D_thermal.py [options]
+
+Options:
+    --Reynolds=<Reynolds>                Reynolds number [default: 5e2]
+    --Prandtl=<Prandtl>                  Prandtl number = nu/kappa (top) [default: 1]
+    --n_rho=<n_rho>                      Density scale heights across layer [default: 1]
+    --epsilon=<epsilon>                  Amplitude of perturbation [default: 1e-4]
+
+    --gamma=<gamma>                      Gamma of ideal gas (cp/cv) [default: 5/3]
+    --aspect=<aspect_ratio>              Physical aspect ratio of the atmosphere (Lx = Ly = aspect*[diameter of thermal]) [default: 0.5]
+
+    --nz=<nz>                            vertical z (chebyshev) resolution [default: 512]
+    --nx=<nx>                            Horizontal x (Fourier) resolution [default: 256]
+    --ny=<ny>                            Horizontal y (Fourier) resolution [default: 256]
+    --mesh=<mesh>                        Processor mesh
+
+    --run_time=<run_time>                Run time, in hours [default: 7.5]
+    --run_time_buoy=<run_time_buoy>      Run time, in buoyancy times [default: 50]
+
+    --restart=<restart_file>             Restart from checkpoint
+
+    --safety_factor=<safety_factor>      Determines CFL Danger.  Higher=Faster [default: 0.2]
+
+    --label=<label>                      Additional label for run output directory
+    --join                               If flagged, join files at end of run
+    --out_cadence=<cadence>              Fraction of a buoyancy time on which to output [default: 0.35]                    
+
+    --chi_nu                             If flagged, do chi/nu formulation
+
+    --verbose
+    --SBDF2                              If flagged use SBDF2 timestepper
+    --443                                If flagged, use RK443 instead of RK222
+    --no_VH                              If flagged, don't include viscous heating
+"""
+import sys
+import os
+import time
[…]

### 2019-06-05 stratified_thermals_code/logic/atmospheres.py

@@ -1,0 +1,131 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+
+from dedalus import public as de
+
+def set_field(field, in_arr, scales=1):
+    """
+    Sets the values in a dedalus field to match those in an input NumPy array
+    at the proper scale. Returns the field at that scale.
+
+    Parameters
+    ----------
+    field   : A Dedalus Field object
+        The field to set the values of
+    in_arr  : A NumPy array
+        The NumPy array to set the field values to
+    scales  : float, optional
+        The size scale at which to set the field.
+    """
+    field.set_scales(scales, keep_data=True)
+    field['g'] = in_arr
+    field.set_scales(scales, keep_data=True)
+    return field
+
+
+
+class IdealGasAtmosphere:
+    """
+    An abstract class which contains many of the attributes of an
+    ideal gas atmosphere, to be extended to more specific cases.
+
+    Attributes:
+    -----------
+        params      : OrderedDict 
+            Scalar atmospheric parameters (floats, ints)
+        gamma       : Float
+            The adiabatic index of the atmosphere
+        Cp, Cv      : Floats
+            Specific heat at constant pressure, volume
+        g           : Float
+            Gravity, constant. (default value sets T_ad_z = -1)
+        R           : Float
+            The ideal gas constant
+        T_ad_z      : Float
+            The adiabatic temperature gradient, as defined in Anders&Brown2017 & elsewhere
+        de_domain   : A DedalusDomain object 
+            The domain on which the atmosphere will be built
+        atmo_fields : OrderedDict 
+            contains fields for the variables: T0, T0_z, T0_zz, rho0, ln_rho0, ln_rho0_z, phi
+    """
+
+    def __init__(self, de_domain, gamma=5./3, R=1, g=None):
+        """
+        Initialize the atmosphere. Inputs that match attributes in the class docstring are
+        defined there.
+        """
+        self.params = OrderedDict()
+        self.rho_fit     = None
+        self.params['R'] = R
+        self.params['gamma'] = gamma
+        self.params['Cp'] = gamma*R/(gamma-1.)
+        self.params['Cv'] = self.params['Cp'] - R
[…]

### 2019-06-05 stratified_thermals_code/logic/equations.py

@@ -1,0 +1,336 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+
+from dedalus import public as de
+from mpi4py import MPI
+
+
+class FullyCompressibleEquations:
+    """
+    An abstract class containing the fully compressible equations which must
+    be extended to specify the type of diffusivities
+
+    Attributes
+    ----------
+    de_domain   : A DedalusDomain object
+        The domain on which the equations are solved
+    atmosphere  : An IdealGasAtmosphere object
+        The atmosphere in which the equations are solved
+    variables   : list
+        A list of strings of problem variables.
+    problem     : A Dedalus Problem object
+        The problem in which the equations are solved.
+    """
+    def __init__(self, de_domain, atmosphere):
+        """
+        Construct the equation class. Inputs are described in the class docstring.
+        """
+        self.de_domain = de_domain
+        self.atmosphere = atmosphere
+        self.variables = ['u','u_z','v', 'v_z', 'w','w_z','T1', 'T1_z', 'ln_rho1']
+        if not self.de_domain.threeD:
+            self.variables.remove('v')
+            self.variables.remove('v_z')
+
+        self.problem = de.IVP(self.de_domain.domain, variables=self.variables)
+        if not self.de_domain.threeD:
+            self.problem.substitutions['v'] = '0'
+            self.problem.substitutions['v_z'] = '0'
+            self.problem.substitutions['dy(A)'] = '0*A'
+
+    def set_equations(self, *args, **kwargs):
+        """ 
+        Sets the fully compressible equations of in a ln_rho / T formulation. These
+        equations take the form:
+        
+        D ln ρ + ∇ · u = 0
+        D u = - ∇ T - T∇ ln ρ - gẑ + (1/ρ) * ∇ · Π
+        D T + (γ - 1)T∇ · u - (1/[ρ Cv]) ∇ · (- Kap∇ T) = (1/[ρ Cv])(Π ·∇ )·u 
+        
+        Where
+
+        D = ∂/∂t + (u · ∇ ) 
+
+        and
+
+        Π = - Mu (∂u_i/∂x_j + ∂u_j/∂x_i - (2/3)D_{ij}∇ · u)
+
[…]

### 2019-06-05 stratified_thermals_code/logic/post_processing.py

@@ -1,0 +1,860 @@
+"""
+Analysis functionality for a 2D, cylindrically symmetric thermal's properties 
+
+Usage:
+    thermal_analysis.py --root_dir=<dir> [options]
+
+Options:
+    --root_dir=<root_dir>               Directory pointing to 'slices', etc
+    --plot                              If flagged, plot colormesh during analysis
+    --no_analyze                        If flagged, do not do full analysis
+    --n_files=<n>                           Number of files [default: 10000]
+    --get_contour                       If flagged, do full contour solve
+    --iterative                         If flagged, use results of previous solve to inform new solve
+"""
+import os
+import glob
+import logging
+logger = logging.getLogger(__name__)
+
+import h5py
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+from scipy.interpolate import interp1d, RegularGridInterpolator
+from scipy.optimize import brentq
+import scipy.optimize as scop
+
+from dedalus import public as de
+
+def differentiate(x, y): 
+    """ Numerical differentiation. Output has 4 fewer points than input. """
+    dx = np.mean(x[1:] - x[:-1])
+    return (-y[4:] + 8*y[3:-1] - 8*y[1:-3] + y[:-4]) / (12*dx)
+
+def linear_fit(x, a, b):
+    """ A linear fit: y = a* x + b """
+    return a*x + b
+
+def theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=-1):
+    """ The constant in stratified thermals theory """
+    return (grad_T_ad * Gamma0 * np.pi**(3./2) / f / (1 + beta)) * np.sqrt(Gamma0/(B0 * chi))
+
+def theory_r(t, B0, Gamma0, chi, t_off, rho_f=None):
+    """ The temperature profile (vs time) from stratified thermals theory """
+    r = np.sqrt(chi*B0*(t + t_off)/np.pi/Gamma0)
+    if rho_f is None:
+        return r
+    return r/np.sqrt(rho_f(t))
+
+def theory_T(t, B0, Gamma0, f, chi, beta, t_off, T0, grad_T_ad=-1, m_ad=1.5):
+    """ The temperature profile (vs time) from stratified thermals theory """
+    C0 = theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=grad_T_ad)
+    Tpow = 1 - (m_ad/2)
[…]

### 2019-06-05 stratified_thermals_code/paper_plots/diff_AN_FC.py

@@ -1,0 +1,141 @@
+import matplotlib
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'dejavuserif'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+import h5py
+
+from scipy.interpolate import interp1d
+
+NRUNS=8
+
+aspect = [0.25, 0.25, 0.25, 0.25]
+CASES = [0.1, 0.5, 1, 2]
+ROOT_DIR='../'#good_2D_runs/z_bot_zero/'
+DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
+
+aspect_2D = [0.25, 0.25, 0.25, 0.25, 0.25, 0.25, 0.25, 0.25]
+CASES_2D = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
+color_dir = [1, 2, 3, 4, 5, 6, 7, 8]
+DIRS_2D=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES_2D, aspect_2D)] 
+
+CASES_3D = [0.1, 0.5, 1, 2]
+AR_3D    = [0.5, 0.5, 0.5, 0.5]
+THREED_DIR = '../'
+DIRS_3D=['{:s}FC_3D_thermal_Re6e2_Pr1_eps1.00e-4_nrho{}_aspect{}/'.format(THREED_DIR,nrho, ar) for nrho, ar in zip(CASES_3D, AR_3D)] 
+dict_3D = {}
+for i in range(len(CASES_3D)):
+    dict_3D[CASES_3D[i]] = DIRS_3D[i]
+
+
+height, width = 2.5, 3.25 
+
+gs = gridspec.GridSpec(1000, 1000)
+fig = plt.figure(figsize=(width, height))
[…]

### 2019-06-05 stratified_thermals_code/paper_plots/overview_fig.py

@@ -1,0 +1,101 @@
+import matplotlib
+matplotlib.use('Agg')
+matplotlib.rcParams['font.family'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.fontset'] = 'custom'
+matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
+matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
+matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
+matplotlib.rcParams.update({'font.size': 9})
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+import numpy as np
+from scipy.interpolate import interp1d
+import h5py
+
+def theory_C(B, Gamma, V0, beta, chi, grad_T_ad=-1):
+    """ The constant in stratified thermals theory """
+    return np.pi**(3./2) * Gamma * grad_T_ad * chi / (V0 * B * beta**(1./2))
+
+def theory_T(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
+    """ The temperature profile (vs time) from stratified thermals theory """
+    C0 = theory_C(B, Gamma, V0, beta, chi, grad_T_ad=grad_T_ad)
+    tau = (B * t + I0)/Gamma
+    tau0 = I0/Gamma
+    Tpow = 1 - (m_ad/2)
+    tau_int  = np.sqrt(tau )*(Gamma - (M0 - I0)/tau)
+    tau_int0 = np.sqrt(tau0)*(Gamma - (M0 - I0)/tau0)
+    return (2*Tpow*C0*(tau_int-tau_int0) + T0**(Tpow))**(1./Tpow)
+
+def theory_dT_dt(t, B, M0, I0, Gamma, V0, T0, beta, chi, grad_T_ad=-1, m_ad=1.5):
+    """ The temperature derivative (vs time) from stratified thermals theory """
+    C0 = theory_C(B, Gamma, V0, beta, chi, grad_T_ad=grad_T_ad)
[…]

### 2019-07-13 tex/stratified_thermals.tex
png->pdf ><
response to referee and corresponding manuscript changes

@@
 \begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{overview_fig.png}
+    \includegraphics[width=\columnwidth]{overview_fig.pdf}
     \caption{
-	Shown is the filling fraction of a dense thermal as a function of depth in an atmosphere which spans three density scale heights (the $n_\rho = 3$ case examined later in this work). 
+	Shown is the filling fraction of a dense thermal as a function of depth in an atmosphere which spans three density scale heights (the $N_\rho = 3$ case examined later in this work). 
 	Thin solid lines indicate the predictions for filling fraction growth in the Boussinesq case (\LJ) and for pure horizontal compression \citep[B16,][]{brandenburg2016}.
@@
 
-Ignoring entropy variations, \citet{brandenburg2016} suggests the filling fraction $f$ of entropy rain should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression.
+Ignoring entropy variations, \citet{brandenburg2016} suggests the filling fraction $f$ of entropy rain should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression, \textbf{where $\rho$ is the density}.
 On the other hand, the filling fraction of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth of the thermal.
@@
 \subsection{Phenomenological description of thermal evolution}
-Fig.~\ref{fig:evolution_colormeshes} depicts the descent of 3D cold thermals released from rest in two domains which span a different number of density scale heights, $n_\rho$.
-The left panel shows a weakly stratified domain with $n_\rho=0.5$, whereas the right panel shows a strongly stratified domain with $n_\rho=3$.
+\textbf{In} Fig.~\ref{fig:evolution_colormeshes}, \textbf{we show snapshots of 3D simulation data depicting} the descent of cold thermals released from rest in two domains which span a different number of density scale heights, $N_\rho$.
+The left panel shows a weakly stratified domain with $N_\rho=0.5$, whereas the right panel shows a strongly stratified domain with $N_\rho=3$.
 In both cases, the thermal is initialized with a spherical negative entropy perturbation whose diameter is 5\% of the domain depth.
 This dense sphere spins up into an axisymmetric vortex ring, and the vertical cross section through this vortex ring shows two circular vorticity and entropy extrema.
-In the $n_\rho = 0.5$ simulation, the thermal grows with depth, similar to thermals in the Boussinesq regime.
-On the other hand, in the $n_\rho = 3$ simulation, the thermal's radius decreases marginally with depth.
+In the $N_\rho = 0.5$ simulation, the thermal grows with depth, similar to thermals in the Boussinesq regime.
+On the other hand, in the $N_\rho = 3$ simulation, the thermal's radius decreases marginally with depth.
 
@@
 In the following sections, we will use the impulse of dense vortex rings to derive expressions for the evolution of their depth and radii with time.
+\textbf{\citet{rast1998} showed that 2D compressible, low entropy plumes in stratified domains emit vortex pairs, and this description of vortex ring evolution should be useful both in our study of thermals and in more time-continuous plume sources.}
 
@@
     \caption{
-	Mass-weighted entropy perturbations, normalized by the thermal's buoyancy perturbation.
-	(left) A thermal in a weakly stratified domain with $n_\rho = 1/2$ density scale heights, and (right) a thermal in a strongly stratified domain with $n_\rho = 3$.
-	While both start with precisely the same initial condition, the thermal in low stratification expands with depth, whereas the thermal in strong stratification compresses with depth.
+	\textbf{Shown is the evolution of mass-weighted entropy perturbations, normalized by the thermal's buoyancy perturbation, from 3D simulations conducted in this work}.
+	(left) A thermal in a weakly stratified domain with $N_\rho = 1/2$ density scale heights, and (right) a thermal in a strongly stratified domain with $N_\rho = 3$.
+	While both start with precisely the same initial condition, the thermal in low stratification expands with depth \textbf{and slows down}, whereas the thermal in strong stratification compresses with depth \textbf{and accelerates}.
     \label{fig:evolution_colormeshes} }
@@
 While many theoretical descriptions rely on self-similarity arguments, we will show how the impulse of a thermal controls its evolution.
-This section parallels a similar analysis for the Boussinesq case, presented in McKim et al (in prep).
+This section parallels a similar analysis for the Boussinesq case, presented in \citet{mckim&all2019}.
 
@@
 \end{equation}
-where $\bm{x}$ is the position vector. 
+where $\bm{x}$ is the position vector \textbf{and $\bm{u}$ is the fluid velocity}. 
 The impulse is the time-integrated work which has acted on the fluid to result in the current fluid motion.
@@
 However, one can also show that the surface terms correspond to the momentum outside the volume $\mathcal{V}$ \citep[e.g.][]{Akhmetov2009}.
-A thermal with volume $\mathcal{V}$, density $\rho$, and translating with velocity $w_{\text{th}} \hat{z}$ thus has an impulse
+A thermal with volume $\mathcal{V}$, density $\rho$, and translating with velocity $\bm{u} = w_{\text{th}} \hat{z}$ thus has an impulse
 \begin{equation}\label{eqn:momentum}
@@
 because the surface terms completely cancel.
-Assuming $\bm{g} = -g\hat{z}$, it is useful to define the buoyancy perturbation,
+Assuming \textbf{a uniform, vertical gravity,} $\bm{g} = -g\hat{z}$, it is useful to define the buoyancy perturbation,
 \begin{equation}
@@
 \begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{constants.png}
+    \includegraphics[width=\columnwidth]{constants.pdf}
     \caption{
-	Evolution of buoyancy perturbation (top), circulation (middle), and volume factor (bottom) in 2D thermal simulations.
-	All are nearly constant after an initial spin-up phase.
-	With increasing stratification, we see marginally more detrainment in the buoyancy perturbation.
+	\textbf{Shown is the} evolution of buoyancy perturbation (top), circulation (middle), and volume factor (bottom) \textbf{for each 2D simulation conducted in this work}.
+	All \textbf{three of these quantities remain} nearly constant after an initial spin-up phase.
+	With increasing stratification, we see marginally more detrainment \textbf{(loss of buoyant signature)} in the \textbf{top panel}.
     \label{fig:constants} }
@@
 
-After spinning up, we assume that the thermal has a negative buoyancy, $B_{\text{th}}$, and circulation, $\Gamma_{\text{th}}$.
-While these thermals began as initial spherical perturbations, they act like vortex rings which evolved from a ``virtual origin'' where the vortex ring had zero radius.
-We model the thermal as having been located at its virtual origin at $t = -t_{\text{off}}$, where $t = 0$ is the time at which the true thermal was released from rest.
+%After spinning up, we assume that the thermal has a \textbf{constant} negative buoyancy \textbf{perturbation} and \textbf{constant} circulation.
+\textbf{The thermals studied here} began as initial spherical perturbations \textbf{and spin up into vortex rings}.
+\textbf{The spun up vortex ring phase can be modeled as having evolved} from a ``virtual origin'' where the vortex ring had zero radius.
+We model the thermal as having been located at its virtual origin at \textbf{a temporal offset} $t = -t_{\text{off}}$, where $t = 0$ is the time at which the true thermal was released from rest.
 
-We find the thermal undergoes weak detrainment, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}, top panel).
+\textbf{In our simulations,} we find the thermal undergoes weak detrainment \textbf{(loss of buoyant signature to environmental fluid)}, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}, top panel).
 We thus express the buoyancy perturbation as 
@@
 \end{equation}
-where $\eta$ is a constant of $\mathcal{O}$(1) which represents this detrainment. 
+where $\eta$ is a constant of $\mathcal{O}$(1) which represents this detrainment \textbf{and $B_{\text{th}}$ is the thermal's characteristic buoyancy perturbation}. 
 We then integrate Eqn.~\ref{eqn:change_in_impulse},
@@
 \end{equation}
-Recall there are no net baroclinic torques, so $\Gamma_{\text{th}}$ stays nearly constant (Fig.~\ref{fig:constants}, middle panel).
+\textbf{$\Gamma_{\text{th}}$ is the characteristic circulation of the thermal.
+As} there are no net baroclinic torques, $\Gamma_{\text{th}}$ \textbf{remains nearly constant in our simulations} (Fig.~\ref{fig:constants}, middle panel).
 In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in \LJ.
@@
 To solve for the vertical evolution of the thermal, we can use Eqn.~\ref{eqn:momentum}.
-We approximate the volume as $\mathcal{V} \approx m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption, as in Fig.~\ref{fig:constants}, bottom panel).
+We approximate the volume as $\mathcal{V} \approx m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption \textbf{in our simulations}; see Fig.~\ref{fig:constants}, bottom panel).
+\textbf{Here, $m$ accounts for volumetric constants, the aspect ratio of the thermal, and the ratio between the full radius of the spheroidal thermal and $r$, the radius to the entropy maxima.}
 Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, we find
@@
 \begin{gather}\label{eqn:T0}
-T_0 = 1 + (\grad_{\text{ad}})(z - L_z), \\
+T_0 = 1 + (z - L_z)\grad_{\text{ad}}, \\
 \rho_0 = T_0^{\,n_{\text{ad}}},
@@
 \end{gather}
-where $n_{\text{ad}} = (\gamma-1)^{-1}$.
+where $n_{\text{ad}} = (\gamma-1)^{-1}$ \textbf{and $\grad_{\text{ad}}$ is the adiabatic temperature gradient}.
 All thermodynamic quantities are nondimensionalized such that $\rho_0 = T_0 = 1$ at $z = L_z$, the top of the domain.
@@
 $$ 
-The thermal is at the virtual origin, $z=z_0$, at time $t=-t_{\text{off}}$, and the temperature there is $T_{\text{th},0} = 1 + \grad_{\text{ad}}(z_{\text{th},0} - L_z)$.
+The thermal is at the virtual origin, $z=z_0$, at time $t=-t_{\text{off}}$, and the temperature there is $T_{\text{th},0} = 1 + (z_{\text{th},0} - L_z)\grad_{\text{ad}}$.
 We define $\alpha^{-1} \equiv 1 - n_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
@@
 \label{sec:experiment}
-To test our theory, we run a series of simulations of the 3D fully compressible equations, as well as 2D simulations of the anelastic equations.
+To test our theory, we run a series of \textbf{thermal} simulations \textbf{using} the 3D fully compressible equations \textbf{in cartesian domains}.
+\textbf{We additionally compute 2D azimuthally-symmetric} simulations \textbf{using} the anelastic equations \textbf{in cylindrical domains}.
 We verify the 3D and 2D simulations produce the same results when run with the same parameters.
@@
 \frac{1}{\text{Re}}\left(\frac{1}{\rho_0c_P\text{Pr} }\right.&[\grad^2 S_1 + \partial_z\ln T_0 \cdot\partial_z S_1]\\
-&+ \left.\frac{-(\grad_{\text{ad}})}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right),
+&+ \left.\frac{-\grad_{\text{ad}}}{\rho_0 T_0}\sigma_{ij}\partial_{x_i}u_j \right),
 \end{split}
@@
 The background density and temperature are given by Eqs.~\ref{eqn:T0} \& \ref{eqn:polytrope}.
-The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{n_\rho/n_{\text{ad}}}-1)/(L_z c_P)$, where $L_z=20$ is the height of the domain.
+The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{N_\rho/n_{\text{ad}}}-1)/(L_z c_P)$, where $L_z=20$ is the height of the domain \textbf{and $N_\rho$ is the number of density scale heights spanned by the domain}.
 
@@
 
-All of the code used to perform the simulations in this work can be found online in the supplementary materials in a Zenodo repository \citep{supp_andersetall2019}.
+\textbf{
+Dedalus currently allows for the direct specification of general boundaries in one direction.
+In the case of our 2D simulations, this direction must be the radial direction in order to capture the singularity at $r = 0$.
+While Dedalus can expand fields in terms of sine or cosine bases (as in \LJ), the mixed parities of terms such as the viscous heating term in the fully compressible or anelastic equations rules out a simple specification in these equation sets.
+We have therefore chosen to use periodic Fourier bases in the vertical direction of our simulations, and end the simulations before the thermal can interact with those boundaries.
+Remarkably, the results of these simulations vary only minimally from our 3D simulations, as we will show in the next section, and the vertical boundaries do not meaningfully affect the evolution of the thermal.
+}
+
+All of the code used to perform the simulations in this work can be found online in the supplementary materials in a Zenodo repository \citep{supp_andersetall2019} \textbf{at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}}.
 
@@
 \begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{results_panels.png}
+    \includegraphics[width=\columnwidth]{results_panels.pdf}
     \caption{
-	(top) The thermal depth as a function of time for the 2D anelastic and 3D fully compressible simulations.
+	(top) The thermal depth as a function of time for the 2D anelastic \textbf{(AN)} and 3D fully compressible \textbf{(FC)} simulations.
 	(bottom) The corresponding thermal velocities as a function of depth.
@@
 \begin{figure}[t!]
-    \includegraphics[width=\columnwidth]{diff_AN_FC.png}
+    \includegraphics[width=\columnwidth]{diff_AN_FC.pdf}
     \caption{
-	(top) Thermal radius as a function of depth for the 2D anelastic and 3D fully compressible simulations.
+	(top) Thermal radius as a function of depth for the 2D anelastic \textbf{(AN)} and 3D fully compressible \textbf{(FC)} simulations.
 	Theoretical predictions from section \ref{sec:theory} are plotted in thin solid lines.
@@
 In the top panel of Fig. \ref{fig:results_panels} we show the depth, $d_{\text{th}} = L_z - z_{\text{th}}$, of the thermal as a function of time for simulations with different stratifications. 
-At very low stratification (e.g., $n_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
+At very low stratification (e.g., $N_\rho = 0.1$), the thermal is small compared to the local density scale height at all depths, and it evolves roughly according to the Boussinesq prediction of $d \propto \sqrt{t}$.
 As the stratification increases, the thermal transits the domain more quickly and approaches the limit of $d \propto t^2$ predicted in the highly stratified limit of Eqn.~\ref{eqn:theory_z}. 
@@
 In the bottom panel of Fig.~\ref{fig:results_panels} we show the corresponding thermal velocity as a function of depth.
-Low density ($n_\rho = 0.1$) thermals decelerate with depth.
-With increasing stratification, this deceleration stops and sufficiently stratified runs ($n_\rho \geq 3$) experience acceleration.
+Low density ($N_\rho = 0.1$) thermals decelerate with depth.
+With increasing stratification, this deceleration stops and sufficiently stratified runs ($N_\rho \geq 3$) experience acceleration.
 
@@
 However, as stratification increases, the thermal entrainment of environmental fluid decreases and it experiences less expansion.
-In the limit of large stratification ($n_\rho \geq 3$), thermals contract with depth, and the thermals accelerate as they fall.
+In the limit of large stratification ($N_\rho \geq 3$), thermals contract with depth, and the thermals accelerate as they fall.
 
 Finally, we quantify the excellent agreement between the 2D anelastic and 3D fully compressible simulations in Fig.~\ref{fig:diff}, bottom panel.
-We ran simulations in both models for $n_\rho = [0.1, 0.5, 1, 2]$.
+We ran simulations in both models for $N_\rho = [0.1, 0.5, 1, 2]$.
 There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the bottom of the domain.
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$m$} & \colhead{$\eta$} & \colhead{$k$}	}	
+\colhead{$N_\rho$} & \colhead{$z_{\text{th},0}$} & \colhead{$t_{\text{off}}$} & \colhead{$B_{\text{th}}$} & \colhead{$\Gamma_{\text{th}}$} & \colhead{$m$} & \colhead{$\eta$} & \colhead{$k$}	}	
 \startdata																																															
@@
 1	 	&  23.6 	& 1.15	& -0.601 & -2.05 & 8.87	& 0.907	& 0.689	\\
-2	 	&  22.9 	& 2.88	& -0.699 & -1.89 & 9.24	& 0.776	& 0.706	\\
+2	 	&  22.4 	& 1.38	& -0.711 & -1.89 & 9.31	& 0.828	& 0.680	\\
+\textbf{3}	 	&  \textbf{21.1} 	& \textbf{0.78}	& \textbf{-0.949} & \textbf{-1.75} & \textbf{9.99}	& \textbf{0.815}	& \textbf{0.648}	\\
 \enddata																																															
@@
 $$
-Nondimensionalizing this by $B_0 = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B_\text{th} = \tilde{B}/B_0 = -3.57$, which lies between the $n_\rho = 5$ and $n_\rho = 6$ simulations we studied here (see table \ref{table:parameters}).
+Nondimensionalizing this by $B_0 = (S_1/c_P) L^2 u_{\text{th}}^2 \rho_0$ with $u_{\text{th}} = c_s \sqrt{S_1/c_P}$, we find $B_\text{th} = \tilde{B}/B_0 = -3.57$, which lies between the $N_\rho = 5$ and $N_\rho = 6$ simulations we studied here (see table \ref{table:parameters}).
 
@@
 These thermals experience radial compression with corresponding increases in velocity, but experience much less compression than a naive approximation based on the density stratification alone.
+\textbf{Interestingly, the thermal's Mach number is roughly a value of 0.1 throughout the full extent of the solar convection zone.}
 Furthermore, throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
@@
 We'd like to thank Brett McKim and Nadir Jeevanjee for discussions about thermals and the laminar entrainment picture.
+\textbf{We'd like to further thank Nadir Jeevanjee, Jeremy Goodman, and the anonymous referee whose careful comments greatly improved the scientific quality and clarity of this manuscript.}
 This work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
@@
 Information regarding the simulation resolution, evolution time, and CFL safety factor for each of the simulations presented in this work is contained in table \ref{table:simulation_info}.
-The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository  \citep{supp_andersetall2019}.
+The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository \citep{supp_andersetall2019} \textbf{at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}}.
+\textbf{The 3D, $N_\rho = 3$ simulation displays spectral instabilities at very late times, affecting radial measurements at depths $\geq 17.5$.
+We therefore truncate the data from that simulation at a depth of 15, which corresponds to multiple freefall times before these instabilities affect the solution.}
 
@@
 \tablehead{																																															
-\colhead{$n_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{\text{evolution}}$} & \colhead{safety}	}	
+\colhead{$N_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{\text{evolution}}$} & \colhead{safety}	}	
 \startdata																																															
@@
 1	 	& 		256			& 512			& 41	 	&	0.15	\\
-2	 	& 		256			& 1024			& 34    	&	0.1	\\
+2	 	& 		\textbf{384}			& 1024			& 34    	&	0.1	\\
+\textbf{3}	 	& 		\textbf{512}			& \textbf{2048}			& \textbf{25}    	&	\textbf{0.15}	\\
 \enddata																																															

### 2019-07-13 code/plotting/thermal_sun_comparison.py

@@ -39,8 +39,9 @@ def theory_dT_dt(t, B0, Gamma0, f, chi, beta, t_off, T0, grad_T_ad=-1, m_ad=1.5)
     return C0*this_T**(m_ad/2)/np.sqrt(t + t_off)
 
 def read_solar_profiles():
-    mesa_data = np.genfromtxt('sun_4.5gyr.data', skip_header=6, usecols=(2, 4)) #logR (in Rsun units), logRho (g/cm^3)
-    mesa_data = 10**(mesa_data)
+    mesa_data = np.genfromtxt('sun_4.5gyr.data', skip_header=6, usecols=(2, 4, 9)) #logR (in Rsun units), logRho (g/cm^3), csound (cm/s)
+    csound = mesa_data[:,2]*cm2Mm
+    mesa_data = 10**(mesa_data[:,:-1])
     radius    = mesa_data[:,0]*Rsun2Mm
     density    = mesa_data[:,1]*(cm2Mm)**(-3)
 
@@ -66,12 +67,13 @@ def read_solar_profiles():
     radii *= Rsun2Mm
 
     rho2r = interp1d(density, radius, bounds_error=False, fill_value='extrapolate')
+    r2cs = interp1d(radius, csound, bounds_error=False, fill_value='extrapolate')
     r2chi = interp1d(radii, chi, bounds_error=False, fill_value='extrapolate')
     r2nu  = interp1d(radii, nu, bounds_error=False, fill_value='extrapolate')
 
-    return rho2r, r2chi, r2nu
+    return rho2r, r2chi, r2nu, r2cs
 
-rho2r, r2chi, r2nu = read_solar_profiles()
+rho2r, r2chi, r2nu, r2cs = read_solar_profiles()
 
 
 
@@ -191,10 +193,12 @@ plt.fill_between(x_values/(Rsun2Mm), lower_y_values, upper_y_values, color='blac
 #plot actual velocity measurements
 for i in range(2):
     plt.plot(solar_radii[i]/(Rsun2Mm), w_outs[i]*(u_th/w_outs[i][0]), c='k', lw=0.5*(i+1))
+plt.plot(solar_radii[i]/Rsun2Mm, r2cs(solar_radii[i]), c='k', lw=1, dashes=(5,1,2,1))
[…]

### 2019-07-17 code/FC_3D_thermal.py
plotting updates

@@ -189,7 +189,7 @@ flow.add_property("vol_avg(rho_fluc*phi)", name='PE_fluc')
 flow.add_property("vel_rms*L/nu", name='Re')
 flow.add_property("Ma_rms", name='Ma')
 flow.add_property("integ(rho_full*s1)", name='integ_s')
-flow.add_property("((dz(T_full)/T_full)**2 - (dz(T0)/T0)**2)", name='dissipation') # good for seeing if the solution isn't resolved.
+flow.add_property("((dz(T_full)/T_full)**2 + (dx(T_full)/T_full)**2 + (dy(T_full)/T_full)**2 - (dz(T0)/T0)**2)", name='dissipation') # good for seeing if the solution isn't resolved.
 
 ################################################
 # CFL and sim stop conditions

### 2019-07-17 code/logic/post_processing.py

@@ -577,6 +577,8 @@ class ThermalPostProcessor():
                             'int_rho_s1_above', 
                             'int_u', 
                             'int_area', 
+                            'int_ke_flux',
+                            'int_enth_flux',
                             'max_s1_therm',
                             'torus_vol',
                             'full_impulse',
@@ -632,6 +634,8 @@ class ThermalPostProcessor():
                             'int_s1' : 2*np.pi*s1[i,:]*integrator.r, 
                             'int_mass' : 2*np.pi*integrator.rho0['g']*integrator.r, 
                             'int_ke' :  2*np.pi*integrator.rho0['g']*w[i,:]**2*integrator.r / 2, 
+                            'int_ke_flux' : 2*np.pi*integrator.rho0['g']*(u[i,:] + w[i,:])**2*w[i,:] * integrator.r / 2,
+                            'int_enth_flux' : 2*np.pi*integrator.r * (integrator.rho0['g']*w[i,:]*(integrator.T0['g']*s1[i,:] - self.g*integrator.z)),
                             'int_mom' : 2*np.pi*integrator.rho0['g']*w[i,:]*integrator.r, 
                             'int_pe' : 2*np.pi*s1[i,:]*integrator.rho0['g']*self.g*-1*integrator.z*integrator.r,
                             'int_impulse' : np.pi*integrator.rho0['g']*V[i,:]*integrator.r**2,
@@ -736,7 +740,7 @@ class ThermalPostProcessor():
         for fn, fp in zip(self.files, self.prof_files):
             #Read entropy, density, velocity, vorticity
             r, z, rr, zz, s1, w, u, V, p = self.read_file(fn)
-            f    = h5py.File(fp, 'r')
+            f    = h5py.File(fn, 'r')
             time = f['scales']['sim_time'].value
             f.close()
             

### 2019-07-17 code/plotting/diff_AN_FC.py

@@ -16,8 +16,8 @@ from scipy.interpolate import interp1d
 
 NRUNS=8
 
-aspect = [0.25, 0.25, 0.25, 0.25]
-CASES = [0.1, 0.5, 1, 2]
+aspect = [0.25, 0.25, 0.25, 0.25, 0.25]
+CASES = [0.1, 0.5, 1, 2, 3]
 ROOT_DIR='../'#good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
@@ -26,8 +26,8 @@ CASES_2D = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
 color_dir = [1, 2, 3, 4, 5, 6, 7, 8]
 DIRS_2D=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES_2D, aspect_2D)] 
 
-CASES_3D = [0.1, 0.5, 1, 2]
-AR_3D    = [0.5, 0.5, 0.5, 0.5]
+CASES_3D = [0.1, 0.5, 1, 2, 3]
+AR_3D    = [0.5, 0.5, 0.5, 0.5, 0.5]
 THREED_DIR = '../'
 DIRS_3D=['{:s}FC_3D_thermal_Re6e2_Pr1_eps1.00e-4_nrho{}_aspect{}/'.format(THREED_DIR,nrho, ar) for nrho, ar in zip(CASES_3D, AR_3D)] 
 dict_3D = {}
@@ -74,6 +74,9 @@ for i, direc in enumerate(DIRS):
     t3, d3, r3  = f_3D['times'].value, 20 - f_3D['vortex_height'].value, f_3D['vortex_radius'].value
     f.close()
     f_3D.close()
+
+    if CASES[i] == 3:
+        t3, d3, r3 = t3[:-15], d3[:-15], r3[:-15]
 
 
     color = sm.to_rgba(i+1)
@@ -130,7 +133,7 @@ cb = plt.colorbar(sm, cax=cax, orientation='horizontal', boundaries=np.linspace(
 cb.solids.set_rasterized(True)
 cax.xaxis.set_ticks_position('top')
[…]

### 2019-07-17 code/plotting/results_panels.py

@@ -19,8 +19,8 @@ CASES = [0.1, 0.5, 1, 2, 3, 4, 5, 6]
 ROOT_DIR='../'#good_2D_runs/z_bot_zero/'
 DIRS=['{:s}AN_2D_thermal_nrho{}_Re6e2_Pr1_aspect{}_Lz20/'.format(ROOT_DIR, nrho, ar) for nrho, ar in zip(CASES, aspect)] 
 
-CASES_3D = [0.1, 0.5, 1, 2]
-AR_3D    = [0.5, 0.5, 0.5, 0.5]
+CASES_3D = [0.1, 0.5, 1, 2, 3]
+AR_3D    = [0.5, 0.5, 0.5, 0.5, 0.5]
 THREED_DIR = '../'
 DIRS_3D=['{:s}FC_3D_thermal_Re6e2_Pr1_eps1.00e-4_nrho{}_aspect{}/'.format(THREED_DIR,nrho, ar) for nrho, ar in zip(CASES_3D, AR_3D)] 
 dict_3D = {}
@@ -60,6 +60,8 @@ for i, direc in enumerate(DIRS):
                 x_3D, y_3D     = f_3Dt['times'].value, f_3D['d_measured'].value
             elif j == 1:
                 x_3D, y_3D     = f_3D['d_measured'].value[2:-2], -f_3D['w_measured'].value
+            if CASES[i] == 3:
+                x_3D, y_3D = x_3D[:-15], y_3D[:-15]
             f_3D.close()
             f_3Dt.close()
             ax.plot(x_3D[:], y_3D[:], marker='+', lw=0, markersize=2, markeredgecolor='k', markeredgewidth=0.5)
@@ -88,7 +90,7 @@ cb = plt.colorbar(sm, cax=cax, orientation='horizontal', boundaries=np.linspace(
 cb.solids.set_rasterized(True)
 cax.xaxis.set_ticks_position('top')
 cax.xaxis.set_ticklabels(CASES)
-cb.set_label(r'$n_\rho$', labelpad=-40)
+cb.set_label(r'$N_\rho$', labelpad=-40)
 
 #ax1.text(0.5, 18.5, 'a', fontsize=12)
 #ax2.text(0.2, 0.225, 'b', fontsize=12)

### 2019-07-17 code/thermal_analysis.py

@@ -77,6 +77,8 @@ def post_process(root_dir, plot=False, get_contour=True, analyze=True, out_dir='
     volumes      = output_file['int_vol'].value
     area         = output_file['int_area'].value
     radius       = output_file['radius'].value
+    avg_ke_flux  = output_file['int_ke_flux'].value/volumes
+    avg_enth_flux  = output_file['int_enth_flux'].value/volumes
     output_file.close()
 
     cb_file           = h5py.File('{:s}/z_cb_file.h5'.format(post.full_out_dir), 'r')
@@ -98,7 +100,7 @@ def post_process(root_dir, plot=False, get_contour=True, analyze=True, out_dir='
     for i in range(contours.shape[0]):
         if not (contours[i,-1] != 0)*(contours[i,-2]==0):
             thermal_found[i] = True
-    good = thermal_found
+    good = thermal_found*(height > 0.25*post.Lz)
 
     #Find Rz based on contour 
     Rz = np.zeros_like(times)
@@ -118,7 +120,7 @@ def post_process(root_dir, plot=False, get_contour=True, analyze=True, out_dir='
 
     #cb fit
     depth = post.Lz - height
-    fit_t = (height < 0.65*post.Lz)*(height > 0.1*post.Lz)
+    fit_t = (height < 0.65*post.Lz)*(height > 0.25*post.Lz)
     fit_t[0] = False
     found_therm = False
     therm_done  = False
@@ -305,6 +307,17 @@ def post_process(root_dir, plot=False, get_contour=True, analyze=True, out_dir='
     fig.savefig('{:s}/w_v_z.png'.format(post.full_out_dir), bbox_inches='tight', dpi=200)
 
 
+    logger.info('plotting fluxes')
+    fig = plt.figure()
+
+    plt.plot(d_measured, avg_ke_flux, c='b')
+    plt.plot(d_measured, avg_enth_flux, c='r')
+    plt.plot(d_measured, avg_enth_flux + avg_ke_flux, c='k')
+    plt.xlabel('depth')
+    plt.ylabel('avg flux')
+    plt.savefig('{:s}/fluxes_v_depth.png'.format(post.full_out_dir), bbox_inches='tight', dpi=200)
+
+
     f = h5py.File('{:s}/fit_file.h5'.format(post.full_out_dir), 'w')
     f['B0']       = fit_B0
     f['Gamma0']   = fit_Gamma0
[…]

### 2019-07-17 submission2/referee_response.txt

Dear Aimee,

We thank you and the anonymous referee for taking the time to consider and review our manuscript, "Entropy Rain: Dilution and Compression of Thermals in Stratified Domains".

In addition to the changes suggested in the referee report (and which we describe inline with the report below), we have made the following small changes to the manuscript as a result of discussions with colleagues:
1. We have computed a 3D, fully compressible simulation at n_rho = 3 and included its results in all relevant figures. We additionally recomputed our 3D, nrho = 2 simulation with a higher horizontal coefficient resolution.
2. We have added a line showing the sound speed to Figure 6, middle panel.
3. Throughout the manuscript, n_rho is now capital N_rho, to avoid confusion with n_ad.
4. Minor clarifications throughout the manuscript, all of which are bolded.

Best wishes,
Evan Anders, Daniel Lecoanet, and Ben Brown

----------------------------------------------------------
RESPONSE TO REFEREE REPORT
----------------------------------------------------------

""" 
The authors analyze the entropy rain scenario by developing an analytic
theory and performing simulations in the presence of negative buoyancy
of the downflow. This is a nice piece of work that should be published,
and I have only relatively minor suggestions for possible improvement.
"""

We thank the referee for taking the time to review our paper and for their useful suggestions to help improve the clarity of the manuscript.
We hope that the changes we have made to address the referees concerns, described below, are sufficient to clear up any points of confusion.

"""
1. The paper is arranged in such a way that subsequent simulation
results are used in quite some detail both in the introduction and in
the discussion of the model. If the authors want to keep it this way,
some additional clarifications should be given in several places (e.g.,
in the captions to Figs. 1-3, and in the text where they refer to these
figures.) Otherwise, details such as nrho=3, the size of the domain,
and other details of Fig.3 remain puzzling. Regarding Fig.2, one could
well imagine that it is just a sketch, but it is actually a simulation
result, right? If so, what are the times in the two panels? Another
option would be a rearrangement and to present the simulations first.
"""

We have elected to keep the overall presentation of the paper the same, but have added explicit callouts throughout the text to inform the reader that they are looking at simulation data in Figs 2 & 3.
See figure captions, the first sentences of section 2.1, and callouts to Fig 3 in section 2.3.

"""
2. Some quantities are not defined explicitly. This should be avoided,
even though the symbols follow standard convention (e.g., rho). It might
also be good to give a name to quantities such as t_off, when they are
first introduced. In the case of t_off, it appears first on page 3 in
Sect.2.3, and only at the end of Sect.2.4 it is called temporal offset.
"""

We have tried to explicitly define all parameters throughout the paper (rho in the sct. 1; u and g in 2.2; t_off, B_th, Gamma_th, m in 2.3, grad_ad in 2.4, and we redefine N_rho in 3.1 as its callout in 2.1 is far enough away from here that it can be forgotten).

"""
3. The expression detainment seems to be used in meteorology, but is
maybe new in astrophysics, where one talks in other contexts about
stripping or even ram pressure stripping. Maybe some comments could
be useful.
"""

We have added a few words to key the reader in on the concept of detrainment shortly before eqn 7.

"""
4. When B_th is first introduced in Sect.2.3, it is not clear to me in
which way it is different from just B that was used in the previous
section 2.2. Only in the second paragraph it seems to become clear
that this is because of detainment. Again, some text earlier on could
be helpful.
"""

We removed the first sentence of sct. 2.3 and have defined B_th and Gamma_th more clearly following eqns. 7 and 8, respectively.

"""
5. nabla_ad is sometimes put in parenthesis. In Eq.(10) one could imagine
that the authors would like to avoid an impression that it could be
an operator (in which case it could be put at the end of (z-L), but in
Eq.(15) it seems really unnecessary.
"""

We have removed these parenthesis and moved nabla_ad to the end of (z-L_z) in eqn. 10.

"""
6. In Eq.(14), should there not be a term in the viscosity expression
that is related to the derivative of the density?
"""

Due to our formulation of diffusivities (kappa = rho*chi = constant in space and time, mu = rho*nu = constant in space and time), the gradient terms are explicitly zero in our formulation.

"""
7. At the end of Sect.3.4, it becomes clear that periodic boundary
conditions are used in the vertical direction. It comes as a surprise
and it is unclear why this is done.
"""

We have added a paragraph explaining the reasoning behind this choice in section 3.4.

"""
8. In the caption to Fig.4, I'd add "(AN)" and "(FC)" after anelastic
and fully compressible. The differences are indeed quite small. Maybe
it would be good to emphasize that the author mean 2D Cartesian and
not 2D cylindrical, if that is indeed the case. 2D Cartesian implies a
very different width of vortices, so it is amazing that this does not
matter. Given that AN and FC are changed at the same time as 2D and 3D,
it is not clear what is caused by what. I agree, the differences are
small, but a comment might be useful. Is 3-D AN harder, or what?
"""

We have added (AN) and (FC) to the captions of figures 4 and 5.
Furthermore, we have added some additional text to 3.1, as it seems that it was unclear that the 3D simulations are in azimuthally symmetric cylindrical domains, while the 3D simulations are in cartesian domains.
Essentially, the 2D simulations are the limit in which a description of the thermal is easily derivable, and the 3D simulations are the "truth," and we wanted to compare those two.

"""
9. Except for general remarks in the introduction, nothing is said about
the enthalpy flux that is accomplished by one plume. It can obviously
not be modeled by a superadiabatic gradient, but maybe some quantitative
statements can be made regarding some of the assumptions made in B16.
"""

The focus of this work is entrainment, as suggested by the title, and entropy rain was merely the context in which we sought to apply this knowledge.
While interesting, descriptions of the flux carried by one of these thermals, especially propagated to the solar context, is outside of the remit of this manuscript.
We do not believe that this can be treated in a satisfying way in a short paragraph or two, and an aside of more length than that which does not address our original hypothesis seems out of place.

### 2019-07-17 submission2/referee_response.txt
incorporates Daniel's suggestions; does not yet put the flux discussion in (need to figure out how to handle PE + KE in addition to F_enth. Or do we ignore them?)

@@
-Dear Aimee,
+Dear Dr. Norton,
 
 We thank you and the anonymous referee for taking the time to consider and review our manuscript, "Entropy Rain: Dilution and Compression of Thermals in Stratified Domains".
-
-In addition to the changes suggested in the referee report (and which we describe inline with the report below), we have made the following small changes to the manuscript as a result of discussions with colleagues:
-1.
-We have computed a 3D, fully compressible simulation at n_rho = 3 and included its results in all relevant figures.
-We additionally recomputed our 3D, nrho = 2 simulation with a higher horizontal coefficient resolution.
-2. We have added a line showing the sound speed to Figure 6, middle panel.
-3. Throughout the manuscript, n_rho is now capital N_rho, to avoid confusion with n_ad.
-4. Minor clarifications throughout the manuscript, all of which are bolded.
+We include below our changes to the manuscript, including inline responses to the full referee report.
 
@@
 ----------------------------------------------------------
+
+In addition to the changes suggested in the referee report (which we describe inline below), we have made the following small changes to the manuscript as a result of discussions with colleagues:
+1.
+We have computed a 3D, fully compressible simulation at n_rho = 3 and included its results in all relevant figures.
+We additionally recomputed our 3D, nrho = 2 simulation with a higher horizontal coefficient resolution.
+2. We have added a line showing the sound speed to velocity panel of Figure 6.
+3. Throughout the manuscript, n_rho is now capital N_rho, to avoid confusion with n_ad.
+4. Minor clarifications throughout the manuscript, all of which are bolded.
 
@@
 
-Due to our formulation of diffusivities (kappa = rho*chi = constant in space and time, mu = rho*nu = constant in space and time), the gradient terms are explicitly zero in our formulation.
+Due to our formulation of diffusivities (kappa = rho*chi = constant in space and time, mu = rho*nu = constant in space and time), the gradients of density cancel with the gradients of nu and/or chi.
 
@@
 Furthermore, we have added some additional text to 3.1, as it seems that it was unclear that the 3D simulations are in azimuthally symmetric cylindrical domains, while the 3D simulations are in cartesian domains.
-Essentially, the 2D simulations are the limit in which a description of the thermal is easily derivable, and the 3D simulations are the "truth," and we wanted to compare those two.
 

### 2019-07-17 tex/stratified_thermals.tex
incorporates Daniel's suggestions; does not yet put the flux discussion in (need to figure out how to handle PE + KE in addition to F_enth. Or do we ignore them?)

@@
 
-The 2D simulation domain is the direct product of a Fourier basis $(z \in [-L_z/4, L_z])$ and a Chebyshev basis $(r \in [0, L_r])$.
+The 2D simulation domain is \textbf{periodic in the z-direction with $z \in [-L_z/4, L_z]$ and the radial direction spans $r \in [0, L_r]$}.
 The boundary conditions are $\partial_r S_1 = w = (\grad\times\bm{u})_\phi = 0$ at $r = L_r$, and the regularity of the equations automatically impose $u = \partial_r(w) = \partial_r(S_1) = 0$ at $r = 0$.
-The 3D simulation domain is the direct product of Fourier bases in the horizontal directions ($x, y \in [-L_r, L_r]$) and a Chebyshev basis ($z \in [0, L_z]$).
+The 3D simulation domain is \textbf{periodic in the horizontal directions ($x, y \in [-L_r, L_r]$) and vertically spans $z \in [0, L_z]$}.
 We impose impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries.
@@
 \textbf{
-Dedalus currently allows for the direct specification of general boundaries in one direction.
-In the case of our 2D simulations, this direction must be the radial direction in order to capture the singularity at $r = 0$.
-While Dedalus can expand fields in terms of sine or cosine bases (as in \LJ), the mixed parities of terms such as the viscous heating term in the fully compressible or anelastic equations rules out a simple specification in these equation sets.
-We have therefore chosen to use periodic Fourier bases in the vertical direction of our simulations, and end the simulations before the thermal can interact with those boundaries.
-Remarkably, the results of these simulations vary only minimally from our 3D simulations, as we will show in the next section, and the vertical boundaries do not meaningfully affect the evolution of the thermal.
+In our 2D simulations, we represent the radial direction with Chebyshev polynomials so that we can include geometric factors in ours equations and capture the singularity at $r = 0$.
+We then assume the z direction is periodic to make the calculations more efficient, and we end the simulations before the thermal can interact with the vertical periodic boundaries.
+Remarkably, the results of these simulations vary only minimally from our 3D simulations, as we will show in the next section, indicating that the vertical periodicity and the different side boundaries (cylinder vs.
+cube) do not influcence the thermal properties.
 }
@@
 2	 	& 		\textbf{384}			& 1024			& 34    	&	0.1	\\
-\textbf{3}	 	& 		\textbf{512}			& \textbf{2048}			& \textbf{25}    	&	\textbf{0.15}	\\
+\textbf{3}	 	& 		\textbf{384}			& \textbf{2048}			& \textbf{25}    	&	\textbf{0.15}	\\
 \enddata																																															

### 2019-07-17 code/plotting/thermal_sun_comparison.py

@@ -39,8 +39,10 @@ def theory_dT_dt(t, B0, Gamma0, f, chi, beta, t_off, T0, grad_T_ad=-1, m_ad=1.5)
     return C0*this_T**(m_ad/2)/np.sqrt(t + t_off)
 
 def read_solar_profiles():
-    mesa_data = np.genfromtxt('sun_4.5gyr.data', skip_header=6, usecols=(2, 4, 9)) #logR (in Rsun units), logRho (g/cm^3), csound (cm/s)
-    csound = mesa_data[:,2]*cm2Mm
+    mesa_data = np.genfromtxt('sun_4.5gyr.data', skip_header=6, usecols=(2, 4, 9, 10, 11)) #logR (in Rsun units), logRho (g/cm^3), grav (cm/s^2), Cp, csound (cm/s)
+    grav = mesa_data[:,2]
+    Cp = mesa_data[:,3] #erg/K?
+    csound = mesa_data[:,4]*cm2Mm
     mesa_data = 10**(mesa_data[:,:-1])
     radius    = mesa_data[:,0]*Rsun2Mm
     density    = mesa_data[:,1]*(cm2Mm)**(-3)
@@ -67,13 +69,17 @@ def read_solar_profiles():
     radii *= Rsun2Mm
 
     rho2r = interp1d(density, radius, bounds_error=False, fill_value='extrapolate')
-    r2cs = interp1d(radius, csound, bounds_error=False, fill_value='extrapolate')
     r2chi = interp1d(radii, chi, bounds_error=False, fill_value='extrapolate')
     r2nu  = interp1d(radii, nu, bounds_error=False, fill_value='extrapolate')
 
-    return rho2r, r2chi, r2nu, r2cs
 
-rho2r, r2chi, r2nu, r2cs = read_solar_profiles()
+    r2cs = interp1d(radius, csound, bounds_error=False, fill_value='extrapolate')
+    r2gDivCp = interp1d(radius, grav/Cp, bounds_error=False, fill_value='extrapolate')
+    r2Cp = interp1d(radius, Cp, bounds_error=False, fill_value='extrapolate')
+
+    return rho2r, r2chi, r2nu, r2cs, r2gDivCp, r2Cp
+
[…]

### 2019-07-18 submission2/referee_response.txt
close to ready for resubmission

@@
 
-The focus of this work is entrainment, as suggested by the title, and entropy rain was merely the context in which we sought to apply this knowledge.
-While interesting, descriptions of the flux carried by one of these thermals, especially propagated to the solar context, is outside of the remit of this manuscript.
-We do not believe that this can be treated in a satisfying way in a short paragraph or two, and an aside of more length than that which does not address our original hypothesis seems out of place.
+We have added two panels to Figure 6 which explore the enthalpy flux achieved by a thermal, and the filling factor required to carry the solar luminosity.
+An accompanying discussion has been added at the end of section 5.

### 2019-07-18 tex/stratified_thermals.tex
close to ready for resubmission

@@
 Such a deceleration may cause the thermals to move so slowly they would diffuse away their entropy perturbation before reaching the bottom of the solar convection zone.
-However, this past work does not include the effects of density stratification.
+\textbf{\citet{brandenburg&hazlehurst2001} found that hot, buoyant thermals in stratified domains behave qualitatively similar to Boussinesq thermals.
+However, we are not aware of past work which carefully examines the effects of stratification on \emph{negatively} buoyant thermals.
+}
 
@@
     \caption{
-	(top) Bounds on the evolution of the radii of entropy rain in the Sun are shown and compared to what the radii would be under purely horizontal compression.
-	(middle) The corresponding range of velocities of solar-like thermals are shown. 
-	(bottom) Shown is the estimated range of the ratio of the thermal diffusion timescale normalized by the freefall timescale over the thermal radial length scale.
+	(First panel) Bounds on the evolution of the radii of entropy rain in the Sun are shown and compared to what the radii would be under purely horizontal compression.
+	(Second panel) The corresponding range of velocities of solar-like thermals are shown. 
+	(Third panel) Shown is the estimated range of the ratio of the thermal diffusion timescale normalized by the freefall timescale over the thermal radial length scale.
 	Diffusivities are calculated using the realistic solar-like diffusion profiles of \citet{brown2011}.
+	\textbf{
+	(Fourth panel) An estimate of the luminosity of these thermals, normalized by the solar luminosity, is shown.
+	(Fifth panel) An estimate of the filling factor of thermals required to carry the solar luminosity.}
     \label{fig:thermal_sun_comparison} }
@@
 \ref{fig:thermal_sun_comparison}.
-In the top and middle panels of Fig.
+In the first and second panels of Fig.
 \ref{fig:thermal_sun_comparison}, we show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
 We use the solar diffusivity models of \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r_{\text{th}}^2$) and the thermal freefall timescale over its own radial length scale ($\tau_{\text{ff}} = r_{\text{th}}/w_{\text{th}}$).
-In the bottom panel of Fig. \ref{fig:thermal_sun_comparison}, we plot the ratio of these two timescales over the thermal's evolution.
+In the third panel of Fig. \ref{fig:thermal_sun_comparison}, we plot the ratio of these two timescales over the thermal's evolution.
 
@@
 Thus, the thermal loses less than 1\% of its entropic signature to diffusion.
-These estimates suggest that entropy rain could transport the solar luminosity.
+
+\textbf{
+We now briefly estimate the enthalpy flux carried by a thermal.
+Following \citet{brandenburg2016}, we estimate the enthalpy flux of the thermal as $F_{\text{enth}} = \rho_0(z_th) T_0(z_th) w_{\text{th}} S_{1,\text{th}}$.
+We estimate the thermal's entropic signature as $S_{1, th} = B_{\text{th}}/(\rho_0(z_{\text{th}}) V_{\text{th}} g/c_P)$, where the thermal volume is $V_{\text{th}} = m r_{\text{th}}^3$.
+We take $\rho_0(z_{\text{th}})$, $T_0(z_{\text{th}})$, and $g/c_P$ from our solar MESA model at the depth of the thermal over its evolution.
+We take $r_{\text{th}}$ and $w_{\text{th}}$ to be the thermal radius and velocity shown in the first and second panels of Fig.~\ref{fig:thermal_sun_comparison}.
+We find $m$ from the data in Table \ref{table:parameters} in the same manner as we found $B_{\text{th}}$ for these solar thermals.
+To estimate the total luminosity carried by one thermal, we calculate $L_{\text{enth, th}} = \pi r_{\text{th}}^2 F_{\text{enth}}$, and we plot this value as a function of depth, normalized by the solar luminosity, in panel 4 of Fig.~\ref{fig:thermal_sun_comparison}.
+}
+
+\textbf{
+From our estimate of the luminosity carried by one thermal, we estimate the filling factor of downward propagating thermals required to carry the solar luminosity through their enthalpy flux.
+We calculate $f_{\text{th}} = (L_{\odot}/L_{\text{enth, th}}) (\pi r_{\text{th}}^2)/(4\pi R^2)$, where $R$ is the thermal's radial distance form the center of the Sun.
+We plot the $f_{\text{th}}$ in panel 5 of Fig.~\ref{fig:thermal_sun_comparison}.
+The filling factor of thermals required to carry $L_\odot$ at the solar surface is greater than unity; this is unsurprising, as we know that solar surface convection carries the solar luminosity through the combined effects of upflows and downflows.
+A few percentage of the solar radius beneath the photosphere, $f_{th}$ drops to a very modest $10^{-4}$, and by the base of the solar convection zone approaches $10^{-7}$.
+These estimates suggest that even if a large fraction of the thermals launched from the solar surface break apart due to turbulence, this mechanism could still efficiently carry the solar luminosity deep in the convection zone.
+}
+
+\textbf{
+While these estimates suggest that entropy rain could effectively transport the solar luminosity, we will briefly note that our handling of the enthalpy flux here ignores the contributions of the kinetic energy flux, potential energy flux, and viscous flux.
+While we expect the last of these to be inconsequential, the kinetic energy flux (which transports luminosity inwards) and the potential energy flux (which transports luminosity outwards) may be large.
+A more thorough examination of these fluxes are outside of the scope of this work, but due to the promising nature of our results found here for the entropy rain hypothesis, such work seems promising.
+}
 
@@
 We'd like to thank Brett McKim and Nadir Jeevanjee for discussions about thermals and the laminar entrainment picture.
-\textbf{We'd like to further thank Nadir Jeevanjee, Jeremy Goodman, and the anonymous referee whose careful comments greatly improved the scientific quality and clarity of this manuscript.}
+\textbf{We'd like to further thank Nadir Jeevanjee, Axel Brandenburg, Jeremy Goodman, and the anonymous referee whose careful comments greatly improved the scientific quality and clarity of this manuscript.}
 This work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.

### 2019-07-18 code/plotting/thermal_sun_comparison.py

@@ -7,12 +7,18 @@ matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
 matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
 matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
 import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
 from scipy.interpolate import interp1d
 
 
 cm2Mm = 1e-8 #Mm / cm
 Rsun2cm = 6.957e10 #cm / Rsun
 Rsun2Mm = 6.957e2 #Mm / Rsun
+
+gs = gridspec.GridSpec(1000, 1000)
+fig = plt.figure(figsize=(3.25, 7))
+
+
 
 
 def theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=-1):
@@ -166,8 +172,8 @@ for Buoy in (B_nondim/2, 2*B_nondim):
 
 
 fig = plt.figure(figsize=(3.25, 6))
-ax = fig.add_subplot(4,1,1)
-axs = [ax]
+#######################################################AX1
+ax = plt.subplot(gs.new_subplotspec((0,  0), 200, 1000))
 
 #Plot radius grey band
 x_values = rho_outs[0]*(rho_top/rho_outs[0][0])
@@ -186,8 +192,8 @@ for i in range(2):
     plt.plot(solar_radii[i]/(Rsun2Mm), solar_therm_radii[i], c='k', lw=0.5*(i+1))
 
 plt.plot(solar_radii[0]/(Rsun2Mm), (L/2)/(rho_outs[0]/rho_outs[0][0])**(1./2), c='k', lw=2)
-ax.text(0.69, 8e-5, r'$r \propto \rho^{-1/2}$', rotation=3)
-ax.text(0.69, 7e-3, 'thermals', rotation=2.5)
+ax.text(0.69, 1e-4, r'$r \propto \rho^{-1/2}$', rotation=3)
+ax.text(0.69, 8e-3, 'thermals', rotation=2)
 
 #Make plot pretty
 plt.xlim(0.68, 0.995)
@@ -195,8 +201,8 @@ plt.yscale('log')
 plt.ylim(1e-5, 1e-1)
 plt.ylabel(r'$r_{\mathrm{th}}$ (Mm)')
 
-ax = fig.add_subplot(4,1,2)
-axs += [ax]
+#######################################################AX2
[…]

### 2019-07-24 tex/stratified_thermals.tex
adds Ben's updates

@@
 In the following sections, we will use the impulse of dense vortex rings to derive expressions for the evolution of their depth and radii with time.
-\textbf{\citet{rast1998} showed that 2D compressible, low entropy plumes in stratified domains emit vortex pairs, and this description of vortex ring evolution should be useful both in our study of thermals and in more time-continuous plume sources.}
+\textbf{In this work we study vortex rings generated by discrete cold thermals, but time-stationary cooling produces similar vortex ring structures \citep[as in e.g.,][]{rast1998}.
+The following description of vortex ring evolution should therefore be broadly applicable.}
 
@@
     \caption{
-	\textbf{Shown is the evolution of mass-weighted entropy perturbations, normalized by the thermal's buoyancy perturbation, from 3D simulations conducted in this work}.
+	\textbf{Shown is the evolution of entropy perturbations, normalized by the thermal's buoyancy perturbation, from 3D simulations conducted in this work}.
 	(left) A thermal in a weakly stratified domain with $N_\rho = 1/2$ density scale heights, and (right) a thermal in a strongly stratified domain with $N_\rho = 3$.
@@
 We now restrict our study to an ideal gas in the low Mach-number regime, in an adiabatic background.
+\textbf{Thi sis the appropriate regime of deep solar convection.}
 Due to rapid pressure equilibration in low Mach-number flows, we can approximate 
@@
 \begin{equation}
-r = \sqrt{\frac{\eta B_{\text{th}} (t + t_{\text{off}})}{\pi\rho_0\Gamma_{\text{th}}}}.
+r = \sqrt{\frac{\eta B_{\text{th}} (t + t_{\text{off}})}{\pi\rho_0\Gamma_{\text{th}}}},
 \label{eqn:r_theory}
 \end{equation}
-\textbf{$\Gamma_{\text{th}}$ is the characteristic circulation of the thermal.
+\textbf{Here, $\Gamma_{\text{th}}$ is the characteristic circulation of the thermal.
 As} there are no net baroclinic torques, $\Gamma_{\text{th}}$ \textbf{remains nearly constant in our simulations} (Fig.~\ref{fig:constants}, middle panel).
@@
 We approximate the volume as $\mathcal{V} \approx m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption \textbf{in our simulations}; see Fig.~\ref{fig:constants}, bottom panel).
-\textbf{Here, $m$ accounts for volumetric constants, the aspect ratio of the thermal, and the ratio between the full radius of the spheroidal thermal and $r$, the radius to the entropy maxima.}
+\textbf{Here, $m$ accounts for volumetric constants (e.g., $4\pi/3$), the aspect ratio of the thermal, and the cubed ratio between the full radius of the spheroidal thermal and $r$.}
 Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, we find
@@
 
-We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform and constant in time.
+We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform \textbf{in space} and constant in time.
 We make this choice because $\mu$ and $\kappa$ appear in the density-weighted momentum and entropy equations, and we find the density-weighted entropy and momentum to be key quantities in our thermal theory.
@@
 As the diffusivities scale with depth, Re is specified at the thermal's initial depth.
-All simulations conducted in this work use a value of Re = 600 and $\mbox{\text{Pr} = 1}$.
+All simulations conducted in this work use \textbf{an initial} value of Re = 600 and $\mbox{\text{Pr} = 1}$.
 
@@
 \end{equation}
+\textbf{In all cases, we do not add any symmetry breaking perturbations (e.g., noise).}
 
@@
 \textbf{
-In our 2D simulations, we represent the radial direction with Chebyshev polynomials so that we can include geometric factors in ours equations and capture the singularity at $r = 0$.
+In our 2D simulations, we represent the radial direction with Chebyshev polynomials so that we can include geometric factors in our equations and capture the singularity at $r = 0$.
 We then assume the z direction is periodic to make the calculations more efficient, and we end the simulations before the thermal can interact with the vertical periodic boundaries.
@@
 Finally, we quantify the excellent agreement between the 2D anelastic and 3D fully compressible simulations in Fig.~\ref{fig:diff}, bottom panel.
-We ran simulations in both models for $N_\rho = [0.1, 0.5, 1, 2]$.
+We ran simulations in both models for $N_\rho = [0.1, 0.5, 1, 2, 3]$.
 There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the bottom of the domain.
-Outside these times, we find differences in the radius of less than 1\%.
+Outside these times, we find differences in the \textbf{measured} radius of less than 1\%.
 This gives us confidence that our high stratification anelastic simulations are producing reliable results.
@@
 \startdata																																															
-\multicolumn{8}{l}{\textbf{2D Anelastic Simulations}}\\
+\multicolumn{8}{l}{\textbf{2D Anelastic Simulations (Cylindrical)}}\\
 0.1 	&  24.6 	& 0.144	& -0.548 & -2.17 & 8.05	& 1.04	& 0.732	\\
@@
 6	 	&  19.8 	& 0.041	& -5.73	 & -1.43 & 10.8	& 0.787	& 0.616	\\
-\multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations}}\\    
+\multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations (Cartesian)}}\\    
 0.1 	&  23.4 	& -0.337& -0.547 & -2.17 & 8.98	& 1.06	& 0.636	\\
@@
 In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
-We also find that the non-dimensional circulation is $\mathcal{O}$(-2) for each of our cases, and decreases in magnitude with increasing stratification.
+We also find that the non-dimensional circulation is \textbf{roughly} $-2$ for each of our cases, and decreases in magnitude with increasing stratification.
 
@@
 Estimating downflows to have a temperature deviation of $T_1 = -500$ K \citep{borrero&bellotrubio2002}, the nondimensional entropy signature of solar downflows is $S_1/c_p \sim \gamma^{-1}\ln(1 + T_1/T_0) = -5.22 \times 10^{-2}$.
-Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$, the buoyancy of a spherical thermal is 
+Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$ \textbf{and assuming thermal formation occurs at the solar photosphere}, the buoyancy of a spherical thermal is 
 $$
@@
 
-We find that our estimated solar thermal is in the falling regime.
+We find that our estimated solar thermal is \textbf{likely} in the falling regime.
 These thermals experience radial compression with corresponding increases in velocity, but experience much less compression than a naive approximation based on the density stratification alone.
@@
 We now briefly estimate the enthalpy flux carried by a thermal.
-Following \citet{brandenburg2016}, we estimate the enthalpy flux of the thermal as $F_{\text{enth}} = \rho_0(z_th) T_0(z_th) w_{\text{th}} S_{1,\text{th}}$.
-We estimate the thermal's entropic signature as $S_{1, th} = B_{\text{th}}/(\rho_0(z_{\text{th}}) V_{\text{th}} g/c_P)$, where the thermal volume is $V_{\text{th}} = m r_{\text{th}}^3$.
+Following \citet{brandenburg2016}, we estimate the enthalpy flux of the thermal as $F_{\text{enth}} = \rho_0(z_{\text{th}}) T_0(z_{\text{th}}) w_{\text{th}} S_{1,\text{th}}$.
+We estimate the thermal's entropic signature as $S_{1, \text{th}} = B_{\text{th}}/(\rho_0(z_{\text{th}}) V_{\text{th}} g/c_P)$, where the thermal volume is $V_{\text{th}} = m r_{\text{th}}^3$.
 We take $\rho_0(z_{\text{th}})$, $T_0(z_{\text{th}})$, and $g/c_P$ from our solar MESA model at the depth of the thermal over its evolution.
@@
 We find $m$ from the data in Table \ref{table:parameters} in the same manner as we found $B_{\text{th}}$ for these solar thermals.
-To estimate the total luminosity carried by one thermal, we calculate $L_{\text{enth, th}} = \pi r_{\text{th}}^2 F_{\text{enth}}$, and we plot this value as a function of depth, normalized by the solar luminosity, in panel 4 of Fig.~\ref{fig:thermal_sun_comparison}.
+To estimate the total luminosity carried by one thermal, we calculate $L_{\text{enth, th}} = \pi r_{\text{th}}^2 F_{\text{enth}}$, and we plot this value as a function of depth, normalized by the solar luminosity, in the fourth panel of Fig.~\ref{fig:thermal_sun_comparison}.
 }
@@
 \textbf{
-From our estimate of the luminosity carried by one thermal, we estimate the filling factor of downward propagating thermals required to carry the solar luminosity through their enthalpy flux.
-We calculate $f_{\text{th}} = (L_{\odot}/L_{\text{enth, th}}) (\pi r_{\text{th}}^2)/(4\pi R^2)$, where $R$ is the thermal's radial distance form the center of the Sun.
-We plot the $f_{\text{th}}$ in panel 5 of Fig.~\ref{fig:thermal_sun_comparison}.
+From this estimate of the luminosity carried by one thermal, we now calulate the filling factor of downward propagating thermals required to carry the solar luminosity.
+We calculate $f_{\text{th}} = [(L_{\odot}/L_{\text{enth, th}}) (\pi r_{\text{th}}^2)]/(4\pi R^2)$, where $R$ is the thermal's radial distance from the center of the Sun.
+Panel 5 of Fig.~\ref{fig:thermal_sun_comparison} displays $f_{\text{th}}$ vs.~depth.
 The filling factor of thermals required to carry $L_\odot$ at the solar surface is greater than unity; this is unsurprising, as we know that solar surface convection carries the solar luminosity through the combined effects of upflows and downflows.
-A few percentage of the solar radius beneath the photosphere, $f_{th}$ drops to a very modest $10^{-4}$, and by the base of the solar convection zone approaches $10^{-7}$.
-These estimates suggest that even if a large fraction of the thermals launched from the solar surface break apart due to turbulence, this mechanism could still efficiently carry the solar luminosity deep in the convection zone.
+A few percentage of the solar radius beneath the photosphere, $f_{\text{th}}$ drops to a very modest $10^{-4}$, and by the base of the solar convection zone approaches $10^{-7}$.
+These estimates suggest that even if a large fraction of the thermals launched from the solar surface break apart due to turbulence, entropy rain could still efficiently carry the solar luminosity deep in the convection zone.
 }
@@
 \textbf{
-While these estimates suggest that entropy rain could effectively transport the solar luminosity, we will briefly note that our handling of the enthalpy flux here ignores the contributions of the kinetic energy flux, potential energy flux, and viscous flux.
+We briefly note that our handling of the enthalpy flux here ignores the contributions of the kinetic energy flux, potential energy flux, and viscous flux.
 While we expect the last of these to be inconsequential, the kinetic energy flux (which transports luminosity inwards) and the potential energy flux (which transports luminosity outwards) may be large.
-A more thorough examination of these fluxes are outside of the scope of this work, but due to the promising nature of our results found here for the entropy rain hypothesis, such work seems promising.
+We encourage future work to examine these fluxes more thoroughly, but such an examination is outside of the scope of this work.
 }
@@
 \label{appendix:measurements}
-Throughout this work, we frequently report the thermal's radius or its depth.
+Throughout this work, we frequently report the thermal's radius or its height.
 We measure the thermal's radius and height as the radius from the axis of symmetry and the height above $z = 0$ at which the thermal's vortex core is located.
@@
 The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository \citep{supp_andersetall2019} \textbf{at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}}.
-\textbf{The 3D, $N_\rho = 3$ simulation displays spectral instabilities at very late times, affecting radial measurements at depths $\geq 17.5$.
+\textbf{The 3D, $N_\rho = 3$ simulation displays spectral instabilities at very late times as the simulation is under-resolved at these times.
+This affects thermal radial measurements at depths $\geq 17.5$.
 We therefore truncate the data from that simulation at a depth of 15, which corresponds to multiple freefall times before these instabilities affect the solution.}
@@
 \tablecomments{
-Our 2D sims have spectral mode resolution of nr x nz, and our 3D sims have spectral mode resolution of nx x ny x nz.
+Our 2D cylindrical sims have spectral mode resolution of nr x nz, and our 3D cartesian sims have spectral mode resolution of nx x ny x nz.
 We evolve our simulations from initial conditions until $t_{\text{evolution}}$ dimensionless freefall times have passed.

### 2019-07-24 code/plotting/thermal_sun_comparison.py

@@ -214,8 +214,8 @@ solar_therm_w = []
 for i in range(2):
     solar_therm_w.append(w_outs[i]*(u_th/w_outs[i][0]))
     plt.plot(solar_radii[i]/(Rsun2Mm), solar_therm_w[i], c='k', lw=0.5*(i+1))
-plt.plot(solar_radii[i]/Rsun2Mm, r2cs(solar_radii[i]), c='k', lw=1, dashes=(5,1,2,1))
-ax.text(0.69, 3.5e-1, r'$c_s$', rotation=-3)
+plt.plot(solar_radii[i]/Rsun2Mm, r2cs(solar_radii[i]), c='k', lw=2)#1, dashes=(5,1,2,1))
+ax.text(0.69, 3.25e-1, r'$c_s$', rotation=-3)
 
 #Make plot pretty
 plt.xlim(0.68, 0.995)

### 2019-07-26 tex/stratified_thermals.tex
as accepted

@@
 \shorttitle{Entropy Rain: Thermals in Stratified Domains}
-\shortauthors{Anders et al.}
+\shortauthors{Anders, Lecoanet, and Brown}
 
@@
 In this work, we develop an analytical theory describing the evolution of dense, negatively buoyant thermals.
-We verify the theory with 2D and 3D simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
+We verify the theory with 2D \textbf{cylindrical} and 3D \textbf{cartesian} simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
 Our results show that dense thermals fall in two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
@@
 In the following sections, we will use the impulse of dense vortex rings to derive expressions for the evolution of their depth and radii with time.
-\textbf{In this work we study vortex rings generated by discrete cold thermals, but time-stationary cooling produces similar vortex ring structures \citep[as in e.g.,][]{rast1998}.
+\textbf{In this work we study vortex rings generated by discrete cold thermals, but ``plumes'' driven by time-stationary cooling produce similar vortex ring structures \citep[as in e.g.,][]{rast1998}.
 The following description of vortex ring evolution should therefore be broadly applicable.}
@@
 We now restrict our study to an ideal gas in the low Mach-number regime, in an adiabatic background.
-\textbf{Thi sis the appropriate regime of deep solar convection.}
+\textbf{This is the appropriate regime of deep solar convection.}
 Due to rapid pressure equilibration in low Mach-number flows, we can approximate 
@@
 $$ 
-The thermal is at the virtual origin, $z=z_0$, at time $t=-t_{\text{off}}$, and the temperature there is $T_{\text{th},0} = 1 + (z_{\text{th},0} - L_z)\grad_{\text{ad}}$.
+The thermal is at the virtual origin, $z=z_{\text{th, 0}}$, at time $t=-t_{\text{off}}$, and the temperature there is $T_{\text{th},0} = 1 + (z_{\text{th},0} - L_z)\grad_{\text{ad}}$.
 We define $\alpha^{-1} \equiv 1 - n_{\text{ad}}/2$, and in the limit of large stratification, we find that $z_{\text{th}} \propto t^2$ for our case of $\alpha = 4$.
@@
 
-Following \LJ\,, we non-dimensionalize the equations with the initial diameter of the thermal and its freefall velocity.
+Following \LJ\,, we non-dimensionalize the equations \textbf{on} the initial diameter of the thermal and its freefall velocity.
 These equations are then fully specified in terms of the Reynolds number and Prandtl number,
@@
 In the first and second panels of Fig.
-\ref{fig:thermal_sun_comparison}, we show the evolution of these thermals' radii and velocities inside of the Sun, and compare their evolution to pure horizontal compression.
+\ref{fig:thermal_sun_comparison}, we show the evolution of these thermals' radii and velocities inside of the Sun, and compare their \textbf{radial} evolution to pure horizontal compression \textbf{and their velocity evolution to the speed of sound}.
 We use the solar diffusivity models of \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r_{\text{th}}^2$) and the thermal freefall timescale over its own radial length scale ($\tau_{\text{ff}} = r_{\text{th}}/w_{\text{th}}$).
@@
 We calculate $f_{\text{th}} = [(L_{\odot}/L_{\text{enth, th}}) (\pi r_{\text{th}}^2)]/(4\pi R^2)$, where $R$ is the thermal's radial distance from the center of the Sun.
-Panel 5 of Fig.~\ref{fig:thermal_sun_comparison} displays $f_{\text{th}}$ vs.~depth.
+The final panel of Fig.~\ref{fig:thermal_sun_comparison} displays $f_{\text{th}}$ vs.~depth.
 The filling factor of thermals required to carry $L_\odot$ at the solar surface is greater than unity; this is unsurprising, as we know that solar surface convection carries the solar luminosity through the combined effects of upflows and downflows.

### 2019-07-27 tex/stratified_thermals.tex
fixes FC nondimensionalization in text...need to make sure that typo doesn't make it through proofing.

@@
 
-\received{\today}
-\revised{??}
-\accepted{??}%\today}
+\received{2019 June 6}
+\revised{2019 July 25}
+\accepted{2019 July 26}
 \submitjournal{ApJ}
@@
 In this work, we develop an analytical theory describing the evolution of dense, negatively buoyant thermals.
-We verify the theory with 2D \textbf{cylindrical} and 3D \textbf{cartesian} simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
+We verify the theory with 2D cylindrical and 3D cartesian simulations of laminar, axisymmetric thermals in highly stratified atmospheres.
 Our results show that dense thermals fall in two categories: a \emph{stalling} regime in which the droplets slow down and expand, and a \emph{falling} regime in which the droplets accelerate and shrink as they propagate downwards.
@@
 Such a deceleration may cause the thermals to move so slowly they would diffuse away their entropy perturbation before reaching the bottom of the solar convection zone.
-\textbf{\citet{brandenburg&hazlehurst2001} found that hot, buoyant thermals in stratified domains behave qualitatively similar to Boussinesq thermals.
+\citet{brandenburg&hazlehurst2001} found that hot, buoyant thermals in stratified domains behave qualitatively similar to Boussinesq thermals.
 However, we are not aware of past work which carefully examines the effects of stratification on \emph{negatively} buoyant thermals.
-}
 
@@
 
-Ignoring entropy variations, \citet{brandenburg2016} suggests the filling fraction $f$ of entropy rain should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression, \textbf{where $\rho$ is the density}.
+Ignoring entropy variations, \citet{brandenburg2016} suggests the filling fraction $f$ of entropy rain should decrease like $f \propto \rho^{-1}$ for horizontal compression and $f \propto \rho^{-2/3}$ for spherical compression, where $\rho$ is the density.
 On the other hand, the filling fraction of Boussinesq thermals \emph{increases} like $f \propto d^2$, where $d$ is the depth of the thermal.
@@
 \subsection{Phenomenological description of thermal evolution}
-\textbf{In} Fig.~\ref{fig:evolution_colormeshes}, \textbf{we show snapshots of 3D simulation data depicting} the descent of cold thermals released from rest in two domains which span a different number of density scale heights, $N_\rho$.
+In Fig.~\ref{fig:evolution_colormeshes}, we show snapshots of 3D simulation data depicting the descent of cold thermals released from rest in two domains which span a different number of density scale heights, $N_\rho$.
 The left panel shows a weakly stratified domain with $N_\rho=0.5$, whereas the right panel shows a strongly stratified domain with $N_\rho=3$.
@@
 In the following sections, we will use the impulse of dense vortex rings to derive expressions for the evolution of their depth and radii with time.
-\textbf{In this work we study vortex rings generated by discrete cold thermals, but ``plumes'' driven by time-stationary cooling produce similar vortex ring structures \citep[as in e.g.,][]{rast1998}.
-The following description of vortex ring evolution should therefore be broadly applicable.}
+In this work we study vortex rings generated by discrete cold thermals, but ``plumes'' driven by time-stationary cooling produce similar vortex ring structures \citep[as in e.g.,][]{rast1998}.
+The following description of vortex ring evolution should therefore be broadly applicable.
 
@@
     \caption{
-	\textbf{Shown is the evolution of entropy perturbations, normalized by the thermal's buoyancy perturbation, from 3D simulations conducted in this work}.
+	Shown is the evolution of entropy perturbations, normalized by the thermal's buoyancy perturbation, from 3D simulations conducted in this work.
 	(left) A thermal in a weakly stratified domain with $N_\rho = 1/2$ density scale heights, and (right) a thermal in a strongly stratified domain with $N_\rho = 3$.
-	While both start with precisely the same initial condition, the thermal in low stratification expands with depth \textbf{and slows down}, whereas the thermal in strong stratification compresses with depth \textbf{and accelerates}.
+	While both start with precisely the same initial condition, the thermal in low stratification expands with depth and slows down, whereas the thermal in strong stratification compresses with depth and accelerates.
     \label{fig:evolution_colormeshes} }
@@
 \end{equation}
-where $\bm{x}$ is the position vector \textbf{and $\bm{u}$ is the fluid velocity}. 
+where $\bm{x}$ is the position vector and $\bm{u}$ is the fluid velocity. 
 The impulse is the time-integrated work which has acted on the fluid to result in the current fluid motion.
@@
 We now restrict our study to an ideal gas in the low Mach-number regime, in an adiabatic background.
-\textbf{This is the appropriate regime of deep solar convection.}
+This is the appropriate regime of deep solar convection.
 Due to rapid pressure equilibration in low Mach-number flows, we can approximate 
@@
 because the surface terms completely cancel.
-Assuming \textbf{a uniform, vertical gravity,} $\bm{g} = -g\hat{z}$, it is useful to define the buoyancy perturbation,
+Assuming a uniform, vertical gravity, $\bm{g} = -g\hat{z}$, it is useful to define the buoyancy perturbation,
 \begin{equation}
@@
     \caption{
-	\textbf{Shown is the} evolution of buoyancy perturbation (top), circulation (middle), and volume factor (bottom) \textbf{for each 2D simulation conducted in this work}.
-	All \textbf{three of these quantities remain} nearly constant after an initial spin-up phase.
-	With increasing stratification, we see marginally more detrainment \textbf{(loss of buoyant signature)} in the \textbf{top panel}.
+	Shown is the evolution of buoyancy perturbation (top), circulation (middle), and volume factor (bottom) for each 2D simulation conducted in this work.
+	All three of these quantities remain nearly constant after an initial spin-up phase.
+	With increasing stratification, we see marginally more detrainment (loss of buoyant signature) in the top panel.
     \label{fig:constants} }
@@
 
-%After spinning up, we assume that the thermal has a \textbf{constant} negative buoyancy \textbf{perturbation} and \textbf{constant} circulation.
-\textbf{The thermals studied here} began as initial spherical perturbations \textbf{and spin up into vortex rings}.
-\textbf{The spun up vortex ring phase can be modeled as having evolved} from a ``virtual origin'' where the vortex ring had zero radius.
-We model the thermal as having been located at its virtual origin at \textbf{a temporal offset} $t = -t_{\text{off}}$, where $t = 0$ is the time at which the true thermal was released from rest.
+The thermals studied here began as initial spherical perturbations and spin up into vortex rings.
+The spun up vortex ring phase can be modeled as having evolved from a ``virtual origin'' where the vortex ring had zero radius.
+We model the thermal as having been located at its virtual origin at a temporal offset $t = -t_{\text{off}}$, where $t = 0$ is the time at which the true thermal was released from rest.
 
-\textbf{In our simulations,} we find the thermal undergoes weak detrainment \textbf{(loss of buoyant signature to environmental fluid)}, so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}, top panel).
+In our simulations, we find the thermal undergoes weak detrainment (loss of buoyant signature to environmental fluid), so the negative buoyancy of the thermal decreases slightly in time (Fig.~\ref{fig:constants}, top panel).
 We thus express the buoyancy perturbation as 
@@
 \end{equation}
-where $\eta$ is a constant of $\mathcal{O}$(1) which represents this detrainment \textbf{and $B_{\text{th}}$ is the thermal's characteristic buoyancy perturbation}. 
+where $\eta$ is a constant of $\mathcal{O}$(1) which represents this detrainment and $B_{\text{th}}$ is the thermal's characteristic buoyancy perturbation. 
 We then integrate Eqn.~\ref{eqn:change_in_impulse},
@@
 \end{equation}
-\textbf{Here, $\Gamma_{\text{th}}$ is the characteristic circulation of the thermal.
-As} there are no net baroclinic torques, $\Gamma_{\text{th}}$ \textbf{remains nearly constant in our simulations} (Fig.~\ref{fig:constants}, middle panel).
+Here, $\Gamma_{\text{th}}$ is the characteristic circulation of the thermal.
+As there are no net baroclinic torques, $\Gamma_{\text{th}}$ remains nearly constant in our simulations (Fig.~\ref{fig:constants}, middle panel).
 In the Boussinesq limit where $\rho \rightarrow \text{constant}$, we retrieve the $r \propto \sqrt{t}$ scaling found in \LJ.
@@
 To solve for the vertical evolution of the thermal, we can use Eqn.~\ref{eqn:momentum}.
-We approximate the volume as $\mathcal{V} \approx m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption \textbf{in our simulations}; see Fig.~\ref{fig:constants}, bottom panel).
-\textbf{Here, $m$ accounts for volumetric constants (e.g., $4\pi/3$), the aspect ratio of the thermal, and the cubed ratio between the full radius of the spheroidal thermal and $r$.}
+We approximate the volume as $\mathcal{V} \approx m r^3$, where $m$ is a parameter which we take to be constant (which is a decent assumption in our simulations; see Fig.~\ref{fig:constants}, bottom panel).
+Here, $m$ accounts for volumetric constants (e.g., $4\pi/3$), the aspect ratio of the thermal, and the cubed ratio between the full radius of the spheroidal thermal and $r$.
 Defining the thermal velocity $w_{\text{th}} \equiv dz_{\text{th}}/dt$, we find
@@
 \end{gather}
-where $n_{\text{ad}} = (\gamma-1)^{-1}$ \textbf{and $\grad_{\text{ad}}$ is the adiabatic temperature gradient}.
+where $n_{\text{ad}} = (\gamma-1)^{-1}$ and $\grad_{\text{ad}}$ is the adiabatic temperature gradient.
 All thermodynamic quantities are nondimensionalized such that $\rho_0 = T_0 = 1$ at $z = L_z$, the top of the domain.
@@
 \label{sec:experiment}
-To test our theory, we run a series of \textbf{thermal} simulations \textbf{using} the 3D fully compressible equations \textbf{in cartesian domains}.
-\textbf{We additionally compute 2D azimuthally-symmetric} simulations \textbf{using} the anelastic equations \textbf{in cylindrical domains}.
+To test our theory, we run a series of thermal simulations using the 3D fully compressible equations in cartesian domains.
+We additionally compute 2D azimuthally-symmetric simulations using the anelastic equations in cylindrical domains.
 We verify the 3D and 2D simulations produce the same results when run with the same parameters.
@@
 
-Following \LJ\,, we non-dimensionalize the equations \textbf{on} the initial diameter of the thermal and its freefall velocity.
+Following \LJ\,, we non-dimensionalize the equations on the initial diameter of the thermal and its freefall velocity.
 These equations are then fully specified in terms of the Reynolds number and Prandtl number,
@@
 The background density and temperature are given by Eqs.~\ref{eqn:T0} \& \ref{eqn:polytrope}.
-The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{N_\rho/n_{\text{ad}}}-1)/(L_z c_P)$, where $L_z=20$ is the height of the domain \textbf{and $N_\rho$ is the number of density scale heights spanned by the domain}.
+The adiabatic temperature gradient is $\nabla_{\text{ad}}=g(e^{N_\rho/n_{\text{ad}}}-1)/(L_z c_P)$, where $L_z=20$ is the height of the domain and $N_\rho$ is the number of density scale heights spanned by the domain.
 
-We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform \textbf{in space} and constant in time.
+We choose an atmospheric model in which the dynamic viscosity, $\mu = \rho_0 \nu$, and the thermal conductivity, $\kappa = \rho_0 \chi$, are both uniform in space and constant in time.
 We make this choice because $\mu$ and $\kappa$ appear in the density-weighted momentum and entropy equations, and we find the density-weighted entropy and momentum to be key quantities in our thermal theory.
@@
 As the diffusivities scale with depth, Re is specified at the thermal's initial depth.
-All simulations conducted in this work use \textbf{an initial} value of Re = 600 and $\mbox{\text{Pr} = 1}$.
+All simulations conducted in this work use an initial value of Re = 600 and $\mbox{\text{Pr} = 1}$.
 
@@
 \begin{split}
-\frac{\partial \bm{u}}{\partial t}  +\grad T_1 + &T_1\grad\ln\rho_0 + T_0\grad\ln\rho_1  =\\
-- \epsilon &T_1\grad\ln\rho_1 + \frac{1}{\rho\text{Re}}\left[\grad^2\bm{u} + \frac{1}{3}\grad(\DivU)\right]
+\frac{\partial \bm{u}}{\partial t}  + \frac{1}{-\grad_\text{ad}}[\grad T_1 + &T_1\grad\ln\rho_0 + T_0\grad\ln\rho_1]  =\\
+- \frac{\epsilon}{-\grad_\text{ad}} &T_1\grad\ln\rho_1 + \frac{1}{\rho\text{Re}}\left[\grad^2\bm{u} + \frac{1}{3}\grad(\DivU)\right]
 \end{split} \\
@@
 &\frac{\partial T_1}{\partial t} + \epsilon^{-1}\left[\bm{u}\cdot\grad T_0 + (\gamma-1)T_0\DivU\right] = \\
-&-\left[\bm{u}\cdot\grad T_1 + (\gamma-1)T_1\DivU\right] + \frac{1}{\rho c_V\text{Re}}\left[\frac{1}{\text{Pr}}\grad^2 T_1 + \sigma_{ij}\partial_{x_i}u_j\right].
+&-\left[\bm{u}\cdot\grad T_1 + (\gamma-1)T_1\DivU\right] + \frac{-\grad_{\text{ad}}}{\rho c_V\text{Re}}\left[\frac{1}{\text{Pr}}\grad^2 T_1 + \sigma_{ij}\partial_{x_i}u_j\right].
 \end{split}
@@
 \end{equation}
-\textbf{In all cases, we do not add any symmetry breaking perturbations (e.g., noise).}
+In all cases, we do not add any symmetry breaking perturbations (e.g., noise).
 
@@
 
-The 2D simulation domain is \textbf{periodic in the z-direction with $z \in [-L_z/4, L_z]$ and the radial direction spans $r \in [0, L_r]$}.
+The 2D simulation domain is periodic in the z-direction with $z \in [-L_z/4, L_z]$ and the radial direction spans $r \in [0, L_r]$.
 The boundary conditions are $\partial_r S_1 = w = (\grad\times\bm{u})_\phi = 0$ at $r = L_r$, and the regularity of the equations automatically impose $u = \partial_r(w) = \partial_r(S_1) = 0$ at $r = 0$.
-The 3D simulation domain is \textbf{periodic in the horizontal directions ($x, y \in [-L_r, L_r]$) and vertically spans $z \in [0, L_z]$}.
+The 3D simulation domain is periodic in the horizontal directions ($x, y \in [-L_r, L_r]$) and vertically spans $z \in [0, L_z]$.
 We impose impenetrable, stress free, fixed-temperature boundary conditions at the upper and lower boundaries.
@@
 
-\textbf{
 In our 2D simulations, we represent the radial direction with Chebyshev polynomials so that we can include geometric factors in our equations and capture the singularity at $r = 0$.
@@
 cube) do not influcence the thermal properties.
-}
 
-All of the code used to perform the simulations in this work can be found online in the supplementary materials in a Zenodo repository \citep{supp_andersetall2019} \textbf{at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}}.
+All of the code used to perform the simulations in this work can be found online in the supplementary materials in a Zenodo repository \citep{supp_andersetall2019} at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}.
 
@@
     \caption{
-	(top) The thermal depth as a function of time for the 2D anelastic \textbf{(AN)} and 3D fully compressible \textbf{(FC)} simulations.
+	(top) The thermal depth as a function of time for the 2D anelastic (AN) and 3D fully compressible (FC) simulations.
 	(bottom) The corresponding thermal velocities as a function of depth.
@@
     \caption{
-	(top) Thermal radius as a function of depth for the 2D anelastic \textbf{(AN)} and 3D fully compressible \textbf{(FC)} simulations.
+	(top) Thermal radius as a function of depth for the 2D anelastic (AN) and 3D fully compressible (FC) simulations.
 	Theoretical predictions from section \ref{sec:theory} are plotted in thin solid lines.
@@
 There are slight discrepancies early in the simulation, when the thermal is spinning up, and late in the simulation, when the 3D simulations begin interacting with the bottom of the domain.
-Outside these times, we find differences in the \textbf{measured} radius of less than 1\%.
+Outside these times, we find differences in the measured radius of less than 1\%.
 This gives us confidence that our high stratification anelastic simulations are producing reliable results.
@@
 \startdata																																															
-\multicolumn{8}{l}{\textbf{2D Anelastic Simulations (Cylindrical)}}\\
+\multicolumn{8}{l}{2D Anelastic Simulations (Cylindrical)}\\
 0.1 	&  24.6 	& 0.144	& -0.548 & -2.17 & 8.05	& 1.04	& 0.732	\\
@@
 6	 	&  19.8 	& 0.041	& -5.73	 & -1.43 & 10.8	& 0.787	& 0.616	\\
-\multicolumn{8}{l}{\textbf{3D Fully Compressible Simulations (Cartesian)}}\\    
+\multicolumn{8}{l}{3D Fully Compressible Simulations (Cartesian)}\\    
 0.1 	&  23.4 	& -0.337& -0.547 & -2.17 & 8.98	& 1.06	& 0.636	\\
@@
 2	 	&  22.4 	& 1.38	& -0.711 & -1.89 & 9.31	& 0.828	& 0.680	\\
-\textbf{3}	 	&  \textbf{21.1} 	& \textbf{0.78}	& \textbf{-0.949} & \textbf{-1.75} & \textbf{9.99}	& \textbf{0.815}	& \textbf{0.648}	\\
+3	 	&  21.1 	& 0.78	& -0.949 & -1.75 & 9.99	& 0.815	& 0.648	\\
 \enddata																																															
@@
 In all cases, the buoyancy $B_{\text{th}}$ is similar to the integrated buoyancy in the initial conditions, with some losses due to detrainment in the spin-up.
-We also find that the non-dimensional circulation is \textbf{roughly} $-2$ for each of our cases, and decreases in magnitude with increasing stratification.
+We also find that the non-dimensional circulation is roughly $-2$ for each of our cases, and decreases in magnitude with increasing stratification.
 
@@
 Estimating downflows to have a temperature deviation of $T_1 = -500$ K \citep{borrero&bellotrubio2002}, the nondimensional entropy signature of solar downflows is $S_1/c_p \sim \gamma^{-1}\ln(1 + T_1/T_0) = -5.22 \times 10^{-2}$.
-Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$ \textbf{and assuming thermal formation occurs at the solar photosphere}, the buoyancy of a spherical thermal is 
+Using a solar surface gravity value of $g = 2.74 \times 10^4$ cm/s$^2$ and assuming thermal formation occurs at the solar photosphere, the buoyancy of a spherical thermal is 
 $$
@@
 	Diffusivities are calculated using the realistic solar-like diffusion profiles of \citet{brown2011}.
-	\textbf{
 	(Fourth panel) An estimate of the luminosity of these thermals, normalized by the solar luminosity, is shown.
-	(Fifth panel) An estimate of the filling factor of thermals required to carry the solar luminosity.}
+	(Fifth panel) An estimate of the filling factor of thermals required to carry the solar luminosity.
     \label{fig:thermal_sun_comparison} }
@@
 In the first and second panels of Fig.
-\ref{fig:thermal_sun_comparison}, we show the evolution of these thermals' radii and velocities inside of the Sun, and compare their \textbf{radial} evolution to pure horizontal compression \textbf{and their velocity evolution to the speed of sound}.
+\ref{fig:thermal_sun_comparison}, we show the evolution of these thermals' radii and velocities inside of the Sun, and compare their radial evolution to pure horizontal compression and their velocity evolution to the speed of sound.
 We use the solar diffusivity models of \citet{brown2011} to estimate the timescale over which the thermal would diffuse its entropy signature ($\tau_\kappa = \chi/r_{\text{th}}^2$) and the thermal freefall timescale over its own radial length scale ($\tau_{\text{ff}} = r_{\text{th}}/w_{\text{th}}$).
@@
 
-We find that our estimated solar thermal is \textbf{likely} in the falling regime.
+We find that our estimated solar thermal is likely in the falling regime.
 These thermals experience radial compression with corresponding increases in velocity, but experience much less compression than a naive approximation based on the density stratification alone.
-\textbf{Interestingly, the thermal's Mach number is roughly a value of 0.1 throughout the full extent of the solar convection zone.}
+Interestingly, the thermal's Mach number is roughly a value of 0.1 throughout the full extent of the solar convection zone.
 Furthermore, throughout the thermal's fall, we find that $\tau_\kappa \gg \tau_{\text{ff}}$, and thus we do not expect the thermal to diffuse its entropic signature.
@@
 
-\textbf{
 We now briefly estimate the enthalpy flux carried by a thermal.
@@
 To estimate the total luminosity carried by one thermal, we calculate $L_{\text{enth, th}} = \pi r_{\text{th}}^2 F_{\text{enth}}$, and we plot this value as a function of depth, normalized by the solar luminosity, in the fourth panel of Fig.~\ref{fig:thermal_sun_comparison}.
-}
 
-\textbf{
 From this estimate of the luminosity carried by one thermal, we now calulate the filling factor of downward propagating thermals required to carry the solar luminosity.
@@
 These estimates suggest that even if a large fraction of the thermals launched from the solar surface break apart due to turbulence, entropy rain could still efficiently carry the solar luminosity deep in the convection zone.
-}
 
-\textbf{
 We briefly note that our handling of the enthalpy flux here ignores the contributions of the kinetic energy flux, potential energy flux, and viscous flux.
@@
 We encourage future work to examine these fluxes more thoroughly, but such an examination is outside of the scope of this work.
-}
 
@@
 We'd like to thank Brett McKim and Nadir Jeevanjee for discussions about thermals and the laminar entrainment picture.
-\textbf{We'd like to further thank Nadir Jeevanjee, Axel Brandenburg, Jeremy Goodman, and the anonymous referee whose careful comments greatly improved the scientific quality and clarity of this manuscript.}
+We'd like to further thank Nadir Jeevanjee, Axel Brandenburg, Jeremy Goodman, and the anonymous referee whose careful comments greatly improved the scientific quality and clarity of this manuscript.
 This work was supported by NASA Headquarters under the NASA Earth and Space Science Fellowship Program -- Grant 80NSSC18K1199.
@@
 Information regarding the simulation resolution, evolution time, and CFL safety factor for each of the simulations presented in this work is contained in table \ref{table:simulation_info}.
-The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository \citep{supp_andersetall2019} \textbf{at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}}.
-\textbf{The 3D, $N_\rho = 3$ simulation displays spectral instabilities at very late times as the simulation is under-resolved at these times.
+The Python scripts used to perform all simulations and analysis in this work are stored online in a Zenodo repository \citep{supp_andersetall2019} at \dataset[10.5281/zenodo.3311894]{https://doi.org/10.5281/zenodo.3311894}.
+The 3D, $N_\rho = 3$ simulation displays spectral instabilities at very late times as the simulation is under-resolved at these times.
 This affects thermal radial measurements at depths $\geq 17.5$.
-We therefore truncate the data from that simulation at a depth of 15, which corresponds to multiple freefall times before these instabilities affect the solution.}
+We therefore truncate the data from that simulation at a depth of 15, which corresponds to multiple freefall times before these instabilities affect the solution.
 
@@
 \startdata																																															
-\multicolumn{5}{l}{\textbf{2D Anelastic Simulations}}\\
+\multicolumn{5}{l}{2D Anelastic Simulations}\\
 0.1 	& 		128			& 512			& 50 	&	0.6	\\
@@
 6	 	& 		256			& 1536			& 23 	&	0.08	\\
-\multicolumn{5}{l}{\textbf{3D Fully Compressible Simulations}}\\
+\multicolumn{5}{l}{3D Fully Compressible Simulations}\\
 0.1 	& 		256			& 512			& 50 		&	0.15	\\
@@
 1	 	& 		256			& 512			& 41	 	&	0.15	\\
-2	 	& 		\textbf{384}			& 1024			& 34    	&	0.1	\\
-\textbf{3}	 	& 		\textbf{384}			& \textbf{2048}			& \textbf{25}    	&	\textbf{0.15}	\\
+2	 	& 		384			& 1024			& 34    	&	0.1	\\
+3	 	& 		384			& 2048			& 25    	&	0.15	\\
 \enddata																																															

### 2019-07-30 tex/stratified_thermals.tex
updates release code

@@
 These equations are non-dimensionalized in the same way as the anelastic equations, and use the same background atmosphere.
-The new parameter $\epsilon = u_{\text{th}}^2$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows analagously to the adiabatic excess in polytropic convection \citep{anders&brown2017}; we use $\epsilon = 10^{-4}$ in this work.
+The new parameter $\epsilon = -u_{\text{th}}^2/\grad_{\text{ad}}$ is the magnitude of entropy perturbations and sets the Mach number of the thermal flows analagously to the adiabatic excess in polytropic convection \citep{anders&brown2017}; we use $\epsilon = 10^{-4}$ in this work.
 

### 2019-07-30 stratified_thermals_code/nondim_FC_stratified_thermals/logic/atmospheres.py

@@ -1,0 +1,132 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+
+from dedalus import public as de
+
+def set_field(field, in_arr, scales=1):
+    """
+    Sets the values in a dedalus field to match those in an input NumPy array
+    at the proper scale. Returns the field at that scale.
+
+    Parameters
+    ----------
+    field   : A Dedalus Field object
+        The field to set the values of
+    in_arr  : A NumPy array
+        The NumPy array to set the field values to
+    scales  : float, optional
+        The size scale at which to set the field.
+    """
+    field.set_scales(scales, keep_data=True)
+    field['g'] = in_arr
+    field.set_scales(scales, keep_data=True)
+    return field
+
+
+
+class IdealGasAtmosphere:
+    """
+    An abstract class which contains many of the attributes of an
+    ideal gas atmosphere, to be extended to more specific cases.
+
+    Attributes:
+    -----------
+        params      : OrderedDict 
+            Scalar atmospheric parameters (floats, ints)
+        gamma       : Float
+            The adiabatic index of the atmosphere
+        Cp, Cv      : Floats
+            Specific heat at constant pressure, volume
+        g           : Float
+            Gravity, constant. (default value sets T_ad_z = -1)
+        R           : Float
+            The ideal gas constant
+        T_ad_z      : Float
+            The adiabatic temperature gradient, as defined in Anders&Brown2017 & elsewhere
+        de_domain   : A DedalusDomain object 
+            The domain on which the atmosphere will be built
+        atmo_fields : OrderedDict 
+            contains fields for the variables: T0, T0_z, T0_zz, rho0, ln_rho0, ln_rho0_z, phi
+    """
+
+    def __init__(self, de_domain, gamma=5./3, R=1, g=None):
+        """
+        Initialize the atmosphere. Inputs that match attributes in the class docstring are
+        defined there.
+        """
+        self.params = OrderedDict()
+        self.rho_fit     = None
+        self.params['R'] = R
+        self.params['gamma'] = gamma
+        self.params['Cp'] = gamma*R/(gamma-1.)
+        self.params['Cv'] = self.params['Cp'] - R
[…]

### 2019-07-30 stratified_thermals_code/nondim_FC_stratified_thermals/logic/domains.py

@@ -1,0 +1,86 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+
+from dedalus import public as de
+
+from mpi4py import MPI
+
+class DedalusDomain:
+    """
+    A struct which contains a dedalus domain, as well as a bunch of info about
+    the domain, for use in broad functions.
+
+    Attributes:
+    -----------
+        nx, ny, nz  : ints
+            The coefficient resolution in x, y, z
+        Lx, Ly, Lz  : floats
+            The size of the domain in simulation units in x, y, z
+        threeD      : bool
+            If True, problem is 3D. Else, problem is 2D.
+        bases       : list
+            The dedalus basis objects in the domain
+        domain      : a Domain object
+            The dedalus domain object
+        x, y, z     : NumPy Arrays
+            The gridpoints of the domain for x,y,z (scales = 1)
+    """
+
+    def __init__(self, nx, ny, nz, Lx, Ly, Lz, threeD=False, mesh=None):
+        """
+        Initializes the dedalus domain object. Many of the inputs match those in
+        the class attribute docstring.
+
+        Other attributes:
+        -----------------
+        mesh    : list of ints
+            The CPU grid on which the domain is distributed.
+        """
+        self.nx, self.ny, self.nz = nx, ny, nz
+        self.Lx, self.Ly, self.Lz = Lx, Ly, Lz
+        self.threeD = threeD
+
+        x_basis = de.Fourier('x', nx, interval=(-Lx/2, Lx/2), dealias=3/2)
+        self.bases = [x_basis,]
+        if threeD:
+            y_basis = de.Fourier('y', ny, interval=(-Ly/2, Ly/2), dealias=3/2)
+            self.bases += [y_basis]
+
+        if isinstance(nz, list) and isinstance(Lz, list):
+            Lz_int = 0
+            z_basis_list = []
+            for Lz_i, nz_i in zip(Lz, nz):
+                Lz_top = Lz_i + Lz_int
+                z_basis = de.Chebyshev('z', nz_i, interval=[Lz_int, Lz_top], dealias=3/2)
+                z_basis_list.append(z_basis)
+                Lz_int = Lz_top
+            self.Lz = Lz_int
+            self.nz = np.sum(nz)
+            self.Lz_list = Lz
+            self.nz_list = nz
+            z_basis = de.Compound('z', tuple(z_basis_list), dealias=3/2)
+        else:
[…]

### 2019-07-30 stratified_thermals_code/nondim_FC_stratified_thermals/logic/equations.py

@@ -1,0 +1,237 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+
+from dedalus import public as de
+from mpi4py import MPI
+
+
+class FullyCompressibleEquations:
+    """
+    An abstract class containing the fully compressible equations which must
+    be extended to specify the type of diffusivities
+
+    Attributes
+    ----------
+    de_domain   : A DedalusDomain object
+        The domain on which the equations are solved
+    atmosphere  : An IdealGasAtmosphere object
+        The atmosphere in which the equations are solved
+    variables   : list
+        A list of strings of problem variables.
+    problem     : A Dedalus Problem object
+        The problem in which the equations are solved.
+    """
+    def __init__(self, de_domain, atmosphere):
+        """
+        Construct the equation class. Inputs are described in the class docstring.
+        """
+        self.de_domain = de_domain
+        self.atmosphere = atmosphere
+        self.variables = ['u','u_z','v', 'v_z', 'w','w_z','T1', 'T1_z', 'ln_rho1']
+        if not self.de_domain.threeD:
+            self.variables.remove('v')
+            self.variables.remove('v_z')
+
+        self.problem = de.IVP(self.de_domain.domain, variables=self.variables, ncc_cutoff=1e-6)
+        if not self.de_domain.threeD:
+            self.problem.substitutions['v'] = '0'
+            self.problem.substitutions['v_z'] = '0'
+            self.problem.substitutions['dy(A)'] = '0*A'
+
+    def set_equations(self, *args, **kwargs):
+        """ 
+        Sets the fully compressible equations of in a ln_rho / T formulation. These
+        equations take the form:
+        
+        D ln ρ + ∇ · u = 0
+        D u = - ∇ T - T∇ ln ρ - gẑ + (1/ρ) * ∇ · Π
+        D T + (γ - 1)T∇ · u - (1/[ρ Cv]) ∇ · (- Kap∇ T) = (1/[ρ Cv])(Π ·∇ )·u 
+        
+        Where
+
+        D = ∂/∂t + (u · ∇ ) 
+
+        and
+
+        Π = - Mu (∂u_i/∂x_j + ∂u_j/∂x_i - (2/3)D_{ij}∇ · u)
+
[…]

### 2019-07-30 stratified_thermals_code/nondim_FC_stratified_thermals/logic/output.py

@@ -1,0 +1,92 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+
+from dedalus import public as de
+
+def initialize_output(data_dir, solver, threeD=False, output_cadence=1, writes_per=2, mode='overwrite', threeD_factor=1):
+    """
+    Initializes output tasks for a convection simulation.
+
+    Parameters
+    ----------
+    data_dir    : string
+        The root directory in which to save the output tasks
+    solver      : A Dedalus solver object
+        The solver for the simulation that output is for.
+    threeD      : bool, optional
+        If True, simulation is 3D.
+    output_cadence : float, optional
+        The output cadence of writes (in simulation time units)
+    writes_per     : int, optional
+        The maximum number of output writes per file.
+    mode           : string, optional
+        "overwrite" or "append" -- The Dedalus output mode.
+    threeD_factor  : float, optional
+        A factor to multiply output_cadence by to increase (or decrease) the time between outputs.
+    """
+    # VOLUMES AND SLICES
+    analysis_tasks = OrderedDict()
+    slices = solver.evaluator.add_file_handler(data_dir+'slices', sim_dt=output_cadence, max_writes=writes_per, mode=mode, parallel=False)
+    analysis_tasks['slices'] = slices
+    if threeD:
+        volumes = solver.evaluator.add_file_handler(data_dir+'volumes', sim_dt=output_cadence*threeD_factor, max_writes=writes_per, mode=mode, parallel=False)
+        analysis_tasks['volumes'] = volumes
+        volumes.add_task('u',          name='u')
+        volumes.add_task('v',          name='v')
+        volumes.add_task('w',          name='w')
+        volumes.add_task('T1',         name='T1')
+        volumes.add_task('s1',         name='entropy')
+
+        slices.add_task('interp(u, x = 0)',         name='u x mid')
+        slices.add_task('interp(u, y = 0)',         name='u y mid')
+        slices.add_task('interp(v, x = 0)',         name='v x mid')
+        slices.add_task('interp(v, y = 0)',         name='v y mid')
+        slices.add_task('interp(w, x = 0)',         name='w x mid')
+        slices.add_task('interp(w, y = 0)',         name='w y mid')
[…]

### 2019-07-30 stratified_thermals_code/nondim_FC_stratified_thermals/logic/post_processing.py

@@ -1,0 +1,852 @@
+"""
+Analysis functionality for a 2D, cylindrically symmetric thermal's properties 
+
+Usage:
+    thermal_analysis.py --root_dir=<dir> [options]
+
+Options:
+    --root_dir=<root_dir>               Directory pointing to 'slices', etc
+    --plot                              If flagged, plot colormesh during analysis
+    --no_analyze                        If flagged, do not do full analysis
+    --n_files=<n>                           Number of files [default: 10000]
+    --get_contour                       If flagged, do full contour solve
+    --iterative                         If flagged, use results of previous solve to inform new solve
+"""
+import os
+import glob
+import logging
+logger = logging.getLogger(__name__)
+
+import h5py
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+from scipy.interpolate import interp1d, RegularGridInterpolator
+from scipy.optimize import brentq
+import scipy.optimize as scop
+
+from dedalus import public as de
+
+def differentiate(x, y): 
+    """ Numerical differentiation. Output has 4 fewer points than input. """
+    dx = np.mean(x[1:] - x[:-1])
+    return (-y[4:] + 8*y[3:-1] - 8*y[1:-3] + y[:-4]) / (12*dx)
+
+def linear_fit(x, a, b):
+    """ A linear fit: y = a* x + b """
+    return a*x + b
+
+def theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=-1):
+    """ The constant in stratified thermals theory """
+    return (grad_T_ad * Gamma0 * np.pi**(3./2) / f / (1 + beta)) * np.sqrt(Gamma0/(B0 * chi))
+
+def theory_r(t, B0, Gamma0, chi, t_off, rho_f=None):
+    """ The temperature profile (vs time) from stratified thermals theory """
+    r = np.sqrt(chi*B0*(t + t_off)/np.pi/Gamma0)
+    if rho_f is None:
+        return r
+    return r/np.sqrt(rho_f(t))
+
+def theory_T(t, B0, Gamma0, f, chi, beta, t_off, T0, grad_T_ad=-1, m_ad=1.5):
+    """ The temperature profile (vs time) from stratified thermals theory """
+    C0 = theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=grad_T_ad)
+    Tpow = 1 - (m_ad/2)
[…]

### 2019-07-30 stratified_thermals_code/nondim_FC_stratified_thermals/logic/thermal.py

@@ -1,0 +1,93 @@
+import numpy as np
+from collections import OrderedDict
+
+import logging
+logger = logging.getLogger(__name__)
+from scipy.special import erf
+
+from mpi4py import MPI
+
+class Thermal:
+    """
+    A class that creates a thermal in a Fully Compressible simulation
+
+    Attributes
+    ----------
+    de_domain   : DedalusDomain object
+        The domain in which the thermal experiment is being done
+    atmosphere  : An IdealGasAtmosphere object
+        The atmosphere in which the thermal is falling.
+    falling     : bool
+        If True, do a cold, falling thermal. Else, do a hot, rising thermal.
+    radius      : float
+        The size of the thermal's radius, in simulation units.
+    r_width     : float
+        The sharpness of the edges of the thermal in the initial conditions.
+    A0          : float
+        The magnitude of the initial thermal's entropy perturbation.
+    z_pert      : float
+        simulation z-location of perturbation
+    """
+
+    def __init__(self, de_domain, atmosphere, falling=False, radius=1, r_width=None, 
+                 A0=1e-4, z_pert = None):
+        """
+        Initialize the thermal class. Inputs are described in the class attributes in the
+        class docstring.
+        """
+        self.de_domain     = de_domain
+        self.atmosphere = atmosphere
+        self.radius     = radius
+        if r_width is None:
+            self.r_width = radius/5
+        else:
+            self.r_width = r_width
+        self.falling    = falling
+        self.A0         = A0
+
+        if self.falling:
+            self.sign   = -1
+        else:
+            self.sign   = 1
+       
+        if z_pert is None:
+            if self.falling:
+                self.z_pert = self.de_domain.Lz - 3*self.radius
+            else:
+                self.z_pert = 3*self.radius
+        else:
+            self.z_pert = z_pert
+
+
+    def set_thermal(self, T1, T1_z, ln_rho1):
+        """
+        Put a thermal into the intial conditions of a simulation. The temperature,
+        temperature derivative, and log density fields from the problem solver must be
+        provided.
+        
+        For pressure equilibrium, rho_fluc * T_fluc = 1, so P0 = rho0*exp(ln_rho1)*(T0+T1), so
+         (1 + T1/T0) = exp(-ln_rho1). Plugging this back into the entropy equation, we find that
[…]

### 2019-07-30 stratified_thermals_code/nondim_FC_stratified_thermals/nondim_FC_3D_thermal.py

@@ -1,0 +1,268 @@
+"""
+Stratified fully compressible thermals in an adibatically stratified polytrope.
+Mu and Kappa are constant with depth.
+
+Usage:
+    nondim_FC_3D_thermal.py [options]
+
+Options:
+    --Reynolds=<Reynolds>                Reynolds number [default: 5e2]
+    --Prandtl=<Prandtl>                  Prandtl number = nu/kappa (top) [default: 1]
+    --n_rho=<n_rho>                      Density scale heights across layer [default: 1]
+    --epsilon=<epsilon>                  Amplitude of perturbation [default: 1e-4]
+
+    --gamma=<gamma>                      Gamma of ideal gas (cp/cv) [default: 5/3]
+    --aspect=<aspect_ratio>              Physical aspect ratio of the atmosphere (Lx = Ly = aspect*[diameter of thermal]) [default: 0.5]
+
+    --nz=<nz>                            vertical z (chebyshev) resolution [default: 512]
+    --nx=<nx>                            Horizontal x (Fourier) resolution [default: 256]
+    --ny=<ny>                            Horizontal y (Fourier) resolution [default: 256]
+    --mesh=<mesh>                        Processor mesh
+
+    --run_time=<run_time>                Run time, in hours [default: 7.5]
+    --run_time_buoy=<run_time_buoy>      Run time, in buoyancy times [default: 50]
+
+    --restart=<restart_file>             Restart from checkpoint
+
+    --safety_factor=<safety_factor>      Determines CFL Danger.  Higher=Faster [default: 0.2]
+
+    --label=<label>                      Additional label for run output directory
+    --join                               If flagged, join files at end of run
+    --out_cadence=<cadence>              Fraction of a buoyancy time on which to output [default: 0.35]                    
+
+    --verbose
+    --SBDF2                              If flagged use SBDF2 timestepper
+    --443                                If flagged, use RK443 instead of RK222
+    --no_VH                              If flagged, don't include viscous heating
+"""
+import sys
+import os
+import time
+import logging
+from fractions import Fraction
+
+import matplotlib.pyplot as plt
[…]

### 2019-07-30 stratified_thermals_code/paper_plots/constants.py

@@ -85,7 +85,7 @@ cb = plt.colorbar(sm, cax=cax, orientation='horizontal', boundaries=np.linspace(
 cb.solids.set_rasterized(True)
 cax.xaxis.set_ticks_position('top')
 cax.xaxis.set_ticklabels(CASES)
-cb.set_label(r'$n_\rho$', labelpad=-35)
+cb.set_label(r'$N_\rho$', labelpad=-35)
 
 #axs[0].text(19, 1.03, 'a', fontsize=12)
 #axs[1].text(19, 1.03, 'b', fontsize=12)

### 2019-07-30 stratified_thermals_code/paper_plots/overview_fig.py

@@ -94,7 +94,7 @@ plt.ylim(5e-2, 1e2)
 
 
 ax.text(14, 52, r'$f \propto d^2\,\mathrm{(LJ19)}$', rotation=12)
-ax.text(11.5, 1.2, r'$\mathrm{simulation}\,(n_\rho=3)$', rotation=-2)
+ax.text(11.5, 1.2, r'$\mathrm{simulation}\,(N_\rho=3)$', rotation=-2)
 ax.text(14, 2.2e-1, r'$f \propto \rho^{-1}\,\mathrm{(B16)}$', rotation=-7)
 
 fig.savefig('overview_fig.png', dpi=300, bbox_inches='tight')

### 2019-07-30 stratified_thermals_code/paper_plots/thermal_sun_comparison.py

@@ -7,12 +7,18 @@ matplotlib.rcParams['mathtext.rm'] = 'DejaVu Serif'
 matplotlib.rcParams['mathtext.it'] = 'DejaVu Serif:italic'
 matplotlib.rcParams['mathtext.bf'] = 'DejaVu Serif:bold'
 import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
 from scipy.interpolate import interp1d
 
 
 cm2Mm = 1e-8 #Mm / cm
 Rsun2cm = 6.957e10 #cm / Rsun
 Rsun2Mm = 6.957e2 #Mm / Rsun
+
+gs = gridspec.GridSpec(1000, 1000)
+fig = plt.figure(figsize=(3.25, 7))
+
+
 
 
 def theory_C(B0, Gamma0, f, chi, beta, grad_T_ad=-1):
@@ -39,8 +45,11 @@ def theory_dT_dt(t, B0, Gamma0, f, chi, beta, t_off, T0, grad_T_ad=-1, m_ad=1.5)
     return C0*this_T**(m_ad/2)/np.sqrt(t + t_off)
 
 def read_solar_profiles():
-    mesa_data = np.genfromtxt('sun_4.5gyr.data', skip_header=6, usecols=(2, 4)) #logR (in Rsun units), logRho (g/cm^3)
-    mesa_data = 10**(mesa_data)
+    mesa_data = np.genfromtxt('sun_4.5gyr.data', skip_header=6, usecols=(2, 4, 9, 10, 11)) #logR (in Rsun units), logRho (g/cm^3), grav (cm/s^2), Cp, csound (cm/s)
+    grav = mesa_data[:,2]
+    Cp = mesa_data[:,3] #erg/K?
+    csound = mesa_data[:,4]*cm2Mm
+    mesa_data = 10**(mesa_data[:,:-1])
     radius    = mesa_data[:,0]*Rsun2Mm
     density    = mesa_data[:,1]*(cm2Mm)**(-3)
 
@@ -69,9 +78,14 @@ def read_solar_profiles():
     r2chi = interp1d(radii, chi, bounds_error=False, fill_value='extrapolate')
     r2nu  = interp1d(radii, nu, bounds_error=False, fill_value='extrapolate')
 
-    return rho2r, r2chi, r2nu
 
-rho2r, r2chi, r2nu = read_solar_profiles()
[…]
